---
title: "CCR Met Plots for EDI"
output: html_document
theme: null
original date made: "Jan 2023"
date last updated: "`r Sys.Date()`"
Author: Adrienne Breef-Pilz
---

This script is the visual inspection scripts which does a lot:

1. QAQCs all the raw data or for a reviewer reads in the data file from EDI for checking. IF YOU ARE QAQCING ALL FILES IT WILL TAKE OVER 20 MINUTES FOR THE SCRIPT TO RUN. 

2. Then the script checks for daily and sub-daily gaps in the current file. 

3. Lists the flag frequency to check if there are any NAs or any assigned the wrong flag. 

4. Checks to see if the Maintenance Log is working correctly by inspecting rows in the data frame. 

5. Creates plots

6. Writes data to new csv

7. Downloads necessary files for EDI publishing


All files are from GitHub or EDI and the source scripts are from GitHub as well. 

If you are REVIEWING this data package, add the pasta URL from EDI in the "READ IN EDI FOR REVIEWER". Make sure eval=FALSE is in the chunk header for "Get raw files", "QAQC all files", "Write CSV" and "Download and save Maintenance Log". You don't need to remake the data files when you are reviewing the data package. These chunks of code will not be run when the R markdown is knitted together and saves you LOTTTS of time. Once that is all set than you can knit the file together as an HTML file to look at all the plots. 

If you are running the code chunk by chunk you mind need to make some adjustments to the code. To make the plots this markdown uses a function called "all_plots". In the function it creates a plots of the most current year, the whole times series, as well as, density and box plots for daily averages. You can also specify if you would like to produce a heat map. Note that heat maps are only produced if your data has a depth column. The function also allows you to choose if you want interactive plots, using plotly, for the most recent year of data. For the met data, I do not use plotly because the files are too big and it will take too long to produce. The plotly plots are designed to be in order with the other plots when knit to together. Therefore if you are running the ploting section, chunk by chunk, then you need to specify the plotly plot from the list of plots labeled "output"

FOR DATA PRODUCT LEAD:

If you are the data product lead and making the data package then:

If you are REVIEWING this data package, add the pasta URL from EDI in the "READ IN EDI FOR REVIEWER". Make sure eval=FALSE is in the chunk header for "Get raw files", "QAQC all files", "Write CSV" and "Download and save Maintenance Log". You don't need to remake the data files when you are reviewing the data package. These chunks of code will not be run when the R markdown is knitted together and saves you LOTTTS of time. Once that is all set than you can knit the file together as an HTML file to look at all the plots. 

If you are the data product lead and making the data package then:

1. Make sure all the date ranges are up to date especially current_time_start and current_time_end.

2. Change the years in the saved data files in "Write CSV" and "Download and save Maintenance Log" chunk.

3. Make sure to un comment and change the settings for the "Get raw files", "QAQC all files",  and "Write CSV" chunks. Also check the settings for the chunk eval=TRUE or it shouldn't be there. 

4. Comment out the Reviewer section and make sure for the settings eval = FALSE.

5. Update the data frame in "Get raw files" to include the most recent file on GitHub.

6. Knit the file. This will take a long time. 

7. Look over the plots and see if there are any issues that need to be added to the maintenance log. I will usually read in the file you just made and make smaller plots with the variable and month in question. Once I have the dates, add them to the maintenance log. 

8. Re-run the inspection script until you have found all of the issues. 

9. Run the "Download and save Maintenance Log" chunk to have the most up to date files in the EDI folder.

10. Make sure large maintenance issues are also documented in the methods.txt file. 


```{r Set Up, include=FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(RCurl,devtools, tidyverse,lubridate, plotly, magrittr, scattermore, knitr, htmltools, pander, suncalc, openair)

# Source scripts from GitHub
source("https://raw.githubusercontent.com/FLARE-forecast/CCRE-data/ccre-dam-data-qaqc/R/met_qaqc_function.R")
source('https://raw.githubusercontent.com/CareyLabVT/Reservoirs/master/Data/DataAlreadyUploadedToEDI/EDIProductionFiles/Plotting_function.R')


 #turn off pander auto asis
        pander::panderOptions('knitr.auto.asis', FALSE)

```

REVIEWERS and DATA PUBLISHERS START HERE BEFORE KNITTING

1.  Update your role

2.  Update dates for current year plots

3.  If you are a reviewer, update the edi link

```{r EDIT HERE, include=FALSE}

# 1. How would you like to use this script. If you are a data publisher write "publisher" if you are a reviewer write "reviewer"

role <- "publisher"

# 2. DATA PUBLISHERS UPDATE DATES HERE
# Set up the current time end time of the file and the current year for QAQC plots
#current time of QAQC for graphing

#current time of QAQC for graphing
current_time_start=force_tz(as.POSIXct("2025-01-01 00:00:00"), tzone = "EST")
current_time_end= force_tz(as.POSIXct("2026-01-01 00:00:00"), tzone = "EST")

# 3. DATA PUBLISHERS UPDATE FILE NAMES
# Update the name of the data files, maintenance log, and qaqc function. Double check the name of the file matches the naming convention and the start and end date of the data file. 

file_name <- "ccre-met_2021_2025.csv"

qaqc_function <- "ccre-met_qaqc_2021_2025.R"

maintenance_log <- "ccre-met_maintenancelog_2021_2025.csv"

# 3. For REVIEWERS: Run this section to pull the data from EDI which is in staging as a check of the data.
# # MAKE SURE TO UPDATE THE PASTA FROM THE VERSION YOU WANT

edi_link <-"https://pasta-s.lternet.edu/package/data/eml/edi/518/34/814580ebec0385c66f0a0a97c38e9136"  

```

```{r set chunks on or off, echo=FALSE}
### Code to determine which chunks are turned on and off

if(role=="publisher"){
  make_data = TRUE
  edi_stage = FALSE
}else if(role == "reviewer"){
  make_data = FALSE
  edi_stage = TRUE
}

```



```{r QAQC all files, eval=make_data, message=TRUE, warning=TRUE, echo=FALSE}

# # This section creates a list of the raw files and the manual files
#
# # For the point person for this EDI package publishing. The code for this section is in RAW_FILES_for_inspection_rmd.R, which is in the MakeEML_CCRMetData. The code in that script needs to be copied here and to include the most recent year of data. When you are making the data file for the new year, make sure eval=TRUE and that eval= TRUE in the QAQC all files chunk.
#
# # List of the streaming raw data files from the Gateway. Since they are so large we have to make raw files for each year



ds <- c(
  'https://raw.githubusercontent.com/FLARE-forecast/CCRE-data/ccre-dam-data-qaqc/ccre-met_legacy_2021.csv',
  'https://raw.githubusercontent.com/FLARE-forecast/CCRE-data/ccre-dam-data-qaqc/ccre-met_legacy_2022.csv',
  'https://raw.githubusercontent.com/FLARE-forecast/CCRE-data/ccre-dam-data-qaqc/ccre-met_legacy_2023.csv',
  'https://raw.githubusercontent.com/FLARE-forecast/CCRE-data/ccre-dam-data-qaqc/ccre-met_legacy_2024.csv',
  # THE CURRENT YEARS FILE
  'https://raw.githubusercontent.com/FLARE-forecast/CCRE-data/ccre-dam-data/ccre-met.csv',

 # Read in and make a data frame of the manual downloaded files. I make these each year with the raw files we have downloaded.
# # See ManualDownloadsSCCData for the script on making the file for each year.
# # Link here : https://github.com/CareyLabVT/ManualDownloadsSCCData/tree/master/MetStation
#

  'https://raw.githubusercontent.com/CareyLabVT/ManualDownloadsSCCData/master/CCR_manual_downloads/CCR_dam_downloads/CCRMetstation_2021.csv',
  'https://raw.githubusercontent.com/CareyLabVT/ManualDownloadsSCCData/master/CCR_manual_downloads/CCR_dam_downloads/CCRMetstation_2022.csv',
  'https://raw.githubusercontent.com/CareyLabVT/ManualDownloadsSCCData/master/CCR_manual_downloads/CCR_dam_downloads/CCRMetstation_2023.csv',
  'https://raw.githubusercontent.com/CareyLabVT/ManualDownloadsSCCData/master/current_files/CCRMetstation_L1.csv'
)



# Run the qaqc file to make the data file for the current publishing year
#
current_df <- qaqc_ccrmet(data_file = ds,
                    maintenance_file ='https://raw.githubusercontent.com/FLARE-forecast/CCRE-data/ccre-dam-data-qaqc/CCRM_Maintenancelog_new.csv',
                    output_file = NULL,
                    start_date = force_tz(as.POSIXct("2021-03-29 19:00:00"), tzone = "EST"),
                    end_date = Sys.Date(),
                    notes = TRUE)
   
   # Filter for the end of the current publishing year in the set up chunk.
current_df <- current_df|>
  dplyr::distinct()|>
  filter(DateTime<(current_time_end))

# make sure no time duplicates.
 current_df <-  current_df[!duplicated(current_df$DateTime), ]

#reorder. Just to be certain everything is in order
  current_df<-current_df[order(current_df$DateTime),]
  

```



REVIEWERS- If you are reviewing this data package replace the pasta link with the one from EDI. If there are questions ask the data point person. There are two ways to use this script. You can either run it by chunks or you can knit it and make an html file. Knitting the file will run all the chunks and create an html page with all the plots. I like doing this because I can see all the plots in one place. The Knit button is on the top of the file with a ball of yarn and a needle next to it. 

```{r READ IN EDI FOR REVIEWER, eval = edi_stage}
 
    # This is the link to the files in the staging environment
                                                                 
    # For staging environment                                                    
  current_df <- read_csv(edi_link)
 
 # # Force files from EDI to have an EST timestamp
   current_df$DateTime <- force_tz(as.POSIXct(current_df$DateTime), tzone = "EST")
```

```{r Download Raw data for plotting, include=FALSE}
# This section reads in raw data to compare to the QAQC data file


CATPRES_COL_NAMES =  c("DateTime","Record", "CR3000Battery_V", "CR3000Panel_Temp_C", 
                   "PAR_umolm2s_Average", "PAR_Total_mmol_m2", "BP_Average_kPa", "AirTemp_C_Average", 
                   "RH_percent", "Rain_Total_mm", "WindSpeed_Average_m_s", "WindDir_degrees", "ShortwaveRadiationUp_Average_W_m2",
                   "ShortwaveRadiationDown_Average_W_m2", "InfraredRadiationUp_Average_W_m2",
                   "InfraredRadiationDown_Average_W_m2", "NetRadio_Temp_C", "Albedo_Average_W_m2")
  
 
  # read in the raw streaming sensors 
  raw <- read_csv("https://raw.githubusercontent.com/FLARE-forecast/CCRE-data/ccre-dam-data/ccre-met.csv", skip = 1, col_names = CATPRES_COL_NAMES,
                      col_types = cols(.default = col_double(), DateTime = col_datetime()))|>
    select(-NetRadio_Temp_C)
  
  
  # convert NaN to NAs in the dataframe
  raw[sapply(raw, is.nan)] <- NA
  
  # force datetime
  raw$DateTime <- force_tz(as.POSIXct(raw$DateTime), tzone = "EST")
  
  # Just the raw file for the year. Used to get column names for the plots. 
current_raw <- raw%>%
  filter(DateTime>=current_time_start & DateTime<current_time_end)%>%
  mutate(type = "raw")

```


## Check for duplicates and  gaps in the data frame

This section identifies if there are any duplicates, daily data, and sub daily gaps in the long-term record. If there are duplicates. Look to see if they are true duplicates and then check the qaqc function and the chunk above where duplicates should be removed. If there is nothing printed then there are no duplicates or missing files. 


### Are there any duplicates?

Check to see there are no duplicates in the data file. If there are then they need to be removed. 


```{r Check duplicates, echo=FALSE}

 # Make sure there are no duplicated dates. 
# Print them if there are
 dups<- current_df[duplicated(current_df$DateTime), ]

dups <- dups%>%
  select(DateTime, Record, CR3000Battery_V, CR3000Panel_Temp_C, 
         PAR_Total_mmol_m2, BP_Average_kPa, AirTemp_C_Average)

knitr::kable((dups))

```

### Are there any subdaily gaps?

This identifies if there are any sub-daily gaps in the current record which gets recorded in the methods section. 

The first row is the time for the first observation and then the subsequent observation. Each observation should be 1 minute apart. The second row is the number of the record for each observation. Most of these gaps happen when we change the program on the data logger. These times will be recorded in the maintenance section of the metadata.

```{r Check for sub daily gaps, echo=FALSE}
# Because we can't have NAs for this for loop let's make a new df
  cat2 <- current_df%>%
   filter(!is.na(Record))%>%
   filter(DateTime>current_time_start)|>
  select(DateTime, Record)

   for(i in 2:length(cat2$Record)){ #this identifies if there are any data gaps in the long-term record, and where they are by record number
     if( abs(cat2$Record[i]-cat2$Record[i-1])>1 & difftime(cat2$DateTime[i], cat2$DateTime[i-1], units="mins")>1){
       print(c(cat2$DateTime[i-1], cat2$DateTime[i]))
       print(c(cat2$Record[i-1], cat2$Record[i]))
     }
   }

print("If there are no times here then there are no missing values")
```



### Let's look at the flag Frequency for each variable. As a reminder here are the flag codes


Let's look at the flag Frequency for each variable. 

As a reminder here are the flag codes Flag values 

0: no flag; 

1: value removed due to maintenance and set to NA; 

2: sample not collected; 

3: negative values set to 0, percent greater than 100 and set to 100, or infinite values set to NA; 

4: potentially questionable value and changed or set to NA, see note; 

5: questionable value but left in the dataset.


```{r Check out the flags, echo=FALSE}

#make sure no NAS in the Flag columns
Flags <- current_df%>%
  select(DateTime, starts_with("Flag"))

RowsNA=Flags[!complete.cases(Flags), ] # Keep only the complete rows

#check the flag column
Flags <- current_df%>%
  select(starts_with("Flag"))

# Make a table with the number of times a flag was used
for(f in 1:ncol(Flags)){
  #print(colnames(Flags[f]))
  print(table(Flags[,f], useNA = "always"))
}
```

### Check to make sure that what is in the maintenance log  was actually removed

### Look at the last rows of the maintenance log 

We want to make sure that our maintenance log actually worked and took out the values or changes those it was supposed to 

```{r Read in the maintenance log and look at the tail, echo=FALSE}

 maint <- read_csv2("https://raw.githubusercontent.com/FLARE-forecast/CCRE-data/ccre-dam-data-qaqc/CCRM_Maintenancelog_new.csv",show_col_types = FALSE)


# name the data file for just the tail of the maintenance log
# you want to filter out 7 because that is if the observation is missing and there are other ways that is flagged in the data besides the maintenance log, so it is not a good check.
sd <- tail(maint)


knitr::kable((tail(sd)))

```

#### Check the that the columns have flags 

Look at the first few rows of the data frame and check that the observations after the TIMESTAMP_start are flagged

#### Look at the first 5 rows for that time

```{r Did the maint log work head, echo=FALSE, message=FALSE, warning=FALSE}
# get the last row of the data file
last_row <- tail(sd, n=1)

# Get starttime and end time
### get start and end time of one maintenance event
    start <- force_tz(as.POSIXct(last_row$TIMESTAMP_start), tzone = "EST")
    end <- force_tz(as.POSIXct(last_row$TIMESTAMP_end), tzone = "EST")
    
    # Get the time of the maintenance
    if(is.na(end)){
      # If there the maintenance is on going then the columns will be removed until
      # and end date is added
      Time <- current_df |> filter(DateTime >= start) |> select(DateTime)
      
    }else if (is.na(start)){
      # If there is only an end date change columns from beginning of data frame until end date
      Time <- current_df |> filter(DateTime <= end) |> select(DateTime)
      
    }else {
      Time <- current_df |> filter(DateTime >= start & DateTime <= end) |> select(DateTime)
    }


### Get the names of the columns affected by maintenance
    colname_start <- last_row$start_parameter
    colname_end <- last_row$end_parameter
    
    
    if(is.na(colname_start)){
      
      maintenance_cols <- colnames(current_df%>%select((colname_end)))
      
    }else if(is.na(colname_end)){
      
      maintenance_cols <- colnames(current_df%>%select((colname_start)))
      
    }else{
      
      maintenance_cols <- colnames(current_df%>%select((colname_start:colname_end)))
      
    }
    # Make list of just the columns we want 
    
    test <- colnames(current_df%>%select(DateTime,  maintenance_cols, paste0("Flag_", maintenance_cols)))
    
    # Print the head of the table to make sure that data are flagged
    
    knitr::kable((head(current_df[current_df$DateTime %in% Time$DateTime, test]))) 

```

#### Look at the last 6 rows for the maintenance time

Make sure the observations are flagged

```{r Print the tails, echo=FALSE, message=FALSE, warning=FALSE}

# Print the tail of the table to make sure that data are flagged
    
    knitr::kable(tail(current_df[current_df$DateTime %in% Time$DateTime, test])) 

```

## QAQC Plots

##### QAQC plot information and all_plot function information

For the plots, they use a function called "all_plot". In all_plot you can specify if you want interactive plots for the current data. You can specify which plotly plots you want on. You can also look at the plotly plots manually in each chunk by running the chunk with Use_plotly=TRUE as an argument. Then look at the list of plots you have made under "output". If you click on the "output" object in your environment it will list all of the plots and which ones are interactive plotly plots. To view the plots run "output[[number of the plot in the list you want to run]]". Eg. If you want to see the 4th plot in the list write output[[4]] then run that line and the plot should appear. 

If you would like to look at one variable then in the function below replace "dx" with the variable column. The object "dx" is just a list of variables so we don't have to list out all of the variables we want to plot. This is used to speed up the process. 

The plotting function is called all_plot() which plots the 4 or more plots described below. The function is sourced from GitHub in the first chunk of the script. The arguments are:
Var, # the variable you would like to plot
data, # the data frame to use
raw_data=NULL, # Is there raw data to compare with. Usually is NULL
reservoir, # the name of the reservoir you would like to filter by 
res_site, # the reservoir Site or Sites you would like to filter by
y_lab,  # This label can take an expression aka have the proper degrees C, 
y_lab2, # This label is for the plotly function which can not handle expression argument. 
Depth=F,  # Do you want depth as a factor
Water=T, # Are these plots for streaming sensors with RDO and temperature sensors
Use_plotly = F, # Do you want to produce interactive plots for observations of the current year?
Heatmap = F) # Do you want to make a heat maps? This only works if there are multiple depths at the same site


The arguments with = followed by a True means that they are the defaults and you don't need to add them to the function when you use it. If you want to use the opposite of the default you must specify that. 
  
##### Plot Description:

The plots below are:
The first 2 plots are the ones you should focus on for the QAQC chec. Spend the most time looking at the most recent data because that one as been checked. Do pay attention to the historical to make sure there are no crazy outliers that were missed in previous years. 

1. A time series of the current years' data. The black dots are the qaqced observations and the red is the raw files that were qaqced. This is to see what kind of values were removed and if there are any the script missed or that need to be added to the maintenance log. 

2. A time series of the historical and the current data just the qaqced values. 

The next two plots are just fun to see trends over time with the data. 

3. Density plots are like a histogram and a grouped by color so you can see where the data are relative to other years. 

4. The box plots look at the spread of the data within the year and we can look at the median and see how that is changing or not. 

Do not over think the last 2 plots, although they are good to look at historical trends to ensure relative data quality consistency. 

## All Met Variables

Note the red raw observations are not included in the final data frame. They are just for comparison, so we can see which values have been removed. 

#### PAR and Temperature Plots

```{r Temp, echo=FALSE, results='asis'}

dx <- colnames(raw |> select(PAR_umolm2s_Average:AirTemp_C_Average))

# If you would like to see the plots for one data column. Replace "dx" with the variable name and run the function. 

# make the plots
outputs <- lapply(dx, all_plot, data = current_df, raw_data= raw , y_lab = 'Var Unit', y_lab2 = "Var Unit", Water = FALSE, Use_plotly = F)

output <- unlist(outputs, recursive = F)

```

```{r Print plotly temp, eval=FALSE, warning=FALSE, include=FALSE, messages=FALSE}

 # Used to print the plotly plots
  # attach the Dependencies
  # since the do not get included with renderTags(...)$html
  deps <- lapply(
    Filter(function(x){inherits(x,"htmlwidget")},output),
    function(hw){
      renderTags(hw)$dependencies
    }
  )
  
  if(length(deps)>0){
  attachDependencies(
    tagList(),
    unlist(deps,recursive=FALSE)
  )
  }  
```

#### Relative Humidity, Wind Speed, and Wind Direction

```{r RH, echo=FALSE}

dx <- colnames(raw |> select(RH_percent:WindDir_degrees))

# If you would like to see the plots for one data column. Replace "dx" with the variable name and run the function. 

# make the plots
outputs <- lapply(dx, all_plot, data = current_df, raw_data= raw , y_lab = 'Var Unit', y_lab2 = "Var Unit", Water = FALSE, Use_plotly = F)

#output <- unlist(outputs, recursive = F)
```


#### Wind Rose plots by Year

The Met station tipped over on the morning of February 28, 2024 and when the station was righted we did not calibrate the wind and it is reading about 47 degrees more than before. These values are corrected in the data frame. We use the raw files to compare wind rose from all the observation and compare to the raw erroneous observation. 

```{r Wind Rose plots, echo=FALSE}


   daily <- current_df%>% 
  select(DateTime, WindDir_degrees, WindSpeed_Average_m_s)|>
  mutate(Date = as.Date(DateTime))|>
  group_by(Date)|>
  summarise_if(is.numeric, mean, na.rm=T)|>
  mutate(Year = year(Date))|>
  filter(Year<year(Sys.Date()))
      
 # Visualize wind directions for all obs by Year     
      chicago_wind <- daily%>%
        dplyr::rename(date = Date, ws = WindSpeed_Average_m_s, wd = WindDir_degrees)
      
      # Make plot
      pollutionRose(chicago_wind, pollutant="ws", type = "year", main= "Wind By Year at the dam")
      
      
# Wind plot before and after the Met station tipped over 
# Make a wind plot of the raw wind direction to compare with corrected values. 
      
      after <- current_raw|>
  filter(DateTime>ymd_hm("2023-02-28 09:00"))|>
  select(DateTime, WindDir_degrees, WindSpeed_Average_m_s)|>
  mutate(Date = as.Date(DateTime))|>
  group_by(Date)|>
  summarise_if(is.numeric, mean, na.rm=T)|>
  mutate(Year = year(Date))|>
        filter(Year<year(Sys.Date()))

 # Visualize wind directions for all obs by Year     
      chicago_wind <- after%>%
        dplyr::rename(date = Date, ws = WindSpeed_Average_m_s, wd = WindDir_degrees)
      
      # Make plot
      pollutionRose(chicago_wind, pollutant="ws", type = "year", main= "Wind After Met Station fell over and not corrected")

```

#### Shortwave, Longwave, and Albedo Plots

```{r Shortwave, echo=FALSE}

dx <- colnames(raw |> select(ShortwaveRadiationUp_Average_W_m2:Albedo_Average_W_m2))

# If you would like to see the plots for one data column. Replace "dx" with the variable name and run the function. 

# make the plots
outputs <- lapply(dx, all_plot, data = current_df, raw_data= raw , y_lab = 'Var Unit', y_lab2 = "Var Unit", Water = FALSE, Use_plotly = F)

#output <- unlist(outputs, recursive = F)
```

### Write to CSV

```{r Write CSV, eval = make_data, include=FALSE}

# convert datetimes to characters so that they are properly formatted in the output file
 current_df$DateTime <- as.character(format(current_df$DateTime))

# Double Check naming convention
# Variable_StartYear_EndYear
write_csv(current_df, file_name)

```

### Download and save Maintenance Log, Plotting function, and QAQC function

```{r Download and save Maintenance Log, eval = make_data, inclue = FALSE}

# Maintenance Log
download.file("https://raw.githubusercontent.com/FLARE-forecast/CCRE-data/ccre-dam-data-qaqc/CCRM_Maintenancelog_new.csv", maintenance_log)

# qaqc function
download.file("https://raw.githubusercontent.com/FLARE-forecast/CCRE-data/ccre-dam-data-qaqc/R/met_qaqc_function.R", qaqc_function)

# streaming plots function
download.file("https://raw.githubusercontent.com/CareyLabVT/Reservoirs/master/Data/DataAlreadyUploadedToEDI/EDIProductionFiles/Plotting_function.R", "Plotting_function.R")


```

