---
title: "Stage_QAQC"
author: "AEB, ABP, and DWH"
date: "2026-01-22"
output: html_document
---

Edits: ABP - changed the barometric pressure to average to get 10 more observations. Calculated depth using the relationship between hydro static pressure and height of the water column. Changed flags - added 2 for missing data, 3 for negative water level and changed to 0, 5 for negative pressure but not changed. Put the code in to run through the maintenance column. For comparing the water level to manual measurements used the closest observation as opposed to the average.
AEB - Made script functional for multiple PT site inputs  ##WHAT IF WE HAD EACH DEPLOYMENT BE A ###.1 etc site number? 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

pacman::p_load(dplyr, tidyverse, httr2, jsonlite, plotly, googlesheets4, ggpmisc, rLakeAnalyzer, zoo, dataRetrieval, here)

```

## Import all PT data

Pull all .csv files of direct data downloads from PT Updating to get: datetime column by GMT- 4 or 5; add serial number and csv name

```{r import data}

#make sure reservoir, site, and folder location are in consistent order for each site data
res <- (c("CCR", "CCR", "CCR"))
site <- (c("101", "301", "1001"))
site_folder <- (c("HPB_waterlevel", "CCR_301", "CCR_1001"))
index <- seq_along(site)

#Identify which GitHub Folder to pull folder names from
url <- "https://api.github.com/repos/CareyLabVT/ManualDownloadsSCCData/contents/CCR_manual_downloads/CCR_Hobos/"

#a list to hold the names of created site data 
dfs <- list()

#loop through each site to pull in data and assign reservoir and site tags
for (i in index) {

#create list of file names
resp <- request(paste0(url, site_folder[i])) |>
  req_headers(Accept = "application/vnd.github+json") |>
  req_perform()

dat <- resp_body_json(resp, simplifyVector = TRUE)

file_names <- dat$name

#only select .csv files
file_names <- file_names[grepl("\\.csv$", file_names)]

#add to link 
git_link <- paste0("https://raw.githubusercontent.com/CareyLabVT/ManualDownloadsSCCData/master/CCR_manual_downloads/CCR_Hobos/", site_folder[i], "/")

file_names <- paste0(git_link, file_names)

#import .csv files
# hobo_raw <- bind_rows(
#   lapply(file_names, function(f) {
# 
#     # Read header line to extract serial number
#     header_line <- readLines(con <- url(f), n = 2); close(con)
#     serial_number <- str_extract(header_line[2], "(?<=LGR S/N: )\\d+")
# 
#     df <- read_csv(
#       f,
#       skip = 1,
#       locale = locale(encoding = "UTF-8"),
#       show_col_types = FALSE
#     )
# 
#     # Extract GMT offset from the raw datetime column name
#     dt_col_name <- names(df)[str_detect(names(df), "Date Time")]
#     tz_offset <- str_extract(dt_col_name, "GMT-0(4|5)")
# 
#     df <- df |>
#       select(
#         DateTime_raw = contains("Date Time"),
#         HOBO_Abs_Pres_kPa = contains("Abs Pres"),
#         Temp_C = contains("Temp")
#       ) |>
#       mutate(
#         source_file = basename(f),
#         serial_number = serial_number,
#         DateTime_raw = parse_datetime(DateTime_raw, format = "%m/%d/%y %I:%M:%S %p"),
#         HOBO_Abs_Pres_kPa = as.numeric(HOBO_Abs_Pres_kPa),
#         Temp_C = as.numeric(Temp_C),
#       )
# 
#     df$DateTime_GMT_min4 <- if (tz_offset == "GMT-04") df$DateTime_raw else as.POSIXct(NA)
#     df$DateTime_GMT_min5 <- if (tz_offset == "GMT-05") df$DateTime_raw else as.POSIXct(NA)
# 
#     df |> select(-DateTime_raw)
#  })
#)

##TRY###
hobo_raw <- bind_rows(
  lapply(file_names, function(f) {
    # Read header line to extract serial number
    header_line <- readLines(con <- url(f), n = 2); close(con)
    serial_number <- str_extract(header_line[2], "(?<=LGR S/N: )\\d+")
    
    df <- read_csv(
      f, 
      skip = 1, 
      locale = locale(encoding = "UTF-8"), 
      show_col_types = FALSE
    )
    
    # Identify the actual raw column names
    col_names <- names(df)
    dt_col_name   <- col_names[str_detect(col_names, "Date Time")]
    temp_col_name <- col_names[str_detect(col_names, "Temp")]
    pres_col_name <- col_names[str_detect(col_names, "Abs Pres")]
    
    tz_offset <- str_extract(dt_col_name, "GMT-0(4|5)")
    
    # Determine unit types from column string contents
    is_fahrenheit <- any(str_detect(temp_col_name, "°F|Fahrenheit"))
    is_psi        <- any(str_detect(pres_col_name, "psi|psi"))
    
    df <- df |> 
      select(
        DateTime_raw       = all_of(dt_col_name),
        HOBO_Abs_Pres_raw  = all_of(pres_col_name),
        Temp_raw           = all_of(temp_col_name)
      ) |> 
      mutate(
        source_file   = basename(f),
        serial_number = serial_number,
        DateTime_raw  = parse_datetime(DateTime_raw, format = "%m/%d/%y %I:%M:%S %p"),
        
        # Convert Temperature: If F, apply (F - 32) * 5/9, otherwise keep as numeric
        Temp_C = if (is_fahrenheit) {
          (as.numeric(Temp_raw) - 32) * 5 / 9
        } else {
          as.numeric(Temp_raw)
        },
        
        # Convert Pressure: If psi, multiply by 6.89476 to get kPa, otherwise keep as numeric
        HOBO_Abs_Pres_kPa = if (is_psi) {
          as.numeric(HOBO_Abs_Pres_raw) * 6.89476
        } else {
          as.numeric(HOBO_Abs_Pres_raw)
        }
      )
    df$DateTime_GMT_min4 <- if (tz_offset == "GMT-04") df$DateTime_raw else as.POSIXct(NA)
    df$DateTime_GMT_min5 <- if (tz_offset == "GMT-05") df$DateTime_raw else as.POSIXct(NA)

    df |> select(-DateTime_raw)
 })
)

#add in Reservoir and Site columns
hobo_raw <- hobo_raw |>
  mutate(Reservoir = res[i],
         Site = site[i])

assign(paste0(res[i], "_", site[i], "_hobo_raw"), hobo_raw)
}
```

```{r}
#combine all site data into master dataframe

# get names of all objects ending in "_hobo_raw"
df_list <- ls(envir = .GlobalEnv)[grepl("_hobo_raw$", ls(envir = .GlobalEnv))]

# pull those objects into a list
hobo_list <- mget(df_list, envir = .GlobalEnv)

# bind them into one data frame (stacks rows, fills mismatched columns with NA)
hobo_raw_all <- bind_rows(hobo_list)

```

check which dates are diff timezones

```{r}

# unique(hobo_raw_all$serial_number)
# 
# # hobo_raw_all |> filter(serial_number == 22423275)
# # ## 22423275 is the newest deployed one; filter it out since its in the well 
# 
# zz <- hobo_raw_all |> filter(is.na(DateTime_GMT_min4))
# unique(zz$source_file)


```

## Manage Data

remove newest HOBO deployed in well for this publication

```{r}
# hobo_raw_all <- hobo_raw_all |> 
#   filter(serial_number != 22423275)

```

Set consistent Timezone,

```{r Data wrangling, echo = TRUE}
#Set tz to EST (UTC-5) for PT data

#check classes and curret tz
class(hobo_raw_all$DateTime_GMT_min4)
attr(hobo_raw_all$DateTime_GMT_min4, "tzone")
class(hobo_raw_all$DateTime_GMT_min5)
attr(hobo_raw_all$DateTime_GMT_min5, "tzone")

# Force correct timezones on each column
hobo_raw_all$DateTime_GMT_min4 <- force_tz(hobo_raw_all$DateTime_GMT_min4, tz = "Etc/GMT+4")
attr(hobo_raw_all$DateTime_GMT_min4, "tzone")
hobo_raw_all$DateTime_GMT_min5 <- force_tz(hobo_raw_all$DateTime_GMT_min5, tz = "Etc/GMT+5")
attr(hobo_raw_all$DateTime_GMT_min5, "tzone")


# Convert GMT-4 values to GMT-5, then coalesce into single DateTime column
hobo_raw_all <- hobo_raw_all |>
  mutate(
    DateTime = coalesce(
      with_tz(DateTime_GMT_min4, "Etc/GMT+5"),
      DateTime_GMT_min5
    )
  ) |>
  arrange(DateTime)


```

##check out data from 2025 storm when hobo1 was lost

```{r}
#plot full TS
hobo_raw_all |> 
  ggplot(aes(x = DateTime, y = HOBO_Abs_Pres_kPa))+
  geom_point() +
  facet_wrap(~ Site)


# #zoom in on when hobo1 moved
# hobo_raw_all |> 
#   mutate(Date = as.Date(DateTime)) |> 
#   filter(Date > ymd("2025-01-01"),
#          Date < ymd("2025-03-01")) |> 
#   ggplot(aes(x = DateTime, y = HOBO_Abs_Pres_kPa))+
#   geom_point()
# 
# zz <- hobo_raw_all |> 
#   mutate(Date = as.Date(DateTime)) |> 
#   filter(Date > ymd("2025-02-07"),
#          Date < ymd("2025-02-21")) |> 
#   ggplot(aes(x = DateTime, y = HOBO_Abs_Pres_kPa))+
#   geom_point()
# 
# zz
# plotly::ggplotly(zz)

```

remove data post feb 10th for sensor that was moved

```{r}

# hobo_raw_all <- hobo_raw_all |>
#   filter(!(serial_number == "21978681" & DateTime > ymd_hms("2025-02-10 00:00:00")))
# 
# 
# #plot full TS that data got removed 
# hobo_raw_all |> 
#   ggplot(aes(x = DateTime, y = HOBO_Abs_Pres_kPa))+
#   geom_point()


```

## Data Manage

Column names, data types, remove dups

```{r}
#select useful columns  
hobo_raw_all <- hobo_raw_all |>
  select(Reservoir, Site, DateTime, HOBO_Abs_Pres_kPa, Temp_C)|>
  arrange(DateTime)|> # put the date time in order
  drop_na() |> # drop any NAs from the data set
  group_by(Site)|>
  dplyr::distinct(DateTime, .keep_all = TRUE)|> # take out dups from overlapping data in uploads
  ungroup()


```

## Look at data before correcting for barometric pressure/maintenence log

This is just a check to make sure all raw data came in and looks like it should

```{r Raw data plot, echo = TRUE}
ggplot(data = hobo_raw_all, aes(x = DateTime)) +
  geom_point(aes(y = HOBO_Abs_Pres_kPa)) +
  scale_x_datetime() +
  facet_wrap(~ Site, scales = "free_x")
  
ggplot(data = hobo_raw_all, aes(x = DateTime)) +
  geom_point(aes(y = Temp_C)) +
  scale_x_datetime() +
  facet_wrap(~ Site, scales = "free")

```

## Correct pressure data with Barometric Pressure from met station on dam

The HOBO PTs are not vented. This corrects for local air pressure fluctuations.

```{r Correct for barometric pressure, echo = TRUE}
ccr_met_edi <- read_csv("https://pasta.lternet.edu/package/data/eml/edi/1105/4/8ebf27393ccafe518328468a260d2e18")
ccr_met_git <- read_csv("https://raw.githubusercontent.com/FLARE-forecast/CCRE-data/refs/heads/ccre-dam-data-qaqc/ccre_met_L1.csv")

ccr_met1 <- ccr_met_edi |>
  select(-starts_with("Note")) |> #remove note columns to bind
  rbind(ccr_met_git)

ccr_met <- ccr_met1 |> 
  select(DateTime, BP_Average_kPa, Flag_BP_Average_kPa, Rain_Total_mm) |> #check BP flag
  mutate(Date = as.Date(DateTime),
         Hour = hour(DateTime),
         Min = minute(DateTime))|>
  # filter(Min %in% c(0,10,20,30,40,50)) |>  #get just minutes to line up w/ HOBO
  # let's average the BP over the 10 minutes
  mutate(DateTime = round_date(DateTime,"10 minutes"))|>
  dplyr::group_by(DateTime)|>
  dplyr::summarise(BP_Average_kPa = mean(BP_Average_kPa, na.rm = T))|>
  select(DateTime, BP_Average_kPa)

#force into correct time zone (EST)
ccr_met$DateTime <- force_tz(as.POSIXct(ccr_met$DateTime), tzone = "EST")

#check that it worked
attr(ccr_met$DateTime, "tzone")

#correct to water level data
hobo <- left_join(hobo_raw_all, ccr_met, by = "DateTime") |> 
  mutate(corrected_Pres_kPa = HOBO_Abs_Pres_kPa - BP_Average_kPa) |>
  select(Reservoir, Site, DateTime, HOBO_Abs_Pres_kPa, BP_Average_kPa, corrected_Pres_kPa, Temp_C) 

# Viz the corrected pressure
pres <- hobo|>
  ggplot(aes(x = DateTime, y = corrected_Pres_kPa))+
  geom_point()+
  facet_wrap(~ Site, scales = "free_x")+
  theme_bw()

pres
#ggplotly(pres)

```

## Assign flags

Data Flags are reported for each variable in the data set.

0 = No Flag

1 = Data removed and set to NA due to maintenance

2 = Missing data; either stream pressure or atmospheric correction pressure

#3 = Negative water level

4 = Correction applied to the data

5 = Negative corrected pressure but left in data set

6 = Flow value outside of range of flow measurements used in rating curve calculations

7 = Data interpolated for gaps \< 3 hours

```{r maintenance log, echo = TRUE}
#Load maintenance log
#UPDATE FOLDER EACH YEAR
log <- read_csv(here("Data", "DataAlreadyUploadedtoEDI", "EDIProductionFiles", "MakeEML_CCR_Inflow", "2026", "pt_maintenancelog_2024_2026.csv"))

# for loop to create flag columns in hobo df
  for(j in colnames(hobo |> select(HOBO_Abs_Pres_kPa:Temp_C))) { 
    #for loop to create new columns in data frame
    hobo[,paste0("Flag_",colnames(hobo[j]))] <- 0 #creates flag column + name of variable
    hobo[c(which(is.na(hobo[,j]))),paste0("Flag_",j)] <-2 #puts in flag 2 if value not collected
  }

#Flag of 2 if BP_Average is missing
hobo <- hobo |>
  mutate(
    Flag_BP_Average_kPa = if_else(
      is.na(BP_Average_kPa),
      2,
      Flag_BP_Average_kPa),
    Flag_corrected_Pres_kPa = if_else(
      is.na(BP_Average_kPa),
      2,
      Flag_corrected_Pres_kPa))

#force Maintenance Log into EST tz
log$TIMESTAMP_start <- force_tz(as.POSIXct(log$TIMESTAMP_start, format = "%m/%d/%Y %H:%M"), tzone = "EST")
log$TIMESTAMP_end <- force_tz(as.POSIXct(log$TIMESTAMP_end, format = "%m/%d/%Y %H:%M"), tzone = "EST")

log_edi <- log |> mutate(TIMESTAMP_start = as.character(format(TIMESTAMP_start)),
                         TIMESTAMP_end = as.character(format(TIMESTAMP_end)))

write_csv(log_edi, "./hpb_maintenancelog_2024_2026.csv", quote = "all")

#loop through each site to handle each site's maintenance log rows separately 
site_list <- unique(log$Site)

for (site_id in site_list) {

  log_site <- log |> filter(Site == site_id)

  if (nrow(log_site) == 0) {

    print(paste0('No Maintenance Events Found for Site ', site_id, "..."))

  } else {

    for (i in 1:nrow(log_site)) {

      start <- log_site$TIMESTAMP_start[i]
      end   <- log_site$TIMESTAMP_end[i]

      Reservoir  <- log_site$Reservoir[i]
      flag <- log_site$flag[i]
      update_value <- as.numeric(log_site$update_value[i])
      adjustment_code <- log_site$adjustment_code[i]

      colname_start <- log_site$start_parameter[i]
      colname_end   <- log_site$end_parameter[i]

      if (is.na(colname_start)) {
        maintenance_cols <- colnames(hobo %>% select(any_of(colname_end)))
      } else if (is.na(colname_end)) {
        maintenance_cols <- colnames(hobo %>% select(any_of(colname_start)))
      } else {
        maintenance_cols <- colnames(hobo %>% select(c(colname_start:colname_end)))
      }

      flag_cols <- paste0("Flag_", maintenance_cols)

      # site condition, evaluated against the full hobo df
      site_match <- hobo$Site == site_id

      # time condition, also evaluated against the full hobo df
      if (is.na(end)) {
        time_match <- hobo$DateTime >= start
      } else if (is.na(start)) {
        time_match <- hobo$DateTime <= end
      } else {
        time_match <- hobo$DateTime >= start & hobo$DateTime <= end
      }

      # combine: this vector is true for only specific site and specific time window
      Time <- site_match & time_match

      if (flag == 1) {
        hobo[Time, maintenance_cols] <- NA
        hobo[Time, flag_cols] <- flag

      } else if (flag == 4) {
        hobo[Time, maintenance_cols] <- eval(parse(text = adjustment_code))
        hobo[Time, flag_cols] <- flag

      } else {
        warning(paste0("Flag ", flag, " used not defined in the L1 script. 
                        Talk to Austin and Adrienne if you get this message"))
      }
    }
  }
}

#write adjusted data back to main data frame
#hobo[hobo$Site == site_id, ] <- hobo_site


#Flag counts 
Flags <- hobo |>
  select(starts_with("Flag"))

# Make a table with the number of times a flag was used
for(f in 1:(ncol(Flags))){
  #print(colnames(Flags[f]))
  print(table(Flags[,f], useNA = "always"))
}

#check
hobo |> 
  filter(if_any(starts_with("Flag_"), ~ . %in% c(1,4))) |> 
  count(Site, across(starts_with("Flag_")))

```

```{r}

#Plot corrected pressure 

check_pressure <- hobo|>
  #filter(DateTime > as.Date("2025-06-10") & DateTime < as.Date("2025-06-15"))|>
  # mutate(cor_pres = HOBO_Abs_Pres_kPa - BP_Average_kPa)|>
  ggplot(aes(x = DateTime))+
  geom_point(aes(y = corrected_Pres_kPa)) +
  # geom_point(aes(y = cor_pres), color = "red") +
  facet_wrap(~ Site, scales = "free")+
  theme_bw()

check_pressure

ggplotly(check_pressure)

```

##Correction offsets for second PT deployement and flag negative PT

```{r Correct offsets flag 4, echo = TRUE}

# calculate the height of the water column from the pressure using the relationship between hydro static pressure and height

# p = ρgh

# p = pressure in liquid (N/m2, Pa, lbf/ft2, psf)

# ρ = density of liquid (kg/m3, slugs /ft3)

# g = acceleration of gravity (9.81 m/s2, 32.17405 ft/s2)

# h = height of fluid column - or depth in the fluid where pressure is measured (m, ft)

# so h = p/(ρg)

# 1) Need to convert temperature to density. 
# 2) We are assuming that salinity is 0 and that is a very fair assumption

stage_obs <- hobo|>
  mutate(density = water.density(Temp_C),
         waterlevel_cm = ((corrected_Pres_kPa*1000)/(9.81*density))*100)|>
  # remove the density column because we don't need it any more
  select(-density)|>
  # make a flag column for water level
  # Add a flag column for when water level is negative and set to 0 and flag when pressure is negative
  mutate(Flag_waterlevel_cm = 0,
         #Flag_waterlevel_cm = ifelse(waterlevel_cm < 0, 3, Flag_waterlevel_cm),
         #waterlevel_cm = ifelse(waterlevel_cm < 0, 0, waterlevel_cm), ##This data actually looks good, the reference elevation of 0 is just higher than the PT
         Flag_corrected_Pres_kPa = ifelse(corrected_Pres_kPa < 0, 5, Flag_corrected_Pres_kPa), 
         Flag_corrected_Pres_kPa = ifelse(Flag_HOBO_Abs_Pres_kPa == 1, 1, Flag_corrected_Pres_kPa),
         Flag_waterlevel_cm = ifelse(Flag_HOBO_Abs_Pres_kPa == 1, 1, Flag_waterlevel_cm))|>
  select(Reservoir, Site, DateTime, HOBO_Abs_Pres_kPa, BP_Average_kPa, corrected_Pres_kPa, waterlevel_cm, Temp_C, everything())

# Double check that all missing data have flags
for(j in colnames(stage_obs |> select(HOBO_Abs_Pres_kPa:Temp_C))) { 
    
    stage_obs[c(which(is.na(stage_obs[,j] & is.na(stage_obs[,paste0("Flag_",j)])))),paste0("Flag_",j)] <- 2 #puts in flag 2 if value not collected
}

#Flag counts 
Flags <- stage_obs |>
  select(starts_with("Flag"))

# Make a table with the number of times a flag was used
for(f in 1:(ncol(Flags))){
  #print(colnames(Flags[f]))
  print(table(Flags[,f], useNA = "always"))
}

```

## Gap fill for missing periods less than 3 hours

Should eventually add... reasonable inference esp since most deleted times of this length we are there and can note any serious waterlevel changes. Better/more continuous we can get the PT data looking, the better the discharge data will be. Should be able to build a complete timeseries df, use zoo na.approx with tsibble for multiple sites, and then remove NA rows of table for gaps longer than fill length. <https://thedatahall.com/filling-gaps-in-time-series-and-panel-data-using-r/>, but

```{r Gap fill}
#gap fill for each site individually
#for (i in site){}

# seq_filled <- seq(
#   from = min(stage_obs$DateTime),
#   to = max(stage_obs$DateTime),
#   by = "10 min"
# )
# 
# stage_filled <- stage_obs |>
#   complete(DateTime = seq_filled)
# 
# stage_filled <- stage_filled |>
#   mutate(
#     waterlevel_cm_filled = na.approx(
#       waterlevel_cm,
#       x = DateTime,
#       maxgap = 18,
#       na.rm = FALSE
#     ), #Fills any gaps less than 3 hrs long with interpolation of pre and post waterlevel
#     Flag_waterlevel_cm = if_else(
#     is.na(waterlevel_cm) & !is.na(waterlevel_cm_filled),
#     as.numeric(paste0(coalesce(as.character(Flag_waterlevel_cm), ""), 7)),
#     as.numeric(Flag_waterlevel_cm)
#     ), #Flags with 7 for all interpolated water levels
#     across(
#       c(Flag_HOBO_Abs_Pres_kPa, Flag_BP_Average_kPa, Flag_corrected_Pres_kPa, Flag_Temp_C),
#       ~ if_else(
#           is.na(HOBO_Abs_Pres_kPa) & is.na(BP_Average_kPa) 
#           & is.na(corrected_Pres_kPa) & is.na(Temp_C) 
#           & !is.na(waterlevel_cm_filled),
#           as.numeric(paste0(coalesce(as.character(.x), ""), 2)),
#           as.numeric(.x)
#         ) #Adds flags for data lines that were not originally collected by sensor but were within a <3hr data gap, so were able to be interpolated
#   ))

# --- gap fill for each site individually ---

stage_filled <- stage_obs |>
  group_by(Site) |>
  # complete() respects the grouping: for EACH site, it builds its own
  # 10-minute sequence spanning just that site's min to max DateTime,
  # and inserts empty rows only within that site's range.
  complete(DateTime = seq(min(DateTime), max(DateTime), by = "10 min")) |>
  mutate(
    # na.approx is called once per group because of group_by(Site) above.
    # That means the interpolation window (maxgap = 18) can never reach
    # across the boundary from one site's data into another's -- it only
    # ever looks at consecutive rows belonging to the same site.
    waterlevel_cm_filled = na.approx(
      waterlevel_cm,
      x = DateTime,
      maxgap = 18,
      na.rm = FALSE
    ), # Fills any gaps less than 3 hrs long with interpolation of pre and post waterlevel, per site

    Flag_waterlevel_cm = if_else(
      is.na(waterlevel_cm) & !is.na(waterlevel_cm_filled),
      as.numeric(paste0(coalesce(as.character(Flag_waterlevel_cm), ""), 7)),
      as.numeric(Flag_waterlevel_cm)
    ), # Flags with 7 for all interpolated water levels

    across(
      c(Flag_HOBO_Abs_Pres_kPa, Flag_BP_Average_kPa, Flag_corrected_Pres_kPa, Flag_Temp_C),
      ~ if_else(
          is.na(HOBO_Abs_Pres_kPa) & is.na(BP_Average_kPa)
          & is.na(corrected_Pres_kPa) & is.na(Temp_C)
          & !is.na(waterlevel_cm_filled),
          as.numeric(paste0(coalesce(as.character(.x), ""), 2)),
          as.numeric(.x)
        ) # Adds flags for data lines that were not originally collected by sensor but were within a <3hr data gap, so were able to be interpolated
    )
  ) |>
  ungroup() # drop the grouping once done so downstream code isn't accidentally grouped


#adjust datum so no negatives for good looking values 
##In future, this will be done in field by choosing reference point elevation well above zero. 
# datum <- 20
# 
# stage_final <- stage_filled |>
#   mutate(
#     stage_cm = waterlevel_cm_filled + datum
#   )|>
#   select (DateTime, HOBO_Abs_Pres_kPa, BP_Average_kPa, corrected_Pres_kPa, stage_cm, Temp_C, Flag_HOBO_Abs_Pres_kPa, Flag_BP_Average_kPa, Flag_corrected_Pres_kPa, Flag_waterlevel_cm, Flag_Temp_C) |>
#   rename(
#     Flag_stage_cm = Flag_waterlevel_cm
#   )

#Flags for gap fill that was not in original data collection


stage_final <- stage_filled |>
  mutate(
    stage_cm = waterlevel_cm_filled
  )|>
  select (Reservoir, Site, DateTime, HOBO_Abs_Pres_kPa, BP_Average_kPa, corrected_Pres_kPa, stage_cm, Temp_C, Flag_HOBO_Abs_Pres_kPa, Flag_BP_Average_kPa, Flag_corrected_Pres_kPa, Flag_waterlevel_cm, Flag_Temp_C) |>
  rename(
    Flag_stage_cm = Flag_waterlevel_cm
  )


#remove rows with NA
stage_final <- drop_na(stage_final, stage_cm)

#Flag counts 
Flags <- stage_final |>
  select(starts_with("Flag"))

# Make a table with the number of times a flag was used
for(f in 1:(ncol(Flags))){
  #print(colnames(Flags[f]))
  print(table(Flags[,f], useNA = "always"))
}

# save data file 
write.csv(stage_final, "pt_stage_2024_2026.csv", row.names = F)

```


```{r Plot final data}

p <- stage_final|>
  ggplot(aes(x = DateTime))+
  geom_point(aes(y = stage_cm)) +
  facet_wrap(~ Site, scales = "free")+
  theme_bw()
p

#ggplotly(p)
```

```{r USGS Reference Gage}
# ref_site <- "USGS-02055100"
# 
# USGS_Ref <- dataRetrieval::read_waterdata_continuous(
#   monitoring_location_id = ref_site,
#   parameter_code = "00065",
#   properties = c("time", "value", "unit_of_measure"),
#   time = paste0(min(stage_final$DateTime), "/",max(stage_final$DateTime))
# )
# 
# USGS_Ref <- USGS_Ref |>
#   mutate(
#     stage_cm = value * 30.48
#   )

```

##View with manual stage measurements

```{r View manual measurements on timeseries, echo = TRUE}

# #Pull manual stage measurement file
#stage_checks <-  gsheet::gsheet2tbl("https://docs.google.com/spreadsheets/d/1OOh1QfOad3ez_Hk4Sl8ziPYxmWWcoSv1GNeuJkrFec8")
# 
# #format date column
# stage_checks$DateTime = lubridate::parse_date_time(stage_checks$DateTime, orders = c('ymd HMS','ymd HM','ymd', 'mdy','mdy HM', 'mdy HMS', 'mdy HM'), tz = "America/New_York")
# 
# # convert to EST
# stage_checks$DateTime <- with_tz(as.POSIXct(stage_checks$DateTime), tz = "EST")
# 
# # convert manual measurements to stage w offset applied above
# stage_checks <- stage_checks |>
#   mutate(
#     manual_stage_cm = manual_depth_cm + datum
#   )
# 
# # make a plot of stage water level with manual points on top
# p <- ggplot() +
#   geom_point(data = stage_final, aes(x = DateTime, y = stage_cm)) +
#   geom_point(data = stage_checks, aes(x = DateTime, y = manual_stage_cm), color = "red") +
#   ggtitle("Staged data with manual points overlaid in red") +
#   theme_bw()
# 
# p
# #ggplotly(p)
# 
# pp <- ggplot() +
#   geom_point(data = stage_final, aes(x = DateTime, y = stage_cm)) +
#   geom_line(data = USGS_Ref, aes(x = time, y = stage_cm), color = 'blue') +
#   ggtitle("Staged data USGS comparison site") +
#   theme_bw()
# 
# pp
# #ggplotly(pp)
# 
#  # find the closest date and then join the two data frames
# # drop the NA waterlevel
# 
# wl <- stage_final|>
#   select(DateTime, stage_cm)|>
#   drop_na()
# 
#   by <- join_by(closest(DateTime <= DateTime))
#   compare <- left_join(stage_checks, wl, by)|>
#     dplyr::rename(DateTime = DateTime.x)
# 
# 
# #Filter to pull dates from each specific PT deployment
# PT1 <- compare %>%
#    filter(DateTime >= as.POSIXct("2024-04-23", tz = "America/New_York"),
#          DateTime <= as.POSIXct("2024-12-17", tz = "America/New_York"))
# 
# PT2 <- compare %>%
#    filter(DateTime >= as.POSIXct("2025-03-01", tz = "America/New_York"),
#          DateTime <= as.POSIXct("2025-12-02", tz = "America/New_York"))
# 
# #Plot comparison of PT to manual measured stage for 1st PT deployment
# ggplot(data = PT1, aes(x = stage_cm, y = manual_stage_cm))+ 
#   geom_point()+
#   stat_poly_line(method = "lm", linewidth = 2)+
#   stat_poly_eq(formula=y~x, label.x = "left", label.y="top", parse=TRUE, inherit.aes = F,
#                aes(x = stage_cm, y = manual_stage_cm, label=paste(..adj.rr.label..,..p.value.label..,sep="~~~"),size=3))+
#   labs(title = "PT1")
# 
# #Plot comparison of PT to manual measured stage for 2nd PT deployment
# ggplot(data = PT2, aes(x = stage_cm, y = manual_stage_cm))+ 
#   geom_point()+
#   stat_poly_line(method = "lm", linewidth = 2)+
#   stat_poly_eq(formula=y~x, label.x = "left", label.y="top", parse=TRUE, inherit.aes = F,
#                aes(x = stage_cm, y = manual_stage_cm, label=paste(..adj.rr.label..,..p.value.label..,sep="~~~"),size=3))+
#   labs(title = "PT2")


```

##Visualize differences between PT sensor reading and manual measurement

# ```{r Visualize PT v manual measurements, echo = TRUE}
# selected_compare <- compare |>
#   filter(!is.na(stage_cm), !is.na(manual_stage_cm))
# 
# selected_compare$difference <- selected_compare$stage_cm - selected_compare$manual_stage_cm
# 
# ggplot(data = selected_compare, aes(x = DateTime, y = difference))+
#   geom_point()+
#   ylab("PT - manual depth (cm)")

```

##Visualize qaqc parameters ie manual measurements, temp Use this graph to visually qaqc PT data-- 1. When PT comes out of the water as seen by drastic temp change/larger diurnal swings and flat lining of PT data 2. When site visit measurements don't line up with PT data 3. Gaps or odd jumps in water level

```{r temp and corrected stage, echo = TRUE}
# 
# a <- ggplot(data = stage_final, aes(x = DateTime)) +
#   geom_point(aes(y = stage_cm)) +
#   geom_line(aes(y = Temp_C), color = "blue")
# a
```

```{r Compare with precip, echo = TRUE}

# rain_comp <- left_join(stage_final, ccr_met1, by = "DateTime")
# 
# ggplot(data = rain_comp, aes(x = DateTime)) +
#   geom_line(aes(y = stage_cm)) +
#   geom_col(aes(y = Rain_Total_mm*10), color = "blue")+ #x 10 rain for better viewing
#   scale_x_datetime()
#   
```

```{r Compare with manual measurements, echo = TRUE}
# a <- ggplot(data = compare, aes(x = DateTime)) +
#   geom_point(aes(y = stage_cm)) +
#   geom_point(aes(y = manual_stage_cm), color = "red")
# 
# a
# #ggplotly(a)

```
