---
title: "Weir Inflow Data collation and Plots for EDI"
output: html_document
date: "2023-02-15"
---

Master QAQC script in prep for publishing FCR inflow data to EDI. This script uses the qaqcfcr_weir function, which automatically QAQCs the data, and produces figures to look over the data and visually inspect for major outliers. 

Use this file path in Carey Lab Reservoir GitHub Repo: "./Data/DataAlreadyUploadedToEDI/EDIProductionFiles/MakeEML_Inflow/2023_Jan/"

This step gets the right packages and sources the QAQC script. Make sure you have the correct year for the script file (e.g., don't use 2023_Jan if it's no longer 2023).


```{r Set Up, include=FALSE}
pacman::p_load("RCurl","tidyverse","lubridate", "knitr", "scattermore")
source("Inflow_QAQC_function_2013_2022.R")

folder<- "./Data/DataAlreadyUploadedToEDI/EDIProductionFiles/MakeEML_Inflow/2023_Jan/"

# Set up the current time end time of the file and the current year for QAQC plots

#current time of QAQC for graphing
current_time_start="2022-01-01 00:00:00, tz=UTC"
current_time_end="2023-01-01 00:00:00, tz=UTC"
```


```{r Create Data folder, include=FALSE}
### Create a misc_data_files folder if one doesn't already exist
misc_folder <- "misc_data_files"
if (file.exists(misc_folder)) {
  cat("The folder already exists")
} else {
  dir.create(misc_folder)
}

```


```{r Download data, include=FALSE, eval=FALSE}

#All the Raw data and the maintenance file is on github. Use this section to download the files so you are working with the most recent ones.

#If you want to download then set eval=TRUE before knitting HTML if not set to FALSE will not run the chunk and use previously downloaded files. 
# Set the timeout option to 100 seconds instead of 60
options(timeout=1000)

# This function to speeds up the download time of the data downloads. 
# If your wifi is slow then it will still take a while. 

bdown=function(url, file){
  library('RCurl')
  f = CFILE(file, mode="wb")
  a = curlPerform(url = url, writedata = f@ref, noprogress=FALSE)
  close(f)
  return(a)
}


# #download current VT sensor data from GitHub
 bdown("https://raw.githubusercontent.com/FLARE-forecast/FCRE-data/fcre-weir-data/FCRweir.csv", "misc_data_files/FCRweir.csv")

# #download maintenance file
 bdown("https://raw.githubusercontent.com/FLARE-forecast/FCRE-data/fcre-weir-data/Weir_MaintenanceLog.txt","misc_data_files/Weir_MaintenanceLog_2013_2022.txt")
 
 # # download readings from staff gugage on Github
 bdown('https://raw.githubusercontent.com/FLARE-forecast/FCRE-data/fcre-weir-data/Inflow_Gauge_Height_at_Weir.csv',"misc_data_files/Inflow_Gauge_Height_at_Weir.csv")
 
# #download the WVWA sensors
bdown('https://raw.githubusercontent.com/CareyLabVT/Reservoirs/master/Data/DataNotYetUploadedToEDI/Raw_inflow/WVWA_pressure_readings_2013_current.csv',"misc_data_files/WVWA_pressure_readings_2013_current.csv") 

```

```{r Read in VT file and clean it up, include=FALSE}

 VTsens<-read_csv("misc_data_files/FCRweir.csv",
                  skip=4,col_names=c("DateTime","Record","BattV","PTemp_C","AirTemp_C","Lvl_psi","wtr_weir"))
   
    # Select the columns you want
    VTdat <- VTsens[,c("DateTime","Lvl_psi","wtr_weir")]
    # Rename the columns
    colnames(VTdat) <- c('DateTime', 'VT_Pressure_psia', 'VT_Temp_C')
    
  #order data by DateTime
VTsens$DOY=yday(VTsens$DateTime)  
    
```

```{r Read in WVWA file, include=FALSE}

WVWA<-read_csv("misc_data_files/WVWA_pressure_readings_2013_current.csv")

  #order data by DateTime
WVWA$DOY=yday(WVWA$DateTime)  

```


# Check for gaps in the data frame
This identifies if there are any daily data gaps in the long-term record.

### Daily Gaps for VT Sensors
```{r Check for daily gaps in VT sensor, echo=FALSE}
for(i in 2:nrow(VTsens)){ #this identifies if there are any data gaps in the long-term record, and where they are by record number
  if(VTsens$DOY[i]-VTsens$DOY[i-1]>1){
    print(c(VTsens$DateTime[i-1],VTsens$DateTime[i]))
  }
}
```
This identifies if there are any sub-daily gaps in the long-term record. 
Most of these gaps happen when we change the program on the data logger. 

### Sub-daily Gaps in VT Sensors
```{r Check for sub daily gaps, echo=FALSE}
for(i in 2:length(VTsens$Record)){ #this identifies if there are any data gaps in the long-term record, and where they are by record number
  if(abs(VTsens$Record[i]-VTsens$Record[i-1])>1){
    print(c(VTsens$DateTime[i-1],VTsens$DateTime[i]))
  }
}
```

### Daily Gaps in WVWA sensors
```{r Check for daily gaps in WVWA sensor, echo=FALSE}
for(i in 2:nrow(WVWA)){ #this identifies if there are any data gaps in the long-term record, and where they are by record number
  if(WVWA$DOY[i]-WVWA$DOY[i-1]>1){
    print(c(WVWA$DateTime[i-1],WVWA$DateTime[i]))
  }
}
```

```{r Run the QAQC function, echo=FALSE}

# QAQC Function

# This section sets up and runs the QAQC function. The first define where the data entered into the function are.

#The output tells you the missing observations.If you can't find them in the manual downloads then make sure to put # #these times in the methods.

#There are also some warnings which are checks to make sure the maintenance log is using the correct columns for #indexing. section under missing.


# run standard qaqc these are where the data entered in the function are defined
VT_data_file <- VTdat # use the cleaned version
WVWA_data_file <- "misc_data_files/WVWA_pressure_readings_2013_current.csv"
maintenance_file <- "misc_data_files/Weir_MaintenanceLog_2013_2022.txt"
Staff_gauge_readings <- "misc_data_files/Inflow_Gauge_Height_at_Weir.csv"
output_file <- "Inflow_2013_2022.csv"
start_date<-NULL
end_date<-NULL

# Run the QAQC function
qaqc_fcrweir(VT_data_file, WVWA_data_file, maintenance_file, Staff_gauge_readings, output_file ,start_date, end_date)

```

## Read in the QAQC File and Check it out

This section reads in the QAQC file and then you can look at the head, tail and structure. Make sure the last row is Dec. 31 23:59 of the publishing year. There should be 45 columns unless a new one has been added.

```{r Read in QAQC file and look at it}
# read in qaqc function output

weirdata <- read_csv(output_file)
#fcrmetdata <- read_csv("FCR_Met_final_2015_2022.csv")

#read_csv(rating_curve)

# subset file to only unpublished data
weirdata <- weirdata[weirdata$DateTime<ymd_hms(current_time_end),]

# what does the beginning look like
head(weirdata)
# Make sure it goes to Dec 31st 23:59 of the previous year or your ending period
tail(weirdata)
# check out the structure
str(weirdata)
```

```{r Make the Maintenance Log file for EDI, include=FALSE}
RemoveWeir=read.csv(maintenance_file)
# Maintenance Log
names(RemoveWeir) = c("Station", "DateTime_start","DateTime_end", "Parameter", "ColumnNumber", "Flag", "FlagColumn","Notes") #finalized column names

RemoveWeir$Reservoir= "FCR"#add reservoir name for EDI archiving
RemoveWeir$Site=100 #add site column for EDI archiving

Final_log=RemoveWeir[,c(9:10,1:8)]

# write it as a csv for EDI
write.csv(Final_log, "Inflow_Maintenance_RatingCurveLog_2013_2022.csv", row.names=F, quote = F)

# Let's do it for the staff guage observations

Height <- read.csv(Staff_gauge_readings)

write.csv(Height, "Inflow_GaugeHeight_2013_2022.csv", row.names=F, quote=F)

```
## Check out the Flag frequency

Let's look at the Flag frequency for each variable. 

As a reminder here are the Flag codes: 

0: no flag; 

1: value corrected to account for artificial increase in pressure after sensor maintenance; 

2: sensor malfunction; 

3: value of NA due to extremely low flows that are not well captured by rectangular or v-notch weir; 

4: demonic intrusion; 

5: value of NA due to leaking at weir;

6: flow topping the v-notch weir;

7: missing observation/not recorded;

8: values removed because of maintenance; 

13: value downcorrected due to low flows on the rectangular weir;

16: value downcorrected due to flow overtopping the rectangular weir;

24: weir damaged due to weather.


```{r Check out the flags, echo=FALSE}

#make sure no NAS in the Flag columns
Flags=weirdata%>%
  select(DateTime, starts_with("Flag"))

RowsNA=Flags[!complete.cases(Flags), ] # Keep only the complete rows

# Make a table with the number of times a flag was used
for(f in 2:(ncol(Flags))){
  print(table(Flags[,f], useNA = "always"))
}
```

## QAQC Plots
These are QAQC plots to see if there are any questionable values we missed. 

## Temperature
```{r Graph Air Temp amd Panel Temp, echo=FALSE}

daily <- weirdata%>% 
  group_by( Date = as.Date(DateTime)) %>% 
  summarise(across(c(WVWA_Pressure_psi, WVWA_Baro_pressure_psi, WVWA_Pressure_psia,WVWA_Flow_cms,WVWA_Temp_C,
                     VT_Pressure_psia,VT_Flow_cms,VT_Temp_C), mean))%>%
  mutate(Year = as.factor(year(Date)),
         Month = month(Date))

weirdata<-weirdata%>%
  mutate(Year=year(DateTime))

colors <- c("WVWA" = "blue", "VT" = "red")


weirdata%>%
  ggplot(., aes(x=DateTime))+
  geom_scattermore(aes(y=WVWA_Flow_cms, color="WVWA"), pointsize = 2)+
  geom_scattermore(aes(y=VT_Flow_cms, color="VT"), pointsize = 2) +
  ggtitle("All Flow Rates") +
    labs(y = "cms",
         color = "Legend") +
    scale_color_manual(values = colors)

# Just the current year

weirdata%>%
  filter(DateTime>=ymd_hms(current_time_start) & DateTime<ymd_hms(current_time_end))%>%
  ggplot(., aes(x=DateTime))+
  geom_point(aes(y=WVWA_Flow_cms, color="WVWA"))+
  geom_point(aes(y=VT_Flow_cms, color="VT")) +
  ggtitle("All Flow Rates") +
    labs(y = "cms",
         color = "Legend") +
    scale_color_manual(values = colors)



ggplot(data = daily, aes(x = WVWA_Flow_cms, group = Year, fill = Year))+
  geom_density(alpha=0.5)+
  xlab("Daily avg. inflow WVWA (cms)")+
  xlim(0,0.5)+
  ggtitle("All WVWA Flow Density Plot") +
  theme_bw()


ggplot(data = daily, aes(x = Year, y = WVWA_Flow_cms, group = Year, fill = Year))+
  geom_boxplot()+
  #geom_jitter(alpha = 0.1)+
  ylab("Daily avg. inflow WVWA (cms)")+
  ylim(0,0.3)+
  ggtitle("All WVWA Flow Boxplot") +
  theme_bw()
  

ggplot(data = daily, aes(x = VT_Flow_cms, group = Year, fill = Year))+
  geom_density(alpha=0.5)+
  xlab("Daily avg. inflow VT (cms)")+
  xlim(0,0.5)+
  ggtitle("All VT Flow Density Plot")+
  theme_bw()


ggplot(data = daily, aes(x = Year, y = VT_Flow_cms, group = Year, fill = Year))+
  geom_boxplot()+
  #geom_jitter(alpha = 0.1)+
  ylab("Daily avg. inflow VT (cms)")+
  ylim(0,0.3)+
  ggtitle("All VT Flow Boxplot")+
  theme_bw()

# Plot one to one of flow 
weirdata%>%
  drop_na(VT_Flow_cms)%>%
  ggplot(.,aes(x=WVWA_Flow_cms, y=VT_Flow_cms, color=as.factor(Year)))+
  geom_point()+
  ggtitle("Compare WVWA flow and VT flow") 
  
```

### Plots for WVWA_Pressure_psi
```{r Raw WVWA pressure not corrected, echo=FALSE}
## Preliminary visualization of raw pressure data from inflow transducer
 ggplot(data =weirdata, aes(x = DateTime, y = WVWA_Pressure_psi))+
  geom_scattermore()+
  ylab("Daily avg. inflow pressure (psi)")+
  geom_vline(xintercept = as.Date('2016-04-18'))+ # Date when downcorrection started
  theme_bw()+
  ggtitle("All WVWA Pressure (psi)")


# Look at daily average WVWA pressure sensor. Change the data to look at days that are funky
ggplot(data = weirdata, aes(x = DateTime, y = WVWA_Pressure_psi))+
  geom_point()+
  ylab("Daily avg. inflow pressure (psi)")+
  theme_bw() +
  ggtitle("Current WVWA Pressure (psi)")+
  xlim(c(ymd_hms(current_time_start),ymd_hms(current_time_end)))


# Look at the histogram of observations
ggplot(data = daily, aes(x = WVWA_Pressure_psi, group = Year, fill = Year))+
  geom_density(alpha=0.5)+
  xlab("Daily avg. inflow pressure (psi)")+
  theme_bw()+
  ggtitle("All WVWA Density Plot")


# Boxplot of weir observations
 ggplot(data = daily, aes(x = Year, y = WVWA_Pressure_psi, group = Year, fill = Year))+
  geom_boxplot()+
  ylab("Daily avg. inflow pressure (psi)")+
   ggtitle("All WVWA Boxplot") +
  theme_bw()
```

### Plots of raw pressure data from catwalk transducer
```{r Raw pressure from catwalk, echo=FALSE}
ggplot(data = weirdata, aes(x = DateTime, y = WVWA_Baro_pressure_psi))+
  scattermore::geom_scattermore()+
  ylab("Daily avg. inflow pressure (psi)")+
  theme_bw() +
  ggtitle("All barometric pressure (psi)") 
 

# Let's look at the current surface pressure 
ggplot(data = weirdata, aes(x = DateTime, y = WVWA_Baro_pressure_psi))+
  geom_point()+
  ylab("Bp pressure (psi)")+
  theme_bw() +
  ggtitle("This year's barometric pressure") +
  xlim(c(ymd_hms(current_time_start),ymd_hms(current_time_end)))


 ggplot(data = daily, aes(x = WVWA_Baro_pressure_psi, group = Year, fill = Year))+
  geom_density(alpha=0.5)+
  xlab("Daily avg. catwalk pressure (psi)")+
   ggtitle("BP Density Plot")+
  theme_bw()


ggplot(data = daily, aes(x = Year, y = WVWA_Baro_pressure_psi, group = Year, fill = Year))+
  geom_boxplot()+
  #geom_jitter(alpha = 0.1)+
  ylab("Daily avg. catwalk pressure (psi)")+
  ggtitle("BP Density Boxplot")+
  theme_bw()
```

### Plots for VT pressure sensor readings ####
```{r VT Pressure Sensor, echo=FALSE}
ggplot(data = weirdata)+
  geom_point(aes(x = DateTime, y = VT_Pressure_psia))+
  ylab("Daily avg. VT pressure (psi)")+
  theme_bw()+
  ggtitle("All VT sensor pressure (psi)") 


# Let's look at current surface pressure 
ggplot(data = weirdata, aes(x = DateTime, y = VT_Pressure_psia))+
  geom_point()+
  ylab("Daily avg. VT pressure (psi)")+
  theme_bw() +
  ggtitle("This year's VT sensor pressure (psi)") +
  xlim(c(ymd_hms(current_time_start),ymd_hms(current_time_end)))


ggplot(data = daily, aes(x = VT_Pressure_psia, group = Year, fill = Year))+
  geom_density(alpha=0.5)+
  xlab("Daily avg. VT pressure (psi)")+
  ggtitle("VT Sensor Pressure Density Plot")+
  theme_bw()


ggplot(data = daily, aes(x = Year, y = VT_Pressure_psia, group = Year, fill = Year))+
  geom_boxplot()+
  ylab("Daily avg. VT pressure (psi)")+
  ggtitle("VT Sensor Pressure Boxplot")+
  theme_bw()
```


##visualization of temp
```{r Temperature plots, echo=FALSE}

weirdata%>%
  ggplot(., aes(x=DateTime))+
  geom_scattermore(aes(y=WVWA_Temp_C, color="WVWA"), pointsize = 2)+
  geom_scattermore(aes(y=VT_Temp_C, color="VT"), pointsize = 2) +
  ggtitle("All Temperatures") +
    labs(y = "degrees C",
         color = "Legend") +
    scale_color_manual(values = colors)

# Just the current year

weirdata%>%
  filter(DateTime>=ymd_hms(current_time_start) & DateTime<ymd_hms(current_time_end))%>%
  ggplot(., aes(x=DateTime))+
  geom_point(aes(y=WVWA_Temp_C, color="WVWA"))+
  geom_point(aes(y=VT_Temp_C, color="VT")) +
  ggtitle("This year's temperatures") +
    labs(y = "degrees C",
         color = "Legend") +
    scale_color_manual(values = colors)


ggplot(data = daily, aes(x = WVWA_Temp_C, group = Year, fill = Year))+
  geom_density(alpha=0.5)+
  xlab("Daily avg. WVWA temp (C)")+
  ggtitle("WVWA Temperature Density Plot")+
  theme_bw()


ggplot(data = daily, aes(x = Year, y = WVWA_Temp_C, group = Year, fill = Year))+
  geom_boxplot()+
  #geom_jitter(alpha = 0.1)+
  ylab("Daily avg. WVWA temp (C)")+
  ggtitle("WVWA Temperature Boxplot")+
  theme_bw()


# VT Temp sensor check
ggplot(data = daily, aes(x = VT_Temp_C, group = Year, fill = Year))+
  geom_density(alpha=0.5)+
  xlab("Daily avg. VT temp (C)")+
  ggtitle("VT Temperature Density Plot")+
  theme_bw()


ggplot(data = daily, aes(x = Year, y = VT_Temp_C, group = Year, fill = Year))+
  geom_boxplot()+
  #geom_jitter(alpha = 0.1)+
  ylab("Daily avg. VT temp (C)")+
  ggtitle("VT Temperature Density Boxplot")+
  theme_bw()

```