---
title: "Time series plots"
author: "Abby Lewis"
date: "2022-09-08"
output: html_document
---

This file creates three summary time series plots that are in the main manuscript:
- Figure OXYGEN
- Figure BLOOM EFFECTS
- Figure PHYTOS

To do so, this file loads chemistry and fluora data from EDI, then loads saved values for metals, GHGs, thermocline depth, light attenuation, CTD data, and calculated fluora metrics, drawn from other scripts. 

TABLE OF CONTENTS:
Code chunk 1: Load packages, define drawdown dates
Code chunk 2: Load and format chemistry data
Code chunk 3: Load fluora data from EDI
Code chunk 4: Load other saved data for line plots
Code chunk 5: Make line plot of metals data, DO, and thermocline depth (Figure OXYGEN)
Code chunk 6: Make line plot of nutrients, phytos, DOC, and CO2 (Figure BLOOM EFFECTS)
Code chunk 7: Make line plot of turbidity, euphotic zone, peak width, and peak depth (Figure PHYTOS)


Code chunk 1: Load packages, define drawdown dates
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
library(akima)
library(colorRamps)

#Define drawdown lines
lines = data.frame(Dates = as.Date(c("2022-06-28", "2022-05-19","2022-05-28", "2022-07-01")), desc = c("closed","opened", "decreasing", "stable"), type = c("close","open","open","close"), status = c("init","init","final","final"), Year = 2022, year_class = "2022")
#Only plot pipe manipulations for now
lines = lines%>%
  filter(status == "init")
#Re-format for rectangle instead of discrete lines
lines_rect = lines%>%
  select(-type)%>%
  pivot_wider(names_from = desc, values_from = Dates)
```

Code chunk 2: Load and format chemistry data
```{r}
inUrl1  <- "https://pasta.lternet.edu/package/data/eml/edi/199/11/509f39850b6f95628d10889d66885b76" 
infile1 <- tempfile()
try(download.file(inUrl1,infile1,method="curl"))
if (is.na(file.size(infile1))) download.file(inUrl1,infile1,method="auto")

                   
 dt1 <-read.csv(infile1,header=F 
          ,skip=1
            ,sep=","  
        , col.names=c(
                    "Reservoir",     
                    "Site",     
                    "DateTime",     
                    "Depth_m",     
                    "Rep",     
                    "TN_ugL",     
                    "TP_ugL",     
                    "NH4_ugL",     
                    "NO3NO2_ugL",     
                    "SRP_ugL",     
                    "DOC_mgL",     
                    "DIC_mgL",     
                    "DC_mgL",     
                    "DN_mgL",     
                    "Flag_DateTime",     
                    "Flag_TN_ugL",     
                    "Flag_TP_ugL",     
                    "Flag_NH4_ugL",     
                    "Flag_NO3NO2_ugL",     
                    "Flag_SRP_ugL",     
                    "Flag_DOC_mgL",     
                    "Flag_DIC_mgL",     
                    "Flag_DC_mgL",     
                    "Flag_DN_mgL"    ), check.names=TRUE)
               
unlink(infile1)

#QAQC following conversation with CCC and HLW
dt1 = dt1%>%
  filter(hour(DateTime)>8,hour(DateTime)<17)%>%
  mutate(DateTime=as.Date(DateTime))%>%
  rename(PO4_ugL = SRP_ugL)%>%
  mutate(PO4_ugL = ifelse(PO4_ugL>TP_ugL,NA,PO4_ugL),
         TP_ugL = ifelse(Flag_TP_ugL%in%c(5,9)|TP_ugL>60,NA,TP_ugL),
         TN_ugL = ifelse(Flag_TN_ugL%in%c(5,9),NA,TN_ugL))

chem_full = dt1%>%
  filter(Reservoir=="BVR",
         Site==50)%>%
  filter(year(DateTime)%in%c(2021,2022))
#Add a "day of year" column with the year 2022 assigned
chem_full$Date_22<-chem_full$DateTime
chem_full$Year = year(chem_full$DateTime)
year(chem_full$Date_22)<-2022
```

Code chunk 3: Load fluora data from EDI
```{r}
#Load data
inUrl1  <- "https://pasta.lternet.edu/package/data/eml/edi/272/7/001cb516ad3e8cbabe1fdcf6826a0a45"
infile1 <- tempfile()
try(download.file(inUrl1,infile1,method="curl"))
if (is.na(file.size(infile1))) download.file(inUrl1,infile1,method="auto")

                   
 dt1 <-read.csv(infile1,header=F 
          ,skip=1
            ,sep=","  
        , col.names=c(
                    "Reservoir",     
                    "Site",     
                    "DateTime",     
                    "Depth_m",     
                    "GreenAlgae_ugL",     
                    "Bluegreens_ugL",     
                    "BrownAlgae_ugL",     
                    "MixedAlgae_ugL",     
                    "YellowSubstances_ugL",     
                    "TotalConc_ugL",     
                    "Transmission",     
                    "Temp_degC",     
                    "RFU_525nm",     
                    "RFU_570nm",     
                    "RFU_610nm",     
                    "RFU_370nm",     
                    "RFU_590nm",     
                    "RFU_470nm",     
                    "Flag_GreenAlgae",     
                    "Flag_BluegreenAlgae",     
                    "Flag_BrownAlgae",     
                    "Flag_MixedAlgae",     
                    "Flag_TotalConc",     
                    "Flag_Temp",     
                    "Flag_Transmission",     
                    "Flag_525nm",     
                    "Flag_570nm",     
                    "Flag_610nm",     
                    "Flag_370nm",     
                    "Flag_590nm",     
                    "Flag_470nm"    ), check.names=TRUE)
               
unlink(infile1)

#Extract surface data
fluora_surface=dt1%>%
  filter(Reservoir=="BVR",
         Site==50,
         Depth_m<1)%>%
  mutate(DateTime = as.Date(DateTime))%>%
  group_by(DateTime)%>%
  mutate(min_depth = min(Depth_m))%>%
  filter(Depth_m==min_depth)%>%
  filter(year(DateTime)%in%c(2021,2022))
```


Code chunk 4: Load other saved data for line plots
```{r}
thermo_depth = read.csv("./Data/thermocline_depth.csv")%>%
  filter(year(Date)%in%c(2022,2021))

light = read.csv("./Data/attenuation_calc.csv")%>%
  filter(year(Date)%in%c(2021,2022))

ctd = read.csv("./Data/CTD at 0.1m.csv")%>%
  filter(year(Date)%in%c(2021,2022))

ghg = read.csv("./Data/GHG at 0.1m.csv")%>%
  filter(year(DateTime)%in%c(2021,2022))

metals_raw = read.csv("./Data/Metals at 0.1m.csv")%>%
  filter(year(Date)%in%c(2021,2022))
#Additional QAQC needed (Days where soluble>total)
metals = metals_raw%>%
  mutate(TFe_mgL = ifelse(Date=="2022-05-09",metals_raw$SFe_mgL[metals_raw$Date=="2022-05-09"],TFe_mgL),
         TMn_mgL = ifelse(Date=="2022-05-09",metals_raw$SMn_mgL[metals_raw$Date=="2022-05-09"],TMn_mgL),
         SFe_mgL = ifelse(Date=="2022-05-09",metals_raw$TFe_mgL[metals_raw$Date=="2022-05-09"],SFe_mgL),
         SMn_mgL = ifelse(Date=="2022-05-09",metals_raw$TMn_mgL[metals_raw$Date=="2022-05-09"],SMn_mgL),
         TFe_mgL = ifelse(Date=="2022-06-07",NA,TFe_mgL),
         TMn_mgL = ifelse(Date=="2022-06-07",NA,TMn_mgL))

cmax_depth = read.csv("./Data/FP_CmaxDepth.csv")%>%
  filter(year(Date)%in%c(2021,2022))

peak_width = read.csv("./Data/FP_PeakWidth.csv")%>%
  filter(year(Date)%in%c(2021,2022))
```


Code chunk 5: Make line plot of metals data, DO, and thermocline depth (Figure OXYGEN)
```{r}
#combine relevant data
sum_plot3 = thermo_depth%>%
  mutate(DateTime = as.Date(Date))%>%
  select(-Date)%>%
  full_join(ctd%>%mutate(DateTime = as.Date(Date))%>%select(-Date,-Year,-Depth_m))%>%
  full_join(metals%>%mutate(DateTime = as.Date(Date))%>%select(-Date,-Date_22))%>%
  select(DateTime, TFe_mgL,TMn_mgL,SFe_mgL,SMn_mgL,DOsat_percent,thermo)%>%
  pivot_longer(cols = c(TFe_mgL,TMn_mgL,SFe_mgL,SMn_mgL,DOsat_percent,thermo))%>% #Pivot for facet wrap
  filter(!is.na(value),
         month(DateTime)>4,
         month(DateTime)<9)%>%
  mutate(Year = year(DateTime),
         color = name,
         name = ifelse(name%in%c("SFe_mgL","TFe_mgL"),"Fe_mgL",name),
         name = ifelse(name%in%c("SMn_mgL","TMn_mgL"),"Mn_mgL",name))%>% #Re-format to put solubles in the same plot as totals
  mutate(name = factor(name, levels=c("thermo","DOsat_percent","Fe_mgL","Mn_mgL")),
         color = factor(color, levels=c("thermo","DOsat_percent","TFe_mgL","TMn_mgL","SFe_mgL","SMn_mgL")),
         lty = ifelse(color %in%c("SFe_mgL","SMn_mgL"),"dashed","solid"))

#Calculate maximum values
maxes = sum_plot3%>%
  group_by(name, color,lty,Year)%>%
  summarize(max_date = DateTime[which.max(value)],
            min_date = DateTime[which.min(value)])%>%
  filter(Year=="2022")%>%
  mutate(max_date = ifelse(name %in% c("thermo","Zeu","DO_mgL","DOsat_percent"),min_date,max_date))

#Stats
sum_plot3%>%
  group_by(name, color,Year)%>%
  summarize(max_date = DateTime[which.max(value)],
            max = max(value),
            min_date = DateTime[which.min(value)],
            min = min(value))%>%
  mutate(max_date = ifelse(name %in% c("thermo","Zeu","DO_mgL","DOsat_percent"),min_date,max_date))

# New facet label names for sum_plot
fac.labs <- c("Surface DO\n(mgL)","Fe (mg/L)","Mn (mg/L)","Thermocline\ndepth (m)","Surface DO\n(% saturation)")
names(fac.labs) <- c("DO_mgL","Fe_mgL","Mn_mgL","thermo","DOsat_percent")
library(ggh4x)
scales <- list(
  scale_y_reverse(limits = c(NA,0)),
  scale_y_continuous(),
  scale_y_continuous(),
  scale_y_continuous()
)

#PLOT
sum_plot3%>%
  mutate(show_points = ifelse(name == "thermo","n","y"))%>%
  ggplot()+
  geom_rect(aes(xmin = opened,xmax = closed,ymin=-Inf,ymax=Inf),fill = "grey40", data = lines_rect, alpha = 0.2)+
  geom_point(aes(alpha = show_points, color = name,x = DateTime, y = value))+
  geom_line(aes(x = DateTime, y = value, lty = lty, color = name))+
  scale_alpha_manual(values = c(0,1))+
  geom_vline(aes(xintercept = max_date, color = name), data = maxes, lwd = 2, alpha = 0.5, show.legend = F)+
  #geom_vline(data=lines,aes(xintercept = Dates), show.legend = F)+
  scale_linetype_manual(values = c("solid","11"),
                        breaks = c("solid","dashed"),
                        labels = c("Total","Soluble"),)+
  scale_color_manual(values = c("darkblue","cyan4","lightsalmon","coral4"))+
  facet_grid(rows = vars(name), cols = vars(Year), scales = "free", switch = "y",
             labeller = labeller(name = fac.labs))+
  theme_bw()+
  theme(strip.placement = "outside", 
        strip.text.x = element_text(
        size = 12, face = "bold"
        ),
        axis.title.x = element_blank(),
        strip.background = element_blank(),
        legend.position = c(0.15,0.42),
        legend.title=element_blank(),
        legend.background = element_blank(),
        legend.key= element_blank(),
        legend.spacing.y = unit(0, 'cm'),
        legend.text=element_text(size=7)
        )+
  guides(lty = guide_legend(byrow = TRUE,keyheight = 0.75),
         color = "none",
         alpha = "none")+
  facetted_pos_scales(y = scales)+
  ylab("")+
  force_panelsizes(rows = unit(.75, "in"),
                   cols = unit(2.5, "in"))
ggsave("./Figs/Abby_money_plot_biogeo.jpeg", dpi = 300, width = 6.5, height = 4)
```

Code chunk 6: Make line plot of nutrients, phytos, DOC, and CO2 (Figure BLOOM EFFECTS)
```{r}
#Combine all data
sum_plot4 = chem_full%>%
  filter(Depth_m ==0.1)%>%
  select(DateTime, TP_ugL, TN_ugL,PO4_ugL,DOC_mgL,DIC_mgL,NO3NO2_ugL,NH4_ugL, NO3NO2_ugL)%>%
  full_join(fluora_surface%>%
              filter(year(DateTime)%in% c(2021,2022)))%>%
  full_join(ghg%>%mutate(DateTime = as.Date(DateTime)))%>%
  mutate(TNTP = TN_ugL/TP_ugL)%>%
  select(DateTime, TP_ugL, TN_ugL,PO4_ugL,DOC_mgL,TotalConc_ugL,NH4_ugL,co2_umolL,Bluegreens_ugL,TNTP)%>%
  pivot_longer(cols = c(TP_ugL, TN_ugL,PO4_ugL,DOC_mgL,TotalConc_ugL,co2_umolL,NH4_ugL,Bluegreens_ugL,TNTP))%>% #pivot for facet wrap
  filter(!is.na(value),
         month(DateTime)>4,
         month(DateTime)<9)%>%
  mutate(Year = year(DateTime),
         color = name,
         name = ifelse(name%in%c("TotalConc_ugL","Bluegreens_ugL"),"Phyto",name), #Re-format to get cyanos on the same plot as totals
         name = ifelse(name%in%c("TP_ugL","PO4_ugL"),"Phosphorus",name), #Re-format to get solubles on the same plot as totals
         name = ifelse(name%in%c("TN_ugL","NO3NO2_ugL","NH4_ugL"),"Nitrogen",name),
         lty = ifelse(color%in%c("NO3NO2_ugL","NH4_ugL","PO4_ugL","Bluegreens_ugL"),"dashed","solid"))%>%
  mutate(name = factor(name, levels=c("Phosphorus","Nitrogen","TNTP","Phyto","DOC_mgL","co2_umolL")),
         color = factor(color, levels=c("TP_ugL","PO4_ugL","TN_ugL","NH4_ugL","TotalConc_ugL","Bluegreens_ugL","DOC_mgL","co2_umolL","TNTP"),
                        labels=c("TP","PO4","TN","NH4","Total phytoplankton", "Cyanobacteria", "DOC", "CO2", "TN:TP"))) #Re-label colors

#Calculate maxes
maxes = sum_plot4%>%
  group_by(name,color, Year)%>%
  summarize(max_date = DateTime[which.max(value)],
            min_date = DateTime[which.min(value)])%>%
  filter(Year=="2022")%>%
  mutate(max_date = ifelse(name %in% c("thermo","Zeu","DO_mgL"),min_date,max_date))

#Stats
maxes%>%
  mutate(max_date=as.Date(max_date, origin="1970-01-01"))
as.Date("2022-07-05")-as.Date("2022-06-27")
as.Date("2022-07-18")-as.Date("2022-06-27")

# New facet label names for sum_plot
fac.labs <- c("Phosphorus\n(µg/L)", "Nitrogen\n(µg/L)","TN:TP ratio","Phytoplankton\n(µg/L)", "DOC\n(mg/L)", "CO2\n(µmol/L)", "NH4 (µg/L)")
names(fac.labs) <- c("Phosphorus", "Nitrogen","TNTP","Phyto", "DOC_mgL", "co2_umolL", "NH4_ugL")
#Specify colors
my_colors = c("black","black","darkgreen","darkgreen","#8E4412","blue","skyblue","skyblue","pink","orange")
names(my_colors)=c("TP","PO4","Total phytoplankton","Cyanobacteria","DOC","CO2","NH4","TN","NO3NO2_ugL","TN:TP")

#PLOT
sum_plot4%>%
  ggplot()+
  geom_rect(aes(xmin = opened,xmax = closed,ymin=-Inf,ymax=Inf),fill = "grey40", data = lines_rect, alpha = 0.2)+
  geom_point(aes(y = value, x = DateTime,color = color))+
  geom_line(aes(y = value, lty=color,x = DateTime,color = color))+
  geom_vline(aes(xintercept = max_date, color = color), data = maxes, lwd = 2, alpha = 0.5, show.legend = F)+
  scale_linetype_manual(values = c("solid","11","solid","11","solid","11","solid","solid","solid"),
                        )+
  scale_color_manual(values = my_colors, 
                     )+
  facet_grid(rows = vars(name), cols = vars(Year), scales = "free", switch = "y",
             labeller = labeller(name = fac.labs))+
  theme_bw()+
  theme(strip.placement = "outside", 
        strip.text.x = element_text(
        size = 12, face = "bold"
        ),
        axis.title.x = element_blank(),
        strip.background = element_blank(),
        legend.position = "bottom",
        legend.title = element_blank())+
  guides(color = guide_legend(byrow = TRUE,keyheight = 0.75))+
  ylab("")+
  force_panelsizes(rows = unit(.75, "in"),
                   cols = unit(2.5, "in"))
ggsave("./Figs/Abby_money_plot_doc_short.jpeg", dpi = 300, width = 6.5, height = 6.5)
```

Code chunk 7: Make line plot of turbidity, euphotic zone, peak width, and peak depth (Figure PHYTOS)
```{r}
#Format data
sum_plot5 = fluora_surface%>%
  full_join(light%>%mutate(DateTime = as.Date(Date))%>%select(-Date))%>%
  full_join(ctd%>%mutate(DateTime = as.Date(Date))%>%select(-Date,-Year,-Depth_m))%>%
  full_join(cmax_depth%>%mutate(DateTime = as.Date(Date))%>%select(-Date))%>%
  full_join(peak_width%>%mutate(DateTime = as.Date(Date))%>%select(-Date))%>%
  select(DateTime, Turbidity_NTU, Zeu, CmaxDepth_TotalConc_ugL, CmaxDepth_Bluegreens_ugL, PeakWidth_TotalConc_m, PeakWidth_Bluegreens_m)%>%
  pivot_longer(cols = c(Turbidity_NTU, Zeu, CmaxDepth_TotalConc_ugL, CmaxDepth_Bluegreens_ugL, PeakWidth_TotalConc_m, PeakWidth_Bluegreens_m))%>%
  filter(!is.na(value),
         month(DateTime)>4,
         month(DateTime)<9)%>%
  mutate(Year = year(DateTime),
         color = ifelse(name%in%c("CmaxDepth_TotalConc_ugL", "PeakWidth_TotalConc_m"),"TotalConc_ugL",
                        ifelse(name%in%c("PeakWidth_Bluegreens_m", "CmaxDepth_Bluegreens_ugL"),"Bluegreens_ugL",name)),
         name = ifelse(name%in%c("CmaxDepth_TotalConc_ugL", "CmaxDepth_Bluegreens_ugL"),"Cmax_depth",name),
         name = ifelse(name%in%c("PeakWidth_TotalConc_m", "PeakWidth_Bluegreens_m"),"PeakWidth",name),
         lty = ifelse(color == "Bluegreens_ugL","dashed","solid"))%>%
  mutate(name = factor(name, levels=c("Turbidity_NTU", "Zeu", "Cmax_depth", "PeakWidth")),
         color = factor(color, levels=c("Turbidity_NTU", "Zeu","TotalConc_ugL", "Bluegreens_ugL")))

#Calculate maxes
maxes = sum_plot5%>%
  group_by(name,color, Year)%>%
  summarize(max_date = DateTime[which.max(value)],
            min_date = DateTime[which.min(value)])%>%
  filter(Year=="2022")%>%
  mutate(max_date = ifelse(name %in% c("thermo","Zeu","DO_mgL","Cmax_depth", "PeakWidth"),min_date,max_date))

#Stats
sum_plot5%>%
  group_by(name,color, Year)%>%
  summarize(max_date = DateTime[which.max(value)],
            max = max(value),
            min_date = DateTime[which.min(value)],
            min = min(value))%>%
  mutate(max_date = ifelse(name %in% c("thermo","Zeu","DO_mgL","Cmax_depth", "PeakWidth"),min_date,max_date),
         max = ifelse(name %in% c("thermo","Zeu","DO_mgL","Cmax_depth", "PeakWidth"),min,max))%>%
  group_by(name,color)%>%
  mutate(pct = (max[Year==2022]-max[Year==2021])/max[Year==2021]*100)

# New facet label names for sum_plot
fac.labs <- c("Turbidity\n(NTU)", "Euphotic zone\ndepth (m)", "C[max]\ndepth(m)", "Peak width\n(m)")
names(fac.labs) <- c("Turbidity_NTU", "Zeu", "Cmax_depth", "PeakWidth")
my_colors = c("grey20","goldenrod","darkgreen","turquoise")
names(my_colors)=c("Turbidity_NTU", "Zeu","TotalConc_ugL", "Bluegreens_ugL")
scales <- list(
  scale_y_continuous(),
  scale_y_reverse(limits = c(NA,0)),
  scale_y_reverse(limits = c(NA,0)),
  scale_y_continuous()
)

#PLOT
sum_plot5%>%
  ggplot()+
  geom_rect(aes(xmin = opened,xmax = closed,ymin=-Inf,ymax=Inf),fill = "grey40", data = lines_rect, alpha = 0.2)+
  geom_point(aes(x = DateTime, y = value, color = color))+
  geom_line(aes(x = DateTime, y = value, color = color,lty=lty))+
  geom_vline(aes(xintercept = max_date, color = color), data = maxes, lwd = 2, alpha = 0.5, show.legend = F)+
  #geom_vline(data=lines,aes(xintercept = Dates, lty = status), show.legend = F)+
  scale_color_manual(breaks = c("TotalConc_ugL","Bluegreens_ugL"),
                     labels = c("Total (µg/L)","Cyanobacteria (µg/L)"),
                     values = my_colors
                     )+
  scale_linetype_manual(values = c("11","solid"))+
  facet_grid(rows = vars(name), cols = vars(Year), scales = "free", switch = "y",
             labeller = labeller(.rows = fac.labs))+
  theme_bw()+
  theme(strip.placement = "outside", 
        legend.position = c(.2,.42),
        legend.title=element_blank(),
        legend.background = element_blank(),
        legend.key= element_blank(),
        legend.spacing.y = unit(0, 'cm'),
        legend.text=element_text(size=7),
        strip.text.x = element_text(
          size = 12, face = "bold"
        ),
        axis.title.x = element_blank(),
        strip.background = element_blank(
     ))+
  ylab("")+
  guides(color = guide_legend(byrow = TRUE,keyheight = 0.75),
         lty = "none")+
  facetted_pos_scales(y = scales)+
  force_panelsizes(rows = unit(.75, "in"),
                   cols = unit(2.5, "in"))

ggsave("./Figs/Abby_money_plot_phytos.jpeg", dpi = 300, width = 6.5, height = 4)
```