---
title: "Chemistry_inspection_2013_2024"
format: html
---

Script to inspect QAQCd 2025 chemistry data and combine with previous EDI publication. 

Script developed by HLW in 2023, edited by DWH in 2024-2025, edited by KKH in 2026.

NOTE! This script does not knit because it incorporates many steps of QAQC that will be moved in subsequent years to the maintenance log/Level 1 generation script. 
Note from KKH in 2026 - we should be able to get this to knit, but not there yet!

NOTE TO REVIEWERS!!! After loading packages on lines 16-19 go to line 145 to begin data review


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Add the names of the packages 
pacman::p_load(tidyverse, lubridate, scales, viridis, plotly, gsheet, here)

```


```{r read in current + historic combined file}

new_chem <- read_csv(paste0(here(), "/Data/DataAlreadyUploadedToEDI/EDIProductionFiles/MakeEMLChemistry/2025/chemistry_2025_woISCO.csv")) 

new_chem <- new_chem |> select(c(Reservoir, Site, DateTime, Depth_m, Rep, TN_ugL, TP_ugL, NH4_ugL, NO3NO2_ugL, SRP_ugL, DOC_mgL, DIC_mgL, DC_mgL, DN_mgL, Flag_DateTime, Flag_TP_ugL, Flag_TN_ugL, Flag_NH4_ugL, Flag_NO3NO2_ugL, Flag_SRP_ugL, Flag_DOC_mgL, Flag_DIC_mgL, Flag_DC_mgL, Flag_DN_mgL))

myEDIAccessKey <- "UsVwoHpF431obnILyyNrNVt-Sdk"

chem_data  <- paste0("https://pasta.lternet.edu/package/data/eml/edi/199/13/3f09a3d23b7b5dd32ed7d28e9bc1b081","?key=",myEDIAccessKey)

old_chem <- read_csv(chem_data , col_types = cols())

##remove reruns from new file 
# DWH manually entered reruns. We need a better way to handle this. 
# new_chem <- new_chem |> 
#   mutate(Year = year(DateTime)) |> 
#   #filter(Year != 2023) |> 
#   select(-Year)

##bind all chem together
allchem <- rbind(old_chem, new_chem) |> 
  mutate(Flag_DIC_mgL = as.numeric(Flag_DIC_mgL),
         Flag_DC_mgL = as.numeric(Flag_DC_mgL))

#check no NAs in flags
summary(allchem)

```

```{r write csv for EDI}

allchem <- allchem |> 
  arrange(Reservoir, DateTime, Site, Depth_m, Rep) |> 
  mutate(DN_mgL = round(DN_mgL, 2)) #fix DN rounding for all years, can cut this next year as now in qaqc

write.csv(allchem, "Chemistry_2013_2025.csv", row.names = FALSE)
```

REVIEWERS START HERE!!!!!!

```{r}
######## UPDATE LINK ###############
#read in the most recent version on EDI staging to work with this version to check on data
allchem <- read_csv( "https://pasta-s.lternet.edu/package/data/eml/edi/1025/17/3f09a3d23b7b5dd32ed7d28e9bc1b081"   , col_types = cols())


```


```{r 2024 diagnostic plots - all sites}


new_chem <- allchem |> 
  filter(year(DateTime) >= 2025 )

#select columns for plotting
new_chem <- new_chem [,(names(new_chem) %in% c("Reservoir","Site","DateTime",
  "Depth_m","Rep","TP_ugL","TN_ugL","NH4_ugL","SRP_ugL","NO3NO2_ugL","DOC_mgL", "DIC_mgL"))]

  #### Chemistry diagnostic plots ####
chemistry_long <- new_chem %>% 
  gather(metric, value, TN_ugL:DIC_mgL) %>% 
  mutate(month = strftime(DateTime, "%b"))

chemistry_long$value <- as.numeric(chemistry_long$value)


# Plot range of values per constituent for each reservoir; 
#mean value per sampling day indicated with large black dot
chemistry_long |> 
  filter(Site == 50, 
         DateTime > ymd("2024-01-01")) |> 
ggplot(aes(x = as.Date(DateTime), y = value, col=Reservoir)) +
  geom_point(size=1) +
  stat_summary(fun.y="mean", geom="point",pch=21,  size=3, fill='black') +
  facet_grid(metric ~ Reservoir, scales= 'free_y') +
  scale_x_date(labels = date_format("%d %b")) +
  scale_y_continuous("Concentration at site 50") +
  theme(axis.text.x = element_text(angle = 45, hjust=1), legend.position='none')

#ggsave("./Figures/FCR_BVR_CCR_all_nutrients_summer2023.jpg", width=4, height=4)

```

```{r Function to make plots}

# Make individual plots of each variable with depth as color

# make a function

#Function to plot all data for a given year as a heatmap
plot_var <- function(var_name, 
                     year, 
                     reservoirs = c("FCR", "BVR", "CCR"),
                     data = qaqc,
                     site = c(10,20,30,40,50,88,90)){
  
  var <- sym(var_name)
  flag <- sym(paste0("Flag_", var_name))
  qaqc_plotly <- data %>%
    filter(Reservoir %in% reservoirs, Site %in% site, year(DateTime) %in% year) %>%
    ggplot(aes(x = DateTime, y = !!var, color = as.factor(Depth_m), shape = as.factor(!!flag))) +
    geom_point() +
    #ggtitle(year)+
    facet_grid(cols = vars(Reservoir),rows = vars(Site), scales = "free_y")+         
    theme_bw()
    #facet_grid(cols = vars(Reservoir))
  ggplotly(qaqc_plotly)
  #print(qaqc_plotly)
}

# list of variables
vars_to_plot <- c("TN_ugL", "TP_ugL", "NH4_ugL", "NO3NO2_ugL", "SRP_ugL", "DOC_mgL", "DIC_mgL", "DC_mgL", "DN_mgL")

```


```{r FCR plots current year}

fcr2024 <-vars_to_plot %>%
  map(plot_var, year = c(2024, 2025), reservoirs = "FCR", data = allchem, site = c(20,50,100,200))

fcr2024

```

```{r BVR plots current year}
bvr2024 <-vars_to_plot %>%
  map(plot_var, year = c(2024,2025),reservoirs = "BVR", data = allchem, site = c(20,50,100,200))

bvr2024
```

```{r CCR plots current year}

y2024 <-vars_to_plot %>%
  map(plot_var, year = c(2024,2025), reservoirs = "CCR", data = allchem, site = c(50,51,88,90, 92,96,98,100,101,301))

y2024

```


```{r Diagnostic plots - FCR 50}

# FCR deep hole data time series
ggplot(subset(chemistry_long, Reservoir=='FCR' & Site=="50"), aes(x = as.Date(DateTime), y = value, col=as.factor(Depth_m))) +
  geom_point(cex=2) + theme_bw()+
  facet_grid(metric ~ ., scales='free') +
  scale_x_date("Date", date_breaks="1 month", date_labels = "%d %b") +
  scale_y_continuous("Concentration at site 50") +
  theme(axis.text.x = element_text(angle = 45, hjust=1, size=6),
        axis.text.y = element_text(size=6),
        legend.key.size = unit(0.5, 'lines'),
        legend.text = element_text(size=5),
        legend.title = element_text(size=6)) +
  scale_color_manual("FCR_Depth (m)", values = viridis(10))
  #geom_vline(xintercept=as.numeric(as.Date(c("2021-06-11", "2021-07-12", "2021-07-26", "2022-03-22")))) +
  #geom_vline(xintercept=as.numeric(as.Date(c("2021-06-26", "2021-07-14","2021-12-06", "2022-03-24"))), linetype="dotted")

#ggsave("./Figures/FCR_all_nutrients_summer2023.jpg", width=4, height=4)

```

```{r 2023 diagnostic plots FCR 100 and 200}

# FCR other sites nutrient data time series
ggplot(subset(chemistry_long, Reservoir=='FCR' & Site!="50"), aes(x = as.Date(DateTime), y = value, col=as.factor(Site))) +
  geom_point(cex=2) + theme_bw() +
  facet_grid(metric ~ ., scales='free') +
  scale_x_date("Date", date_breaks="1 month", date_labels = "%d %b") +
  scale_y_continuous("Concentration") +
  theme(axis.text.x = element_text(angle = 45, hjust=1, size=6),
        axis.text.y = element_text(size=6),
        legend.key.size = unit(0.5, 'lines'),
        legend.text = element_text(size=5),
        legend.title = element_text(size=6)) + 
  scale_color_manual("FCR_Site", values = rainbow(10)) 

#ggsave("./Figures/FCR_sites_all_nutrients_summer2023.jpg", width=4, height=4)

```

```{r 2023 diagnostic plots - BVR 50}

# BVR deep hole data time series
ggplot(subset(chemistry_long, Reservoir=='BVR' & Site=="50"), aes(x = as.Date(DateTime), y = value, col=as.factor(Depth_m))) +
  geom_point(cex=2) + theme_bw() +
  facet_grid(metric ~ ., scales='free') +
  scale_x_date("Date", date_breaks="1 month", date_labels = "%d %b") +
  scale_y_continuous("Concentration at site 50") +
  theme(axis.text.x = element_text(angle = 45, hjust=1, size=6),
        axis.text.y = element_text(size=6),
        legend.key.size = unit(0.5, 'lines'),
        legend.text = element_text(size=5),
        legend.title = element_text(size=6)) + 
  scale_color_manual("BVR_Depth (m)", values = plasma(10)) 

# ggsave("./Figures/BVR_all_nutrients_summer2023.jpg", width=4, height=4ggsave("./Figures/BVR_all_nutrients_summer2023.jpg", width=4, height=4ggsave("./Figures/BVR_all_nutrients_summer2023.jpg", width=4, height=4)

```

```{r 2023 diagnostic plots BVR inflows}

 #BVR other sites nutrient time series #no 2024 inflow samples so no figure :)
ggplot(subset(chemistry_long, Reservoir=='BVR' & Site!="50"), aes(x = as.Date(DateTime), y = value, col=as.factor(Site))) +
  geom_point(cex=2) + theme_bw() +
  facet_grid(metric ~ ., scales='free') +
  scale_x_date("Date", date_labels = "%d %b") +
  scale_y_continuous("Concentration") +
  theme(axis.text.x = element_text(angle = 0, hjust=0.5)) + 
  scale_color_manual("BVR_Site", values = plasma(8)) 
#ggsave("./Figures/BVR_sites_all_nutrients_summer2023.jpg", width=4, height=4)

```

```{r 2023 diagnostic plots - CCR 50}

# CCR site 50 nutrient time series
ggplot(subset(chemistry_long, Reservoir=='CCR' & Site=="50"), aes(x = as.Date(DateTime), y = value, col=as.factor(Depth_m))) +
  geom_point(cex=2) + theme_bw() +
  facet_grid(metric ~ ., scales='free') +
  scale_x_date("Date", date_breaks="1 month", date_labels = "%d %b") +
  scale_y_continuous("Concentration") +
  theme(axis.text.x = element_text(angle = 45, hjust=1, size=6),
        axis.text.y = element_text(size=6),
        legend.key.size = unit(0.5, 'lines'),
        legend.text = element_text(size=5),
        legend.title = element_text(size=6)) + 
  scale_color_manual("CCR_Depth (m)", values = plasma(7)) 

#ggsave("./Figures/CCR_50_all_nutrients_summer2023.jpg", width=4, heighggsave("./Figures/CCR_50_all_nutrients_summer2023.jpg", width=4, heighggsave("./Figures/CCR_50_all_nutrients_summer2023.jpg", width=4, height=4)

```

```{r 2023 diagnostic plots- CCR inflows}

# CCR other sites nutrient time series
ggplot(subset(chemistry_long, Reservoir=='CCR' & Site!="50"), aes(x = as.Date(DateTime), y = value, col=as.factor(Site))) +
  geom_point(cex=2) + theme_bw() +
  facet_grid(metric ~ ., scales='free') +
  scale_x_date("Date", date_breaks="1 month", date_labels = "%d %b") +
  scale_y_continuous("Concentration") +
  theme(axis.text.x = element_text(angle = 45, hjust=1, size=6),
        axis.text.y = element_text(size=6),
        legend.key.size = unit(0.5, 'lines'),
        legend.text = element_text(size=5),
        legend.title = element_text(size=6)) + 
  scale_color_manual("CCR_Site", values = plasma(7)) 

#ggsave("./Figures/CCR_sites_all_nutrients_summer2023.jpg", width=4, heggsave("./Figures/CCR_sites_all_nutrients_summer2023.jpg", width=4, heggsave("./Figures/CCR_sites_all_nutrients_summer2023.jpg", width=4, height=4)

```

```{r add additional columns to all chem df}
#add column for year
allchem$year <- year(allchem$DateTime)

#### chem diagnostic plots #### 
all_chem_long <- allchem %>%
  gather(metric, value, TN_ugL:DIC_mgL) %>% 
  mutate(month = strftime(DateTime, "%b"))

#value as numeric
all_chem_long$value<- as.numeric(all_chem_long$value)
all_chem_long$Depth_m<- as.numeric(all_chem_long$Depth_m)

```

```{r all data plots}

# Plot all values
ggplot(all_chem_long, aes(x = as.Date(DateTime), y = value, col=Reservoir)) +
  geom_point(size=1) +
  stat_summary(fun.y="mean", geom="point",pch=21,  size=3, fill='black') +
  facet_grid(metric ~ Reservoir, scales= 'free_y') +
  scale_x_date("Date", date_breaks="6 months", date_labels = "%b %Y") +
  scale_y_continuous("") +
  theme(axis.text.x = element_text(angle = 45, hjust=1), legend.position='none')

#ggsave("./Figures/All_reservoirs_2013_2023.jpg", width=4, height=4)

```

```{r}

plot_chem_vars <- function(
    data,
    reservoir, 
    site){
ggplot(subset(data, Reservoir %in% reservoir & Site %in% site), aes(x = as.Date(DateTime), y = value, col=as.factor(Depth_m))) +
  geom_point(cex=2) +
  facet_grid(metric ~ Site, scales='free') +
  scale_x_date("Date", date_breaks = "6 months" ,date_labels = "%b %y") +
  scale_y_continuous("Concentration") +
  theme(axis.text.x = element_text(angle = 45, hjust=1)) 
  #scale_color_gradient("Depth (m)", high = "black", low = "deepskyblue")
}
```


```{r all data plots BVR}

plot_chem_vars(data = all_chem_long, reservoir = "BVR", site = 50)

```

```{r all data plots FCR}

# FCR only; all sampling sites 
plot_chem_vars(data = all_chem_long, reservoir = "FCR", site = 50)

#ggsave("./Figures/FCR_ChembySite_2013_2023.jpg",width=3.5, height=4)

```

```{r all data plots}

# CCR only; site 50
plot_chem_vars(data = all_chem_long, reservoir = "CCR", site = 50)

#ggsave("./Figures/CCR_Site50_2013_2023.jpg",width=3.5, height=4)

```


```{r Make site description file}
 # These lines of code make the csv of the site descriptions with lat and long

  # Use Gsheet because you don't need to authenticate it. 
sites <- gsheet::gsheet2tbl("https://docs.google.com/spreadsheets/d/1TlQRdjmi_lzwFfQ6Ovv1CAozmCEkHumDmbg_L4A2e-8/edit#gid=1244423834")

  data <- allchem #This is the line you need to modify!
  
  trim_sites = function(data,sites){
    data_res_site = data %>% #Create a Reservoir/Site combo column
      mutate(res_site = trimws(paste0(Reservoir,Site)))
    sites_merged = sites%>% #Filter to Sites that are in the dataframe
      mutate(res_site = trimws(paste0(Reservoir,Site)))%>%
      filter(res_site%in%data_res_site$res_site)%>%
      select(-res_site)
  }
  
sites_trimmed = trim_sites(data,sites) 
  
write.csv(sites_trimmed, "reservoir_site_descriptions.csv", row.names=F)# Write to file

```

