---
title: "TICTOC"
format: html
---
TICTOC script needs: 
Step toward the beginning to flag bad things from the rack map

getting formulas to the correct rows
any injection we know is bad
any standard we want to exclude

Notes section for notes about the entire run
would ideally have a place fo rthe full run notes
for any high DIC C samples, DOC will be less accurate

What are TICTOC flags? 
- maintenance log - a .csv - needs to be flexible
- digitized rack map

- date run
- hole pos
- sample #
- No. - line #
- and analyte
- and notes col. 

csv pull date based on 1st line. 

May need to be able to set up or id segmented regression (single breakpoint)
- needs would go in the maintenance log. 

Ideally this would all be able to be run as an html
Set anything bad to NA using the maintenance log


```{r settings}
# Set to TRUE to add entries to the maintenance log interactively
# Set to FALSE when knitting
run_interactive <- TRUE
```

```{r libraries}
library(pacman)

pacman::p_load(here, tidyverse, ggplot2, dplyr, janitor, ggpmisc, segmented, kableExtra, knitr)

```

Bring in the data! This requires the data to be in the folder and should allow running all of the files at once
```{r read data}

file <- paste0(here(), "/Raw/TICTOC/20260327_KKH_LTREB7_5.csv")
file #something is not right with this
tictoc <- read.csv(file, skip = 1) |> clean_names()

```

Real #1. Apply maintenance log
Takes the data and the maintenance log, matches by no, hole pos. and date run. 
```{r maint log application}

maintenancelog <- paste0(here(),"/maintenance_logs/TICTOC_maintlog.csv")
maintenancelog
maintenancelog <- read.csv(maintenancelog)

source(paste0(here(), "/functions/TICTOC functions/TICTOC_applymaintlog.R"))

TICTOC_applymaintlog(maintenancefile = maintenancelog, tictoc)

TICTOC_applymaintlog(maintenance_file = maintenancelog,  
                                 directory = paste0(here(), "/Raw/TICTOC"), #this is the folder where all of the TICTOC runs are stored
                                 outfile = "Results/TICTOC/TICTOC_postmaintlog.csv",
                                 start_date = NULL,
                                 end_date = NULL, 
                                 outputcheck_folder = paste0(here()))

```

1. plot standards and water blanks using the area from each injection. Prioritize the last 2 injections from each sample. 
```{r get concentrations}
tictoc <- read.csv(paste0(here(), "/Results/TICTOC/TICTOC_postmaintlog.csv"))


standards_all <- tictoc |> filter(grepl(pattern = "Mixed Check", x = name))


get_last_injections <- function(df, n = 2) {
  df |>
    arrange(hole_pos, no) |>
    group_by(hole_pos) |>
    slice_tail(n = n) |>
    ungroup()
}

standards_avg <- standards_all |> 
  get_last_injections() |> 
  group_by(Date_processed) |> 
  group_by(hole_pos) |> 
  mutate(avg_tic = mean(tic_area), 
         avg_tc = mean(tc_area), 
         avg_tnb = mean(t_nb_area)) |> 
  mutate(conc_tic = ifelse(grepl("3/6/0.3", x = name), 3, 
                           ifelse(grepl("9/18/0.9", x = name), 9, NA)), 
         conc_tc = ifelse(grepl("3/6/0.3", x = name), 6, 
                           ifelse(grepl("9/18/0.9", x = name), 18, NA)),
         conc_tnb = ifelse(grepl("3/6/0.3", x = name), 0.3, 
                           ifelse(grepl("9/18/0.9", x = name), 0.9, NA))) |> 
  mutate(stconc_tic = (tic_vol_ml * conc_tic), 
         stconc_tc = (tc_vol_ml * conc_tc), 
         stconc_tnb = (tc_vol_ml * conc_tnb))
```

```{r plot standards}

pivot_analytes <- function(df) {
  df |>
    rename(area_tnb = t_nb_area, 
           area_tc = tc_area, 
           area_tic = tic_area) |>
    pivot_longer(
      cols = c(stconc_tc, stconc_tic, stconc_tnb,
               avg_tc, avg_tic, avg_tnb,
               area_tc, area_tic, area_tnb, Date_processed),
      names_to = c(".value", "analyte"),
      names_pattern = "^(.+)_(tc|tic|tnb)$"
    )
}

dates <- unique(standards_avg$Date_processed)

for(d in dates){
  
  d <- as.Date(d, origin = "1970-01-01")
  
  p <- standards_avg |>
    filter(Date_processed == d) |>
    dplyr::select(no, hole_pos, stconc_tc, stconc_tic, stconc_tnb, 
                  avg_tic, avg_tc, avg_tnb, 
                  tic_area, tc_area, t_nb_area, Date_processed) |>
    pivot_analytes() |>
    ggplot(aes(x = stconc, y = avg)) +
    geom_point() +
    geom_point(aes(x = stconc, y = area), colour = "red") +
    geom_smooth(method = "lm", se = FALSE) +
    stat_poly_eq(
      aes(label = after_stat(eq.label)),
      formula = y ~ x,
      parse = TRUE,
      label.y = 0.95
    ) +
    stat_poly_eq(
      aes(label = after_stat(rr.label)),
      formula = y ~ x,
      parse = TRUE,
      rr.digits = 5,
      label.y = 0.85
    ) +
    facet_wrap(~analyte, scales = "free") +
    labs(title = paste("Date processed:", d))
  
  print(p)
}

# test <- standards_avg |> 
#   dplyr::select(no, hole_pos, stconc_tc, stconc_tic, stconc_tnb, avg_tic, avg_tc, avg_tnb, tic_area, tc_area, t_nb_area, Date_processed) |> 
# pivot_analytes() |> 
#   ggplot(aes(x = stconc, y = avg)) +
#   geom_point() +
#   geom_point(aes(x = stconc, y = area), colour = "red")+
#   geom_smooth(method = "lm", se = FALSE) +
# stat_poly_eq(
#     aes(label = after_stat(eq.label)),
#     formula = y ~ x,
#     parse = TRUE,
#     label.y = 0.95
#   ) +
#   stat_poly_eq(
#     aes(label = after_stat(rr.label)),
#     formula = y ~ x,
#     parse = TRUE,
#     rr.digits = 5,
#     label.y = 0.85
#   ) +
#   facet_wrap(~analyte, scales = "free")
# test
```

```{r}
#with 120% error? 

pivot_analytes <- function(df) {
  df |>
    rename(area_tnb = t_nb_area, 
           area_tc = tc_area, 
           area_tic = tic_area) |>
    pivot_longer(
      cols = c(stconc_tc, stconc_tic, stconc_tnb,
               avg_tc, avg_tic, avg_tnb,
               area_tc, area_tic, area_tnb, Date_processed),
      names_to = c(".value", "analyte"),
      names_pattern = "^(.+)_(tc|tic|tnb)$"
    )
}

dates <- unique(standards_avg$Date_processed)

for(d in dates){
  
  d <- as.Date(d, origin = "1970-01-01")
  
  plot_data <- standards_avg |>
    filter(Date_processed == d) |>
    dplyr::select(no, hole_pos, stconc_tc, stconc_tic, stconc_tnb, 
                  avg_tic, avg_tc, avg_tnb, 
                  tic_area, tc_area, t_nb_area, Date_processed) |>
    pivot_analytes() |>
    mutate(
      pct_error = ((avg - stconc) / stconc) * 100,
      out_of_range = abs(pct_error) > 15
    )
  
  # Standard curve plot
  p <- plot_data |>
    ggplot(aes(x = stconc, y = avg)) +
    geom_point(aes(color = out_of_range)) +
    scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red"),
                       name = ">15% error") +
    geom_point(aes(x = stconc, y = area), colour = "red", shape = 17) +
    geom_smooth(method = "lm", se = FALSE) +
    geom_abline(aes(slope = 1.2, intercept = 0),
                linetype = "dashed", colour = "darkred") +
    stat_poly_eq(
      aes(label = after_stat(eq.label)),
      formula = y ~ x,
      parse = TRUE,
      label.y = 0.95
    ) +
    stat_poly_eq(
      aes(label = after_stat(rr.label)),
      formula = y ~ x,
      parse = TRUE,
      rr.digits = 5,
      label.y = 0.85
    ) +
    facet_wrap(~analyte, scales = "free") +
    labs(title = paste("Standard curve - Date processed:", d))
  
  print(p)
  
  # % error table
  error_table <- plot_data |>
    dplyr::select(no, hole_pos, analyte, stconc, avg, pct_error, out_of_range) |>
    arrange(analyte, stconc) |>
    mutate(pct_error = round(pct_error, 2)) |>
    knitr::kable(
      caption = paste("% Error by standard - Date processed:", d),
      col.names = c("No", "Hole Pos", "Analyte", "Known Std", 
                    "Measured Avg", "% Error", ">15% Error")
    ) |>
    kableExtra::kable_styling(bootstrap_options = c("striped", "hover")) |>
    kableExtra::row_spec(which(plot_data$out_of_range), background = "#ffcccc")
  
  print(error_table)
}
```


This section plots a segmented regression. This is NOT what will be used in most cases. 

```{r segmented regression if necessary}
dates <- unique(standards_avg$Date_processed)

for(d in dates){
  
  d <- as.Date(d, origin = "1970-01-01")
  
  p <- standards_avg |>
    filter(Date_processed == d) |>
    dplyr::select(no, hole_pos, stconc_tc, stconc_tic, stconc_tnb, 
                  avg_tic, avg_tc, avg_tnb, 
                  tic_area, tc_area, t_nb_area, Date_processed) |>
    pivot_analytes() |>
    dplyr::filter(!is.na(analyte), !is.na(avg), !is.na(stconc)) |>
    dplyr::group_by(analyte) |>
    dplyr::mutate(
      seg_fitted = {
        fit_lm <- lm(avg ~ stconc)
        fit_seg <- segmented(fit_lm, seg.Z = ~stconc)
        fitted(fit_seg)
      },
      breakpoint = {
        fit_lm <- lm(avg ~ stconc)
        fit_seg <- segmented(fit_lm, seg.Z = ~stconc)
        fit_seg$psi[, "Est."]
      }
    ) |>
    dplyr::ungroup() |>
    ggplot(aes(x = stconc, y = avg)) +
    geom_point() +
    geom_point(aes(y = area), colour = "red") +
    geom_line(aes(y = seg_fitted), colour = "blue") +
    geom_vline(aes(xintercept = breakpoint), 
               linetype = "dashed", colour = "darkred") +
    stat_poly_eq(aes(label = after_stat(rr.label)),
                 formula = y ~ x,
                 parse = TRUE,
                 rr.digits = 5,
                 label.y = 0.95) +
    facet_wrap(~analyte, scales = "free") +
    labs(title = paste("Date processed:", d))
  
  print(p)
}
# 
# test <- standards_avg |>
#   dplyr::select(no, hole_pos, stconc_tc, stconc_tic, stconc_tnb, avg_tic, avg_tc, avg_tnb, tic_area, tc_area, t_nb_area, Date_processed) |>
#   pivot_analytes() |>
#   dplyr::filter(!is.na(analyte), !is.na(avg), !is.na(stconc)) |>
#   dplyr::group_by(analyte) |>
#   dplyr::mutate(
#     seg_fitted = {
#       fit_lm <- lm(avg ~ stconc)
#       fit_seg <- segmented(fit_lm, seg.Z = ~stconc)
#       fitted(fit_seg)
#     },
#     breakpoint = {
#       fit_lm <- lm(avg ~ stconc)
#       fit_seg <- segmented(fit_lm, seg.Z = ~stconc)
#       fit_seg$psi[, "Est."]
#     }
#   ) |>
#   dplyr::ungroup() |>
#   ggplot(aes(x = stconc, y = avg)) +
#   geom_point() +
#   geom_point(aes(y = area), colour = "red") +
#   geom_line(aes(y = seg_fitted), colour = "blue") +
#   geom_vline(aes(xintercept = breakpoint),
#              linetype = "dashed", colour = "darkred") +
#   stat_poly_eq(aes(label = after_stat(rr.label)),
#                formula = y ~ x,
#                parse = TRUE,
#                rr.digits = 5,
#                label.y = 0.95) +
#   facet_wrap(~analyte, scales = "free")
# test
```



```{r water blanks}
waterblanks <- tictoc |> filter(grepl(pattern = "Water", x = name))

get_last_injections_time <- function(df, n = 2, window_hours = 2) {
  df |>
    arrange(date, time) |>
    mutate(
      datetime = as.POSIXct(paste(date, time)),
      time_group = floor(as.numeric(datetime) / (window_hours * 3600))
    ) |>
    group_by(hole_pos, time_group) |>
    slice_tail(n = n) |>
    ungroup() 
}

blanks <- waterblanks |> 
  get_last_injections_time() |> 
  group_by(hole_pos, time_group) |>
  mutate(avg_tic = mean(tic_area, na.rm = T), 
         avg_tc  = mean(tc_area, na.rm = T), 
         avg_tnb = mean(t_nb_area, na.rm = T)) 

dates <- unique(blanks$Date_processed)


pivot_analytes_blanks <- function(df) {
  df |>
    rename(area_tnb = t_nb_area, 
           area_tc  = tc_area, 
           area_tic = tic_area) |>
    pivot_longer(
      cols = c(avg_tc, avg_tic, avg_tnb,
               area_tc, area_tic, area_tnb),
      names_to = c(".value", "analyte"),
      names_pattern = "^(.+)_(tc|tic|tnb)$"
    )
}

dates <- unique(blanks$Date_processed)

for(d in dates){
  
  d <- as.Date(d, origin = "1970-01-01")
  
  p <- blanks |>
    filter(Date_processed == d) |>
    dplyr::select(no, hole_pos, avg_tic, avg_tc, avg_tnb, 
                  tic_area, tc_area, t_nb_area) |>
    pivot_analytes_blanks() |>
    ggplot(aes(x = no, y = area)) +
    geom_point() +
    geom_point(aes(x = no, y = avg), color = "green") +
    facet_wrap(~analyte, scales = "free") +
    labs(title = paste("Date processed:", d))
  
  print(p)
}

# waterblanks <- tictoc |> filter(grepl(pattern = "Water", x = name))
# 
# #this function is time based and should solve issues pertaining to duplicate hole pos/dates/names. However, keep an eye on this!
# get_last_injections_time <- function(df, n = 2, window_hours = 2) {
#   df |>
#     arrange(date, time) |>
#     mutate(
#       datetime = as.POSIXct(paste(date, time)),
#       time_group = floor(as.numeric(datetime) / (window_hours * 3600))
#     ) |>
#     group_by(hole_pos, time_group) |>
#     slice_tail(n = n) |>
#     ungroup() 
# }
# 
# blanks <- waterblanks |> 
#   get_last_injections_time() |> 
#   group_by(hole_pos, time_group) |>
#   mutate(avg_tic = mean(tic_area, na.rm = T), 
#          avg_tc = mean(tc_area, na.rm = T), 
#          avg_tnb = mean(t_nb_area, na.rm = T)) 
# 
# pivot_analytes <- function(df) {
#   df |>
#     rename(area_tnb = t_nb_area, 
#            area_tc = tc_area, 
#            area_tic = tic_area) |>
#     pivot_longer(
#       cols = c(avg_tc, avg_tic, avg_tnb,
#                area_tc, area_tic, area_tnb),
#       names_to = c(".value", "analyte"),
#       names_pattern = "^(.+)_(tc|tic|tnb)$"
#     )
# }
# 
# 
# # add a line for the blanks rolling average
# blanks |> 
#   dplyr::select(no, hole_pos, avg_tic, avg_tc, avg_tnb, tic_area, tc_area, t_nb_area) |> 
# pivot_analytes() |> 
#   ggplot(aes(x = no, y = area)) +
#   geom_point() +
#     geom_point(aes(x = no, y = avg), color = "green") +
#   facet_wrap(~analyte, scales = "free")

```

2a. Add a chunk to take out any standards as needed, print a list for the maintenance log, ideally add straight to maintenance log

```{r interactive maintenance log 1}
### Add entries to the maintenance log interactively

# Read in the maintenance log to see its structure
maintenancelog <- paste0(here(), "/maintenance_logs/TICTOC_maintlog.csv")
log_current <- read_csv(maintenancelog)

# Print current samples in the data to help identify what to log
print("Current unique sample names in raw_df:")
print(sort(unique(tictoc$name)))

# Enter a value for each column interactively
new_entry <- data.frame(
  date_run     = as.Date(readline(prompt = "date_run (YYYY-MM-DD): ")),
  hole_pos     = readline(prompt = "hole_pos: "),
  name         = readline(prompt = "name: "),
  line_no      = as.integer(readline(prompt = "line_no: ")),
  analyte      = readline(prompt = "analyte (all/tic/tc/tnb): "),
  lab_flag     = as.integer(readline(prompt = "lab_flag (1-9): ")),
  notes        = readline(prompt = "notes: ")
)

# Print the entry so you can confirm it looks right
print("New entry to be added:")
print(new_entry)

# Confirm before appending
confirm <- readline(prompt = "Add this entry to the maintenance log? (yes/no): ")

if(tolower(confirm) == "yes"){
  write.table(new_entry, 
              maintenancelog, 
              append = TRUE, 
              sep = ",", 
              row.names = FALSE, 
              col.names = FALSE)
  print("Entry added to maintenance log.")
} else {
  print("Entry not added.")
}
```


3a. default linear and plot standards. 

```{r plot standards post maint log application}
# KKH recommends going up to the previous chunk and rerunning there. Not adding this section here so that this doesn't get too long. 
```


3a. always ignore the first injection, if both injections are available, average, otherwise take only one

Plotting all samples by hole position, plotting both average area and individual injection areas
```{r plot all samples}

samples_all <- tictoc_conc |> filter(grepl(pattern = "Sample|SPIKE|DUP", x = name, ignore.case = TRUE)) |> get_last_injections()

sample_avg <- samples_all |> 
  #get_last_injections() |> 
  group_by(Date_processed) |> 
  group_by(hole_pos) |> 
  mutate(avg_tic = mean(tic_area), 
         avg_tc = mean(tc_area), 
         avg_tnb = mean(t_nb_area)) |> 
  pivot_analytes_blanks() |>
    ggplot(aes(x = hole_pos, y = area)) +
    geom_point() +
    geom_point(aes(x = hole_pos, y = avg), color = "green") +
    facet_wrap(~analyte, scales = "free") +
    labs(title = paste("Date processed:", d))

sample_avg

```


4. calculate % error on each of the injection volumes for the standard curve, present as a table. Color points red if std dev is greater than 15%

([conc.] - [kn. std])/[kn. std]

add line to the graph at 120% of known standard to id anything out of range

```{r}
# Step 1: Fit linear regressions per analyte per date from the standard curve
pivot_analytes <- function(df) {
  df |>
    rename(area_tnb = t_nb_area, 
           area_tc = tc_area, 
           area_tic = tic_area) |>
    pivot_longer(
      cols = c(stconc_tc, stconc_tic, stconc_tnb,
               avg_tc, avg_tic, avg_tnb,
               area_tc, area_tic, area_tnb),
      names_to = c(".value", "analyte"),
      names_pattern = "^(.+)_(tc|tic|tnb)$"
    )
}

regressions <- standards_avg |>
  ungroup() |> 
  dplyr::select(no, hole_pos, stconc_tc, stconc_tic, stconc_tnb,
                avg_tic, avg_tc, avg_tnb,
                tic_area, tc_area, t_nb_area, Date_processed) |>
  pivot_analytes() |>
  filter(!is.na(avg), !is.na(stconc)) |>
  group_by(analyte, Date_processed) |>
  summarise(
    model = list(lm(avg ~ stconc)),
    .groups = "drop"
  )

# Helper to apply a model to an area value: solves avg = a + b*stconc for stconc
# i.e. conc = (area - intercept) / slope
calc_conc <- function(model, area){
  intercept <- coef(model)[1]
  slope     <- coef(model)[2]
  (area - intercept) / slope
}

# Step 2: Apply regressions to all samples to calculate concentrations
tictoc_conc <- tictoc |>
  group_by(Date_processed) |>
  group_modify(~ {
    df <- .x
    d  <- .y$Date_processed
    
    for(analyte in c("tic", "tc", "tnb")){
      
      area_col  <- switch(analyte,
                          "tic" = "tic_area",
                          "tc"  = "tc_area",
                          "tnb" = "t_nb_area")
      
      conc_col  <- switch(analyte,
                          "tic" = "calc_conc_tic",
                          "tc"  = "calc_conc_tc",
                          "tnb" = "calc_conc_tnb")
      
      mod <- regressions |>
        filter(analyte == !!analyte, Date_processed == d) |>
        pull(model)
      
      if(length(mod) == 0){
        df[[conc_col]] <- NA_real_
      } else {
        df[[conc_col]] <- calc_conc(mod[[1]], df[[area_col]])
      }
    }
    df
  }) |>
  ungroup()

# Step 3: Apply regressions back to standard areas and calculate % error
standards_pct_error <- standards_avg |>
  dplyr::select(no, hole_pos, stconc_tc, stconc_tic, stconc_tnb,
                avg_tic, avg_tc, avg_tnb,
                tic_area, tc_area, t_nb_area, Date_processed) |>
  pivot_analytes() |>
  filter(!is.na(avg), !is.na(stconc)) |>
  group_by(Date_processed) |>
  group_modify(~ {
    df <- .x
    d  <- .y$Date_processed
    
    for(a in c("tic", "tc", "tnb")){
      mod <- regressions |>
        filter(analyte == a, Date_processed == d) |>
        pull(model)
      
      rows <- df$analyte == a
      
      if(length(mod) == 0){
        df$calc_conc[rows] <- NA_real_
      } else {
        df$calc_conc[rows] <- calc_conc(mod[[1]], df$area[rows])
      }
    }
    df
  }) |>
  ungroup() |>
  mutate(
    pct_error    = ((calc_conc - stconc) / stconc) * 100,
    out_of_range = abs(pct_error) > 15
  )

# Step 4: Plot standard curve with % error and print table, looped by date
dates <- unique(standards_avg$Date_processed)

for(d in dates){
  
  d <- as.Date(d, origin = "1970-01-01")
  
  plot_data <- standards_pct_error |> filter(Date_processed == d)
  
  p <- plot_data |>
    ggplot(aes(x = stconc, y = avg)) +
    geom_point(aes(color = out_of_range)) +
    scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red"),
                       name = ">15% error") +
    geom_point(aes(x = stconc, y = area), colour = "red", shape = 17) +
    geom_smooth(method = "lm", se = FALSE) +
    geom_abline(aes(slope = 1.2, intercept = 0),
                linetype = "dashed", colour = "darkred") +
    stat_poly_eq(
      aes(label = after_stat(eq.label)),
      formula = y ~ x,
      parse = TRUE,
      label.y = 0.95
    ) +
    stat_poly_eq(
      aes(label = after_stat(rr.label)),
      formula = y ~ x,
      parse = TRUE,
      rr.digits = 5,
      label.y = 0.85
    ) +
    facet_wrap(~analyte, scales = "free") +
    labs(title = paste("Standard curve - Date processed:", d))
  
  print(p)
  
  error_table <- plot_data |>
    dplyr::select(no, hole_pos, analyte, stconc, avg, calc_conc, pct_error, out_of_range) |>
    arrange(analyte, stconc) |>
    mutate(pct_error = round(pct_error, 2),
           calc_conc = round(calc_conc, 4)) |>
    knitr::kable(
      caption = paste("% Error by standard - Date processed:", d),
      col.names = c("No", "Hole Pos", "Analyte", "Known Std",
                    "Measured Avg", "Calc. Conc", "% Error", ">15% Error")
    ) |>
    kableExtra::kable_styling(bootstrap_options = c("striped", "hover")) |>
    kableExtra::row_spec(which(plot_data$out_of_range), background = "#ffcccc")
  
  print(error_table)
}

```
```{r}
# Step 1: Calculate percent difference between duplicate injections
pct_diff <- samples_all |>
  get_last_injections() |> 
  group_by(Date_processed, name, hole_pos) |>
  summarise(
    n_injections  = n(),
    mean_conc_tic = mean(calc_conc_tic, na.rm = TRUE),
    mean_conc_tc  = mean(calc_conc_tc,  na.rm = TRUE),
    mean_conc_tnb = mean(calc_conc_tnb, na.rm = TRUE),
    rpd_tic = {
      vals <- calc_conc_tic[!is.na(calc_conc_tic)]
      if(length(vals) == 2) abs(vals[1] - vals[2]) / mean(vals) * 100 else NA_real_
    },
    rpd_tc = {
      vals <- calc_conc_tc[!is.na(calc_conc_tc)]
      if(length(vals) == 2) abs(vals[1] - vals[2]) / mean(vals) * 100 else NA_real_
    },
    rpd_tnb = {
      vals <- calc_conc_tnb[!is.na(calc_conc_tnb)]
      if(length(vals) == 2) abs(vals[1] - vals[2]) / mean(vals) * 100 else NA_real_
    },
    .groups = "drop"
  ) |>
  pivot_longer(
    cols = c(mean_conc_tic, mean_conc_tc, mean_conc_tnb,
             rpd_tic, rpd_tc, rpd_tnb),
    names_to = c(".value", "analyte"),
    names_pattern = "^(.+)_(tic|tc|tnb)$"
  )

# Step 2: Plot looped by date
dates <- unique(pct_diff$Date_processed)

for(d in dates){
  
  d <- as.Date(d, origin = "1970-01-01")
  
  plot_data <- pct_diff |> filter(Date_processed == d)
  
  # Figure 1: Concentration by sample
  p1 <- plot_data |>
    ggplot(aes(x = name, y = mean_conc, color = hole_pos)) +
    geom_point(size = 2) +
    facet_wrap(~analyte, scales = "free_y") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
    labs(title = paste("Sample concentrations - Date processed:", d),
         x = "Sample",
         y = "Calculated concentration",
         color = "Hole position")
  
  print(p1)
  
  # Figure 2: Percent difference between duplicate injections
p2_data <- plot_data |> filter(!is.na(rpd))
  
  if(nrow(p2_data) > 0){
    p2 <- p2_data |>
      ggplot(aes(x = name, y = rpd, color = rpd > 15)) +
      geom_point(size = 2) +
      geom_hline(yintercept = 15, linetype = "dashed", colour = "darkred") +
      scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red"),
                         name = ">15% RPD") +
      facet_wrap(~analyte, scales = "free_y") +
      theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
      labs(title = paste("Injection RPD - Date processed:", d),
           x = "Sample",
           y = "Relative percent difference (%)",
           color = ">15% RPD")
    
    print(p2)
    
  } else {
    message("No RPD values to plot for date: ", d)
  }
}

```


-- here: look back at the notes and make decisions about any injections to exclude if necessary --
- add this list to maint log if necessary

6. Check dups - perc diff (avg. orig - avg. dup)/avg. of all injections
```{r}
# Define duplicate pairings
dup_pairs <- tibble(
  sample_name = c("Sample 5",  "Sample 15"),
  dup_hole_pos = c("20", "32")
)

# Calculate RPD between each sample and its paired DUP
dup_rpd <- dup_pairs |>
  rowwise() |>
  reframe(
    samples_all |>
      filter(Date_processed %in% unique(samples_all$Date_processed)) |>
      group_by(Date_processed) |>
      summarise(
        sample_conc_tic = mean(calc_conc_tic[name == sample_name],  na.rm = TRUE),
        sample_conc_tc  = mean(calc_conc_tc[name == sample_name],   na.rm = TRUE),
        sample_conc_tnb = mean(calc_conc_tnb[name == sample_name],  na.rm = TRUE),
        dup_conc_tic    = mean(calc_conc_tic[name == "DUP" & hole_pos == dup_hole_pos],  na.rm = TRUE),
        dup_conc_tc     = mean(calc_conc_tc[name == "DUP" & hole_pos == dup_hole_pos],   na.rm = TRUE),
        dup_conc_tnb    = mean(calc_conc_tnb[name == "DUP" & hole_pos == dup_hole_pos],  na.rm = TRUE),
        sample_name     = sample_name,
        dup_hole_pos    = dup_hole_pos,
        .groups         = "drop"
      )
  ) |>
  mutate(
    rpd_tic = abs(sample_conc_tic - dup_conc_tic) / mean(c(sample_conc_tic, dup_conc_tic)) * 100,
    rpd_tc  = abs(sample_conc_tc  - dup_conc_tc)  / mean(c(sample_conc_tc,  dup_conc_tc))  * 100,
    rpd_tnb = abs(sample_conc_tnb - dup_conc_tnb) / mean(c(sample_conc_tnb, dup_conc_tnb)) * 100
  ) |>
  pivot_longer(
    cols = c(sample_conc_tic, sample_conc_tc, sample_conc_tnb,
             dup_conc_tic, dup_conc_tc, dup_conc_tnb,
             rpd_tic, rpd_tc, rpd_tnb),
    names_to = c(".value", "analyte"),
    names_pattern = "^(.+)_(tic|tc|tnb)$"
  )

# Plot looped by date
dates <- unique(dup_rpd$Date_processed)

for(d in dates){
  
  d <- as.Date(d, origin = "1970-01-01")
  
  plot_data <- dup_rpd |> filter(Date_processed == d)
  
  p <- plot_data |>
    ggplot(aes(x = sample_name, y = rpd, fill = rpd > 15)) +
    geom_col() +
    geom_hline(yintercept = 15, linetype = "dashed", colour = "darkred") +
    scale_fill_manual(values = c("FALSE" = "steelblue", "TRUE" = "red"),
                      name = ">15% RPD") +
    facet_wrap(~analyte, scales = "free_y") +
    labs(title = paste("Duplicate RPD - Date processed:", d),
         x = "Sample",
         y = "Relative percent difference (%)") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
  
  print(p)
}
```


7. Check spikes - conc. difference to calculate % recovery

FRANCES YOU NEED TO FILL THIS IN, RAN OUT OF STEAM LAST NIGHT. OTHERWISE SHOULD WORK

```{r}
# Known spike concentrations - FILL IN THESE VALUES
spike_conc_tic <- NA_real_  # fill in known TIC spike concentration
spike_conc_tc  <- NA_real_  # fill in known TC spike concentration
spike_conc_tnb <- NA_real_  # fill in known TNB spike concentration

# Define spike pairings
spike_pairs <- tibble(
  sample_name   = c("Sample 10", "Sample 20"),
  spike_hole_pos = c("19", "31")
)

# Calculate spike recovery
spike_recovery <- spike_pairs |>
  rowwise() |>
  reframe(
    tictoc_conc |>
      group_by(Date_processed) |>
      summarise(
        sample_conc_tic  = mean(calc_conc_tic[name == sample_name],                          na.rm = TRUE),
        sample_conc_tc   = mean(calc_conc_tc[name == sample_name],                           na.rm = TRUE),
        sample_conc_tnb  = mean(calc_conc_tnb[name == sample_name],                          na.rm = TRUE),
        spike_conc_tic   = mean(calc_conc_tic[name == "SPIKE" & hole_pos == spike_hole_pos], na.rm = TRUE),
        spike_conc_tc    = mean(calc_conc_tc[name == "SPIKE" & hole_pos == spike_hole_pos],  na.rm = TRUE),
        spike_conc_tnb   = mean(calc_conc_tnb[name == "SPIKE" & hole_pos == spike_hole_pos], na.rm = TRUE),
        sample_name      = sample_name,
        spike_hole_pos   = spike_hole_pos,
        .groups          = "drop"
      )
  ) |>
  mutate(
    recovery_tic = (spike_conc_tic - sample_conc_tic) / spike_conc_tic * 100,
    recovery_tc  = (spike_conc_tc  - sample_conc_tc)  / spike_conc_tc  * 100,
    recovery_tnb = (spike_conc_tnb - sample_conc_tnb) / spike_conc_tnb * 100
  ) |>
  pivot_longer(
    cols = c(sample_conc_tic, sample_conc_tc, sample_conc_tnb,
             spike_conc_tic,  spike_conc_tc,  spike_conc_tnb,
             recovery_tic,    recovery_tc,    recovery_tnb),
    names_to  = c(".value", "analyte"),
    names_pattern = "^(.+)_(tic|tc|tnb)$"
  )

# Plot looped by date
dates <- unique(spike_recovery$Date_processed)

for(d in dates){
  
  d <- as.Date(d, origin = "1970-01-01")
  
  plot_data <- spike_recovery |> filter(Date_processed == d)
  
  p <- plot_data |>
    ggplot(aes(x = sample_name, y = recovery, fill = recovery < 80 | recovery > 120)) +
    geom_col() +
    geom_hline(yintercept = 80,  linetype = "dashed", colour = "darkred") +
    geom_hline(yintercept = 120, linetype = "dashed", colour = "darkred") +
    scale_fill_manual(values = c("FALSE" = "steelblue", "TRUE" = "red"),
                      name = "Outside 80-120%") +
    facet_wrap(~analyte, scales = "free_y") +
    labs(title = paste("Spike recovery - Date processed:", d),
         x     = "Sample",
         y     = "% Recovery") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
  
  print(p)
}
```

8. Spk taps - see next page - apply flag for outside range - plot, also calc % difference from the 1st spk tap over the course of the run

STILL NEED TO DO THIS PART! WHAT ARE THE VALUES THAT THEY SHOULD BE?
```{r}

```

9. average reps 2 & 3, flag anything that is over 120% of the top std. 
WHAT IS THE FLAG THAT WE ARE USING FOR THIS?
These reps are averaged based on concentration, not area! Technically should be the same. Might not be the same if using a segmented regression. That might be a can of worms we open only if we must.
```{r}

```



ADDING A MANUAL WAY TO ADD FLAGS TO THE MAINTENANCE LOG HERE AGAIN FOR THIS
```{r interactive maintenance log 2}
### Add entries to the maintenance log interactively

# Read in the maintenance log to see its structure
maintenancelog <- paste0(here(), "/maintenance_logs/TICTOC_maintlog.csv")
log_current <- read_csv(maintenancelog)

# Print current samples in the data to help identify what to log
print("Current unique sample names in raw_df:")
print(sort(unique(tictoc$name)))

# Enter a value for each column interactively
new_entry <- data.frame(
  date_run     = as.Date(readline(prompt = "date_run (YYYY-MM-DD): ")),
  hole_pos     = readline(prompt = "hole_pos: "),
  name         = readline(prompt = "name: "),
  line_no      = as.integer(readline(prompt = "line_no: ")),
  analyte      = readline(prompt = "analyte (all/tic/tc/tnb): "),
  lab_flag     = as.integer(readline(prompt = "lab_flag (1-9): ")),
  notes        = readline(prompt = "notes: ")
)

# Print the entry so you can confirm it looks right
print("New entry to be added:")
print(new_entry)

# Confirm before appending
confirm <- readline(prompt = "Add this entry to the maintenance log? (yes/no): ")

if(tolower(confirm) == "yes"){
  write.table(new_entry, 
              maintenancelog, 
              append = TRUE, 
              sep = ",", 
              row.names = FALSE, 
              col.names = FALSE)
  print("Entry added to maintenance log.")
} else {
  print("Entry not added.")
}
```



Output the Excel sheet that is delivered. 
We might need to change this naming convention.
```{r}
write.csv(paste0(here(), "/Results/TICTOC/", paste0(Sys.Date()), "_TICTOCresults.csv"))

Sys.Date()
```





