---
title: "Lachat_QAQC_test"
format: html
editor: visual
author: "Frances Iannucci and Adrienne Breef-Pilz"
---

Instructions: This is a script to analyze the TP an TN data from the Lachat. To run this script run it chunk by chunk and don't knit it together.

```{r Setup}

# load packages
# install.packages("pacman")
pacman::p_load(tidyverse, plotly, here, htmltools, manipulateWidget, htmlwidgets)


# load the functions
helper.functions <- list.files("functions/Lachat/")
sapply(paste0("functions/Lachat/", helper.functions),source,.GlobalEnv)


# analytes for this workflow
analytes <- c("TN", "TP")

# Read in a historical MDL file and get values

# Check the methods of detection [delete/move this section once we can read in a real MDL file]
#Estimated method detection limits (update periodically from rolling charts):
est.MDL.TP= 4.9
est.MDL.TN= 67    #values as of summer 2024

#read in rolling checks file
load(paste0(getwd(),'/MDLs/Rolling.Checks.TNTP.RData')) 

    #calculate MDLs using everything from two years prior to run date
    #maybe move this section after run file is created, so you can reference run date from there?
        #now creates both runDate and runDate.posix- can reference that.


# Flags used throughout and can update here: 
#List of possible flags for data (used throughout):
flags= c('1: Recalculated standard curve',
         '2: Did not apply reduction efficiency correction',
         '3: High concentration in blanks',
         '4: Poor recovery (spikes or digestion checks)',
         '5: High relative percent difference (dups or checks)',
         '6: Messy peak integration',
         '7: Concentration out of range',
         '8: Just wrong in some way',
         '9: Use with caution')


# Make folder to put standard curve plots in 

  if (!file.exists("preliminary_plots")){
    # make the folder
    dir.create(file.path("preliminary_plots"))
  } 
```

```{r load in raw data}
print('Select your raw data file. If you have multiple segments, choose the first one.')
#
all= read.csv(file.choose(new = F))
#This will trigger you to open up a data file to run this QA/QC script on. Choose one or more data files within the Raw/Totals/ directory
rl= readline('Do you have additional run segments to add? (y/n): ')
while (rl=='y'|rl=='Y') {
  seg.b= read.csv(file.choose(new = F))
  all= rbind(all, seg.b)
  rl= readline('Do you have additional run segments to add? (y/n): ')
}

#Enter run information:
runDate= readline('Enter the date your samples were run (YYYY-MM-DD format): ')
#no quotes are needed for your date string
runDate.posix= as.POSIXct(runDate)

# project information
project= readline('Enter a brief description of what was run (e.g., LTREB_2025_batch1): ')
#this is an internal note for you only

# # added this line so that we can add project information
# print(runDate)
```

```{r Spiking information}
# Default spiking information:
sb.di= 10000
sb.std= 250
sb.conc= 1000
ss.sample= 10000
ss.std= 250
ss.conc= 1000
n.factor= 10

cat("Spiking information:", "\n",
 "Volume of DI or sample added = ", sb.di,"uL", "\n", "Volume of standard added to blanks and samples =", sb.std,
 "uL", "\n", "Concentration of P standard added =", sb.conc, "ppb", "\n", "Factor to scale up from P to N concentrations =", n.factor)

rl= readline('Do you need to change any of these default values? (y/n): ')
#for some reason it will make you say yes twice before it will let you edit values, but then it works

while (rl=='y'|rl=='Y') {
  param= readline('What parameter do you want to change? Options are sb.di, sb.std, sb.conc, ss.sample, ss.std, ss.conc, and n.factor: ')
  if (param=='sb.di') {sb.di= as.numeric(readline('Enter volume of water used for spike blanks (in uL): '))}
  if (param=='sb.std') {sb.std= as.numeric(readline('Enter volume of standard added to spike blanks (in uL): '))}
  if (param=='sb.conc') {sb.conc= as.numeric(readline('Enter concentration of TP standard added to spike blanks (in ug/L): '))}
  if (param=='ss.sample') {ss.sample= as.numeric(readline('Enter volume of water used for spiked samples (in uL): '))}
  if (param=='ss.std') {ss.std= as.numeric(readline('Enter volume of standard added to spiked samples (in uL): '))}
  if (param=='ss.conc') {ss.conc= as.numeric(readline('Enter concentration of TP standard added to spiked samples (in ug/L): '))}
  if (param=='n.factor') {n.factor= as.numeric(readline('Enter the scaling factor to convert from TP to TN standard concentration (normally 10): '))}
  cat("Spiking information:", "\n",
 "Volume of DI or sample added = ", sb.di,"uL", "\n", "Volume of standard added to blanks and samples =", sb.std,
 "uL", "\n", "Concentration of P standard added =", sb.conc, "ppb", "\n", "Factor to scale up from P to N concentrations =", n.factor)
  rl= readline('Do you need to change any other parameters? (y/n): ')
}

```

```{r Set up the data frame}
#### START BUILDING OUTPUT DATAFRAME ####

# Build analyte rows dynamically from repeated analyte blocks.
# This handles runs with 2+ analytes and preserves NH4-before-PO4 ordering from raw data.

# make a vector of the common names
common_cols <- c(
  "Detection.Date", "Detection.Time", "Run.File.Name", "Sample.ID", "Cup.Number", "Sample.Type",
  "Auto.Dilution.Factor", "Manual.Dilution.Factor"
)

# get the column names with the analyte labeled. If none then stop
analyte_cols <- grep("^Analyte.Name(\\.[0-9]+)?$", names(all), value = TRUE)
if (length(analyte_cols) == 0) {
  stop("No analyte columns found. Check raw file format.")
}

suffixes <- sub("Analyte.Name", "", analyte_cols)
block_fields <- c("Analyte.Name", "Concentration.Units", "Peak.Height", "Peak.Area", "Peak.Concentration")

# make 3 lists of the different analytes
blocks <- lapply(suffixes, function(sfx) {
  block_names <- paste0(block_fields, sfx)
  keep <- block_names %in% names(all)
  if (!all(keep)) {
    return(NULL)
  }
  
  out <- all |>
    select(all_of(common_cols), all_of(block_names))
  
  names(out)[(length(common_cols) + 1):ncol(out)] <- block_fields
  out
})

blocks <- blocks[!sapply(blocks, is.null)]
if (length(blocks) == 0) {
  stop("Could not construct analyte blocks from raw data.")
}

# bind them all together
long_data <- bind_rows(blocks)

# Expected check standard concentration from Sample ID digits
long_data <- long_data |>
  mutate(expected.conc = ifelse(grepl("Standard", Sample.Type, ignore.case = TRUE),
                                as.numeric(gsub("[^0-9.-]", "", Sample.ID)),
                                NA),
         Analyte.Name = gsub("-.*", "", Analyte.Name)) # clean up the names and take out the dash

# Add notes/flags before pivot wider
long_data <- long_data |>
  mutate(
    Notes = NA,
    Flag = NA
  )

# One row per sample with analyte-specific columns
# Use run row id to keep duplicate sample IDs from collapsing together
long_data <- long_data |>
  group_by(Detection.Date, Detection.Time, Run.File.Name, Sample.ID, Cup.Number, Sample.Type,
           Auto.Dilution.Factor, Manual.Dilution.Factor) |>
  mutate(run_row_id = cur_group_id()) |>
  ungroup()

data_raw <- long_data |>
  select(-Concentration.Units) |>
  pivot_longer(
    cols = !c(Detection.Date, Detection.Time, Run.File.Name, Sample.ID, Cup.Number,
              Sample.Type, Auto.Dilution.Factor, Manual.Dilution.Factor, run_row_id, Analyte.Name),
    names_to = "var",
    values_to = "obs"
  ) |>
  pivot_wider(
    id_cols = c(Detection.Date, Detection.Time, Run.File.Name, Sample.ID, Cup.Number,
                Sample.Type, Auto.Dilution.Factor, Manual.Dilution.Factor, run_row_id),
    names_from = c(var, Analyte.Name),
    names_glue = "{var}.{Analyte.Name}",
    values_from = obs
  ) |>
  mutate(
    Detection.Time = paste0(Detection.Date, " ", Detection.Time),
    Detection.Time = as.POSIXct(Detection.Time, format = "%m/%d/%Y %I:%M:%S %p"),
    expected.conc.TN = expected.conc.TP * n.factor, # get the expected TN conc based on TP
    row.numbers = row_number() # create column of row numbers
  ) |>
  select(-run_row_id) # take out the column

names(data_raw) <- gsub("Peak.Concentration", "Conc.ugL", names(data_raw))

# numeric run time for plotting/regression in downstream checks
data_raw$Detection.Time <- as.numeric(data_raw$Detection.Time - data_raw$Detection.Time[1])

# put the time in usable YYYY-MM-DD format

data_raw$Detection.Date <- as.Date(data_raw$Detection.Date, "%m/%d/%Y")

```

```{r Review and Edit Data Frame (currently just sample ID's)}
#### REVIEW AND EDIT DATA FRAME ####

# View the data frame and make any needed corrections to Sample.ID. Can add the other columns
# before proceeding with QA/QC checks.

View(data_raw)

rl <- readline("Do you need to make any changes to the data frame? (e.g., typos in sample IDs) (y/n): ")
while (rl == "y" | rl == "Y") {
  rn  <- readline("Which row number(s) need to be changed? (single number, range like 3:7, or list like 1,4,6): ")
  
  if(rn == ""){
    
    rn  <- readline("Which row number(s) need to be changed? (single number, range like 3:7, or list like 1,4,6): ")
  }
  new_val <- readline(paste0("What should the new value of be?: "))
  
  if(new_val == ""){
    new_val <- readline(paste0("What should the new value of be?: "))
  }

  # change the Sample.ID here 
    data_raw <- edit_sample_info(df = data_raw, rn = rn, new_sample_id = new_val)
    
    # add a note that the Sample.ID was changed 
    data_raw <- append_flag_note(df = data_raw, rn = rn, analyte = 'TNTP', flag_num = NA, note_text = "Sample.Id changed")
  

  View(data_raw)
  rl <- readline("Do you need to make any more changes? (y/n): ")
}

```

```{r Evaluate Standard Curves}
#### EVALUATE STANDARD CURVES ####

# Check the standard curve. Plots are saved in an intermediate folder for you to look at because you need to make decisions based on the plots. 

data_scurv_TP <- standard_curve(
   analyte = "TP",
   lachat_data = data_raw
)

#repeat the process for TN:

data_scurv <- standard_curve(
  analyte = "TN",
  lachat_data = data_scurv_TP
)

print("Finished checking the standard curves")

```

```{r Calculate and Evaluate TN reduction efficiency}

#EVENTUALLY: EDIT SO THAT CUP NUMBER IS RETAINED IN R.EFFICIENCY_DF AND REDUCTION.POINTS - Not sure how this would work because there are two cups per a row. Isn't that what S1 and S2 are?


# Calculate efficiency as nitrate (S2) divided by nitrite (S1) concentration.
# S1 = nitrite/NO2 (odd rows), S2 = nitrate/NO3 (even rows)

r.efficiency <- data_scurv |>
  filter(grepl("^n", Sample.ID, ignore.case = TRUE)) |>
  select(row.numbers, Detection.Time, Sample.ID, Cup.Number, Peak.Area.TN, Conc.ugL.TN)

S1.r.efficiency <- r.efficiency |>
  filter(row_number() %% 2 == 1) |>
  dplyr::rename("S1.Peak.Area.TN" = Peak.Area.TN, "S1.Conc.ugL.TN" = Conc.ugL.TN)

r.efficiency_df <- r.efficiency |>
  filter(row_number() %% 2 == 0) |>
  dplyr::rename("S2.Peak.Area.TN" = Peak.Area.TN, "S2.Conc.ugL.TN" = Conc.ugL.TN) |>
  bind_cols(S1.r.efficiency, ..2 = _) |>
  select(row.numbers...1, Detection.Time...2, Sample.ID...3,
         S1.Peak.Area.TN, S1.Conc.ugL.TN, S2.Peak.Area.TN, S2.Conc.ugL.TN) |>
  dplyr::rename("row.numbers"    = row.numbers...1,
                "Detection.Time" = Detection.Time...2,
                "Sample.ID"      = Sample.ID...3) |>
  mutate(reduction.efficiency = S2.Conc.ugL.TN / S1.Conc.ugL.TN)

# Join efficiency back to the main data frame
data_eff <- left_join(data_scurv,
                      r.efficiency_df |> select(Detection.Time, Sample.ID, reduction.efficiency),
                      by = c("Detection.Time", "Sample.ID"))

# helper to save the efficiency plot
save_eff_plot <- function(df, title) {
  p <- ggplot(df, aes(x = Detection.Time, y = reduction.efficiency)) +
    geom_smooth(method = "lm") +
    geom_point() +
    ggtitle(title) +
    theme_bw() +
    theme(text = element_text(size = 18))
  png("preliminary_plots/reduction_efficiency_3.png", width = 10, height = 10, units = "in", res = 600)
  plot(p)
  dev.off()
}

save_eff_plot(r.efficiency_df, "Reduction efficiency over the time of the run. Can remove bad points later on.")
View(r.efficiency_df)

cat("Review efficiency checks for TN- ideally >= 90% and stable over the run.\n",
    "By default an efficiency correction should be applied unless there are problems with the efficiency checks.\n",
    "You can also apply a correction to specific segments if there are step changes.\n",
    "See preliminary_plots/reduction_efficiency_3.png.\n")

rl <- readline("Would you like to apply an efficiency correction to the data? (y/n): ")

if (rl == "n" | rl == "N") {
  note <- readline("Enter a note- explain why efficiency was not corrected: ")
  data_eff <- append_flag_note(df = data_eff, rn = data_eff$row.numbers, analyte = "TN",
                               flag_num = 2, note_text = note)

} else if (rl == "y" | rl == "Y") {

  reduction.points <- r.efficiency_df

  or <- readline("Look at reduction_efficiency_3.png (estimate; true model will be forced through 1). Do you want to remove any outliers from the regression? (y/n): ")
  while (or == "y" | or == "Y") {
    View(r.efficiency_df)
    rn.rp <- readline("Enter the row.numbers of the efficiency check(s) to exclude (e.g. 3, 5): ")
   # rn.d  <- readline("Enter the same row.numbers in the full data set (for flagging): ")

    # parse the row number strings
    parse_rn <- function(s) as.numeric(unlist(strsplit(gsub(",", " ", s), "\\s+")))
    rp_vec   <- parse_rn(rn.rp)
   # data_vec <- parse_rn(rn.d)

    # set outlier efficiency to NA in the efficiency data frame
    r.efficiency_df$reduction.efficiency[r.efficiency_df$row.numbers %in% rp_vec] <- NA

    save_eff_plot(r.efficiency_df, "Reduction efficiency. Check that outliers are removed.")
    View(r.efficiency_df)

    kc <- readline("Keep changes? Saying no restores all outliers to the regression. (y/n): ")

    if (kc == "y" | kc == "Y") {
      reduction.points <- r.efficiency_df
      data_eff <- append_flag_note(df = data_eff, rn = rp_vec, analyte = "TN",
                                   flag_num = 9, note_text = "Point excluded from efficiency correction.")
    } else {
      # restore all points
      reduction.points <- data_eff[!is.na(data_eff$reduction.efficiency), ]
    }

    save_eff_plot(reduction.points, "Reduction efficiency. Check that you have all the outliers.")
    View(reduction.points)
    or <- readline("Do you want to remove any more outliers from the regression? (y/n): ")
  }

  sub <- readline("Do you want to apply the regression to a specific run segment only? (y/n): ")
  
  if (sub == "n" | sub == "N") {
    efficiency.reg <- lm((reduction.efficiency - 1) ~ 0 + Detection.Time, reduction.points)
    data_eff$Conc.ugL.TN <- data_eff$Conc.ugL.TN /
      (coef(efficiency.reg) * data_eff$Detection.Time + 1)
  }
  while (sub == "y" | sub == "Y") {
    View(reduction.points)
    reg.start <- as.numeric(readline("Enter the row number of the first reduction check for the regression: "))
    reg.end   <- as.numeric(readline("Enter the row number of the last reduction check for the regression: "))
    data_eff <- append_flag_note(df = data_eff, rn = reg.start, analyte = "TN",
                                 note_text = "Start of RE regression segment.")
    data_eff <- append_flag_note(df = data_eff, rn = reg.end,   analyte = "TN",
                                 note_text = "End of RE regression segment.")
    View(data_eff)
    data.start <- as.numeric(readline("Enter the row where you want to start applying this regression: "))
    data.end   <- as.numeric(readline("Enter the row where you want to stop applying this regression: "))
    efficiency.reg <- lm((reduction.efficiency - 1) ~ 0 + Detection.Time, reduction.points[reg.start:reg.end, ])
    for (i in data.start:data.end) {
      data_eff$Conc.ugL.TN[i] <- data_eff$Conc.ugL.TN[i] /
        (coef(efficiency.reg) * data_eff$Detection.Time[i] + 1)
    }
    sub <- readline("Do you need to apply a separate regression to another run segment? (y/n): ")
  }
}

print("Finished adding the efficiency correction to the data frame.")
```

#### REVIEW QUALITY CHECKS

#EVENTUALLY EDIT FUNCTIONS FOR ROLLING CHARTS TO EXCLUDE POINTS FLAGGED 6 (MESSY PEAK INTEGRATION) FROM PLOTTING AND CALCULATIONS #ALSO MAKE SURE CHECKS.RPD (OR ANY RPD OR PCT.RECOVERY COLUMNS) IS RETAINED THROUGHOUT THE ENTIRE LOOP

```{r Water blanks }
# Check out the water blanks

# Make a data frame of stats. The check argument should be: water blank, digest check, spike blank, check standards.

data_list <- qc_check(lachat_data = data_eff, check = "water blank")


# add the qc check to the rolling charts
rc_digested.blanks <- add_rollingcharts(rolling_chart = digested.blanks)

# check the qc check and how they relate to the Rolling Charts

print('Generating rolling charts plots- this will take a minute')

rc_digested.blanks <- run_mdl_rolling_charts(df = rc_digested.blanks)

# Get the main dataframe from the list

data_blank <- data_list[[1]]

# update the flag and notes from the mdl function
data_blank <- update_data_from_rolling(
  lachat_data = data_blank,
    rolling_export = rc_digested.blanks)

print("Water Blank check finished")

```

```{r digestion checks}
#digestion checks:
# The check argument should be: water blank, digest check, spike blank, check standards.

data_list <- qc_check(lachat_data = data_blank, check = "digest check")

# add the qc check to the rolling charts
rc_digest.checks <- add_rollingcharts(rolling_chart = digest.checks)

# check the qc check and how they relate to the Rolling Charts

print('Generating rolling charts plots- this will take a minute')

rc_digest.checks <- run_mdl_rolling_charts(df = rc_digest.checks)

# Get the main dataframe from the list

data_digest <- data_list[[1]]

# update the flag and notes from the mdl function
data_digest <- update_data_from_rolling(
  lachat_data = data_digest,
    rolling_export = rc_digest.checks)

# Need to have an output so the readline will work in the function. Not sure why
print("Digestions check finished")

```

```{r Spike blanks}
#spike blanks:
# The check argument should be: water blank, digest check, spiked blank, check standards.

data_list <- qc_check(lachat_data = data_digest, check = "spiked blank")

# add the qc check to the rolling charts
rc_spiked.blanks <- add_rollingcharts(rolling_chart = spiked.blanks)

# check the qc check and how they relate to the Rolling Charts

print('Generating rolling charts plots- this will take a minute')

rc_spiked.blanks <- run_mdl_rolling_charts(df = rc_spiked.blanks)

# Get the main dataframe from the list

data_sp_blank <- data_list[[1]]

# update the flag and notes from the mdl function
data_sp_blank <- update_data_from_rolling(
  lachat_data = data_sp_blank,
    rolling_export = rc_spiked.blanks)

# Need to have an output so the readline will work in the function. Not sure why
print("Spiked blanks check finished")

```

```{r Check standards}


#WOULD LIKE TO UPDATE SO ALL CHECK STANDARDS ARE REVIEWED AT FIRST, BUT ONLY CHECK 25'S ARE ADDED TO THE ROLLING CHARTS - Done
  #FILTER BY SAMPLE TYPE == CHECK STANDARD?
  #CURRENTLY MISSES THINGS THAT DON'T HAVE CHECK OR CHK IN THE NAME - Done. In the qc script changed the filter to the Sample.Type column


#relative percent difference of check standards from expected concentrations:
# The check argument should be: water blank, digest check, spike blank, check standards.

data_list <- qc_check(lachat_data = data_sp_blank, check = "check standards")

# filter out the checks that are not 25 
check_25_df <- data_list[[2]] |>
  filter(expected.conc.TN %in% 250,
         expected.conc.TP %in% 25)


# add the qc check to the rolling charts
rc_check.25.standards <- add_rollingcharts(data_file = check_25_df,
                                           rolling_chart = check.25.standards)

# check the qc check and how they relate to the Rolling Charts

print('Generating rolling charts plots- this will take a minute')

rc_check.25.standards <- run_mdl_rolling_charts(df = rc_check.25.standards)

# Get the main dataframe from the list

data_checks <- data_list[[1]]

# update the flag and notes from the mdl function
data_checks <- update_data_from_rolling(
  lachat_data = data_checks,
    rolling_export = rc_check.25.standards)

# Need to have an output so the readline will work in the function. Not sure why
print("Check standards check finished")
#
```

```{r Dups check}
#relative percent difference of duplicate samples:

# make a df of just the obs with dups
data_dups <- data_checks

dups_check <- data_dups|>
      filter(grepl("Du", Sample.Type,ignore.case = T))|>
      # make a column of just sample ids without the dups
      mutate(clean_ids = gsub("[^0-9.-]", "", Sample.ID))|>
      # select the columns we care about
      select(Detection.Date, Sample.Type, Sample.ID, clean_ids ,Conc.ugL.TN, Conc.ugL.TP)|>
      group_by(Sample.Type, clean_ids)|>
      # look at summarise across 
      summarise(Duplicates.RPD.TN = (abs(diff(Conc.ugL.TN))/mean(Conc.ugL.TN)*100),
                Duplicates.RPD.TP = (abs(diff(Conc.ugL.TP))/mean(Conc.ugL.TP)*100))|>
  ungroup()

# make a data frame of just the samples that were duped

# lets add all the to the data 
data_dups <- data_dups|>
   mutate(clean_ids = gsub("[^0-9.-]", "", Sample.ID))|>
  merge(dups_check, by = c("clean_ids", "Sample.Type"), all = T)|>
  mutate(dup_id = case_when(
    grepl("DUP", Sample.ID, ignore.case = TRUE) ~ "duplicate",  # e.g. "DUP S23" or "S23 DUP"
    TRUE ~ "original"  # e.g. "S23"
  ))|> # label original vs. duplicate based on presence of "DUP" anywhere in Sample.ID
  # set the RPD to NA for the original sample
  mutate(Duplicates.RPD.TN = ifelse(grepl("Du", Sample.Type, ignore.case = T) & dup_id == "original", NA, Duplicates.RPD.TN),
         Duplicates.RPD.TP = ifelse(grepl("Du", Sample.Type, ignore.case = T) & dup_id == "original", NA, Duplicates.RPD.TP))
 

# flag pairs with high relative percent difference
# helper: append flag 5 if RPD exceeds threshold (>20% above MDL, >100% near/below MDL)
flag_high_rpd <- function(flag, notes, rpd, conc, mdl) {
  needs_flag <- !is.na(rpd) & (
    (conc >  2 * mdl & rpd >  20) |
    (conc <= 2 * mdl & rpd > 100)
  )
  ifelse(needs_flag, ifelse(!is.na(flag), paste(flag, 5), 5), flag)
}

data_dups2 <- data_dups |>
  mutate(
    Flag.TP = flag_high_rpd(Flag.TP, Notes.TP, Duplicates.RPD.TP, Conc.ugL.TP, est.MDL.TP),
    Flag.TN = flag_high_rpd(Flag.TN, Notes.TN, Duplicates.RPD.TN, Conc.ugL.TN, est.MDL.TN),
    Notes.TP = ifelse(grepl("5", Flag.TP), "RPD exceeds threshold (>20% above MDL, >100% near/below MDL)", Notes.TP),
    Notes.TN = ifelse(grepl("5", Flag.TN), "RPD exceeds threshold (>20% above MDL, >100% near/below MDL)", Notes.TN))

# create a smaller data frame
dups_view <- data_dups2|>
  filter(grepl("Du", Sample.Type,ignore.case = T))|>
  select(row.numbers,Sample.ID, clean_ids, dup_id, Sample.Type, Conc.ugL.TP, Duplicates.RPD.TP, Flag.TP, Notes.TP,
         Conc.ugL.TN, Duplicates.RPD.TN, Flag.TN, Notes.TN)

# add in reruns with matching clean ids, to help decide which numbers to believe:
rr_dups <- data_dups2|>
  filter(clean_ids %in% dups_view$clean_ids & !grepl("stand", Sample.Type, ignore.case = T))|>
  select(row.numbers,Sample.ID, clean_ids, Sample.Type, Conc.ugL.TP, Duplicates.RPD.TP, Flag.TP, Notes.TP,
         Conc.ugL.TN, Duplicates.RPD.TN, Flag.TN, Notes.TN)

View(rr_dups)


rl= readline('Review the duplicates and the plot- high RPD is flagged automatically. Remember to compare dups to reruns when deciding which data to use, and flag bad data. Do you want to add any flags/notes? (y/n): ')
while (rl=='y'|rl=='Y') {
  rn= readline('Enter the row number or numbers (from row.numbers) you want to add a flag+note to: ')
  type= readline('Which analyte needs a note? (TN, TP): ')
  print(flags)
  f= as.numeric(readline('Enter the flag number (see list above): '))
  note= as.character(readline('Enter your note: '))
  
  # Flag and add the note using this function
  data_dups2 <- append_flag_note(df = data_dups2, rn = rn, analyte = type, flag_num = f, note_text = note)
  
  
  View(data_dups2|>
  filter(clean_ids %in% dups_view$clean_ids & !grepl("stand", Sample.Type, ignore.case = T))|>
  select(row.numbers,Sample.ID, clean_ids, Sample.Type, Conc.ugL.TP, Duplicates.RPD.TP, Flag.TP, Notes.TP,
         Conc.ugL.TN, Duplicates.RPD.TN, Flag.TN, Notes.TN))
      #can this be edited so it displays reruns and dilutions as well? like how it's displayed in rr_dups - done!
  rl= readline('Do you want to add any more notes? (y/n): ')
}

#add just the dups (not the originals) to the rolling charts:
dups_rc= data_dups2|>
  filter(grepl("Du", Sample.ID,ignore.case = T))|>
  select(Detection.Date, Detection.Time, Sample.ID, Cup.Number, Peak.Area.TP, Conc.ugL.TP, Notes.TP, Flag.TP, Duplicates.RPD.TP, Peak.Area.TN, Conc.ugL.TN, Notes.TN, Flag.TN, Duplicates.RPD.TN, Sample.Type, row.numbers)
    #row.numbers is kept so add_rollingcharts will work. Cup.Number is kept for update_data_from_rolling.

dups_rc= dups_rc|>
  filter(Sample.Type!='Unknown')|>
  select(!Sample.Type)

#then just feed dups_rc into the add_rollingcharts function??
rc_duplicates <- add_rollingcharts(rolling_chart = duplicates, data_file = dups_rc)

# make a plot of the dups that is saved in the preliminary plots folder

a <- build_rolling_plot(df = rc_duplicates, analyte = "TP", metric = "Duplicates.RPD")

b <- build_rolling_plot(df = rc_duplicates, analyte = "TN", metric = "Duplicates.RPD")

combined_fig <- manipulateWidget::combineWidgets(a, b, height = 1000)
                                                 
htmlwidgets::saveWidget(combined_fig, paste0(here(),"/preliminary_plots/Dups_", runDate,".html"), selfcontained = TRUE)

# update the flag and notes from the mdl function
data_dups2 <- update_data_from_rolling(
  lachat_data = data_dups2,
    rolling_export = rc_duplicates)

#take off cup number now that we're done using it:
rc_duplicates= rc_duplicates|>
  select(!Cup.Number)


cat('Remember to look at the rolling dups plot in preliminary plots!')

```

```{r Spike Recovery}

#EVENTUALLY: ADD AN OPTION TO ADD A FLAG TO EVERY SINGLE SPIKED SAMPLE WITHOUT NEEDING TO ENTER ALL ROW NUMBERS - Done

#spike recovery for spiked samples:
data_spikes <- data_dups2

# make a vector of all the row numbers for the spiked samples. Check if you want spike blanks in this too. - removed spiked blanks
spike_row_numbers <- data_spikes |>
  filter(grepl("SP", Sample.ID, ignore.case = TRUE)) |>
  filter(grepl("bl", Sample.ID, ignore.case = TRUE)==F)
  
# USE sp_row_numbers WHICH IS A LIST OF ALL THE ROW NUMBERS FOR SPIKES. 
sp_row_numbers <- spike_row_numbers$row.numbers


expected.spike.change.TP= (ss.conc * ss.std)/(ss.std+ss.sample)
expected.spike.change.TN= expected.spike.change.TP * n.factor

spike_recovery <- data_spikes|>
      filter(grepl("Sp", Sample.Type,ignore.case = T))|>
      # make a column of just sample ids without the dups
      mutate(clean_ids = gsub("[^0-9.-]", "", Sample.ID))|>
      # select the columns we care about
      select(Detection.Date, Sample.Type, Sample.ID, clean_ids ,Conc.ugL.TN, Conc.ugL.TP)|>
      group_by(Sample.Type, clean_ids)|>
      # look at summarise across 
      summarise(Spikes.PctRecovery.TN = (diff(Conc.ugL.TN)/expected.spike.change.TN*100),
                Spikes.PctRecovery.TP = (diff(Conc.ugL.TP)/expected.spike.change.TP*100))|>
                        ## SOMETIMES CALCULATES INCORRECTLY- MAYBE DOESN'T DISTINGUISH BETWEEN "ORIGINAL MINUS SPIKE" AND "SPIKE MINUS ORIGINAL"?
                        ## we want this to be calculated as (spike minus original) / expected change * 100
  ungroup()

data_spikes_merge <- data_spikes|>
   mutate(clean_ids = gsub("[^0-9.-]", "", Sample.ID))|>
  merge(spike_recovery, by = c("clean_ids", "Sample.Type"), all = T)|>
  mutate(dup_id = case_when(
    grepl("SP", Sample.ID, ignore.case = TRUE) ~ "duplicate",  # e.g. "DUP S23" or "S23 DUP"
    TRUE ~ "original"  # e.g. "S23"
  ))|> # label original vs. duplicate based on presence of "DUP" anywhere in Sample.ID
  # set the RPD to NA for the original sample. 
  mutate(Spikes.PctRecovery.TN = ifelse(grepl("Sp", Sample.Type, ignore.case = T) & dup_id == "original", NA, Spikes.PctRecovery.TN),
         Spikes.PctRecovery.TP = ifelse(grepl("Sp", Sample.Type, ignore.case = T) & dup_id == "original", NA, Spikes.PctRecovery.TP))
 

# Flag if spike recovery is out of acceptable range (80-120%)
# Only applied to the spiked sample row, not the original sample.

rn_flag_TP <- data_spikes_merge$row.numbers[
  !is.na(data_spikes_merge$Spikes.PctRecovery.TP) &
  (data_spikes_merge$Spikes.PctRecovery.TP < 80 | data_spikes_merge$Spikes.PctRecovery.TP > 120)
]
rn_flag_TN <- data_spikes_merge$row.numbers[
  !is.na(data_spikes_merge$Spikes.PctRecovery.TN) &
  (data_spikes_merge$Spikes.PctRecovery.TN < 80 | data_spikes_merge$Spikes.PctRecovery.TN > 120)
]

if (length(rn_flag_TP) > 0) {
  data_spikes_merge <- append_flag_note(df = data_spikes_merge, rn = rn_flag_TP, analyte = "TP",
                                        flag_num = 4, note_text = "Recovery outside acceptable range (80-120%).")
}
if (length(rn_flag_TN) > 0) {
  data_spikes_merge <- append_flag_note(df = data_spikes_merge, rn = rn_flag_TN, analyte = "TN",
                                        flag_num = 4, note_text = "Recovery outside acceptable range (80-120%).")
}

spikes <- data_spikes_merge|>
  filter(grepl("Sp", Sample.Type,ignore.case = T))|>
  select(row.numbers,Sample.ID, clean_ids, dup_id, Sample.Type, Conc.ugL.TP, Spikes.PctRecovery.TP, Flag.TP, Notes.TP,
         Conc.ugL.TN, Spikes.PctRecovery.TN, Flag.TN, Notes.TN) |>
  arrange(row.numbers)


View(spikes)
print(paste('Expected TP concentration change =',expected.spike.change.TP))
print(paste('Expected TN concentration change =',expected.spike.change.TN))


cat("Review percent recovery of the spiked samples- target is 80-120% recovery.\n",
    "This threshold is less strict if samples are near the detection limit or if the sample concentration and spike amount are poorly matched.\n",
    "If you suspect this is the case, add a note.\n")
rl <- readline("Do you want to add any notes? (y/n): ")
while (rl=='y'|rl=='Y') {
  repeat {
    rn <- readline('Enter the row number or numbers you want to add a note to- eg. 3,4,5 or sp_row_numbers for all spikes: ')
    if (nchar(trimws(rn)) > 0) break # add this because it would skip over entering the row numbers
  }
  print(flags)
  f= as.numeric(readline('Enter the flag number (see list above): '))
  type= readline('Which analyte needs a note? (TN, TP): ')
  note= as.character(readline('What do you want to say?: '))
  
  # add the notes for spiked samples
  data_spikes_merge <- append_flag_note(df = data_spikes_merge, rn = rn, analyte = type, flag_num = f, note_text = note)
  
# View the data frame 
  
  spikes <- data_spikes_merge|>
  filter(grepl("Sp", Sample.Type,ignore.case = T))|>
  select(row.numbers,Sample.ID, clean_ids, dup_id, Sample.Type, Conc.ugL.TP, Spikes.PctRecovery.TP, Flag.TP, Notes.TP,
         Conc.ugL.TN, Spikes.PctRecovery.TN, Flag.TN, Notes.TN) |>
  arrange(row.numbers)

View(spikes)
  
  rl= readline('Do you want to add any more notes? (y/n): ')
}

#add just the spikes (not the originals) to the rolling charts:
spikes_rc= data_spikes_merge|>
  filter(grepl("Sp", Sample.ID,ignore.case = T))|>
  select(Detection.Date, Detection.Time, Sample.ID, Peak.Area.TP, Conc.ugL.TP, Notes.TP, Flag.TP, Spikes.PctRecovery.TP, Peak.Area.TN, Conc.ugL.TN, Notes.TN, Flag.TN, Spikes.PctRecovery.TN, Sample.Type, row.numbers, Cup.Number)
    #row.numbers is kept so add_rollingcharts will work. Cup.Number needed for update_data_from_rolling.

spikes_rc= spikes_rc|>
  filter(Sample.Type!='Unknown')|>
  select(!Sample.Type)

#then just feed spikes_rc into the add_rollingcharts function??
rc_spiked.samples <- add_rollingcharts(rolling_chart = spiked.samples, data_file = spikes_rc)

# make a plot of the dups that is saved in the preliminary plots folder


#EVENTUALLY: EDIT SO ROWS FLAGGED AS 8 ARE EXCLUDED FROM PLOTTING - Done - still getting newly flagged rows in the plot

# make a new data frame that sets values flagged as 8 to NA but only for plotting

rc_spiked_plot_df <- rc_spiked.samples|>
  mutate(Conc.ugL.TN = ifelse(grepl("7|8", Flag.TN), NA, Conc.ugL.TN),
    Conc.ugL.TP = ifelse(grepl("7|8", Flag.TP), NA, Conc.ugL.TP))

# Make plots
a <- build_rolling_plot(df = rc_spiked_plot_df, analyte = "TP", metric = "Spikes.PctRecovery")

b <- build_rolling_plot(df = rc_spiked_plot_df, analyte = "TN", metric = "Spikes.PctRecovery")

combined_fig <- manipulateWidget::combineWidgets(a, b, height = 1000)
                                                 
htmlwidgets::saveWidget(combined_fig, paste0(here(),"/preliminary_plots/SpikeRecovery_", runDate,".html"), selfcontained = TRUE)

# update the flag and notes from the mdl function
data_spikes_merge <- update_data_from_rolling(
  lachat_data = data_spikes_merge,
    rolling_export = rc_spiked.samples)

#take off cup number now that we're done using it:
rc_spiked.samples= rc_spiked.samples|>
  select(!Cup.Number)


cat('Remember to look at the rolling spikes plot in preliminary plots!')

#

```

```{r Reruns}

data_reruns <- data_spikes_merge
View(data_reruns)
cat("Review the data before saving. This section flags reruns and sets keep/discard for each analyte.\n")

rl <- readline("Do you need to flag any samples that were rerun (without diluting)? (y/n): ")
while (rl == "y" | rl == "Y") {
  repeat {
    rerun.sample <- readline("Enter the sample number from the clean_ids column for the sample that was rerun: ")
    if (nchar(trimws(rerun.sample)) > 0) break # add this because it would skip over entering the row numbers
  }
  comparison <- data_reruns[data_reruns$clean_ids == as.numeric(rerun.sample), ] |>
    select(row.numbers, Sample.ID, Cup.Number, Conc.ugL.TP, Conc.ugL.TN, Notes.TP, Flag.TP, Notes.TN, Flag.TN)
  View(comparison)

  rn.original <- readline("Enter the row number of the original sample (from row.numbers): ")
  rn.rerun    <- readline("Enter the row number of the rerun (from row.numbers): ")

  cat("Which result do you want to use as the true result?\n",
      " 1: original  (rerun discarded for all analytes)\n",
      " 2: rerun  (original discarded for all analytes)\n",
      " 3: rerun for single analyte\n",
      "Preference is to use the rerun unless something is obviously wrong.\n")
  decision <- readline("Enter 1, 2, or 3: ")

  if (decision == "1") {
    # keep original — discard rerun for both analytes
    data_reruns <- append_flag_note(df = data_reruns, rn = rn.rerun, analyte = "TN TP",
                                    flag_num = 8, note_text = "Discard data- use results from original sample.")
  }
  
  if (decision == "2") {
    # keep original — discard rerun for both analytes
    data_reruns <- append_flag_note(df = data_reruns, rn = rn.original, analyte = "TN TP",
                                    flag_num = 8, note_text = "Discard data- use results from rerun.")
  }

  if (decision == "3") {
    x <- readline("Use rerun for which analyte- TN or TP?: ")
    print(flags)
    flag <- as.numeric(readline("Enter the flag number for the discarded original result: "))

    if (toupper(x) %in% c("TN", "N")) {
      # keep rerun TN — discard original TN, discard rerun TP
      data_reruns <- append_flag_note(df = data_reruns, rn = rn.original, analyte = "TN",
                                      flag_num = flag, note_text = "Discard data- use results from rerun.")
      data_reruns <- append_flag_note(df = data_reruns, rn = rn.rerun,    analyte = "TP",
                                      flag_num = 8,    note_text = "Discard data- use results from original sample.")
    } else if (toupper(x) %in% c("TP", "P")) {
      # keep rerun TP — discard original TP, discard rerun TN
      data_reruns <- append_flag_note(df = data_reruns, rn = rn.original, analyte = "TP",
                                      flag_num = flag, note_text = "Discard data- use results from rerun.")
      data_reruns <- append_flag_note(df = data_reruns, rn = rn.rerun,    analyte = "TN",
                                      flag_num = 8,    note_text = "Discard data- use results from original sample.")
    }
  }

  View(data_reruns)
  rl <- readline("Do any more reruns need to be flagged? (y/n): ")
}

```

```{r Dilutions}

#THIS SECTION IS A PAIN WHEN DILUTION FACTOR IS INCLUDED IN SAMPLE ID. 

View(data_reruns)   #helpful to have open in the background in case of naming issues

data_dilutions <- data_reruns

# make a smaller data frame with just the dilutions 
# get a data frame of the original and the dilution
qw <- data_dilutions |>
  filter(grepl("dil",Sample.ID, ignore.case=T)) |>
  select(clean_ids)

# make a data frame of the duplicates and original
comparison <- data_dilutions |>
  filter(clean_ids %in% qw[["clean_ids"]],
         Sample.Type %in% c("Unknown", "Duplicate Set", "Spike Set"))

View(comparison|>
       select(clean_ids, row.numbers, everything()))

cat("NOTE ON PROCESSING DILUTIONS:\n
    If you ran a dilution of a sample from a previous run, choose one of the 'dye' rows when prompted to enter the row of the original sample.")

rl <- readline("Did you need to dilute any samples during this run? (y/n): ")
while (rl == "y" | rl == "Y") {
  dilution.sample <- as.numeric(readline("Enter the sample number from the clean_ids column for the sample that was diluted: "))
  # just the samples that match the id
  indv_samp <- data_dilutions[data_dilutions$clean_ids == dilution.sample, ]
  View(indv_samp|>
         select(row.numbers, everything()))
  
  #NOTE FOR WHEN UPDATING TO READ IN DIGITIZED DILUTIONS SHEET:
  #instead of row.numbers, have it search for cup number for the original and the dilution
  #that way it can automatically loop through all dilutions instead of requiring manual entry of row.number
  
  rn.original <- readline("Enter the row number of the original sample (from row.numbers): ")
  rn.dilution  <- readline("Enter the row number of the dilution (from row.numbers): ")
  v.sample <- as.numeric(readline("Enter the volume of sample used for the dilution (uL): "))
  v.water  <- as.numeric(readline("Enter the volume of water used for the dilution (uL): "))
  dilution.factor <- (v.sample + v.water) / v.sample

  # back-calculate the undiluted concentration from the diluted row
  rn.dil.num <- as.numeric(rn.dilution)
  data_dilutions$Conc.ugL.TN[data_dilutions$row.numbers == rn.dil.num] <-
    data_dilutions$Conc.ugL.TN[data_dilutions$row.numbers == rn.dil.num] * dilution.factor
  data_dilutions$Conc.ugL.TP[data_dilutions$row.numbers == rn.dil.num] <-
    data_dilutions$Conc.ugL.TP[data_dilutions$row.numbers == rn.dil.num] * dilution.factor

  x <- toupper(readline("Which analyte was out of range- TN, TP, or TN TP?: "))

  if (x %in% c("TN", "N")) {
    # discard original TN (out of range), discard dilution TP (not needed)
    data_dilutions <- append_flag_note(df = data_dilutions, rn = rn.original, analyte = "TN",
                                       flag_num = 7, note_text = "Discard data- TN out of range.")
    data_dilutions <- append_flag_note(df = data_dilutions, rn = rn.dilution,  analyte = "TP",
                                       flag_num = 8, note_text = "Discard data- dilution not needed for TP.")
  } else if (x %in% c("TP", "P")) {
    # discard original TP (out of range), discard dilution TN (not needed)
    data_dilutions <- append_flag_note(df = data_dilutions, rn = rn.original, analyte = "TP",
                                       flag_num = 7, note_text = "Discard data- TP out of range.")
    data_dilutions <- append_flag_note(df = data_dilutions, rn = rn.dilution,  analyte = "TN",
                                       flag_num = 8, note_text = "Discard data- dilution not needed for TN.")
  } else if (x == "TN TP") {
    # discard original for both analytes
    data_dilutions <- append_flag_note(df = data_dilutions, rn = rn.original, analyte = "TN TP",
                                       flag_num = 7, note_text = "Discard data- out of range.")
  }
  
  comparison <- data_dilutions |>
  filter(clean_ids %in% qw[["clean_ids"]],
         Sample.Type %in% c("Unknown", "Duplicate Set", "Spike Set"))

  View(comparison|>
       select(clean_ids, row.numbers, everything()))
  rl <- readline("Do any more dilutions need to be addressed? (y/n): ")
}
```

```{r Final Review}
#other notes/flags:
data_final <- data_dilutions

# make a data frame of the duplicates and dilutions to make sure that everything is flagged as it should be

check_dil <- data_final |>
  filter(Sample.Type %in% c("Unknown", "Duplicate Set", "Spike Set")) |>
  select(clean_ids, Sample.ID, Cup.Number, Sample.Type,
         Conc.ugL.TP, Flag.TP, Notes.TP,
         Conc.ugL.TN, Flag.TN, Notes.TN) |>
  filter(!grepl("S", Cup.Number, ignore.case = TRUE)) |>
  filter(!grepl("bl|che|sp", Sample.ID, ignore.case = TRUE)) |>
   group_by(clean_ids)|>
  summarise(n = n()) |>
  filter(n >1)

# make a data frame of the clean_ids 
View(data_final |>
       filter(clean_ids %in% check_dil[[1]])|>
       select(row.numbers, clean_ids, Sample.Type, Sample.ID, Cup.Number,
              Conc.ugL.TP, Flag.TP, Notes.TP, Conc.ugL.TN, Flag.TN, Notes.TN, everything())|>
       filter(Sample.Type %in% c("Unknown", "Duplicate Set", "Spike Set")))

print("Review data frame of clean id's that have dups. Make sure all dups, spikes, dilutions, and reruns look correct.")
  
rl= readline('Do you have any other notes to add to these samples? (y/n): ')
while (rl=='y'|rl=='Y') {
  rn= readline('Enter the row number or numbers you want to flag (eg. 3,4,5): ') 
  var= readline('Which solute needs the flag? (TN, TP): ')
  print(flags)
  f= as.numeric(readline('Enter the flag number (see list above): '))
  note= as.character(readline('Enter a comment for the Notes column: '))
  
  # use the flag function to add notes and flags
  data_final <- append_flag_note(df = data_final, rn = rn, analyte = var, flag_num = f, note_text = note)
  
  View(data_final |>
       filter(clean_ids %in% check_dil[[1]])|>
       select(row.numbers, clean_ids, Sample.Type, Sample.ID, Cup.Number,
              Conc.ugL.TP, Flag.TP, Notes.TP, Conc.ugL.TN, Flag.TN, Notes.TN, everything())|>
       filter(Sample.Type %in% c("Unknown", "Duplicate Set", "Spike Set")))
  rl= readline('Do you have any other notes to add to these samples? (y/n): ')
}


#SOMEDAY: ADD A SECTION THAT DISPLAYS ANYTHING OUT OF RANGE OF CAL CURVE (>120% OF TOP STANDARD CONC) TO CHECK THAT ALL NECESSARY DILUTIONS WERE DONE

# View the entire dataset and add notes if needed
data_final= data_final[order(data_final$row.numbers),]   #makes it easier to compare to rack map
View(data_final |>
 select(row.numbers, everything()))
print("Now review the full data set and make sure everything looks correct.")
rl= readline('Do you have any other notes + flags to add? (y/n): ')
while (rl=='y'|rl=='Y') {
  rn= readline('Enter the row number or numbers you want to flag (eg. 3,4,5): ') 
  var= readline('Which solute needs the flag? (TN, TP): ')
  print(flags)
  f= as.numeric(readline('Enter the flag number (see list above): '))
  note= as.character(readline('Enter a comment for the Notes column: '))
  
  # use the flag function to add notes and flags
  data_final <- append_flag_note(df = data_final, rn = rn, analyte = var, flag_num = f, note_text = note)
  
  View(data_final |>
 select(row.numbers, everything()))
  rl= readline('Do you need to add any more notes? (y/n): ')
}
```

```{r Write files}

# Save updated rolling charts
check.25.standards= rc_check.25.standards |>
  select(-expected.conc)
digest.checks= rc_digest.checks |>
  select(-expected.conc)
digested.blanks= rc_digested.blanks |>
  select(-expected.conc)
spiked.blanks= rc_spiked.blanks |>
  select(-expected.conc)
duplicates= rc_duplicates
spiked.samples= rc_spiked.samples
save(check.25.standards, digest.checks, digested.blanks, spiked.blanks, duplicates, spiked.samples,
     file = "MDLs/Rolling.Checks.TNTP.RData")

# Full QAQC file with all rows and flag/note columns
data_final= data_final[order(data_final$row.numbers),]
write.csv(data_final, file = paste0(getwd(),"/Results/TNTP/TNTP Results_withQAQC_", runDate, "_", project, ".csv"), row.names = FALSE)

# I don't think this should be part of this script. To me this makes more sense in the flagging script after this. 
      #It's something I will need to do for other projects. -F
# Cleaned file: samples only, no QC rows, no dilution/rerun duplicates
cleaned <- data_final |>
  filter(Sample.Type %in% c("Unknown", "Duplicate Set", "Spike Set")) |>
  select(clean_ids, Sample.ID, Cup.Number, Sample.Type,
         Conc.ugL.TP, Flag.TP, Notes.TP,
         Conc.ugL.TN, Flag.TN, Notes.TN) |>
  filter(!grepl("S", Cup.Number, ignore.case = TRUE)) |>
  filter(!grepl("bl|che|sp", Sample.ID, ignore.case = TRUE)) |> # it looks like the spikes are removed. Is this right? yes!
  # remove rows flagged as discard (flag 7 = out of range, flag 8 = discard)
  mutate(
    Conc.ugL.TN = ifelse(grepl("7|8", Flag.TN), NA, Conc.ugL.TN),
    Conc.ugL.TP = ifelse(grepl("7|8", Flag.TP), NA, Conc.ugL.TP),
    Flag.TN = as.character(Flag.TN),
    Flag.TP = as.character(Flag.TP)
  )|>
  pivot_longer(cols = c(Conc.ugL.TN, Flag.TN, Notes.TN, Conc.ugL.TP, Flag.TP, Notes.TP),
    names_to = c(".value", "analyte"),
    names_pattern = "^(.+)\\.(TN|TP)$"
) |> 
 # drop_na(Conc.ugL) |> # drop any of the rows that have NA for concentration|>
pivot_wider(names_from = analyte,
    names_sep = ".",
    values_from = c(Conc.ugL, Flag, Notes)) 

# how to handle dups? Average later?
#lab dups have never been averaged (at least during Dexter's time here)
#added this to give option me the option to delete dups from the list for other projects
rl= readline("Do you want to retain lab dups in the cleaned data file? (y/n): ")
if (rl=='n'|rl=='N'){cleaned= cleaned[grepl('DUP',cleaned$Sample.ID, ignore.case = F)==F,]}


# make the date the run date
cleaned$Date <- runDate

write.csv(cleaned, file = paste0(getwd(),"/Results/TNTP/TNTP Results_", runDate, "_", project, ".csv"), row.names = FALSE)

print(paste("Done! Results files are saved in", paste0(getwd(),'/Results/TNTP')))
```
