---
title: "Chemisty_QAQC_2025_2025"
format: html
editor: 
  markdown: 
    wrap: 72
---

# Chemistry QAQC script

Post-processing 2025 data.

This .qmd is a set of functions designed to compile all of the data from
Lachat and TICTOC runs. As of 2025, this script 1.) processes and
compiles data for totals, solubles, and DOC reviewed by the Stream Team
analytical lab chemist 2.) identifies any samples that were run multiple
times 3.) Condenses reruns and dilutions into one sample 4.) Associates
run samples with collected samples and time collected (Nutrients &
Metals Times) 5.) outputs a dataset for totals, solubles, and DOC 6.)
combines totals, solubles, and DOC into one dataframe

Still needs to do: 7.) sets all samples \<0 to 0 8.) adds flags based on
flagging conventions 9.) reference a functions script to condense this
code to be more manageable

Each section of this script (totals, DOC, compilation) was designed to
be separate scripts to run individually for data processing. They are
presented here in this QAQC document as an example of what was done to
compile this data. This .qmd will not run! (as of 2SEP2026)

This code in this .qmd was developed in 2026 by KKH with the assistance
of Claude Sonnet 5, Anthropic, 2026.

## Lachat

Starting with Lachat Totals and Solubles

```{r}
pacman::p_load(tidyverse, gsheet, arsenal, here, lubridate, janitor, readr, purrr, stringr, tidyr)
select <- dplyr::select
folder_path <- paste0(here(), "/Results/TNTP")

# URL for the rack map Google Sheet
totals_rackmap_url <- "https://docs.google.com/spreadsheets/d/1J5UtMFPWTNcb6QhcdCjEs1JUf5FtyiNm-WKGvCAtLAM/edit?gid=0#gid=0"

# ---- Load the rack map ONCE, outside the per-file loop ----
# ASSUMPTION: after clean_names(), the rack map has columns `vial_number`,
# `batch`, and `sample_name`. If your actual sheet uses different column
# names (e.g. "Vial #", "Batch #"), update the names referenced below.
rack_map <- gsheet::gsheet2tbl(totals_rackmap_url) |>
  clean_names()

# ---- Helper functions ----

# Returns the first non-missing value in a vector, or NA if all missing.
coalesce_first <- function(x) {
  non_na <- x[!is.na(x)]
  if (length(non_na) == 0) NA else non_na[1]
}

# Concatenates all non-missing, DISTINCT values in a vector with a space
# separator. Returns NA if all values are missing. If both rows have the
# same flag (e.g. "7" and "7"), it appears only once in the result.
combine_flags <- function(x) {
  vals <- unique(x[!is.na(x)])
  if (length(vals) == 0) return(NA_character_)
  paste(vals, collapse = " ")
}

# Returns the smaller of the non-missing values in a vector, or NA if all missing.
min_ignore_na <- function(x) {
  vals <- x[!is.na(x)]
  if (length(vals) == 0) return(NA_real_)
  min(vals)
}

# Checks ONLY conc_ug_l_tn and conc_ug_l_tp for real conflicts (two
# different non-missing values) within a sample_name + lab_dup group.
find_coalesce_conflicts <- function(data, group_col = c("sample_name", "lab_dup"), file_path) {

  data |>
    # 1. Select the cup column along with the others
    dplyr::select(all_of(group_col), any_of(c("cup_number", "cup")), conc_ug_l_tn, conc_ug_l_tp) |>
    mutate(across(everything(), as.character)) |>
    # 2. Pivot ONLY the concentration columns (keep group cols and cup cols intact)
    pivot_longer(
      cols = c(conc_ug_l_tn, conc_ug_l_tp), 
      names_to = "column", 
      values_to = "value"
    ) |>
    filter(!is.na(value)) |>
    # 3. Group ONLY by your original group columns and the concentration column name
    group_by(across(all_of(group_col)), column) |>
    # 4. Collapse the unique cup numbers inside summarise
    summarise(
      n_distinct_values = n_distinct(value),
      conflicting_values = paste(unique(value), collapse = " | "),
      # Paste all unique cup numbers associated with this group/conflict
      cup_number = paste(unique(na.omit(pick(any_of(c("cup_number", "cup")))[[1]])), collapse = " | "),
      .groups = "drop"
    ) |>
    filter(n_distinct_values > 1) |>
    mutate(file = file_path)
}

process_one_file <- function(file_path) {

  message("Reading: ", file_path)

  # Extract the date and batch number from the filename
  # (e.g. "TNTP Results_2025-08-21_LTREB_2025_batch1.csv")
  file_date <- as.Date(str_extract(file_path, "\\d{4}-\\d{2}-\\d{2}"), format = "%Y-%m-%d")
  batch_num <- as.numeric(str_extract(file_path, "(?<=batch)\\d+"))

  data <- read_csv(
    file_path,
    col_types = cols(
      Sample.ID   = col_character(),
      Sample.Type = col_character(),
      Flag.TN     = col_character(),
      Flag.TP     = col_character(),
      Notes.TN    = col_character(),
      Notes.TP    = col_character(),
      Date        = col_character(),
      clean_ids   = col_double(),
      Cup.Number  = col_double(),
      Conc.ugL.TN = col_double(),
      Conc.ugL.TP = col_double()
    ),
    show_col_types = FALSE
  ) |>
    clean_names()

  # ---- 1. Identify duplicates and dilutions from sample_id text ----
  data <- data |>
    mutate(
      lab_dup = if_else(str_detect(sample_id, regex("dup", ignore_case = TRUE)),
                         "DUP", NA_character_),
      lab_dil = if_else(str_detect(sample_id, regex("dil", ignore_case = TRUE)),
                         "DIL", NA_character_)
    ) |>
    filter(!sample_id %in% c("NO2", "NO3"))

  # ---- 2. Assign sample_name from the rack map ----
  # Joined on cup_number = vial_number, restricted to this file's batch.
  rack_map_this_batch <- rack_map |>
    filter(totals_run_number == batch_num) |>
    dplyr::select(vial_number, sample_name, res_site, date_collected, rep, depth)

  data <- data |>
    left_join(rack_map_this_batch, by = c("cup_number" = "vial_number"))

  unmatched <- data |>
    filter(is.na(sample_name)) |>
    mutate(file = file_path, batch = batch_num)

  n_unmatched <- nrow(unmatched)
  if (n_unmatched > 0) {
    warning(paste0(n_unmatched, " row(s) in ", file_path,
                    " did not match a rack map sample_name for batch ", batch_num,
                    " (check cup_number/vial_number and batch alignment)."))
  }

  # ---- 3. Combined dup/dilution column ----
  data <- data |>
    mutate(
      dup_dil_flag = case_when(
        !is.na(lab_dup) & !is.na(lab_dil) ~ "DUP_DIL",
        !is.na(lab_dup) ~ "DUP",
        !is.na(lab_dil) ~ "DIL",
        TRUE ~ NA_character_
      )
    )

  # ---- Check for conc_ug_l_tn / conc_ug_l_tp conflicts BEFORE coalescing ----
  conflicts <- find_coalesce_conflicts(data, group_col = c("sample_name", "lab_dup"), file_path = file_path) |> 
    mutate(date = file_date, batch = batch_num)

  # ---- 4. Coalesce reruns within this file ----
  # Grouped by sample_name + lab_dup, so a dup and its non-dup counterpart
  # are NEVER merged together -- they stay as two separate rows. A dilution
  # merges with whichever group it belongs to (dilutions aren't flagged as dup).
  # - flag_tn / flag_tp: combine ALL flags from both rows (space-separated), kept separate
  # - cup_number: take the SMALLER of the two values
  # - everything else (including conc_ug_l_tn / conc_ug_l_tp): first non-missing value
  data_coalesced <- data |>
    group_by(sample_name, lab_dup) |>
    mutate(
      flag_tn = combine_flags(flag_tn),
      flag_tp = combine_flags(flag_tp),
      cup_number = min_ignore_na(cup_number),
      across(-any_of(c("flag_tn", "flag_tp", "cup_number", "sample_name", "lab_dup")), coalesce_first)
    ) |>
    slice(1) |>
    ungroup() |>
    mutate(date = file_date, batch = batch_num)

  list(data = data_coalesced, conflicts = conflicts, unmatched = unmatched)
}

# ---- Loop over all files and combine ----
files <- list.files(
  path = folder_path,
  pattern = "^TNTP Results_\\d{4}-\\d{2}-\\d{2}.*\\.csv$",
  full.names = TRUE
)

if (length(files) == 0) {
  warning("There are no csv files in the directory you listed")
} else {
  results <- map(files, process_one_file)

  all_data      <- map_dfr(results, "data")
  all_conflicts <- map_dfr(results, "conflicts")
  all_unmatched <- map_dfr(results, "unmatched")

# Normalize sample_name BEFORE batch preference filtering, so grouping matches
# what coalesce_all_totals() will use downstream.
all_data <- all_data |>
  dplyr::mutate(sample_name = stringr::str_squish(sample_name))

  # ---- Batch preference: prefer batch 6 over batch 9 when both exist ----
  # for the same sample_name/lab_dup group ----
  batch_pref_dropped <- all_data |>
    group_by(sample_name, lab_dup) |>
    filter(any(batch == 6) & any(batch == 9) & batch == 9) |>
    ungroup()

  if (nrow(batch_pref_dropped) > 0) {
    warning(paste(nrow(batch_pref_dropped),
                   "row(s) dropped from batch 9 in favor of batch 6",
                   "(sample_name/lab_dup present in both batches)."))
  }

  all_data <- all_data |>
    group_by(sample_name, lab_dup) |>
    group_modify(function(g, key) {
      if (any(g$batch == 6) & any(g$batch == 9)) {
        g <- g |> filter(batch == 6)
      }
      g
    }) |>
    ungroup()

  if (nrow(all_conflicts) > 0) {
    warning(paste(nrow(all_conflicts),
                   "conc_ug_l_tn/conc_ug_l_tp conflict(s) found during coalescing across files.",
                   "Review the `all_conflicts` data frame -- the first non-missing value was kept by default."))
  }

  if (nrow(all_unmatched) > 0) {
    warning(paste(nrow(all_unmatched),
                   "row(s) across all files did not match a rack map sample_name.",
                   "Review the `all_unmatched` data frame."))
  }
}

all_conflicts

all_unmatched <- all_unmatched |>
  dplyr::select(batch, cup_number, sample_id, sample_type, date, notes_tn, notes_tp)

coalesce_all_totals <- function(df, batch_col, date_col, dup_col = "dup_dil_flag", key_col = "sample_name") {
  analytes <- names(df) |> stringr::str_subset("^conc_ug_l_") |> stringr::str_remove("^conc_ug_l_")
  analyte_col_map <- lapply(analytes, function(a) {
    cols <- names(df)[grepl(paste0("(^conc_ug_l_", a, "$)|(_", a, "$)"), names(df))]
    names(cols) <- cols
    cols
  })
  names(analyte_col_map) <- analytes
  analyte_cols <- unique(unlist(analyte_col_map))
  list_all_cols <- c(batch_col, date_col)
  other_cols <- setdiff(names(df), c(key_col, dup_col, list_all_cols, analyte_cols))
  is_dup <- function(x) x %in% c("DUP", "DUP_DIL", "DIL")

  merged <- df |>
    dplyr::group_by(dplyr::across(dplyr::all_of(key_col))) |>
    dplyr::group_modify(function(g, key) {
      out <- tibble::tibble(.rows = 1)
      conflict_rows <- list()

      for (col in other_cols) {
        vals <- g[[col]]
        non_na <- vals[!is.na(vals)]
        out[[col]] <- if (length(non_na) == 0) vals[NA_integer_] else non_na[1]
      }

      batch_vals <- unique(stats::na.omit(g[[batch_col]]))
      out[[batch_col]] <- if (length(batch_vals) == 0) NA_character_ else paste(batch_vals, collapse = " | ")

      date_vals <- unique(stats::na.omit(as.character(g[[date_col]])))
      out[[date_col]] <- if (length(date_vals) == 0) NA_character_ else paste(date_vals, collapse = " | ")

is_dil <- function(x) x %in% c("DIL")
is_dup <- function(x) x %in% c("DUP")

for (a in analytes) {
  conc_col <- paste0("conc_ug_l_", a)
  analyte_cols_this <- analyte_col_map[[a]]

  primary_rows <- g[is.na(g[[dup_col]]), , drop = FALSE]
  dil_rows     <- g[is_dil(g[[dup_col]]), , drop = FALSE]
  dup_rows     <- g[is_dup(g[[dup_col]]), , drop = FALSE]

  selected_row <- NULL
  conflict <- FALSE
  conflicting_values <- NULL

  for (candidate_rows in list(primary_rows, dil_rows, dup_rows)) {
    if (!is.null(selected_row)) break
    if (conc_col %in% names(candidate_rows)) {
      idx <- which(!is.na(candidate_rows[[conc_col]]))
      if (length(idx) > 0) {
        vals <- candidate_rows[[conc_col]][idx]
        if (length(unique(vals)) > 1) { conflict <- TRUE; conflicting_values <- unique(vals) }
        selected_row <- candidate_rows[idx[1], , drop = FALSE]
      }
    }
  }

  if (is.null(selected_row)) {
    for (col in analyte_cols_this) {
      out[[col]] <- if (is.numeric(g[[col]])) NA_real_
        else if (is.integer(g[[col]])) NA_integer_
        else if (inherits(g[[col]], "Date")) as.Date(NA)
        else NA
    }
  } else {
    for (col in analyte_cols_this) out[[col]] <- selected_row[[col]]
  }

  if (conflict) {
    conflict_rows[[length(conflict_rows) + 1]] <- tibble::tibble(
      analyte = a,
      conflicting_values = paste(conflicting_values, collapse = " | "),
      batches = paste(batch_vals, collapse = " | "),
      dates = paste(date_vals, collapse = " | ")
    )
  }
}

      out$.conflicts <- list(if (length(conflict_rows) > 0) dplyr::bind_rows(conflict_rows) else tibble::tibble())
      out
    }) |>
    dplyr::ungroup()

  conflicts <- merged |>
    dplyr::select(dplyr::all_of(key_col), .conflicts) |>
    tidyr::unnest(.conflicts, keep_empty = TRUE) |>
    dplyr::filter(!is.na(analyte))

  merged <- merged |> dplyr::select(-.conflicts)

  ordered_cols <- c(key_col, other_cols, batch_col, date_col, unname(unlist(analyte_col_map)))
  ordered_cols <- ordered_cols[ordered_cols %in% names(merged)]
  merged <- merged |> dplyr::select(dplyr::all_of(ordered_cols))

  list(data = merged, conflicts = conflicts)
}


all_data_dup_coalesce1 <- all_data |>
  rename(sample_id_totals = sample_id,
         cup_number_totals = cup_number,
         sample_type_totals = sample_type,
         date_run_totals = date,
         batch_totals = batch) |>
  dplyr::mutate(
    sample_name = stringr::str_squish(sample_name),
    dup_dil_flag = dplyr::na_if(dup_dil_flag, "")
  )
  
totals_result <- coalesce_all_totals(all_data_dup_coalesce1, batch_col = "batch_totals", date_col = "date_run_totals")
totals_coalesced <- totals_result$data
totals_conflicts <- totals_result$conflicts

unique(totals_coalesced$res_site)

sites <- c("B50", "B100", "B200", "B175", "C101", "C50", "C301", "C501", "C51", "F50", "F20", "F199.8", "F199.9", "F701", "F702", "F703", "F704", "F705", "F706", "F707", "F200", "B40", "F10.1", "F10.2", "F100", "F100.1", "F20.1", "F20.9", "F30.1", "F30.9", "F45.1")

totals_data <- totals_coalesced |>
  dplyr::select(sample_name, sample_id_totals, sample_type_totals, date_run_totals, batch_totals, cup_number_totals, conc_ug_l_tn, conc_ug_l_tp, notes_tn, notes_tp, flag_tn, flag_tp, res_site) |> 
  mutate(sample_name = str_to_upper(sample_name)) |> 
  filter(res_site %in% sites) |> 
  filter(!is.na(conc_ug_l_tp) | !is.na(conc_ug_l_tn)) |> 
  unique()

howmany <- unique(totals_data$sample_name)

test <- totals_data |> group_by(sample_name) %>%
  filter(n() > 1) %>% 
  ungroup() # there are still 2 samples that are not coalescing. I think this is because the cup numbers are not the same. Frustrating. 

```

Solubles. Copied from the totals, should be the same/similar, I hope!
#totals has been edited, this may need to be updated

```{r solubles}

pacman::p_load(tidyverse, gsheet, arsenal, here, lubridate, janitor, readr, purrr, stringr, tidyr)

folder_path <- paste0(here(), "/Results/Solubles")

# URL for the rack map Google Sheet
solubles_rackmap_url <- "https://docs.google.com/spreadsheets/d/1R19yrWLrRCrEkE3Dg2g1D9ZjAsW3C3KMBuD0R9jFMRQ/edit?usp=sharing"

# ---- Load the rack map ONCE, outside the per-file loop ----
rack_map <- gsheet::gsheet2tbl(solubles_rackmap_url) |>
  clean_names()

# ---- Helper functions ----

# Returns the first non-missing value in a vector, or NA if all missing.
coalesce_first <- function(x) {
  non_na <- x[!is.na(x)]
  if (length(non_na) == 0) NA else non_na[1]
}

# Concatenates all non-missing, DISTINCT values in a vector with a space
# separator. Returns NA if all values are missing. If both rows have the
# same flag (e.g. "7" and "7"), it appears only once in the result.
combine_flags <- function(x) {
  vals <- unique(x[!is.na(x)])
  if (length(vals) == 0) return(NA_character_)
  paste(vals, collapse = " ")
}

# Returns the smaller of the non-missing values in a vector, or NA if all missing.
min_ignore_na <- function(x) {
  vals <- x[!is.na(x)]
  if (length(vals) == 0) return(NA_real_)
  min(vals)
}

# Checks all conc_ug_l_* columns (auto-detected -- works for NH4/PO4/NO3,
# or any other analyte set) for real conflicts (two different non-missing
# values) within a sample_name + lab_dup group.
find_coalesce_conflicts <- function(data, group_col = c("sample_name", "lab_dup"), file_path) {

  conc_cols <- names(data)[str_detect(names(data), "^conc_ug_l_")]

  data |>
    # 1. Select the cup column along with the others
    dplyr::select(all_of(group_col), any_of(c("cup_number", "cup")), all_of(conc_cols)) |>
    mutate(across(everything(), as.character)) |>
    # 2. Pivot ONLY the concentration columns (keep group cols and cup cols intact)
    pivot_longer(
      cols = all_of(conc_cols),
      names_to = "column",
      values_to = "value"
    ) |>
    filter(!is.na(value)) |>
    # 3. Group ONLY by your original group columns and the concentration column name
    group_by(across(all_of(group_col)), column) |>
    # 4. Collapse the unique cup numbers inside summarise
    summarise(
      n_distinct_values = n_distinct(value),
      conflicting_values = paste(unique(value), collapse = " | "),
      cup_number = paste(unique(na.omit(pick(any_of(c("cup_number", "cup")))[[1]])), collapse = " | "),
      .groups = "drop"
    ) |>
    filter(n_distinct_values > 1) |>
    mutate(file = file_path)
}

process_one_file <- function(file_path) {

  message("Reading: ", file_path)

  # Extract the date and batch number from the filename
  # (e.g. "Solubles Results_2025-08-21_LTREB_2025_batch1.csv")
  file_date <- as.Date(str_extract(file_path, "\\d{4}-\\d{2}-\\d{2}"), format = "%Y-%m-%d")
  batch_num <- as.numeric(str_extract(file_path, "(?<=batch)\\d+"))

  data <- read_csv(
    file_path,
    col_types = cols(
      Date        = col_character(),
      clean_ids   = col_double(),
      Cup.Number  = col_double(),
      .default    = col_guess()
    ),
    show_col_types = FALSE
  ) |>
    clean_names() |>
    # Force flag_* and notes_* columns to character. col_guess() can infer
    # these as numeric in files where they only ever contain bare digits
    # (or are blank), and as character in files with combined/non-numeric
    # values (e.g. "7 3" from combine_flags()). That mismatch breaks
    # map_dfr()/bind_rows() later when stacking files together.
    mutate(
      across(starts_with("flag_"), as.character),
      across(starts_with("notes_"), as.character)
    )

  # ---- 1. Identify duplicates and dilutions from sample_id text ----
  data <- data |>
    mutate(
      lab_dup = if_else(str_detect(sample_id, regex("dup", ignore_case = TRUE)),
                         "DUP", NA_character_),
      lab_dil = if_else(str_detect(sample_id, regex("dil", ignore_case = TRUE)),
                         "DIL", NA_character_), 
      lab_spk = if_else(str_detect(sample_id, regex("sp", ignore_case = TRUE)),
                         "SPK", NA_character_)
    ) |>
    filter(!sample_id %in% c("NO2", "NO3"))

  # ---- 2. Assign sample_name from the rack map ----
  # Joined on cup_number = hole_position, restricted to this file's batch.
  rack_map_this_batch <- rack_map |>
    filter(lachat_run_number == batch_num) |>
    dplyr::select(hole_position, sample_name, res_site, date_collected, rep, depth)

  data <- data |>
    left_join(rack_map_this_batch, by = c("cup_number" = "hole_position"))

  unmatched <- data |>
    filter(is.na(sample_name)) |>
    mutate(file = file_path, batch = batch_num)

  n_unmatched <- nrow(unmatched)
  if (n_unmatched > 0) {
    warning(paste0(n_unmatched, " row(s) in ", file_path,
                    " did not match a rack map sample_name for batch ", batch_num,
                    " (check cup_number/hole_position and batch alignment)."))
  }

  # ---- 3. Combined dup/dilution column ----
  data <- data |>
    mutate(
      dup_dil_flag = case_when(
        !is.na(lab_dup) & !is.na(lab_dil) ~ "DUP_DIL",
        !is.na(lab_dup) ~ "DUP",
        !is.na(lab_dil) ~ "DIL",
        TRUE ~ NA_character_
      )
    )

  # ---- Check for conc_ug_l_* conflicts BEFORE coalescing ----
  # NOTE: batch is included here via mutate() right below.
  conflicts <- find_coalesce_conflicts(data, group_col = c("sample_name", "lab_dup", "lab_spk"), file_path = file_path) |>
    mutate(date = file_date, batch = batch_num)

  # ---- 4. Coalesce reruns within this file ----
  # Grouped by sample_name + lab_dup, so a dup and its non-dup counterpart
  # are NEVER merged together -- they stay as two separate rows. A dilution
  # merges with whichever group it belongs to (dilutions aren't flagged as dup).
  # - flag_* (flag_nh4/flag_po4/flag_no3): combine ALL flags from both rows
  #   (space-separated, de-duplicated), each kept separate
  # - cup_number: take the SMALLER of the two values
  # - everything else (including conc_ug_l_*): first non-missing value
  # data_coalesced <- data |>

data_coalesced <- data |>
  group_by(sample_name, lab_dup) |>
  mutate(
    across(starts_with("flag_"), function(x) {
      data_col <- stringr::str_remove(cur_column(), "^flag_")
      
      # if there's no matching data column, fall back to old behavior
      if (!data_col %in% names(pick(everything()))) {
        return(combine_flags(x))
      }
      
      data_vals <- pick(all_of(data_col))[[1]]
      valid <- !is.na(data_vals)
      
      if (sum(valid) == 0) {
        NA_character_          # neither row has data -> flag doesn't matter
      } else if (sum(valid) == 1) {
        x[valid]               # only one row has data -> keep just that flag
      } else {
        combine_flags(x[valid]) # both have data -> combine as before
      }
    }),
    cup_number = min_ignore_na(cup_number),
    across(
      -c(starts_with("flag_"), any_of(c("cup_number", "sample_name", "lab_dup"))),
      coalesce_first
    )
  ) |>
  slice(1) |>
  ungroup() |>
  mutate(date = file_date, batch = batch_num)

combine_if_data <- function(x, data_vals, combine_fn) {
  valid <- !is.na(data_vals)
  if (sum(valid) == 0) {
    NA_character_
  } else if (sum(valid) == 1) {
    x[valid]
  } else {
    combine_fn(x[valid])
  }
}

combine_notes <- function(x) {
  x <- x[!is.na(x)]
  if (length(x) == 0) return(NA_character_)
  paste(x, collapse = "|")
}

data_coalesced <- data |>
  group_by(sample_name, lab_dup) |>
  mutate(
    across(
      c(starts_with("flag_"), starts_with("notes_")),
      function(x) {
        analyte <- stringr::str_remove(cur_column(), "^(flag_|notes_)")
        data_col <- paste0("conc_ug_l_", analyte)
        
        data_vals <- pick(everything())[[data_col]]   # <-- fixed
        
        combine_fn <- if (stringr::str_starts(cur_column(), "flag_")) {
          combine_flags
        } else {
          combine_notes
        }
        
        combine_if_data(x, data_vals, combine_fn)
      }
    ),
    cup_number = min_ignore_na(cup_number),
    across(
      -c(starts_with("flag_"), starts_with("notes_"),
         any_of(c("cup_number", "sample_name", "lab_dup"))),
      coalesce_first
    )
  ) |>
  slice(1) |>
  ungroup() |>
  mutate(date = file_date, batch = batch_num)
#possible issues with this, trying a new option
  #   group_by(sample_name, lab_dup) |>
  #   mutate(
  #     across(starts_with("flag_"), combine_flags),
  #     cup_number = min_ignore_na(cup_number),
  #     across(
  #       -c(starts_with("flag_"), any_of(c("cup_number", "sample_name", "lab_dup"))),
  #       coalesce_first
  #     )
  #   ) |>
  #   slice(1) |>
  #   ungroup() |>
  #   mutate(date = file_date, batch = batch_num)

  list(data = data_coalesced, conflicts = conflicts, unmatched = unmatched)
}

# ---- Loop over all files and combine ----
# (This was missing -- process_one_file() was defined but never actually run
# across your files, so all_data/all_conflicts/all_unmatched didn't exist yet.)
files <- list.files(
  path = folder_path,
  pattern = "^Solubles Results_\\d{4}-\\d{2}-\\d{2}.*\\.csv$",
  full.names = TRUE
)

if (length(files) == 0) {
  warning("There are no csv files in the directory you listed")
} else {
  results <- map(files, process_one_file)

  all_data      <- map_dfr(results, "data")
  all_conflicts <- map_dfr(results, "conflicts")
  all_unmatched <- map_dfr(results, "unmatched")

  if (nrow(all_conflicts) > 0) {
    warning(paste(nrow(all_conflicts),
                   "conflict(s) found in concentration values during coalescing across files.",
                   "Review `all_conflicts` -- the first non-missing value was kept by default."))
  }

  if (nrow(all_unmatched) > 0) {
    warning(paste(nrow(all_unmatched),
                   "row(s) across all files did not match a rack map sample_name.",
                   "Review `all_unmatched`."))
  }
}

# ---- View everything ----
# View(all_data)

# NOTE: fixed from `unmatched` (didn't exist outside a single file's call)
# to `all_unmatched` (combined across all files). Also changed notes_tn/notes_tp
# (Totals column names) to notes_nh4/notes_po4/notes_no3 -- let me know if
# these aren't the right Solubles column names.
all_unmatched <- all_unmatched |>
  dplyr::select(batch, cup_number, sample_id, sample_type, date, notes_nh4, notes_po4, notes_no3)
# View(all_unmatched)

# NOTE: fixed from `conflicts` (single-file only) to `all_conflicts` (combined)
# View(all_conflicts |>
#        dplyr::select(batch, cup_number, sample_name, lab_dup, column, n_distinct_values, conflicting_values, file))

#now keep only the sites that we want
unique(all_data$res_site)
sites <- c("B50", "B100", "B200", "B175", "C101", "C50", "C301", "C501", "C51", "F50", "F20", "F199.8", "F199.9", "F701", "F702", "F703", "F704", "F705", "F706", "F707", "F200", "F100")

dataforcoalesce <- all_data |> 
  rename(sample_id_solubles = sample_id, 
         cup_number_solubles = cup_number, 
         sample_type_solubles = sample_type, 
         date_run_solubles = date, 
         batch_solubles = batch) 

coalesce_all_solubles <- function(df, batch_col, date_col, dup_col = "dup_dil_flag", key_col = "sample_name") {
  analytes <- names(df) |> stringr::str_subset("^conc_ug_l_") |> stringr::str_remove("^conc_ug_l_")
  analyte_col_map <- lapply(analytes, function(a) {
    cols <- names(df)[grepl(paste0("(^conc_ug_l_", a, "$)|(_", a, "$)"), names(df))]
    names(cols) <- cols
    cols
  })
  names(analyte_col_map) <- analytes
  analyte_cols <- unique(unlist(analyte_col_map))
  list_all_cols <- c(batch_col, date_col)
  other_cols <- setdiff(names(df), c(key_col, dup_col, list_all_cols, analyte_cols))
  is_dup <- function(x) x %in% c("DUP", "DUP_DIL", "DIL")

  merged <- df |>
    dplyr::group_by(dplyr::across(dplyr::all_of(key_col))) |>
    dplyr::group_modify(function(g, key) {
      out <- tibble::tibble(.rows = 1)
      conflict_rows <- list()

      for (col in other_cols) {
        vals <- g[[col]]
        non_na <- vals[!is.na(vals)]
        out[[col]] <- if (length(non_na) == 0) vals[NA_integer_] else non_na[1]
      }

      batch_vals <- unique(stats::na.omit(g[[batch_col]]))
      out[[batch_col]] <- if (length(batch_vals) == 0) NA_character_ else paste(batch_vals, collapse = " | ")

      date_vals <- unique(stats::na.omit(as.character(g[[date_col]])))
      out[[date_col]] <- if (length(date_vals) == 0) NA_character_ else paste(date_vals, collapse = " | ")

      for (a in analytes) {
        conc_col <- paste0("conc_ug_l_", a)
        analyte_cols_this <- analyte_col_map[[a]]
        primary_rows <- g[is.na(g[[dup_col]]), , drop = FALSE]
        dup_rows <- g[is_dup(g[[dup_col]]), , drop = FALSE]
        selected_row <- NULL
        conflict <- FALSE
        conflicting_values <- NULL

        if (conc_col %in% names(primary_rows)) {
          idx <- which(!is.na(primary_rows[[conc_col]]))
          if (length(idx) > 0) {
            vals <- primary_rows[[conc_col]][idx]
            if (length(unique(vals)) > 1) { conflict <- TRUE; conflicting_values <- unique(vals) }
            selected_row <- primary_rows[idx[1], , drop = FALSE]
          }
        }
        if (is.null(selected_row) && conc_col %in% names(dup_rows)) {
          idx <- which(!is.na(dup_rows[[conc_col]]))
          if (length(idx) > 0) {
            vals <- dup_rows[[conc_col]][idx]
            if (length(unique(vals)) > 1) { conflict <- TRUE; conflicting_values <- unique(vals) }
            selected_row <- dup_rows[idx[1], , drop = FALSE]
          }
        }

        if (is.null(selected_row)) {
          for (col in analyte_cols_this) {
            out[[col]] <- if (is.numeric(g[[col]])) NA_real_
              else if (is.integer(g[[col]])) NA_integer_
              else if (inherits(g[[col]], "Date")) as.Date(NA)
              else NA
          }
        } else {
          for (col in analyte_cols_this) out[[col]] <- selected_row[[col]]
        }

        if (conflict) {
          conflict_rows[[length(conflict_rows) + 1]] <- tibble::tibble(
            analyte = a,
            conflicting_values = paste(conflicting_values, collapse = " | "),
            batches = paste(batch_vals, collapse = " | "),
            dates = paste(date_vals, collapse = " | ")
          )
        }
      }

      out$.conflicts <- list(if (length(conflict_rows) > 0) dplyr::bind_rows(conflict_rows) else tibble::tibble())
      out
    }) |>
    dplyr::ungroup()

  conflicts <- merged |>
    dplyr::select(dplyr::all_of(key_col), .conflicts) |>
    tidyr::unnest(.conflicts, keep_empty = TRUE) |>
    dplyr::filter(!is.na(analyte))

  merged <- merged |> dplyr::select(-.conflicts)

  ordered_cols <- c(key_col, other_cols, batch_col, date_col, unname(unlist(analyte_col_map)))
  ordered_cols <- ordered_cols[ordered_cols %in% names(merged)]
  merged <- merged |> dplyr::select(dplyr::all_of(ordered_cols))

  list(data = merged, conflicts = conflicts)
}


sol_result <- coalesce_all_solubles(
  dataforcoalesce,
  batch_col = "batch_solubles",
  date_col  = "date_run_solubles")

sol_coalesced <- sol_result$data
sol_conflicts <- sol_result$conflicts #I AM HERE! I need to go through all the duplicates in the solubles now. Totals is very close. 

solubles_data <- sol_coalesced |> 
  dplyr::select(sample_name, sample_id_solubles, sample_type_solubles, date_run_solubles, batch_solubles, cup_number_solubles, conc_ug_l_po4, conc_ug_l_nh4, conc_ug_l_no3, conc_ug_l_no3, flag_po4, flag_nh4, flag_no3, flag_no3, notes_nh4, notes_po4, notes_no3, res_site) |> 
  mutate(sample_name = str_to_upper(sample_name)) |> 
  filter(res_site %in% sites) |> 
  unique() |>  #make sure there aren't exact duplicates
  filter(!is.na(conc_ug_l_no3) | !is.na(conc_ug_l_nh4) | !is.na(conc_ug_l_po4)) #make sure there aren't any samples listed with no data available whatsoever

```

Time to bring the data together. Left join the totals data with the
solubles data based on sample ID.

```{r}
solubles_data <- solubles_data |> mutate(sample_name = stringr::str_squish(sample_name))
totals_data <- totals_data |> mutate(sample_name = stringr::str_squish(sample_name))

# write.csv(solubles_data, "~/GitHubRepos/CareyLabVT/Chemistry-QAQC-Frances/Results/Compiled_Results/solubles_runsfor2025.csv")
# 
# write.csv(totals_data, "~/GitHubRepos/CareyLabVT/Chemistry-QAQC-Frances/Results/Compiled_Results/totals_runsfor2025.csv")

#Saving this for a 3rd script! Leaving code here for now. 
totsol <- full_join(solubles_data, totals_data, by = c("sample_name"))
totsol_anti <- anti_join(solubles_data, totals_data, by = c("sample_name"))

totsol_anti2 <- anti_join(totals_data, solubles_data, by = c("sample_name")) |> 
  separate(sample_name, into = c("res_site", "date", "depth", "rep"),
           sep = "\\s+", remove = FALSE) |> 
  filter(res_site != "F100.1", 
         batch_totals != "0", 
         depth != "0.25")
```

There are too many matches, I'm going to work through by matching each
individually with the nutrients and metals times sheet

```{r}
#LTREB datetimes
datetimes_gsheet <- gsheet::gsheet2tbl("https://docs.google.com/spreadsheets/d/1MbSN2G_NyKyXQUEzfMHmxEgZYI_s-VDVizOZM8qPpdg/edit?gid=0#gid=0")

ltreb_datetimes <- datetimes_gsheet |> 
  mutate(Site = as.character(Site)) |> 
  select(1:11) |> 
  clean_names() |> 
  filter(!is.na(totals_tntp)|!is.na(solubles)) |> 
  select(1:6) |> 
  mutate(res_site = paste0(str_sub(reservoir, 1, 1), site), 
         depth = as.numeric(depth_m), 
         date = ymd(date), 
         time2 = ifelse(is.na(time), hms(hours = 12), time)) |> 
  mutate(time = hms::as_hms(time2)) |> 
   filter(date > "2024-01-01") |> 
  filter(date < "2026-04-01") |> 
select(-reservoir, -site, -depth_m, -time2)
  

#now set up totals so we can match to this sheet. Need to separate based on reservoir, site, date, depth. rep is irrelevant for now. 

try <- totals_data |> 
separate(sample_name, into = c("res_site", "date", "depth", "rep"),
           sep = "\\s+", remove = FALSE) |> 
  mutate(depth = as.numeric(depth), 
         date = dmy(date))


# check to see which samples did not join up!
eek <- full_join(ltreb_datetimes, try)

anti_totals <- anti_join(ltreb_datetimes, try) |> 
filter(date > "2024-12-31") |> 
filter(date < "2026-01-01") |> #excluding anything that is not from 2025
filter(depth != 0.25) #DXE's samples are not included on the LTREB samples collected sheet. This may be something that we want to fix in the future but I don't want to deal with it now. 

#see which samples did not match that existed in samples run! There are 2 that could be problems, everything else run in batch 0 by Dexter, hoping those got fixed already! 
anti2_totals <- anti_join(try, ltreb_datetimes)|> 
filter(depth != 0.25) #|> 


# filter(res_site != "F100.1") |> 
# filter(res_site != "F20")

#this is to set up a sheet that has all of the days that we were in the field!
help <- ltreb_datetimes |> select(res_site, date) |> 
  unique()

#now set up solubles so we can match to this sheet. Need to separate based on reservoir, site, date, depth. rep is irrelevant for now. 

try_sol <- solubles_data |> 
separate(sample_name, into = c("res_site", "date", "depth", "rep"),
           sep = "\\s+", remove = FALSE) |> 
  mutate(depth = as.numeric(depth), 
         date = dmy(date)) |> 
mutate(sample_name = stringr::str_squish(sample_name))

# ltreb_datetimes <- ltreb_datetimes |> 
# mutate(sample_name = stringr::str_squish(sample_name))

eek_sol <- full_join(ltreb_datetimes, try_sol)
anti_sol <- anti_join(ltreb_datetimes, try_sol, by = c("date", "res_site", "depth")) |> filter(date > "2024-12-31") |> 
filter(date < "2026-01-01") |> 
filter(res_site != "F100.1") |> 
filter(date != "2025-04-16") |> 
filter(date != "2025-02-26") #DWH ran these already


anti2_sol <- anti_join(try_sol, ltreb_datetimes, by = c("date", "res_site", "depth"))

#Dexter has already published samples for CCR 50 26feb25 and 16apr25 in the 2024 rendition
```

## TICTOC

Combine TICTOC

```{r}
pacman::p_load(tidyverse, gsheet, arsenal, here, lubridate, janitor, readr, purrr, stringr, tidyr, readxl)
select <- dplyr::select
folder_path <- paste0(here(), "/Results/TICTOC")

# URL for the rack map Google Sheet
tictoc_rackmap_url <- "https://docs.google.com/spreadsheets/d/1xqC1nvlrWYKvvtlIm-Pb2Rp0P-KBXipoDgoRb49pVdo/edit?usp=sharing"

# ---- Load the rack map ONCE, outside the per-file loop ----
# ASSUMPTION: after clean_names(), the rack map has columns `vial_number`,
# `batch`, and `sample_name`. If your actual sheet uses different column
# names (e.g. "Vial #", "Batch #"), update the names referenced below.
rack_map <- gsheet::gsheet2tbl(tictoc_rackmap_url) |>
  clean_names()

# ---- Helper functions ----

# Returns the first non-missing value in a vector, or NA if all missing.
fill_na_by_sample <- function(data, 
                               sample_col = "sample_name",
                               value_cols = c("tic_mean_of_2_reps", "tc_mean_of_2_reps", 
                                              "toc_mean_of_2_reps", "t_nb_mean_of_2_reps")) {
  data |>
    group_by(across(all_of(sample_col))) |>
    mutate(
      across(all_of(value_cols), ~ if_else(is.na(.x), coalesce_first(.x), .x))
    ) |>
    ungroup()
}

coalesce_first <- function(x) {
  non_na <- x[!is.na(x)]
  if (length(non_na) == 0) NA else non_na[1]
}
# # Concatenates all non-missing, DISTINCT values in a vector with a space
# # separator. Returns NA if all values are missing. If both rows have the
# # same flag (e.g. "7" and "7"), it appears only once in the result.
# combine_flags <- function(x) {
#   vals <- unique(x[!is.na(x)])
#   if (length(vals) == 0) return(NA_character_)
#   paste(vals, collapse = " ")
# }
# 
# # Returns the smaller of the non-missing values in a vector, or NA if all missing.
# min_ignore_na <- function(x) {
#   vals <- x[!is.na(x)]
#   if (length(vals) == 0) return(NA_real_)
#   min(vals)
# }

# Checks ONLY conc_ug_l_tn and conc_ug_l_tp for real conflicts (two
# different non-missing values) within a sample_name + lab_dup group.
find_coalesce_conflicts <- function(data, 
                                     group_col = c("sample_name", "dup_spike"), 
                                     value_cols = c("tic_mean_of_2_reps", "tc_mean_of_2_reps", 
                                                    "toc_mean_of_2_reps", "t_nb_mean_of_2_reps"),
                                     file_path) {
  data |>
    # 1. Select the cup column along with the others
    dplyr::select(all_of(group_col), any_of(c("hole_position")), all_of(value_cols), date_started) |>
    mutate(across(everything(), as.character)) |>
    # 2. Pivot ONLY the concentration columns (keep group cols and cup cols intact)
    pivot_longer(
      cols = all_of(value_cols), 
      names_to = "column", 
      values_to = "value"
    ) |>
    filter(!is.na(value)) |>
    # 3. Group ONLY by your original group columns and the concentration column name
    group_by(across(all_of(group_col)), column) |>
    # 4. Collapse the unique cup numbers inside summarise
    summarise(
      n_distinct_values = n_distinct(value),
      conflicting_values = paste(unique(value), collapse = " | "),
      # Paste all unique cup numbers associated with this group/conflict
      cup_number = paste(unique(na.omit(pick(any_of(c("hole_position", "hole_pos", "cup")))[[1]])), collapse = " | "),
      date_started = paste(unique(na.omit(date_started)), collapse = " | "),
      .groups = "drop"
    ) |>
    filter(n_distinct_values > 1) |>
    mutate(file = file_path)
}

process_one_file <- function(file_path) {

  message("Reading: ", file_path)

  # Extract the batch number from the filename
  #date is not included because there are multiple dates in each batch
  # (e.g. "Results TIC TC 2025 Batch 1.csv")
  # file_date <- as.Date(str_extract(file_path, "\\d{4}-\\d{2}-\\d{2}"), format = "%Y-%m-%d")
batch_num <- as.numeric(str_extract(file_path, "(?i)(?<=Batch\\s)\\d+"))

  data1 <- readxl::read_excel(
    file_path,
    sheet = 1
  ) |>
  clean_names() |>
  mutate(
    date_started              = as.character(date_started),
    lachat_run_number         = as.numeric(lachat_run_number),
    tic_toc_run_number        = as.numeric(tic_toc_run_number),
    hole_position              = as.character(hole_position),
    sample_number              = as.character(sample_number),
    tic_mean_of_2_reps         = as.numeric(tic_mean_of_2_reps),
    tc_mean_of_2_reps          = as.numeric(tc_mean_of_2_reps),
    toc_mean_of_2_reps         = as.numeric(toc_mean_of_2_reps),
    t_nb_mean_of_2_reps        = as.numeric(t_nb_mean_of_2_reps),
    analyst_code                = as.character(analyst_code),
    notes                       = as.character(notes)
  )
  
  #0a. remove extraneous rows
data <- data1 |> 
  filter(if_any(c(tic_mean_of_2_reps, tc_mean_of_2_reps, toc_mean_of_2_reps, t_nb_mean_of_2_reps), ~ !is.na(.x))) |> 
  mutate(hole_position = as.numeric(hole_position), 
         date_started = ymd(date_started), 
         lachat_run_number = as.numeric(lachat_run_number), 
         tictoc_run_number = as.numeric(tic_toc_run_number))
#merging on hole position, not sample number!

#commented out so that we can link to sample names first in case the dup or spike came from somewhere other than 5/10/15/20 

 # ---- 1. Identify duplicates and dilutions from sample_id text ---- 
  # data <- data |>
  #   mutate(
  #     lab_dup = if_else(str_detect(sample_id, regex("dup", ignore_case = TRUE)),
  #                        "DUP", NA_character_),
  #     lab_dil = if_else(str_detect(sample_id, regex("dil", ignore_case = TRUE)),
  #                        "DIL", NA_character_)
  #   ) |>
  #   filter(!sample_id %in% c("NO2", "NO3"))

  # ---- 2. Assign sample_name from the rack map ----
  # Joined on cup_number = vial_number, restricted to this file's batch.

  rack_map_this_batch <- rack_map |>
    filter(lachat_run_number == batch_num)  |>
  mutate(hole_position = as.numeric(hole_position), 
         date_started = mdy(date_started), 
         lachat_run_number = as.numeric(lachat_run_number), 
         tictoc_run_number = as.numeric(tictoc_run_number))
    # dplyr::select(vial_number, sample_name, res_site, date_collected, rep, depth)

  data2 <- full_join(rack_map_this_batch, data, by = c("hole_position" = "hole_position", "date_started" = "date_started", "lachat_run_number" = "lachat_run_number", "tictoc_run_number" = "tictoc_run_number"))

  unmatched <- data2 |>
    filter(is.na(sample_number.y)) |>
    mutate(file = file_path, batch = batch_num)

  n_unmatched <- nrow(unmatched)
  if (n_unmatched > 0) {
    warning(paste0(n_unmatched, " row(s) in ", file_path,
                    " did not match a rack map sample_name for batch ", batch_num,
                    " (check cup_number/vial_number and batch alignment)."))
  }

  # ---- 3. Combined dup/dilution column ----
  data <- data2 |>
    mutate(
      dup_spk_flag = case_when(
        dup_spike == "duplicate" ~ "DUP",
        dup_spike == "spike" ~ "SPK",
        TRUE ~ NA_character_
      )
    )

  # ---- Check for conc_ug_l_tn / conc_ug_l_tp conflicts BEFORE coalescing ----
  conflicts <- find_coalesce_conflicts(data, group_col = c("sample_name", "dup_spike"), file_path = file_path) 

  # ---- 4. Coalesce reruns within this file ----
  # Grouped by sample_name + lab_dup, so a dup and its non-dup counterpart
  # are NEVER merged together -- they stay as two separate rows. A dilution
  # merges with whichever group it belongs to (dilutions aren't flagged as dup).
  # - flag_tn / flag_tp: combine ALL flags from both rows (space-separated), kept separate
  # - cup_number: take the SMALLER of the two values
  # - everything else (including conc_ug_l_tn / conc_ug_l_tp): first non-missing value
 data_coalesced <- data |>
    fill_na_by_sample() |> #this gets data to all the right places, but now it's duplicated
 distinct(sample_name, tic_mean_of_2_reps, tc_mean_of_2_reps, 
           toc_mean_of_2_reps, t_nb_mean_of_2_reps, .keep_all = TRUE)
    
  # group_by(sample_name, dup_spike) |>
  # mutate(
  #   notes = combine_flags(notes.y),
  #   across(-any_of(c("notes", "cup_number", "sample_name", "dup_spike")), coalesce_first)
  # ) |>
  # slice(1) |>
  # ungroup()

  list(data = data_coalesced, conflicts = conflicts, unmatched = unmatched)
}

#process_one_file("~/GitHubRepos/CareyLabVT/Chemistry-QAQC-Frances/Results/TICTOC/Results TIC TC 2025 Batch 1.xlsx")

# ---- Loop over all files and combine ----
files <- list.files(
  path = folder_path,
  pattern = "^Results TIC TC \\d{4} Batch \\d+\\.xlsx$",
  full.names = TRUE
)

if (length(files) == 0) {
  warning("There are no csv files in the directory you listed")
} else {
  results <- map(files, process_one_file)

  all_data      <- map_dfr(results, "data")
  all_conflicts_TICTOC <- map_dfr(results, "conflicts")
  all_unmatched <- map_dfr(results, "unmatched")

  if (nrow(all_conflicts_TICTOC) > 0) {
    warning(paste(nrow(all_conflicts_TICTOC),
                   "conc_ug_l_tn/conc_ug_l_tp conflict(s) found during coalescing across files.",
                   "Review the `all_conflicts` data frame -- the first non-missing value was kept by default."))
  }

  if (nrow(all_unmatched) > 0) {
    warning(paste(nrow(all_unmatched),
                   "row(s) across all files did not match a rack map sample_name.",
                   "Review the `all_unmatched` data frame."))
  }
}

all_conflicts_TICTOC

batch1_TICTOC <- all_data |> filter(lachat_run_number == 1)

# all_unmatched <- all_unmatched |>
#   dplyr::select(batch, hole_position, sample_name, date_started, notes.x, notes.y)

#removed the coalesce step because there shouldn't be any need to coalesce TICTOC data


sites <- c("B50", "B100", "B200", "B175", "C101", "C50", "C301", "C501", "C51", "F50", "F20", "F199.8", "F199.9", "F701", "F702", "F703", "F704", "F705", "F706", "F707", "F200", "B40", "F10.1", "F10.2", "F100", "F20.1", "F20.9", "F30.1", "F30.9", "F45.1")

tictoc_data_problems <- all_data |> 
  filter(is.na(dup_spike)) |> 
  filter(!is.na(sample_name)) |> 
  add_count(sample_name) |> 
   filter(n > 1)
 
 tictoc_data <- all_data |> 
  filter(is.na(dup_spike)) |> 
  filter(!is.na(sample_name))

howmany <- unique(tictoc_data$sample_name)

test <- tictoc_data |> group_by(sample_name) %>%
  filter(n() > 1) %>% 
  ungroup() # there is one sample that was run twice. Really not sure how this happened. 
```

## Compile all chem data

Compile totals, solubles and DOC together.

```{r}
pacman::p_load(tidyverse, gsheet, arsenal, here, lubridate, janitor, readr, purrr, stringr, tidyr)
select <- dplyr::select
```

```{r}
solubles <- read.csv("~/GitHubRepos/CareyLabVT/Chemistry-QAQC-Frances/Results/Compiled_Results/solubles_runsfor2025.csv")

totals <- read.csv("~/GitHubRepos/CareyLabVT/Chemistry-QAQC-Frances/Results/Compiled_Results/totals_runsfor2025.csv")

tictoc <- read.csv("~/GitHubRepos/CareyLabVT/Chemistry-QAQC-Frances/Results/Compiled_Results/tictoc_runsfor2025.csv")
```

This was cleaned up individually prior to coming into this .qmd. A
version of this code exists in the TICTOC and Lachat compilation .qmds.
Keeping a slightly more in depth version here to make sure everything
still looks ok.

```{r}
#LTREB datetimes
datetimes_gsheet <- gsheet::gsheet2tbl("https://docs.google.com/spreadsheets/d/1MbSN2G_NyKyXQUEzfMHmxEgZYI_s-VDVizOZM8qPpdg/edit?gid=0#gid=0")

ltreb_datetimes <- datetimes_gsheet |> 
  mutate(Site = as.character(Site)) |> 
  select(1:11) |> 
  clean_names() |> 
  filter(!is.na(totals_tntp)|!is.na(solubles)) |> 
  select(1:7) |> 
  mutate(res_site = paste0(str_sub(reservoir, 1, 1), site), 
         depth = as.numeric(depth_m), 
         date = ymd(date), 
         time2 = ifelse(is.na(time), hms(hours = 12), time)) |> 
  mutate(time = hms::as_hms(time2)) |> 
   filter(date > "2024-01-01") |> 
  filter(date < "2026-04-01") |> 
select(-reservoir, -site, -depth_m, -time2)
  

#now set up totals so we can match to this sheet. Need to separate based on reservoir, site, date, depth. rep is irrelevant for now. 

totals_data <- totals |> 
separate(sample_name, into = c("res_site", "date", "depth", "rep"),
           sep = "\\s+", remove = FALSE) |> 
  mutate(depth = as.numeric(depth), 
         date = dmy(date))


# check to see which samples did not join up!
eek <- full_join(ltreb_datetimes, totals_data)

anti_totals <- anti_join(ltreb_datetimes, totals_data) |> 
filter(date > "2024-12-31") |> 
filter(date < "2026-01-01") |> #excluding anything that is not from 2025
filter(depth != 0.25) #DXE's samples are not included on the LTREB samples collected sheet. This may be something that we want to fix in the future but I don't want to deal with it now. 

#see which samples did not match that existed in samples run! There are 2 that could be problems, everything else run in batch 0 by Dexter, hoping those got fixed already! 
anti2_totals <- anti_join(totals_data, ltreb_datetimes)|> 
filter(depth != 0.25) #|> 


#now set up solubles so we can match to this sheet. Need to separate based on reservoir, site, date, depth. rep is irrelevant for now. 

try_sol <- solubles |> 
separate(sample_name, into = c("res_site", "date", "depth", "rep"),
           sep = "\\s+", remove = FALSE) |> 
  mutate(depth = as.numeric(depth), 
         date = dmy(date)) |> 
mutate(sample_name = stringr::str_squish(sample_name))

# ltreb_datetimes <- ltreb_datetimes |> 
# mutate(sample_name = stringr::str_squish(sample_name))

eek_sol <- full_join(ltreb_datetimes, try_sol)
anti_sol <- anti_join(ltreb_datetimes, try_sol, by = c("date", "res_site", "depth")) |> filter(date > "2024-12-31") |> 
filter(date < "2026-01-01") |> 
filter(res_site != "F100.1") |> 
filter(date != "2025-04-16") |> 
filter(date != "2025-02-26") #DWH ran these already


anti2_sol <- anti_join(try_sol, ltreb_datetimes, by = c("date", "res_site", "depth"))

#Dexter has already published samples for CCR 50 26feb25 and 16apr25 in the 2024 rendition

#And now TICTOC
try_tictoc <- tictoc |> 
separate(sample_name, into = c("res_site", "date", "depth", "rep"),
           sep = "\\s+", remove = FALSE) |> 
  mutate(depth = as.numeric(depth), 
         date = dmy(date))

eek_tictoc <- full_join(ltreb_datetimes, try_tictoc)
anti_tictoc_nuts <- anti_join(ltreb_datetimes, try_tictoc) |> 
filter(date > "2024-12-31") |> 
filter(date < "2026-01-01")
  

anti_tictoc_run <- anti_join(try_tictoc, ltreb_datetimes) |> 
filter(date > "2024-12-31") |> 
filter(date < "2026-01-01") |> 
  select(c(sample_name, lachat_run_number, tictoc_run_number, hole_position, date_started))
```

\`\`\`{r} tictoc_join \<- try_tictoc \|\> select(c(sample_name,
res_site, date, depth, rep, lachat_run_number, tictoc_run_number,
tic_mean_of_2_reps, tc_mean_of_2_reps, toc_mean_of_2_reps,
t_nb_mean_of_2_reps, notes.y)) \|\> mutate(sample_name =
stringr::str_squish(sample_name))

sol_join \<- try_sol \|\> select(c(sample_name, res_site, date, depth,
rep, batch_solubles, conc_ug_l_po4, flag_po4, conc_ug_l_nh4, flag_nh4,
conc_ug_l_no3, flag_no3)) \|\> mutate(sample_name =
stringr::str_squish(sample_name))

totals_join \<- totals_data \|\> select(c(sample_name, res_site, date,
depth, rep, batch_totals, conc_ug_l_tn, flag_tn, notes_tn, conc_ug_l_tp,
flag_tp, notes_tp))

all_sol \<- full_join(tictoc_join, sol_join)

all_join \<- ltreb_datetimes \|\> full_join(all_sol) \|\>
full_join(totals_join) \|\> filter(!is.na(sample_name)) \|\>
mutate(Flag_DateTime = 0, Flag_TP_ugL = 0, Flag_TN_ugL = 0,
Flag_NO3NO2_ugL = 0, Flag_SRP_ugL = 0, Flag_NH4_ugL = 0, Flag_DOC_mgL =
0, Flag_DIC_mgL = 0, Flag_DC_mgL =0, Flag_DN_mgL = 0, time2 =
ifelse(is.na(time), hms::hms(hours = 12), time), time =
hms::as_hms(time2), DateTime = paste(date, time), Reservoir = case_when(
grepl("\^F", res_site) \~ "FCR", grepl("\^B", res_site) \~ "BVR",
grepl("\^C", res_site) \~ "CCR", TRUE \~ res_site), Site =
as.numeric(gsub("\[\^0-9.\]", "", res_site))) \|\> rename( Depth_m =
depth, Rep = rep, TN_ugL = conc_ug_l_tn, TP_ugL = conc_ug_l_tp, NH4_ugL
= conc_ug_l_nh4, NO3NO2_ugL = conc_ug_l_no3, SRP_ugL = conc_ug_l_po4,
DOC_mgL = toc_mean_of_2_reps, DIC_mgL = tic_mean_of_2_reps, DC_mgL =
tc_mean_of_2_reps, DN_mgL = t_nb_mean_of_2_reps) \|\> select(c(res_site,
Reservoir, Site, DateTime, Depth_m, Rep, TN_ugL, TP_ugL, NH4_ugL,
NO3NO2_ugL, SRP_ugL, DOC_mgL, DIC_mgL, DC_mgL, DN_mgL, Flag_DateTime,
Flag_TP_ugL, Flag_TN_ugL, Flag_NH4_ugL, Flag_NO3NO2_ugL, Flag_SRP_ugL,
Flag_DOC_mgL, Flag_DIC_mgL, Flag_DC_mgL, Flag_DN_mgL))

all_join_woISCO \<- all_join \|\> filter(res_site != "F100.1")

write.csv(all_join,
"\~/GitHubRepos/CareyLabVT/Chemistry-QAQC-Frances/Results/Compiled_Results/chemistry_2025_wISCO.csv")

write.csv(all_join_woISCO,
"\~/GitHubRepos/CareyLabVT/Reservoirs/Data/DataAlreadyUploadedToEDI/EDIProductionFiles/MakeEMLChemistry/2025/chemistry_2025_wISCO.csv")

write.csv(all_join_woISCO,
"\~/GitHubRepos/CareyLabVT/Reservoirs/Data/DataAlreadyUploadedToEDI/EDIProductionFiles/MakeEMLChemistry/2025/chemistry_2025_woISCO.csv")
