---
title: "Sed traps CN 2019-present"
author: "Abby Lewis"
date: "2023-02-01"
updated: "2024-08-22 by Carly Bauer"
output: html_document
---

This file loads data exported from the CN analyzer, formats it to combine with metals fluxes, adds information from the filtering log, and finally combines CN with metals data to export for EDI.

## Load packages and data and combine files from CN analyzer. 
In an ideal world (admittedly unlikely) this is the only chunk you would need to modify to process new data.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)

cn1 = read.csv("./2023 sed trap runs/ASL 23jan23.csv")
cn2 = read.csv("./2023 sed trap runs/ASL 24jan23.csv")
cn3 = read.csv("./2023 sed trap runs/ASL 26jan23.csv")
cn4 = read.csv("./2023 sed trap runs/ASL 27jan23.csv")
cn5 = read.csv("./2023 sed trap runs/ASL 23mar22.csv")
cn6 = read.csv("./2023 sed trap runs/ASL 10feb22.csv")
#Add new file here

cn_raw = cn1 %>%
  full_join(cn2) %>%
  full_join(cn3) %>%
  full_join(cn4) %>%
  full_join(cn5) %>%
  full_join(cn6) %>%
  #full_join([new file]) %>%
  dplyr::select(-X)
```


## Re-format
Name format for export should be F_sed_8m_R2_F2_02May22, which means we will have to do some re-formatting
```{r}
cn_processed = cn_raw%>%
  filter(!Name %in% c("aa as unknown", #remove reference sediments
                      "aspartic acid",
                      "RunIn",
                      "ref zzyzx",
                      "crucible blank",
                      "internal reference zzyzx"),
         Method == "very low") %>%
  #Lots of code to extract information stored in sample name
  mutate(
    #Reservoir name
    Reservoir = ifelse(substring(Name,1,1)%in%c("f","F"),"FCR",NA),
    Reservoir = ifelse(substring(Name,1,1)%in%c("b","B"),"BVR",Reservoir),
    cut = substring(Name,2), #Remove reservoir from sample name
    #Date
    Date_sampled = as.Date(sub("_.*","",cut),format = "%d%b%y"),
    cut = sub("[0-9]+[a-z]+[0-9]+","",cut,ignore.case=T), #Remove date from sample name
    #Depth
    Depth_m = as.numeric(sub("_","",sub("m.+","",cut))),
    cut = sub("_[0-9]+m_","",cut), #Remove depth from sample name
    cut = ifelse(cut=="r1f2","r1f2_r1f2",cut), #Manually deal with one weird case
    #Standardize filter names
    Filter1ID = ifelse(grepl("_",cut), #If there is an underscore, both have been specified
                       sub("_.+","",cut),
                       paste0("r1",cut)), #If not, only the filter number was provided
    Filter2ID = ifelse(grepl("_",cut),
                       sub(".+_","",cut),
                       paste0("r2",cut)),
    #Fill in the full sample name
    Filter1ID = paste0(substr(Reservoir,1,1),"_sed_",
                       Depth_m,"m_R",substr(Filter1ID,2,2),"_F",substr(Filter1ID,4,4),"_",
                       format(Date_sampled,"%d%b%y")),
    Filter2ID = paste0(substr(Reservoir,1,1),"_sed_",
                       Depth_m,"m_R",substr(Filter2ID,2,2),"_F",substr(Filter2ID,4,4),"_",
                       format(Date_sampled,"%d%b%y")))%>%
  select(-cut,-No.,-Hole..Pos.,-Method,-Info,-C..Blank,-N..Blank)%>%
  rename(Time_run = Time,
         Weight_mg = Weight...mg.,
         N_area = N..Area,
         C_area = C..Area,
         N_pct = N.....,
         C_pct = C.....,
         CN_ratio = C.N..ratio,
         N_factor = N..Factor,
         C_factor = C..Factor,
         Date_run = Date)

#Plot
cn_processed%>%
  mutate(layer=ifelse(Depth_m%in%c(4,5),"EPI","HYPO"))%>%
  ggplot(aes(x=Date_sampled,y=C_pct,color=layer))+
  #ggplot(aes(x=Date_sampled,y=C_pct,color=as.factor(Depth_m)))+
  geom_point()+
  facet_wrap(~Reservoir)

#Final formatting to combine with metals
cn_to_combine = cn_processed%>%
  dplyr::select(Weight_mg,
                N_pct,
                C_pct,
                Filter1ID,
                Filter2ID,
                Date_sampled)
```

## Get sediment weights from filtering log

This bit is copied from the metals script and could be standardized in the future. 

In general, our goal here is to match up information from the filtering log with information from CN analysis. In the CN analysis, we combined two filters, so we need to combine information for the mass of sediment and volume filtered on BOTH of those filters.
```{r}
frame1 = read.csv("../Filtering logs/FilteringLog_EDI.csv")

#let's use the first filter ID to extract reservoir and depth info (should be the same year to year)
#also add in info that never changes
frame2 = cn_to_combine
frame2 <- frame2 %>% 
  mutate(Reservoir = ifelse(substring(frame2$Filter1ID, 1,1) == 'F',
                            'FCR',NA),
         Reservoir = ifelse(substring(frame2$Filter1ID, 1,1) == 'B',
                            'BVR', Reservoir),
         Depth_m = as.numeric(str_extract(frame2$Filter1ID, 
                                          '(?<=_)[:digit:]+(?=m)')),
         Site = 50)

#Need to get data from each filter separately. Doing that in a for loop
#Set up empty columns
frame2_complete = frame2%>%
  mutate(CombinedCollectionVol_L = NA,
         CombinedFilterVol_L = NA,
         CombinedSedMass_g = NA,
         CombinedXSA_m2 = NA,
         Duration_days = NA,
         Flag_CombinedCollectionVol_L = 1,
         Flag_Filter2ID = 1, 
         Flag_CombinedSedMass_g = 1, 
         Flag_TOC_g = 1, #Not currently changing these below
         Flag_TN_g= 1)
#Loop through all rows and sum data
for(i in 1:nrow(frame2_complete)){
  
  #Isolate the two filters used
  filter1 = frame1 %>% 
    filter(tolower(FilterID)==tolower(frame2_complete$Filter1ID[i])) #identify first filter
  filter2 = frame1 %>% 
    filter(tolower(FilterID)==tolower(frame2_complete$Filter2ID[i])) #identify second filter
  
  #Fill in information for CN
  #If there is exactly one match for each filter, we can proceed, otherwise, we have problems (dealt with below)
  if(nrow(filter1)==1 & nrow(filter2)==1){ 
    frame2_complete$CombinedCollectionVol_L[i] <- 
      filter1$CollectionVol_L + filter2$CollectionVol_L #sum collection volumes
    frame2_complete$CombinedFilterVol_L[i] <- 
      filter1$FilterVol_L + filter2$FilterVol_L #sum filter volumes
    frame2_complete$CombinedSedMass_g[i] <- 
      filter1$SedMass_g + filter2$SedMass_g #sum sed mass
    frame2_complete$CombinedXSA_m2[i] <- 
      filter1$TrapXSA_m2 + filter2$TrapXSA_m2 #sum surface area
    frame2_complete$Duration_days[i] <- 
      filter1$Duration_days #save duration
    frame2_complete$Flag_CombinedCollectionVol_L[i] <- 
      ifelse(filter1$Flag_CollectionVol_L == 2 | filter2$Flag_CollectionVol_L == 2,
             3,
             frame2_complete$Flag_CombinedCollectionVol_L[i]) #Save flag for volume
    
  } else { #If there is more or less than one match for each filter, give a warning
    
    if(!nrow(filter1) == 1){ #Warn for filter 1
      warning(
        paste0("Filter ",
               frame2_complete$Filter1ID[i], 
               " is in the filtering log ",  nrow(filter1)," times\n"))
    }
    
    if(!nrow(filter2) == 1 & !is.na(frame2_complete$Filter2ID[i])){ #Warn for filter 2
      warning(
        paste0("Filter ",
               frame2_complete$Filter2ID[i], 
               " is in the filtering log ",  nrow(filter2)," times\n"))
    }
    
    #If only one filter was used that's fine, but we need to process things slightly differently
    if(is.na(frame2_complete$Filter2ID[i]) & nrow(filter1) == 1){ 
      frame2_complete$CombinedCollectionVol_L[i]=filter1$CollectionVol_L 
      frame2_complete$CombinedFilterVol_L[i]=filter1$FilterVol_L
      frame2_complete$CombinedSedMass_g[i]=filter1$SedMass_g
      frame2_complete$CombinedXSA_m2[i]=filter1$TrapXSA_m2 
      frame2_complete$Duration_days[i]=filter1$Duration_days #save duration
      frame2_complete$Flag_CombinedCollectionVol_L[i]=2
      frame2_complete$Flag_Filter2ID[i]=2
      frame2_complete$Flag_CombinedCollectionVol_L[i]=2
      frame2_complete$Flag_CombinedSedMass_g[i]=2
    }
  }
}
```

## Finish processing CN

The hard part is done! Now just some simple arithmetic to get the CN flux values we need. This is where we deal with the fact that the sediment weights entered on the instrument were not the exact mass of sediment from the two combined filters
```{r}
CN_DONE = frame2_complete %>%
  filter(!is.na(CombinedXSA_m2)) %>%
  rename(Entered_weight_mg = Weight_mg) %>%
  mutate(C_mass_CN_g = C_pct / 100 * Entered_weight_mg / 1000, #convert to g
         N_mass_CN_g = N_pct / 100 * Entered_weight_mg / 1000,
         C_pct = C_mass_CN_g / CombinedSedMass_g * 100, #convert to pct
         N_pct = N_mass_CN_g / CombinedSedMass_g * 100)%>%
  dplyr::select(Reservoir, Date_sampled, Depth_m, Site, Duration_days,
                Filter1ID, Filter2ID, CombinedCollectionVol_L, CombinedFilterVol_L, 
                CombinedSedMass_g, CombinedXSA_m2, C_mass_CN_g, N_mass_CN_g, 
                Flag_CombinedCollectionVol_L, Flag_Filter2ID, 
                Flag_CombinedCollectionVol_L, Flag_CombinedSedMass_g, Flag_TOC_g, 
                Flag_TN_g)%>%
  mutate(Filt_ratio = CombinedCollectionVol_L / CombinedFilterVol_L, 
         C_mass_traps_g = C_mass_CN_g * Filt_ratio,
         N_mass_traps_g = N_mass_CN_g * Filt_ratio,
         C_flux_gm2d = C_mass_traps_g / CombinedXSA_m2/Duration_days,
         N_flux_gm2d = N_mass_traps_g / CombinedXSA_m2/Duration_days)
  
#Plot
CN_DONE%>%
  ggplot(aes(x = Date_sampled,y=C_flux_gm2d,color = as.factor(Depth_m)))+
  geom_point()+
  facet_wrap(~Reservoir)
```

## Combine with metals and export for EDI

```{r}
metals_to_combine = read.csv("../Metals/2023_allMetals.csv")%>%
  mutate(Date=as.Date(Date))

comb_raw = CN_DONE%>%
  rename(Date = Date_sampled)%>%
  full_join(metals_to_combine)

comb_formatted = comb_raw%>%
  rename(TOCFlux_gm2d = C_flux_gm2d,
         TNFlux_gm2d = N_flux_gm2d,
         TOC_g = C_mass_traps_g,
         TN_g = N_mass_traps_g)%>%
  dplyr::select(Reservoir, 
                Date,
                Site,
                Duration_days,
                Depth_m,
                CombinedXSA_m2,
                Filter1ID,
                Filter2ID,
                CombinedCollectionVol_L,
                CombinedFilterVol_L,
                CombinedSedMass_g,
                ICPTLi_mgL,
                ICPTNa_mgL,
                ICPTMg_mgL,
                ICPTAl_mgL,
                ICPTK_mgL,
                ICPTCa_mgL,
                ICPTFe_mgL,
                ICPTMn_mgL,
                ICPTCu_mgL,
                ICPTSr_mgL,
                ICPTBa_mgL,
                AcidVol_L,
                DilutionFactor,
                TLi_g,
                TNa_g,
                TMg_g,
                TAl_g,
                TK_g,
                TCa_g,
                TFe_g,
                TMn_g,
                TCu_g,
                TSr_g,
                TBa_g,
                TLiFlux_gm2d,
                TNaFlux_gm2d,
                TMgFlux_gm2d,
                TAlFlux_gm2d,
                TKFlux_gm2d,
                TCaFlux_gm2d,
                TFeFlux_gm2d,
                TMnFlux_gm2d,
                TCuFlux_gm2d,
                TSrFlux_gm2d,
                TBaFlux_gm2d,
                TOC_g,
                TN_g,
                TOCFlux_gm2d,
                TNFlux_gm2d,
                Flag_Filter2ID,
                Flag_CombinedCollectionVol_L,
                Flag_CombinedSedMass_g,
                Flag_TOC_g,
                Flag_TN_g,
                Flag_ICPTLi_mgL,
                Flag_ICPTNa_mgL,
                Flag_ICPTMg_mgL,
                Flag_ICPTAl_mgL,
                Flag_ICPTK_mgL,
                Flag_ICPTCa_mgL,
                Flag_ICPTFe_mgL,
                Flag_ICPTMn_mgL,
                Flag_ICPTCu_mgL,
                Flag_ICPTSr_mgL,
                Flag_ICPTBa_mgL)%>%
  arrange(Date) %>%
  mutate(Flag_ICPTLi_mgL = ifelse(is.na(ICPTLi_mgL), 2, Flag_ICPTLi_mgL),
         Flag_ICPTNa_mgL = ifelse(is.na(ICPTNa_mgL), 2, Flag_ICPTNa_mgL),
         Flag_ICPTMg_mgL = ifelse(is.na(ICPTMg_mgL), 2, Flag_ICPTMg_mgL),
         Flag_ICPTAl_mgL = ifelse(is.na(ICPTAl_mgL), 2, Flag_ICPTAl_mgL),
         Flag_ICPTK_mgL = ifelse(is.na(ICPTK_mgL), 2, Flag_ICPTK_mgL),
         Flag_ICPTCa_mgL = ifelse(is.na(ICPTCa_mgL), 2, Flag_ICPTCa_mgL),
         Flag_ICPTFe_mgL = ifelse(is.na(ICPTFe_mgL), 2, Flag_ICPTFe_mgL),
         Flag_ICPTMn_mgL = ifelse(is.na(ICPTMn_mgL), 2, Flag_ICPTMn_mgL),
         Flag_ICPTCu_mgL = ifelse(is.na(ICPTCu_mgL), 2, Flag_ICPTCu_mgL),
         Flag_ICPTSr_mgL = ifelse(is.na(ICPTSr_mgL), 2, Flag_ICPTSr_mgL),
         Flag_ICPTBa_mgL = ifelse(is.na(ICPTBa_mgL), 2, Flag_ICPTBa_mgL),
         Flag_TOC_g = ifelse(is.na(TOC_g), 2, Flag_TOC_g),
         Flag_TN_g = ifelse(is.na(TN_g), 2, Flag_TN_g))

#Some durations are unknown at the beginning of each year
comb_formatted = comb_formatted%>%
  mutate(Flag_Duration_days = 1,
         Flag_Duration_days = ifelse(Date == "2018-05-21" & Reservoir == "FCR", 
                                     2, 
                                     Flag_Duration_days),
         Flag_Duration_days = ifelse(Date == "2020-07-06" & Reservoir == "FCR", 
                                     2, 
                                     Flag_Duration_days),
         Flag_Duration_days = ifelse(Date == "2020-07-02" & Reservoir == "BVR", 
                                     2, 
                                     Flag_Duration_days),
         Flag_Duration_days = ifelse(Date == "2021-06-28" & Reservoir == "BVR", 
                                     2, 
                                     Flag_Duration_days))

write.csv(comb_formatted,"../CN_Metals_Flux_EDI.csv",row.names=F)

mean(unique(frame1$CollectionVol_L), na.rm=T)
```
