---
title: "CCR Met Plots for EDI"
output: html_document
theme: null
date: "`r Sys.Date()`"
---

This script is the visual inspection scripts. 
1. It takes the data file on EDI and combines it with the L1 file which has already been QAQCed. 
2. Then the script checks for daily and subdaily gaps in the current file. 
3. Lists the flag frequency to check if there are any NAs or any assigned the wrong flag. 
4. If necessary can QAQC data already on EDI using the QAQC function
5. Creates plots
6. Writes data to new csv

For the plots, they use a function called "all_plot". In all_plot you can specify if you want plotly plots for the current data. BEWARE if you turn on the plotly plots and try to knit the markdown it will fail! I am working on a fix. For right now you can specify which plotly plots you want on. You can also look at the plotly plots manually in each chunk by running the chunk with Use_plotly=TRUE as an argument and then at the end of the chunk output[[1]]. 


All files are from the link to GitHub and the source scripts are from GitHub as well. 

```{r Set Up, include=FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(RCurl,devtools, tidyverse,lubridate, plotly, magrittr, scattermore, knitr, htmltools, pander, suncalc)

# Source scripts from GitHub
devtools::source_url("https://raw.githubusercontent.com/FLARE-forecast/CCRE-data/ccre-dam-data-qaqc/R/met_qaqc_function.R")
devtools::source_url('https://raw.githubusercontent.com/CareyLabVT/Reservoirs/master/Data/DataAlreadyUploadedToEDI/EDIProductionFiles/Plotting_function.R')


 #turn off pander auto asis
        pander::panderOptions('knitr.auto.asis', FALSE)

# Set up the current time end time of the file and the current year for QAQC plots

#current time of QAQC for graphing
current_time_start=force_tz(as.POSIXct("2023-01-01 00:00:00"), tzone = "EST")
current_time_end= force_tz(as.POSIXct("2024-01-01 00:00:00"), tzone = "EST")
```

```{r Read in EDI Files, include=FALSE}

# Add timezones

inUrl1  <- "https://pasta-s.lternet.edu/package/data/eml/edi/779/19/c716e0cd3ccad6664b5894d9164a9004" 
infile1 <- tempfile()
try(download.file(inUrl1,infile1,method="curl"))
if (is.na(file.size(infile1))) download.file(inUrl1,infile1,method="auto")

                   
 historic <-read_csv(infile1) 
 
  historic$DateTime <- force_tz(as.POSIXct(historic$DateTime), tzone = "EST")

```

```{r Read in current L1 file and get the notes column, include=FALSE}

# Add time zones

# Use the qaqc script to get the qaqc file for the year with notes
L1 <- qaqc_ccrmet(
         output_file = NULL, 
         start_date = current_time_start, 
         end_date = Sys.Date(), 
         notes = TRUE)

L1$DateTime <- force_tz(as.POSIXct(L1$DateTime), tzone = "EST")

#L1 <- read_csv("https://raw.githubusercontent.com/FLARE-forecast/CCRE-data/ccre-dam-data-qaqc/ccre_met_L1.csv")

```

```{r Bind historic and L1 files together, include=FALSE}

# Add time zone

current_df <- dplyr::bind_rows(historic, L1)%>%
  filter(DateTime<current_time_end)

```

```{r Download Raw data for plotting, include=FALSE}
# Add timezone

CATPRES_COL_NAMES =  c("DateTime","Record", "CR3000Battery_V", "CR3000Panel_Temp_C", 
                   "PAR_umolm2s_Average", "PAR_Total_mmol_m2", "BP_Average_kPa", "AirTemp_C_Average", 
                   "RH_percent", "Rain_Total_mm", "WindSpeed_Average_m_s", "WindDir_degrees", "ShortwaveRadiationUp_Average_W_m2",
                   "ShortwaveRadiationDown_Average_W_m2", "InfraredRadiationUp_Average_W_m2",
                   "InfraredRadiationDown_Average_W_m2", "Albedo_Average_W_m2")
  
 
  # read catwalk data and maintenance log
  # NOTE: date-times throughout this script are processed as UTC
  raw <- read_csv("https://raw.githubusercontent.com/FLARE-forecast/CCRE-data/ccre-dam-data/ccre-met.csv", skip = 1, col_names = CATPRES_COL_NAMES,
                      col_types = cols(.default = col_double(), DateTime = col_datetime()))
  
  
  # convert NaN to NAs in the dataframe
  raw[sapply(raw, is.nan)] <- NA
  
  # force datetime
  raw$DateTime <- force_tz(as.POSIXct(raw$DateTime), tzone = "EST")

```

## Check for gaps in the data frame

This identifies if there are any daily data gaps in the long-term record

```{r Check for daily gaps, echo=FALSE}

# Get DOY
catwalk <- current_df
 catwalk$DOY=yday(catwalk$DateTime)

 for(i in 2:nrow(catwalk)){ #this identifies if there are any data gaps in the long-term record, and where they are by record number
    if(catwalk$DOY[i]-catwalk$DOY[i-1]>1){
      print(c(catwalk$DateTime[i-1],catwalk$DateTime[i]))
    }
 }
```

This identifies if there are any sub-daily gaps in the current record, as gaps of the long term record are found in the metadata.

The first row is the time for the first observation and then the subsequent observation. Each observation should be 10 minutes apart. The second row is the number of the record for each observation. Most of these gaps happen when we change the program on the data logger. These times will be recorded in the maintenance section of the metadata and are also noted in the maintenance log.

```{r Check for sub daily gaps, echo=FALSE}
# Because we can't have NAs for this for loop let's make a new df
  cat2 <- current_df%>%
   filter(!is.na(Record))%>%
   filter(DateTime>current_time_start)

   for(i in 2:length(cat2$Record)){ #this identifies if there are any data gaps in the long-term record, and where they are by record number
     if( abs(cat2$Record[i]-cat2$Record[i-1])>1 & difftime(cat2$DateTime[i], cat2$DateTime[i-1], units="mins")>1){
       print(c(cat2$DateTime[i-1], cat2$DateTime[i]))
       print(c(cat2$Record[i-1], cat2$Record[i]))
     }
   }
```

QAQC Historical Files: If you need to QAQC the historical file then run it through the qaqc function without start_date and end_date as NULL

```{r Run the QAQC function again if we need to, eval=FALSE, include=FALSE}

# Run the QAQC function
current_df <- qaqc_ccrmet(data_file= current_df,
         data2_file = NULL,
         maintenance_file = "https://raw.githubusercontent.com/FLARE-forecast/CCRE-data/ccre-dam-data-qaqc/CCRM_Maintenancelog_new.csv", 
         output_file = NULL, 
         start_date = NULL, 
         end_date = NULL, 
         notes = FALSE)

```

### Let's look at the flag Frequency for each variable. As a reminder here are the flag codes


Let's look at the flag Frequency for each variable. 

As a reminder here are the flag codes Flag values 

0: no flag; 

1: value removed due to maintenance and set to NA; 

2: sample not collected; 

3: negative values set to 0, percent greater than 100 and set to 100, or infinite values set to NA; 

4: potentially questionable value and changed or set to NA, see note; 

5: questionable value but left in the dataset.


```{r Check out the flags, echo=FALSE}

#make sure no NAS in the Flag columns
Flags <- current_df%>%
  select(DateTime, starts_with("Flag"))

RowsNA=Flags[!complete.cases(Flags), ] # Keep only the complete rows

#check the flag column
Flags <- current_df%>%
  select(starts_with("Flag"))

# Make a table with the number of times a flag was used
for(f in 1:ncol(Flags)){
  #print(colnames(Flags[f]))
  print(table(Flags[,f], useNA = "always"))
}
```

```{r Filter for current year and daily average, include=FALSE}

# Raw files
current_raw <- raw%>%
  filter(DateTime>=current_time_start & DateTime<current_time_end)%>%
  mutate(type = "raw")

current <- current_df%>%
  filter(DateTime>=current_time_start & DateTime<current_time_end)%>%
  mutate(type = "qaqc")%>%
  select(DateTime:Albedo_Average_W_m2,type, -contains("adjusted"))


# Let's only keep values that are different instead of plotting the raw and the qaqc value
current_plot_df <- bind_rows(current, current_raw)%>%
  dplyr::distinct(across(DateTime:Albedo_Average_W_m2), .keep_all = T)
    

daily <- current_df%>% 
  group_by( Date = as.Date(DateTime)) %>% 
  summarise_if(is.numeric, mean, na.rm=T)%>%
  mutate(Year = as.factor(year(Date)),
         Month = month(Date),
         Time = "12:00:00")%>%
  mutate(DateTime= paste0(Date, Time, sep=" "))%>%
  mutate(DateTime=ymd_hms(DateTime))

  
catdata <- current_df%>%
  mutate(Year=year(DateTime))

colors <- c("raw" = "red", "qaqc" = "black")
# colors for comparing Thermistor, RDO and Pressure sensor

#colors2 <- c("Therm"="magenta","RDO"="dodgerblue2" ,"Pressure"="black")
```



## QAQC Plots

For the plots, they use a function called "all_plot". In all_plot you can specify if you want plotly plots for the current data. BEWARE if you turn on the plotly plots and try to knit the markdown it will fail! I am working on a fix. For right now you can specify which plotly plots you want on. You can also look at the plotly plots manually in each chunk by running the chunk with Use_plotly=TRUE as an argument and then at the end of the chunk output[[1]]. 


## All Met Variables
```{r Temp, echo=FALSE, results='asis'}

dx <- colnames(raw |> select(PAR_umolm2s_Average:Albedo_Average_W_m2))

# make the plots
outputs <- lapply(dx, all_plot,y_lab = 'Var Unit', y_lab2 = "Var Unit", Water = FALSE, Raw_file = T, Use_plotly = F)

output <- unlist(outputs, recursive = F)

```

```{r Print plotly temp, echo=FALSE, messages=FALSE, warning=FALSE}

 # Used to print the plotly plots
  # attach the Dependencies
  # since the do not get included with renderTags(...)$html
  deps <- lapply(
    Filter(function(x){inherits(x,"htmlwidget")},output),
    function(hw){
      renderTags(hw)$dependencies
    }
  )
  
  if(length(deps)>0){
  attachDependencies(
    tagList(),
    unlist(deps,recursive=FALSE)
  )
  }  
```


### Write to CSV

```{r Make new CSV with current and historic files}

# make date time a character so no confusion with timezones
current_df$DateTime <- as.character(current_df$DateTime)
  

# Double Check naming convention
# Variable_StartYear_EndYear
write_csv(current_df, "CCRMet_2021_2023.csv")

```

### Download and save Maintenance Log, Plotting function, and QAQC function

```{r Download and save Maintenance Log, include=FALSE}

# Maintenance Log
download.file("https://raw.githubusercontent.com/FLARE-forecast/CCRE-data/ccre-dam-data-qaqc/CCRM_Maintenancelog_new.csv", "CCRMet_MaintenanceLog_2021_2023.csv")

# qaqc function
download.file("https://raw.githubusercontent.com/FLARE-forecast/CCRE-data/ccre-dam-data-qaqc/R/met_qaqc_function.R", "CCRMet_qaqc_2021_2023.R")

# streaming plots function
download.file("https://raw.githubusercontent.com/CareyLabVT/Reservoirs/master/Data/DataAlreadyUploadedToEDI/EDIProductionFiles/Plotting_function.R", "Plotting_function.R")


```

