---
title: "Compare the Old CTD vs. New CTD"
author: "Adrienne, modified by Abby"
date: "2023-09-06"
output: html_document
---

This document:

1. Reads in the CTD files

2. Does QAQC if necessary, 

3. Finds casts taken at the same reservoir on the same day for comparisons, 

4. Plot comparison casts for each date, variable, and reservoir

5. Make a regression plot for each variable

6. Run t-tests for each variable

7. Plot and run Bland Altman Test

8. Plot and run Passin Bablok Test


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
# the MCR package is archived 
if (! "mcr" %in% installed.packages()) devtools::install_version('mcr', version = '1.3.2')

# Load packages
pacman::p_load("lubridate", "tidyverse", "mcr", "BlandAltmanLeh")

```


```{r Read CTD files, include=FALSE}
old_CTD<- read_csv("../CTD_2018_2023.csv")%>%
  select(-starts_with("Flag_"))%>%
  filter(SN=="7809")

new_CTD<-read_csv("../CTD_2018_2023.csv")%>%
  select(-starts_with("Flag_"))%>%
  filter(SN=="8188")
```

```{r Find casts for comparisons, echo=FALSE}
# Select casts that we only have one for each

CTD_dates_new<-new_CTD%>%
  select(DateTime,Reservoir,Site)%>%
  mutate(Date=as.Date(DateTime))%>%
  select(-DateTime)%>%
  unique()

CTD_dates_old<-old_CTD%>%
  select(DateTime,Reservoir,Site)%>%
  mutate(Date=as.Date(DateTime))%>%
  select(-DateTime)%>%
  unique()

com_date<-merge(CTD_dates_new,CTD_dates_old, by=c('Reservoir','Site','Date'))

```

```{r Make big data frame, echo=FALSE}

# Make a huge data frame of old and new CTD

all_CTD<-old_CTD%>%
  bind_rows(.,new_CTD)%>%
  mutate(Date=as.Date(DateTime))

# Select only dates that we have casts for both

all_CTD2<-left_join(com_date,all_CTD, by=c('Reservoir','Site','Date'))

# Now pivot longer for plotting

dfg<-all_CTD2%>%
  select(Reservoir, Site, SN, DateTime, Date, Depth_m,DescRate_ms, everything())%>%
  pivot_longer(cols=c(Temp_C:Phycocyanin_ugL), 
                 names_to='variable',
                 values_to='observation')%>%
  filter(Depth_m>0)


# create list of variables

vari<-unique(dfg[['variable']])

```

## Comparison Plots from both CTDs split by date, variable, and reservoir

```{r Plots of each variable for each Reservoir, echo=FALSE}

for(i in 1:length(vari)){
  print(dfg %>%
          filter(variable==vari[i]) %>%
          #filter(observation<100)%>%
          filter(Site==50)%>%
          filter(Reservoir=="FCR")%>%
          ggplot(., aes(x=observation, y=Depth_m, color=as.factor(SN)))+
          geom_point()+
          facet_wrap(~Date, scales="free")+ 
          scale_y_reverse()+
          ggtitle(paste0(vari[i]," in FCR"))+
          theme_bw()+
          theme(plot.title = element_text(hjust = 0.5)))
  
}

# Let's do it for BVR 

for(i in 1:length(vari)){
print(dfg%>%
  filter(variable==vari[i])%>%
  #filter(observation<100)%>%
  filter(Site==50)%>%
  filter(Reservoir=="BVR")%>%
  ggplot(., aes(x=observation, y=Depth_m, color=as.factor(SN)))+
  geom_point()+
  facet_wrap(~Date, scales="free")+ 
  scale_y_reverse()+
    ggtitle(paste0(vari[i]," in BVR"))+
    theme_bw()+
    theme(plot.title = element_text(hjust = 0.5)))
  
}

# And CCR

for(i in 1:length(vari)){
print(dfg%>%
  filter(variable==vari[i])%>%
  #filter(observation<100)%>%
  filter(Site==50)%>%
  filter(Reservoir=="CCR")%>%
  ggplot(., aes(x=observation, y=Depth_m, color=as.factor(SN)))+
  geom_point()+
  facet_wrap(~Date, scales="free")+ 
  scale_y_reverse()+
    ggtitle(paste0(vari[i]," in CCR"))+
    theme_bw()+
    theme(plot.title = element_text(hjust = 0.5)))
  
}
```

### Scatterplots of the old CTD vs. new CTD

```{r Scatterplots, echo=FALSE}

# Now let's do a scatterplot for each variable
# Will will color code by site

#Round the depth column to the hundredths columns and then average over that depth
dfg$round_depth=round(dfg$Depth_m, digits=2)

sum_CTD<-dfg%>%
  filter(variable == c("Temp_C", "DO_mgL", "DOsat_percent", "Cond_uScm", "SpCond_uScm",
                       "Chla_ugL", "Turbidity_NTU", "PAR_umolm2s"))%>%
  group_by(Reservoir, Site, Date, SN, variable, round_depth)%>%
  dplyr::summarise(mean_obs = mean(observation, na.rm=T))%>%
  ungroup()

# Separate by serial numbers to create 2 columns

sum_CTD_S8188<-sum_CTD%>%
  filter(SN=="8188")%>%
  select(-SN)%>%
  dplyr::rename("obs_S8188" = "mean_obs")

sum_CTD_S7809<-sum_CTD%>%
  filter(SN=="7809")%>%
  select(-SN)%>%
  dplyr::rename("obs_S7809" = "mean_obs")

# merge the two data frames to get two columns of observations

round_CTD <- merge(sum_CTD_S7809, sum_CTD_S8188, by=c("Reservoir", "Site", "Date","variable", "round_depth"))

# We have 2608 points of comparison

# Make a plot of the observations from the new CTD and the Old CTD
ggplot(round_CTD, aes(x=obs_S7809, y=obs_S8188, col=Reservoir))+
  geom_point()+
  geom_abline(slope=1, intercept=0) +
  facet_wrap(~variable, scales="free")+
  ggtitle("One to One Comparison of Old CTD vs. New CTD")+
    theme_bw()+
    theme(plot.title = element_text(hjust = 0.5))
  

```

### Notes from Bobbie's R Script comparing methods in the Analytical Lab

 R Script to compare methods in the Analytical Lab
 Authors: Bobbie Niederlehner
 Last Edited: 06/07/2022

 Steps
     1) load the libraries and the data
     2) remove lines with missing values for either analysis
     3) OPTIONAL: restrict the concentration range being analyzed
     4) Paired T-Test- Test differences = 0 with paired T (NOT a preferred way to look at these data but magnitude of difference is interesting)
     5) Bland Altman - Visualize differences over concentration (difference over mean concentration)
     6) Passing Bablok - Test coincidence across concentrations - regression of new vs reference method.  Does it have a slope of 1 and an intercept of 0


 BACKGROUND INFO: Some web resources explaining method comparison regressions
 https://www.r-bloggers.com/deming-and-passing-bablok-regression-in-r/
 https://www.r-bloggers.com/2015/09/deming-and-passing-bablok-regression-in-r/
 http://labrtorian.com/tag/passing-bablok/
 https://www.r-bloggers.com/2016/08/a-shiny-app-for-passing-bablok-and-deming-regression/
 https://bahar.shinyapps.io/method_compare/


 Notes
  NOTE: the order of the variables in each analysis can matter
     FOR paired T-test it doesn't matter.  Just pay attention to sign for difference.  Difference is calculated as 1st specified (x) minus 2nd specified (y) 
     FOR Bland Altman it doesn't matter,  Default difference is 1st specified (x) minus 2nd specified (y) 
     FOR Passing Bablok first listed is reference method (x, Method1, or current),  second listed is is test method (y, Method2, or new)
    The intercept is often smean difference, but will have the reverse sign.  

### Output from t-tests

```{r Comparison stats, echo=FALSE}

# Make a list of variables for for loops

# create list of variables

var<-unique(round_CTD[['variable']])


# Paired T Test
#sink (file = "results/mcr_results.txt", append=TRUE)

for(b in 1:length(var)){
  a <-round_CTD%>%
    filter(variable==var[b])
  
  print(var[b])
  
    print(t.test(a$obs_S7809, a$obs_S8188, paired=TRUE,
            conf.level=0.95))
}

```

### Plots and outputs from Bland Altman

```{r Bland Altman, echo=TRUE}
 
#  Bland Altman Plots (difference over mean)
#      Estimates an agreement interval, within which 95% of the differences fall. 
#      BUT criterion for agreement should be decided on apriori and is completely based on judgement - what can you tolerate?

for(b in 1:length(var)){
  a <-round_CTD%>%
    filter(variable==var[b])
  
  print(var[b])
  
   ba<-bland.altman.stats(a$obs_S7809,a$obs_S8188, conf.int = 0.95)
#}

print (c("mean difference", "lower limit", "upper limit","sample size"))
print (c(ba$mean.diffs, ba$lower.limit, ba$upper.limit, ba$based.on))

#     IF you prefer GGPLOT2 specify that graph.sys  
#         geom_count = TRUE handles overlapping points by making the plot symbol larger
ba2 <- bland.altman.plot(a$obs_S7809,a$obs_S8188, graph.sys = "ggplot2", conf.int=.95, geom_count = F)
print (ba2 +
         xlab("Average of Two Measurments") + 
         ylab ("Difference of Two Measurments") +
         ggtitle(paste0(var[b]," Bland Altman plot")) +
         theme_bw()+
          theme(plot.title = element_text(hjust = 0.5)))
}
```

### Passin Bablok Test and Output

 Method Comparison Regression using nonparametric Passing Bablok (MORE RESISTANT TO OUTLIERS) 
     The first listed variable definitely ends up on the X axis and documentation says it is the "reference" method
     The second listed variable ends up on the y axis and documentation says it is the "test" method


```{r Passin Bablok, echo=FALSE}

for(b in 1:length(var)){
  a <-round_CTD%>%
    filter(variable==var[b],
           !is.na(obs_S7809),
           !is.na(obs_S8188))
  
  print(var[b])

  PB.reg <- mcreg(a$obs_S7809, a$obs_S8188, method.reg = "PaBa",
                  mref.name = 'obs_S7809', mtest.name = 'obs_S8188')
  
  print ("Passing Bablok")
  printSummary (PB.reg)
  print ("pearson correlation coefficient")
  cor.test(a$obs_S7809,a$obs_S8188,
           method = "pearson")
  
  ## Custom plots
  MCResult.plot(PB.reg, alpha=0.05,equal.axis = TRUE, x.lab = "Reference Method - S7809", y.lab = "Test Method - S8188", 
                points.col = "black", points.pch = 1, 
                ci.area = TRUE, ci.area.col = "gray", 
                identity.col="red3",
                main = paste0(var[b]," CTD Method Switch - Passing Bablok"), sub = "", add.grid = FALSE, points.cex = 1) 
  #dev.off()
  
  
  # a residuals plot
  MCResult.plotResiduals (PB.reg, 
                          ref.line = TRUE, ref.line.col = "gray", 
                          main = paste0(var[b], " CTD Method Switch - Passing Bablok Residuals")) 
  #dev.off()
  
  # a bias plot
  MCResult.plotBias (PB.reg, 
                     ci.area = TRUE, ci.area.col = "gray", 
                     main = paste0(var[b], " CTD Method Switch - Passing Bablok Bias")) 
  #dev.off()
  


}
```