---
title: "Compare the Old CTD vs. New CTD"
author: "Adrienne"
date: "2023-09-06"
output: html_document
---

This document:

1. Reads in the CTD files

2. Does QAQC if necessary, 

3. Finds casts taken at the same reservoir on the same day for comparisons, 

4. Plot comparison casts for each date, variable, and reservoir

5. Make a regression plot for each variable

6. Run t-tests for each variable

7. Plot and run Bland Altman Test

8. Plot and run Passin Bablok Test


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
# the MCR package is archived 
if (! "mcr" %in% installed.packages()) devtools::install_version('mcr', version = '1.3.2')

# Load packages
pacman::p_load("lubridate", "tidyverse", "mcr", "BlandAltmanLeh")

```


```{r Combine CTD files, include=FALSE}

# Read in EDI CTD file

inUrl1  <- "https://pasta.lternet.edu/package/data/eml/edi/200/13/27ceda6bc7fdec2e7d79a6e4fe16ffdf" 
infile1 <- tempfile()
try(download.file(inUrl1,infile1,method="curl"))
if (is.na(file.size(infile1))) download.file(inUrl1,infile1,method="auto")

EDI_CTD<-read_csv(infile1)%>%
  filter(DateTime>ymd_hms("2022-04-01 00:00:00"))%>%
  filter(Depth_m>0)


# Read in L1 file which is only from S7809

old_CTD<- read_csv("../ctd_L1.csv")%>%
  bind_rows(EDI_CTD,.)%>%
  select(-starts_with("Flag_"))%>%
  mutate(SN="S7809")

```

```{r Make S8188 df, include=FALSE}

# Combine all of the S8188 files

lookup <- c(PAR_umolm2s  = "PAR",
              DescRate_ms  = 'Descent Rate (m/s)',
              DateTime = "Date",
              DOsat_percent = "DO_pSat",
              SpCond_uScm = "Spec_Cond_uScm",
              Turbidity_NTU = "Turb_NTU",
              Phycoerythrin_ugL = "Phycoerythrin",
              Phycocyanin_ugL = "Phycocyanin")

# This reads all the files into the R environment
files = list.files("../csv_outputs/",pattern = "_S8188")%>%
  stringr::str_subset(., ".csv", negate = F) #only .csv files

#This reads the first file in
ctd = read_csv(paste0("../csv_outputs/",files[1])) 
location <- sub("^[0-9]*_","",sub("\\.csv","",files[1]))
ctd = ctd%>%
    mutate(Reservoir = toupper(sub("[0-9]+.*","",location)),
           Site = as.numeric(sub("_.*","",sub("^[A-Z|a-z]*","",sub("_[a-z]+","",location)))))%>%
    dplyr::rename(any_of(lookup))%>%
    select(-Salinity)
    

# Loop through and pull all the files in
for (i in 2:length(files)){
  new = read_csv(paste0("../csv_outputs/",files[i]))
  location <- sub("^[0-9]*_","",sub("\\.csv","",files[i]))
new = new%>%
    mutate(Reservoir = toupper(sub("[0-9]+.*","",location)),
           Site = as.numeric(sub("_.*","",sub("^[A-Z|a-z]*","",sub("_[a-z]+","",location)))))%>%
    dplyr::rename(any_of(lookup))%>%
    select(-Salinity)
    
  ctd = ctd %>%
    full_join(new)
}

# Change some Columns and rund through a quick QAQC
new_CTD<-ctd%>%
  filter(Depth_m>0)%>%
  mutate(SN="S8188")%>%
  select(-Flag)%>%
  #dplyr::rename(SpCond_uScm="Spec_Cond_uScm",
   #             DOsat_percent="DO_pSat",
   #             Turbidity_NTU="Turb_NTU")%>%

# Run through a quick QAQC

mutate(
  
      #DO
      DO_mgL = ifelse(DO_mgL < 0, 0, DO_mgL), #Flag DO<0
      
      #DO pSat
      DOsat_percent = ifelse(DOsat_percent < 0, 0, DOsat_percent), #Flag pSat<0
      
      #COND
      Cond_uScm = ifelse(Cond_uScm < 0, NA, Cond_uScm), #Flag Cond < 0. 
      
      #SPECCOND
      SpCond_uScm = ifelse(SpCond_uScm < 0, NA, SpCond_uScm), #Flag Cond < 0.
      
      #CHLA
      Chla_ugL = ifelse(Chla_ugL < 0, 0, Chla_ugL), #Flag Chla <0
      
      #Phycoerythrin
      Phycoerythrin_ugL = ifelse(Phycoerythrin_ugL < 0, 0, Phycoerythrin_ugL), #Flag Chla <0
      
      #Phycocyanin
      Phycocyanin_ugL = ifelse(Phycocyanin_ugL < 0, 0, Phycocyanin_ugL), #Flag Chla <0
      
      #TURB
      Turbidity_NTU = ifelse(Turbidity_NTU < 0, 0, Turbidity_NTU), #Flag turbidity <0
      
      #PAR
      PAR_umolm2s = ifelse(!is.na(PAR_umolm2s)&PAR_umolm2s < 0, NA, PAR_umolm2s))%>%
      
      
  
  #Fix for CTD when conductivity and specific conductivity columns were switched
  #spec_Cond_uScm=Cond_uScm/(1+(0.02*(Temp_C-25)))) so if temp is less than 25 conductivity is
  # less than specific conductivity and if temp is greater than 25 then conductivity is greater than 
  # specific conductivity. Based on this I created the a CTD_check column if the columns were good or bad. 
  # If they were bad then the conductivity and the spec. conductivity column need to be flipped. 
  
  #ABP 10 DEC 21
  
  
    add_column(CTD_check = NA)%>%#create the CTD_check column
    #sets up criteria for the CTD_check column either "good","bad" or "NA"(if no data)
    mutate(
      CTD_check=ifelse(Temp_C<25& Cond_uScm<SpCond_uScm & !is.na(SpCond_uScm), "good",CTD_check),
      CTD_check=ifelse(Temp_C<25& Cond_uScm>SpCond_uScm & !is.na(SpCond_uScm), "bad",CTD_check),
      CTD_check=ifelse(Temp_C>25& Cond_uScm>SpCond_uScm & !is.na(SpCond_uScm), "good",CTD_check),
      CTD_check=ifelse(Temp_C>25& Cond_uScm<SpCond_uScm & !is.na(SpCond_uScm), "bad",CTD_check),
      CTD_check=ifelse(is.na(SpCond_uScm), "good",CTD_check),
      CTD_check=ifelse(Cond_uScm==0, "bad", CTD_check))%>%
    #the next part switches the column if labeled "bad" in CTD_check 
    transform(., SpCond_uScm = ifelse(CTD_check == 'bad' & !is.na(SpCond_uScm), Cond_uScm, SpCond_uScm), 
              Cond_uScm = ifelse(CTD_check == 'bad' & !is.na(SpCond_uScm), SpCond_uScm, Cond_uScm))%>%
    select(-CTD_check)


```

```{r Find casts for comparisons, echo=FALSE}

# Select casts that we only have one for each

CTD_dates_new<-new_CTD%>%
  select(DateTime,Reservoir,Site)%>%
  mutate(Date=as.Date(DateTime))%>%
  select(-DateTime)%>%
  unique()

CTD_dates_old<-old_CTD%>%
  select(DateTime,Reservoir,Site)%>%
  mutate(Date=as.Date(DateTime))%>%
  select(-DateTime)%>%
  unique()

com_date<-merge(CTD_dates_new,CTD_dates_old, by=c('Reservoir','Site','Date'))

```

```{r Make big data frame, echo=FALSE}

# Make a huge data frame of old and new CTD

all_CTD<-old_CTD%>%
  bind_rows(.,new_CTD)%>%
  mutate(Date=as.Date(DateTime))

# Select only dates that we have casts for both

all_CTD2<-left_join(com_date,all_CTD, by=c('Reservoir','Site','Date'))

# Now pivot longer for plotting

dfg<-all_CTD2%>%
  select(Reservoir, Site, SN, DateTime, Date, Depth_m,DescRate_ms, everything())%>%
  pivot_longer(cols=c(Temp_C:Phycocyanin_ugL), 
                 names_to='variable',
                 values_to='observation')%>%
  filter(Depth_m>0)


# create list of variables

vari<-unique(dfg[['variable']])

```

## Comparison Plots from both CTDs split by date, variable, and reservoir

```{r Plots of each variable for each Reservoir, echo=FALSE}

for(i in 1:length(vari)){
print(dfg%>%
  filter(variable==vari[i])%>%
  #filter(observation<100)%>%
  filter(Site==50)%>%
  filter(Reservoir=="FCR")%>%
  ggplot(., aes(x=observation, y=Depth_m, color=as.factor(SN)))+
  geom_point()+
  facet_wrap(~Date, scales="free")+ 
  scale_y_reverse()+
    ggtitle(paste0(vari[i]," in FCR"))+
    theme_bw()+
    theme(plot.title = element_text(hjust = 0.5)))
  
}

# Let's do it for BVR 

for(i in 1:length(vari)){
print(dfg%>%
  filter(variable==vari[i])%>%
  #filter(observation<100)%>%
  filter(Site==50)%>%
  filter(Reservoir=="BVR")%>%
  ggplot(., aes(x=observation, y=Depth_m, color=as.factor(SN)))+
  geom_point()+
  facet_wrap(~Date, scales="free")+ 
  scale_y_reverse()+
    ggtitle(paste0(vari[i]," in BVR"))+
    theme_bw()+
    theme(plot.title = element_text(hjust = 0.5)))
  
}

# And CCR

for(i in 1:length(vari)){
print(dfg%>%
  filter(variable==vari[i])%>%
  #filter(observation<100)%>%
  filter(Site==50)%>%
  filter(Reservoir=="CCR")%>%
  ggplot(., aes(x=observation, y=Depth_m, color=as.factor(SN)))+
  geom_point()+
  facet_wrap(~Date, scales="free")+ 
  scale_y_reverse()+
    ggtitle(paste0(vari[i]," in CCR"))+
    theme_bw()+
    theme(plot.title = element_text(hjust = 0.5)))
  
}
```

### Scatterplots of the old CTD vs. new CTD

```{r Scatterplots, echo=FALSE}

# Now let's do a scatterplot for each variable
# Will will color code by site

#Round the depth column to the hundredths columns and then average over that depth
dfg$round_depth=round(dfg$Depth_m, digits=2)

sum_CTD<-dfg%>%
  filter(variable == c("Temp_C", "DO_mgL", "DOsat_percent", "Cond_uScm", "SpCond_uScm",
                       "Chla_ugL", "Turbidity_NTU", "PAR_umolm2s"))%>%
  group_by(Reservoir, Site, Date, SN, variable, round_depth)%>%
  dplyr::summarise(mean_obs = mean(observation, na.rm=T))%>%
  ungroup()

# Separate by serial numbers to create 2 columns

sum_CTD_S8188<-sum_CTD%>%
  filter(SN=="S8188")%>%
  select(-SN)%>%
  dplyr::rename("obs_S8188" = "mean_obs")

sum_CTD_S7809<-sum_CTD%>%
  filter(SN=="S7809")%>%
  select(-SN)%>%
  dplyr::rename("obs_S7809" = "mean_obs")

# merge the two data frames to get two columns of observations

round_CTD <- merge(sum_CTD_S7809, sum_CTD_S8188, by=c("Reservoir", "Site", "Date","variable", "round_depth"))

# We have 2608 points of comparison

# Make a plot of the observations from the new CTD and the Old CTD
ggplot(round_CTD, aes(x=obs_S7809, y=obs_S8188, col=Reservoir))+
  geom_point()+
  geom_abline(slope=1, intercept=0) +
  facet_wrap(~variable, scales="free")+
  ggtitle("One to One Comparison of Old CTD vs. New CTD")+
    theme_bw()+
    theme(plot.title = element_text(hjust = 0.5))
  

```

### Notes from Bobbie's R Script comparing methods in the Analytical Lab

 R Script to compare methods in the Analytical Lab
 Authors: Bobbie Niederlehner
 Last Edited: 06/07/2022

 Steps
     1) load the libraries and the data
     2) remove lines with missing values for either analysis
     3) OPTIONAL: restrict the concentration range being analyzed
     4) Paired T-Test- Test differences = 0 with paired T (NOT a preferred way to look at these data but magnitude of difference is interesting)
     5) Bland Altman - Visualize differences over concentration (difference over mean concentration)
     6) Passing Bablok - Test coincidence across concentrations - regression of new vs reference method.  Does it have a slope of 1 and an intercept of 0


 BACKGROUND INFO: Some web resources explaining method comparison regressions
 https://www.r-bloggers.com/deming-and-passing-bablok-regression-in-r/
 https://www.r-bloggers.com/2015/09/deming-and-passing-bablok-regression-in-r/
 http://labrtorian.com/tag/passing-bablok/
 https://www.r-bloggers.com/2016/08/a-shiny-app-for-passing-bablok-and-deming-regression/
 https://bahar.shinyapps.io/method_compare/


 Notes
  NOTE: the order of the variables in each analysis can matter
     FOR paired T-test it doesn't matter.  Just pay attention to sign for difference.  Difference is calculated as 1st specified (x) minus 2nd specified (y) 
     FOR Bland Altman it doesn't matter,  Default difference is 1st specified (x) minus 2nd specified (y) 
     FOR Passing Bablok first listed is reference method (x, Method1, or current),  second listed is is test method (y, Method2, or new)
    The intercept is often smean difference, but will have the reverse sign.  

### Output from t-tests

```{r Comparison stats, echo=FALSE}

# Make a list of variables for for loops

# create list of variables

var<-unique(round_CTD[['variable']])


# Paired T Test
#sink (file = "results/mcr_results.txt", append=TRUE)

for(b in 1:length(var)){
  a <-round_CTD%>%
    filter(variable==var[b])
  
  print(var[b])
  
    print(t.test(a$obs_S7809, a$obs_S8188, paired=TRUE,
            conf.level=0.95))
}

```

### Plots and outputs from Bland Altman

```{r Bland Altman, echo=TRUE}
 
#  Bland Altman Plots (difference over mean)
#      Estimates an agreement interval, within which 95% of the differences fall. 
#      BUT criterion for agreement should be decided on apriori and is completely based on judgement - what can you tolerate?

for(b in 1:length(var)){
  a <-round_CTD%>%
    filter(variable==var[b])
  
  print(var[b])
  
   ba<-bland.altman.stats(a$obs_S7809,a$obs_S8188, conf.int = 0.95)
#}

print (c("mean difference", "lower limit", "upper limit","sample size"))
print (c(ba$mean.diffs, ba$lower.limit, ba$upper.limit, ba$based.on))

#     IF you prefer GGPLOT2 specify that graph.sys  
#         geom_count = TRUE handles overlapping points by making the plot symbol larger
ba2 <- bland.altman.plot(a$obs_S7809,a$obs_S8188, graph.sys = "ggplot2", conf.int=.95, geom_count = F)
print (ba2 +
         xlab("Average of Two Measurments") + 
         ylab ("Difference of Two Measurments") +
         ggtitle(paste0(var[b]," Bland Altman plot")) +
         theme_bw()+
          theme(plot.title = element_text(hjust = 0.5)))
}
```

### Passin Bablok Test and Output

 Method Comparison Regression using nonparametric Passing Bablok (MORE RESISTANT TO OUTLIERS) 
     The first listed variable definitely ends up on the X axis and documentation says it is the "reference" method
     The second listed variable ends up on the y axis and documentation says it is the "test" method


```{r Passin Bablok, echo=FALSE}

for(b in 1:length(var)){
  a <-round_CTD%>%
    filter(variable==var[b])
  
  print(var[b])

PB.reg <- mcreg(a$obs_S7809,a$obs_S8188, method.reg = "PaBa",mref.name = 'obs_S7809', mtest.name = 'obs_S8188')

print ("Passing Bablok")
printSummary (PB.reg)
print ("pearson correlation coefficient")
cor.test(a$obs_S7809,a$obs_S8188,
         method = "pearson")

## Custom plots
MCResult.plot(PB.reg, alpha=0.05,equal.axis = TRUE, x.lab = "Reference Method - S7809", y.lab = "Test Method - S8188", 
              points.col = "black", points.pch = 1, 
              ci.area = TRUE, ci.area.col = "gray", 
              identity.col="red3",
              main = paste0(var[b]," CTD Method Switch - Passing Bablok"), sub = "", add.grid = FALSE, points.cex = 1) 
#dev.off()


# a residuals plot
MCResult.plotResiduals (PB.reg, 
                        ref.line = TRUE, ref.line.col = "gray", 
                        main = paste0(var[b], " CTD Method Switch - Passing Bablok Residuals")) 
#dev.off()

# a bias plot
MCResult.plotBias (PB.reg, 
                   ci.area = TRUE, ci.area.col = "gray", 
                   main = paste0(var[b], " CTD Method Switch - Passing Bablok Bias")) 
#dev.off()



}
```

```{r eval=FALSE, include=FALSE}
#Leaving Code Here for Later
#add in catwalk data 
cat=read_csv("Data/DataNotYetUploadedToEDI/Raw_CTD/csv_outputs/New_CTD_S8188/fcre-waterquality.csv")

new$Date=as.Date(new$Date)

cdom=new%>%
  filter(Date<"2022-07-13 00:00")%>%
  filter(Depth_m>1.2 & Depth_m<1.8)

ca=cat%>%
  filter(TIMESTAMP>"2022-05-24 00:00")
ca$Date=as.Date(ca$TIMESTAMP)

plot(ca$Date, ca$fDOM_RFU_1, type="l")
points(cdom$Date, cdom$CDOM_ugL, type="p", col="red")

#Graph just from FCR 
com%>%
  filter(Date<"2022-07-14")%>%
  #filter(Cond_uScm>0 & Cond_uScm<100)%>%
ggplot(data=., aes(x=PAR, y=Depth_m, col=as.factor(SN)))+
  geom_point()+
  scale_y_reverse()+
  facet_wrap( ~ Date, ncol=2)

```       
