---
title: "CNV Processing"
output: html_notebook
---
2019 CTD Processing for cnv files
First written by ASL 02 Aug 2019

# Load packages and assign global variables
```{r}
#First written by RPM April 2018
#06 June 2019 updated by RPM

### Load OCE Libraries and Carey Lab ctd functions###
pacman::p_load(oce, ocedata, tidyverse, lubridate)
source("ctd_functions.R") #Load Carey Lab ctd functions
source("CTD_matlab_functions.R") #Load Carey Lab ctd function for creating the glm aed dataset and a file for matlab

#Specify global variables
DATE_TEXT <- "02-Aug-2021" #format should be "01-Aug-2019"
SITE <- "fcr50"
SAMPLER <- ""
MAX_DEPTH <- 100 #9.3 for FCR, 11 for BVR




#Advanced customization
REP <- "" #If multiple casts were taken this will be _a, _b, _c, etc. Be sure to include an underscore if there is one in the file name
AUTO_NAME <- TRUE #If using a nonstandard name format. Must also fill in NAME_OVERRIDE below
NAME_OVERRIDE <- "MSN2_CTD_CASTS_072419/072519_bvr50_d" #For example, "080119_fcr50"
AUTO_FOLDER <- TRUE 
CSV_FOLDER_OVERRIDE <- "" #Enter "MSN_CTD_DATA" here for MSN data
```


#Choose the scan number that starts the cast
  -Verify that this starts above 0 dbar, only includes the downcast, and both plots are identical
  -You can ignore the "unrecognized SBE name" warning message
```{r}
SCAN_NUMBER <- 5
ctdTrimmed <- trim_ctd(SCAN_NUMBER, DATE_TEXT, AUTO_NAME, SITE, REP, NAME_OVERRIDE)
```

Everything else should be automated, just run this chunk of code!
```{r}
epic_ctd_function(ctdTrimmed, DATE_TEXT, SITE, SAMPLER, REP, AUTO_NAME, NAME_OVERRIDE, AUTO_FOLDER, CSV_FOLDER_OVERRIDE, MAX_DEPTH)

on = as_datetime(c("2021-06-11 10:40:00"))
off = as_datetime(c("2021-01-01"))

catwalk_compare = F

#Create dataframes and catwalk comparison for the whole season at fcr50
if(SITE %in% c("fcr50", "bvr50")){
  pacman::p_load(tidyverse, zoo, lubridate, rLakeAnalyzer,reshape2,akima,dplyr,gridExtra,grid,colorRamps,RCurl)
  if(year(as.Date(DATE_TEXT, format = "%d-%b-%Y")) == 2021){
    forCatwalkComparison <- fcr_data_wrangling(SITE)
  }
  #Compare to catwalk
  if(catwalk_compare == T){
      ctd_vs_catwalk(on,off, SITE) #This step takes a couple minutes
  }
}
```



Do not run during normal processing:
```{r}
library(lubridate)
startDate = as.Date("2020-06-15")

ctd <- read_csv("../CTD_season_csvs/CTD_notmatlab_ready_2019_fcr50.csv")
ctd$Date <- force_tz(ctd$Date+13*60*60, tz = "America/New_York")
dates <- unique(ctd$Date)
cat_init <- read_csv(file = getURL("https://raw.githubusercontent.com/CareyLabVT/SCCData/mia-data/Catwalk.csv"),skip = 1)
cat <- cat_init %>% 
  select(TIMESTAMP, doobs_1, doobs_5, doobs_9,EXO_depth,wtr_1, wtr_2, wtr_3, wtr_4, wtr_5, wtr_6, wtr_7, wtr_8, wtr_9, dotemp_5, dotemp_9) %>%
  filter(doobs_1 != "NAN") %>%
  filter(doobs_5 != "NAN") %>%
  filter(doobs_9 != "NAN") %>%
  filter(TIMESTAMP != "NAN") %>%
  filter(TIMESTAMP != "YYYY_MM_DD_HH_MM_SS")%>%
  mutate(TIMESTAMP = as.POSIXct(TIMESTAMP, format = "%Y-%m-%d %H:%M:%S"))%>%
  filter(TIMESTAMP >= startDate)
cats <- cat[which.min(abs(as.POSIXct(cat$TIMESTAMP)-dates[1])),]
for(i in 2:length(dates)){
  cats_new <- cat[which.min(abs(as.POSIXct(cat$TIMESTAMP)-dates[i])),]
  cats <- cats%>%
    full_join(cats_new)
}
cats[2:8]<-lapply(cats[2:8], as.numeric)
ysi <- read.csv("../ysi_22jun20.csv")

for(i in 1:length(dates)){
  ctd_toPlot =ctd%>%
    filter(Date == dates[i])
  xlim = range(c(cats$wtr_1,ysi$Temp_C,ctd$Temp_C))
  plot(ctd_toPlot$Temp_C,-ctd_toPlot$Depth_m, type = "l", xlab = "Temp (ºC)", ylab = "Depth (m)",xlim = xlim)
  if (i==2){
    points(ysi$Temp_C, -ysi$Depth_m, col = "blue", pch = 16)
  }
  #points(cats$wtr_1[i],-cats$EXO_depth[1],col = "red", pch = 16)
  #points(cats$dotemp_5[i],-cats$EXO_depth[1]+1.6-5,col = "red", pch = 16)
  #points(cats$dotemp_9[i],-cats$EXO_depth[1]+1.6-9,col = "red", pch = 16)
  points(cats$wtr_1[i],-1,col = "hotpink", pch = 16)
  points(cats$wtr_2[i],-2,col = "hotpink", pch = 16)
  points(cats$wtr_3[i],-3,col = "hotpink", pch = 16)
  points(cats$wtr_4[i],-4,col = "hotpink", pch = 16)
  points(cats$wtr_5[i],-5,col = "hotpink", pch = 16)
  points(cats$wtr_6[i],-6,col = "hotpink", pch = 16)
  points(cats$wtr_7[i],-7,col = "hotpink", pch = 16)
  points(cats$wtr_8[i],-8,col = "hotpink", pch = 16)
  points(cats$wtr_9[i],-9,col = "hotpink", pch = 16)
  points(cats$dotemp_5[i],-5,col = "hotpink", pch = 16)
  points(cats$dotemp_9[i],-9,col = "hotpink", pch = 16)
  legend("bottomright", c("catwalk","catwalk adj","ysi"), col = c("hotpink","red","blue"),pch = 16,)
  
  xlim = range(c(cats$doobs_1,ysi$DO_mgL,ctd$DO_mgL))
  plot(ctd_toPlot$DO_mgL,-ctd_toPlot$Depth_m, type = "l", xlab = "DO (mg/L)", ylab = "Depth (m)", xlim = xlim)
  if (i==2){
    points(ysi$DO_mgL, -ysi$Depth_m, col = "blue", pch = 16)
  }
  #points(cats$doobs_1[i],-cats$EXO_depth[1],col = "red", pch = 16)
  #points(cats$doobs_5[i],-cats$EXO_depth[1]+1.6-5,col = "red", pch = 16)
  #points(cats$doobs_9[i],-cats$EXO_depth[1]+1.6-9,col = "red", pch = 16)
  points(cats$doobs_1[i],-1.6,col = "hotpink", pch = 16)
  points(cats$doobs_5[i],-5,col = "hotpink", pch = 16)
  points(cats$doobs_9[i],-9,col = "hotpink", pch = 16)
  legend("bottomright", c("catwalk","ysi"), col = c("hotpink","blue"),pch = 16,)
  abline(v = 2)
}
dates
```

```{r}
sit_1.6 = read.csv("../csv_outputs/072121_fcr50_sit_1.6m.csv")%>%
  mutate(row = row_number())%>%
  mutate(Date = as_datetime(Date)+hours(14)+seconds(row/4))

cat <- read_csv(file = getURL("https://raw.githubusercontent.com/FLARE-forecast/FCRE-data/fcre-catwalk-data/Catwalk.csv"),skip = 1)

cat = cat%>%
  mutate(TIMESTAMP = as_datetime(TIMESTAMP))%>%
  filter(TIMESTAMP>as_datetime("2021-07-21 11:42:00"),
         TIMESTAMP<as_datetime("2021-07-21 14:13:00"))

sit_1.6%>%
  ggplot(aes(x=Date, y = DO_mgL))+
  geom_line()+
  geom_point(aes(x = TIMESTAMP, y = as.numeric(doobs_1)), data = cat)

sit_1.6%>%
  ggplot(aes(x=Date, y = DO_pSat))+
  geom_line()+
  geom_point(aes(x = TIMESTAMP, y = as.numeric(dosat_1)), data = cat)

sit_1.6%>%
  ggplot(aes(x=Date, y = Depth_m))+
  geom_line()+
  geom_point(aes(x = TIMESTAMP, y = as.numeric(EXO_depth)), data = cat)

sit_1.6%>%
  ggplot(aes(x=Date, y = Temp_C))+
  geom_line()+
  geom_point(aes(x = TIMESTAMP, y = as.numeric(EXO_wtr_1)), data = cat)

```

