---
title: "GHG_inspection_2015_2023"
author: "Freya Olsson"
date: "2023-11-30"
output: html_document
---

This is the visualisation script for the greenhouse gas data product which was used in the QA/QC process and review of the data package
1. It takes the data file on EDI and combines it with the L1 file which has already been QAQCed. 
3. Lists the flag frequency to check if there are any NAs or any assigned the wrong flag. 
5. Creates plots to visualise all variables and sites
6. Writes the new comined data to new csv

```{r setup packages, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

# Add the names of the packages 
pacman::p_load(tidyverse, lubridate, gsheet)

# source the qaqc code for GHG from GitHub
source("https://raw.githubusercontent.com/CareyLabVT/Reservoirs/refs/heads/master/Scripts/L1_functions/ghg_create.R")
```



```{r QAQC all files}

current_df <- ghg_qaqc(
  directory = "./../../Data/DataNotYetUploadedToEDI/Raw_GHG/",
  maintenance_file = "./Data/DataNotYetUploadedToEDI/Raw_GHG/GHG_Maintenance_Log.csv",
  gdrive = F, # Are the files on Google Drive. True or False
  gshared_drive = as_id("1OMx7Bq9_8d6J-7enC9ruPYuvE43q9uKn"),
  Air_Pressure = c("https://docs.google.com/spreadsheets/d/1YH9MrOVROyOgm0N55WiMxq2vDexdGRgG",                              "https://docs.google.com/spreadsheets/d/1ON3ZxDqfkFm65Xf5bbeyNFQGBjqYoFQg"),
  vial_digitized_sheet = "https://docs.google.com/spreadsheets/d/1HoBeXWUm0_hjz2bmd-ZmS0yhgF1WvLenpvwEa8dL008/edit#gid=1256821207",
  Rolling_MDL = "https://docs.google.com/spreadsheets/d/1AcqbdwbogWtO8QnLH1DmtZd47o323hG9/edit#gid=571411555",
 # historical_file = "" add in link
output_file = NULL,
MDL_file = "MDL_GHG_file.csv", 
Vial_Number_Check = "Vial_Number_Check.csv", #Use as a qaqc check to make sure you didn't miss any vials
start_date = NULL,
end_date = NULL)
```

```{r Reviewers start here}

current_df <- dplyr::bind_rows(historic, L1)

```

This section checks to make sure each observation has a data flag. It also checks to make sure the frequency of flags match what we expect to see. 

```{r Check there are no NAs in Flag columns}

#make sure no NAS in the Flag columns
Flags <- current_df |> 
  select(DateTime, starts_with("Flag"))

RowsNA <- Flags[!complete.cases(Flags), ] # Keep only the complete rows

#check the flag column
Flags <- current_df |> 
  select(starts_with("Flag"))

# Make a table with the number of times a flag was used
for(f in 1:(ncol(Flags))){
  #print(colnames(Flags[f]))
  print(table(Flags[,f], useNA = "always"))
}

```

## Check to make sure that what is in the maintenance log  was actually removed

### Look at the last rows of the maintenance log 

We want to make sure that our maintenance log actually worked and took out the values or changes those it was supposed to 

```{r Read in the maintenance log and look at the tail, echo=FALSE}

maint <- read_csv("../../../DataNotYetUploadedToEDI/Raw_GHG/GHG_Maintenance_Log.csv")

# name the data file
sd <- tail(maint) %>%
  filter(flag!=7)

# let's see what the tails look like
print(tail(sd))

knitr::kable((tail(sd)))

```
#### Check the that the columns have flags 

Look at the first few rows of the data frame and check that the observations after the TIMESTAMP_start are flagged

#### Look at the first 5 rows for that time

```{r Did the maint log work head, echo=FALSE}
# get the last row of the data file
last_row <- tail(sd, n=1)

# Get starttime and end time
### get start and end time of one maintenance event
start <- as_datetime(last_row$TIMESTAMP_start)
end <- as_datetime(last_row$TIMESTAMP_end)
    
# Get the time of the maintenance
if(is.na(end)){
  # If there the maintenance is on going then the columns will be removed until
  # and end date is added
  Time <- current_df |> filter(DateTime >= start) |> select(DateTime)
  
}else if (is.na(start)){
  # If there is only an end date change columns from beginning of data frame until end date
  Time <- current_df |> filter(DateTime <= end) |> select(DateTime)
  
}else {
  Time <- current_df |> filter(DateTime >= start & DateTime <= end) |> select(DateTime)
}


### Get the names of the columns affected by maintenance
colname_start <- last_row$start_parameter
colname_end <- last_row$end_parameter

# Make list of just the columns we want 

test <- colnames(current_df%>%select(DateTime, colname_start, paste0("Flag_",colname_start), colname_end, paste0("Flag_",colname_end)))

# Print the head of the table to make sure that data are flagged

head(current_df[current_df$DateTime %in% Time$DateTime, test])
tail(current_df[current_df$DateTime %in% Time$DateTime, test])

```

```{r Plots}
# Plot CH4 at Site 50 in FCR
current_df |>  
  filter(Depth_m<100,  Site == 50,
         Reservoir == "FCR") |> 
    mutate(Depth_m = as_factor(Depth_m)) |> 
  ggplot(aes(x = DateTime, y = CH4_umolL, colour = Depth_m))+
  geom_point() +
  labs(title = 'FCR CH4')

# Plot CO2 at Site 50 in FCR
current_df |>  
  filter(Depth_m<100, Site == 50,
         Reservoir == "FCR") |> 
    mutate(Depth_m = as_factor(Depth_m)) |> 
  ggplot(aes(x = DateTime, y = CO2_umolL, colour = Depth_m))+
  geom_point()+
  labs(title = 'FCR CO2')

# Plot CH4 at Site 50 in BVR
current_df |>  
  filter(Depth_m<100, Site == 50,
         Reservoir == "BVR") |> 
    mutate(Depth_m = as_factor(Depth_m)) |> 
  ggplot(aes(x = DateTime, y = CH4_umolL, colour = Depth_m))+
  geom_point()+
  labs(title = 'BVR CH4')

# Plot CO2 at Site 50 in BVR
current_df |>  
  filter(Depth_m<100, Site == 50,
         Reservoir == "BVR") |> 
    mutate(Depth_m = as_factor(Depth_m)) |> 
  ggplot(aes(x = DateTime, y = CO2_umolL, colour = Depth_m))+
  geom_point() +
  labs(title = 'BVR CO2')



# FCR NOT Site 50 - CH4
current_df |>  
  filter(Reservoir == "FCR", Site != 50) |> 
  ggplot(aes(x=DateTime, y=CH4_umolL, colour=as.factor(Site)))+
  geom_point() +
  labs(title = 'FCR CH4 other sites')


current_df |>  
  filter(Reservoir == "FCR", Site != 50) |> 
  ggplot(aes(x=DateTime, y=CO2_umolL, colour=as.factor(Site)))+
  geom_point() +
  labs(title = 'FCR CO2 other sites')


# BVR NOT Site 50 
current_df %>% 
  filter(Reservoir == "BVR", Site != 50) |> 
  ggplot(aes(x = DateTime, y = CH4_umolL, colour = as.factor(Site)))+
  geom_point() +
  labs(title = 'BVR CH4 other sites')

current_df %>% 
  filter(Reservoir == "BVR", Site != 50) |>  
  ggplot(aes(x = DateTime, y = CO2_umolL, colour = as.factor(Site)))+
  geom_point() +
  labs(title = 'BVR CO2 other sites')


```

Look at this year only:

```{r plots-current-year}
# CH4 plots current year
current_df |>  
  filter(Depth_m<100,
         Reservoir == "FCR", Site != 50, 
         DateTime >= '2023-01-01') |>
  mutate(Site = as.factor(Site)) |> 
  ggplot(aes(x = DateTime, y = CH4_umolL, colour = Site))+
  geom_point() +
  labs(title = 'FCR CH4')

current_df |>  
  filter(Depth_m<100,
         Reservoir == "FCR", Site == 50, 
         DateTime >= '2023-01-01') |> 
  mutate(Depth_m = as_factor(Depth_m)) |> 
  ggplot(aes(x = DateTime, y = CH4_umolL, colour = Depth_m))+
  geom_point() +
  labs(title = 'FCR Site 50, CH4')

current_df |>  
  filter(Depth_m<100,
         Reservoir == "BVR", Site != 50, 
         DateTime >= '2023-01-01') |>
  mutate(Site = as.factor(Site)) |> 
  ggplot(aes(x = DateTime, y = CH4_umolL, colour = Site))+
  geom_point() +
  labs(title = 'BVR CH4')

current_df |>  
  filter(Depth_m<100,
         Reservoir == "BVR", Site == 50, 
         DateTime >= '2023-01-01') |> 
  mutate(Depth_m = as_factor(Depth_m)) |> 
  ggplot(aes(x = DateTime, y = CH4_umolL, colour = Depth_m))+
  geom_point() +
  labs(title = 'BVR Site 50, CH4')

# CO2 plots current year
current_df |>  
  filter(Depth_m<100,
         Reservoir == "FCR", Site != 50, 
         DateTime >= '2023-01-01') |>
  mutate(Site = as.factor(Site)) |> 
  ggplot(aes(x = DateTime, y = CO2_umolL, colour = Site))+
  geom_point() +
  labs(title = 'FCR CO2')

current_df |>  
  filter(Depth_m<100,
         Reservoir == "FCR", Site == 50, 
         DateTime >= '2023-01-01') |> 
  mutate(Depth_m = as_factor(Depth_m)) |> 
  ggplot(aes(x = DateTime, y = CO2_umolL, colour = Depth_m))+
  geom_point() +
  labs(title = 'FCR Site 50, CO2')

current_df |>  
  filter(Depth_m<100,
         Reservoir == "BVR", Site != 50, 
         DateTime >= '2023-01-01') |>
  mutate(Site = as.factor(Site)) |> 
  ggplot(aes(x = DateTime, y = CO2_umolL, colour = Site))+
  geom_point() +
  labs(title = 'BVR CO2')

current_df |>  
  filter(Depth_m<100,
         Reservoir == "BVR", Site == 50, 
         DateTime >= '2023-01-01') |> 
  mutate(Depth_m = as_factor(Depth_m)) |> 
  ggplot(aes(x = DateTime, y = CO2_umolL, colour = Depth_m))+
  geom_point() +
  labs(title = 'BVR Site 50, CO2')

```


```{r Make new CSV with current and historic files}

# Need to decide on a naming convention for this file
write.csv(current_df, "GHG_2015_2023.csv", row.names = F)

```

```{r download files}

```



```{r Make site description file}
 # These lines of code make the csv of the site descriptions with lat and long

  # Use Gsheet because you don't need to authenticate it. 
  sites <- gsheet::gsheet2tbl("https://docs.google.com/spreadsheets/d/1TlQRdjmi_lzwFfQ6Ovv1CAozmCEkHumDmbg_L4A2e-8/edit#gid=1244423834")
  #data<- read_csv("YOUR DATA.csv")# Use this if you read in a csv
  data <- current_df #This is the line you need to modify!
  trim_sites = function(data,sites){
    data_res_site=data%>% #Create a Reservoir/Site combo column
      mutate(res_site = trimws(paste0(Reservoir,Site)))
    sites_merged = sites%>% #Filter to Sites that are in the dataframe
      mutate(res_site = trimws(paste0(Reservoir,Site)))%>%
      filter(res_site%in%data_res_site$res_site)%>%
      select(-res_site)
  }
  sites_trimmed = trim_sites(data,sites) 
  write.csv(sites_trimmed,"site_descriptions.csv", row.names=F)# Write to file

```

