---
title: "FCR Catwalk Plots for EDI"
output: html_document
date: "2023-01-10"
---
 This script takes the raw outputs from the water quality sensors at Falling Creek and combines them into one file, identifies gaps in the data, runs the data through the QAQC function (qaqc_fcr), and produces QAQC plots for visual inspection. 
 
 1. Open the script and check you have the correct function in line 19
 2. Change the current start and end times to match the year you are publishing for
 3. If there are more than one csv make sure they are all in the Download data chunk. Currently there is only one csv with all of the observations. 
 4. Once you have made sure everything is up to date press the knit button and it will produce an html file with all of the outputs and plots. 
 
 Use this file path in Carey Lab Reservoir GitHub Repo:
"./Data/DataAlreadyUploadedToEDI/EDIProductionFiles/MakeEML_FCRcatwalk/2023/"
 

```{r Set Up, include=FALSE}
pacman::p_load("RCurl","tidyverse","lubridate", "plotly", "magrittr","scattermore", "knitr")
source("FCR_catwalk_QAQC_function_2018_2023.R")


# Set up the current time end time of the file and the current year for QAQC plots

#current time of QAQC for graphing
current_time_start="2023-01-01 00:00:00, tz=UTC"
current_time_end="2023-12-31 23:59:00, tz=UTC"
```


```{r Create Data folder, include=FALSE}
### Create a misc_data_files folder if one doesn't already exist
misc_folder <- "misc_data_files"
if (file.exists(misc_folder)) {
  cat("The folder already exists")
} else {
  dir.create(misc_folder)
}
```


```{r Download data, include=FALSE}
# This section downloads the data from Github and the maintenance file. 
# If there are changes to the data on Github then you have to redownload the files

# Set the timeout option to 100 seconds instead of 60
options(timeout=200)

# This function to speeds up the download time of the data downloads. 
# If your wifi is slow then it will still take a while. 

bdown=function(url, file){
  library('RCurl')
  f = CFILE(file, mode="wb")
  a = curlPerform(url = url, writedata = f@ref, noprogress=FALSE)
  close(f)
  return(a)
}

# download most up to date catwalk data, manual downloads and maintenance log
# goal in 2023 is to have the missing files on the data logger-no time now and need to talk to CCC
bdown("https://raw.githubusercontent.com/FLARE-forecast/FCRE-data/fcre-catwalk-data/CAT_MaintenanceLog.txt", "misc_data_files/FCR_CAT_MaintenanceLog.txt")
bdown("https://raw.githubusercontent.com/FLARE-forecast/FCRE-data/fcre-catwalk-data/fcre-waterquality.csv", "misc_data_files/fcre-waterquality.csv")
bdown('https://raw.githubusercontent.com/CareyLabVT/ManualDownloadsSCCData/master/CR6_Files/FCRcatwalk_manual_2022.csv', "misc_data_files/CAT_2.csv")

```

```{r Read in file, include=FALSE}

    CATPRES_COL_NAMES = c("DateTime", "RECORD", "CR6Battery_V", "CR6Panel_Temp_C", "ThermistorTemp_C_surface",
                        "ThermistorTemp_C_1", "ThermistorTemp_C_2", "ThermistorTemp_C_3", "ThermistorTemp_C_4",
                        "ThermistorTemp_C_5", "ThermistorTemp_C_6", "ThermistorTemp_C_7", "ThermistorTemp_C_8",
                        "ThermistorTemp_C_9", "RDO_mgL_5", "RDOsat_percent_5", "RDOTemp_C_5", "RDO_mgL_9",
                        "RDOsat_percent_9", "RDOTemp_C_9", "EXO_Date", "EXO_Time", "EXOTemp_C_1", "EXOCond_uScm_1",
                        "EXOSpCond_uScm_1", "EXOTDS_mgL_1", "EXODOsat_percent_1", "EXODO_mgL_1", "EXOChla_RFU_1",
                        "EXOChla_ugL_1", "EXOBGAPC_RFU_1", "EXOBGAPC_ugL_1", "EXOfDOM_RFU_1",    "EXOfDOM_QSU_1","EXOTurbidity_FNU_1",
                        "EXOPressure_psi", "EXODepth_m", "EXOBattery_V", "EXOCablepower_V", "EXOWiper_V","LvlPressure_psi_9", "LvlTemp_C_9")
  

  # read catwalk data and maintenance log
  # NOTE: date-times throughout this script are processed as UTC
  
  catdata1 <- read_csv("misc_data_files/fcre-waterquality.csv", skip=1, col_names = CATPRES_COL_NAMES,
                       col_types = cols(.default = col_double(), DateTime = col_datetime()))
  
  catdata2<-read_csv("misc_data_files/CAT_2.csv", skip=1, col_names = CATPRES_COL_NAMES,
                     col_types = cols(.default = col_double(), DateTime = col_datetime()))

  # Bind the 2 data frames and drop duplicates
  catdata= catdata1%>%
    rbind(.,catdata2)%>% #combine manual and most recent files
    drop_na(DateTime)%>% #take out the rows with blank timestamps
    distinct(DateTime, .keep_all= TRUE) #taking out the duplicate values 
  
    #bad headers so remove them
  
  catdata<-catdata%>%filter(grepl("^20", DateTime)) #keep only the right TIMESTAMP rows 
  
  # Change NaN into NA
  catdata[sapply(catdata, is.nan)] <- NA
  
   # Order the data frame by date from oldest to youngest
   catdata=catdata[order(catdata$DateTime),]
  
```

```{r Fix Timezone, include=FALSE}
#Fix the timezone issues  
  #time was changed from GMT-4 to GMT-5 on 15 APR 19 at 10:00
  #have to seperate data frame by year and record because when the time was changed 10:00-10:40 were recorded twice
  #once before the time change and once after so have to seperate and assign the right time. 
  before=catdata%>%
    filter(DateTime<"2019-04-15 6:50")%>%
    filter(DateTime<"2019-04-15 6:50" & RECORD < 32879)#Don't know how to change timezones so just subtract 4 from the time we want
    
  
  #now put into GMT-5 from GMT-4
  before$DateTime<-as.POSIXct(strptime(before$DateTime, "%Y-%m-%d %H:%M"), tz = "Etc/GMT+5") #get dates aligned
  before$DateTime<-with_tz(force_tz(before$DateTime,"Etc/GMT+4"), "Etc/GMT+5") #pre time change data gets assigned proper timezone then corrected to GMT -5 to match the rest of the data set
  
  
  #filter after the time change 
  after=catdata%>%
    filter(DateTime>"2019-04-15 05:50")%>%
    slice(-c(1,3,5,7,9))
    
  
  after$DateTime<-as.POSIXct(strptime(after$DateTime, "%Y-%m-%d %H:%M"), tz = "Etc/GMT+5")#change or else after is off by an hour
  
 
  #merge before and after so they are one dataframe in GMT-5 but give it a UTC timestamp because it makes QAQC easier.
  # So the data are in EST but labeled UTC. 
  
  catdata=rbind(before, after)
  
  catdata=catdata[!duplicated(catdata$DateTime), ]
  
  catdata$DateTime<-as.POSIXct(strptime(catdata$DateTime, "%Y-%m-%d %H:%M:%S"), tz = "UTC")

```

```{r Check for daily gaps and record gaps, include=FALSE}

#order data by DateTime
FCRdata=catdata
  FCRdata=FCRdata[order(FCRdata$DateTime),]
  FCRdata$DOY=yday(FCRdata$DateTime)
# Add depth 
FCRdata=FCRdata%>%mutate(LvlDepth_m_9=(LvlPressure_psi_9*0.70455))
```

## Check for gaps in the data frame
This identifies if there are any daily data gaps in the long-term record
```{r Check for daily gaps, echo=FALSE}
 for(i in 2:nrow(FCRdata)){ #this identifies if there are any data gaps in the long-term record, and where they are by record number
    if(FCRdata$DOY[i]-FCRdata$DOY[i-1]>1){
      print(c(FCRdata$DateTime[i-1],FCRdata$DateTime[i]))
    }
 }
```
This identifies if there are any sub-daily gaps in the long-term record. 
Most of these gaps happen when we change the program on the data logger. 
```{r Check for sub daily gaps, echo=FALSE}
 cat2=FCRdata%>%filter(!is.na(RECORD))
  for(i in 2:length(cat2$RECORD)){ #this identifies if there are any data gaps in the long-term record, and where they are by record number
    if(abs(cat2$RECORD[i]-cat2$RECORD[i-1])>1){
      print(c(cat2$DateTime[i-1],cat2$DateTime[i]))
    }
  }
```

```{r Run the QAQC function, include=FALSE}
# run standard qaqc function from FCR_catwalk_QAQC_function_2018_2023.R

# run standard qaqc these are where the data entered in the function are defined
#current file from the data logger
data_file <-catdata
#maintenance file
maintenance_file <-file.path(getwd(),  "misc_data_files/FCR_CAT_MaintenanceLog.txt")
#name of the output file
output_file <- file.path(getwd(), "FCR_Catwalk_EDI_2018_2023.csv")
start_date <- NULL # Used for daily QAQC. Leave as NULL
end_date <- NULL # Used for daily QAQC. Leave as NULL


# Run the QAQC function
qaqc_fcr(data_file,maintenance_file, output_file, start_date, end_date)

```

```{r Make Maintenance Log for pub, include=FALSE}
# Make the Maintenance Log into a csv and add Reservoir and Site column 
  Log <- read.csv(maintenance_file)
 names(Log) = c("Station", "DateTime_start","DateTime_end", "Parameter", "ColumnNumber","Flag", "FlagColumn", "Notes") #finalized column names
Log$Reservoir= "BVR"#add reservoir name for EDI archiving
Log$Site=50 #add site column for EDI archiving

Log=Log[,c(9:10,1:8)]

Log_final <- Log[Log$DateTime_start<ymd_hms(current_time_start),]
 
write.csv(Log_final, "FCR_CAT_MaintenanceLog_2018_2023.csv", row.names=F, quote=F)
```


## Read in the QAQC File and Check it out
This section reads in the QAQC file and then you can look at the head, tail and structure. 
Make sure the last row is Dec. 31 23:50 of the publishing year. There should be 83 columns unless a new one has been added. 
```{r Read in QAQC file and look at it, echo=FALSE}
# read in qaqc function output

catdata <- read_csv(output_file)
#catdata <- read_csv(paste0(getwd(), 'FCR_Catwalk_EDI_2018_2023.csv'))

# subset file to only unpublished data
catdata <- catdata[catdata$DateTime<ymd_hms(current_time_end),]

# what does the beginning look like
head(catdata)
# Make sure it goes to Dec 31st 23:50 of the previous year or your ending period
tail(catdata)
# check out the structure
str(catdata)
```


Let's look at the flag Frequency for each variable. As a reminder here are the flag codes
 Flag values
 
  0: no flag
  
  1: value removed due to maintenance and set to NA
  
  2: negative or outlier value removed and set to NA, see Methods section for more detail on QAQC process
  
  3: negative values set to 0
  
  4: value removed due to fouling and set to NA
  
  5: questionable value due to potential fouling
  
  6: very questionable value due to potential fouling. Values adjusted using a linear or square root function     to match high-resolution CTD profiles are given in RDO_mgL_5 and RDO_sat_percent_5
  
  7: missing data
  
  8: Value corrected using a constant offset due to two thermistor malfunctions in Fall 2020

```{r Check out the flags, echo=FALSE}

#make sure no NAS in the Flag columns
Flags=catdata%>%
  select(DateTime, starts_with("Flag"))

RowsNA=Flags[!complete.cases(Flags), ] # Keep only the complete rows

#check the flag column
Flags=catdata%>%
  select(starts_with("Flag"))

# Make a table with the number of times a flag was used
for(f in 1:ncol(Flags)){
  #print(colnames(Flags[f]))
  print(table(Flags[,f], useNA = "always"))
}
```

```{r Filter for current year and daily average, include=FALSE}

# Raw files
current_raw <- FCRdata%>%
  filter(DateTime>=ymd_hms(current_time_start) & DateTime<ymd_hms(current_time_end))

current <- catdata%>%
  filter(DateTime>=ymd_hms(current_time_start) & DateTime<ymd_hms(current_time_end))

daily <- catdata%>% 
  group_by( Date = as.Date(DateTime)) %>% 
  summarise_if(is.numeric, mean, na.rm=T)%>%
  mutate(Year = as.factor(year(Date)),
         Month = month(Date),
         Time = "12:00:00")%>%
  mutate(DateTime= paste0(Date, Time, sep=" "))%>%
  mutate(DateTime=ymd_hms(DateTime))

  
catdata<-catdata%>%
  mutate(Year=year(DateTime))

colors <- c("raw" = "red", "QAQCd" = "black")
# colors for comparing Thermistor, RDO and Pressure sensor
colors2 <- c("Therm"="magenta","RDO"="dodgerblue2" ,"Pressure"="black")
```

```{r Plot functions, echo=FALSE}
# plotting function for each plot

all_plot<-function(Var,y_lab){
 if(Var=="ThermistorTemp_C_5"|Var=="ThermistorTemp_C_9"){
   
    if (Var=="ThermistorTemp_C_5"){
      Var2="RDOTemp_C_5"
      Switch=F # Used to switch on and off the layer for the pressure sensor
    }else if (Var=="ThermistorTemp_C_9"){
      Var2="RDOTemp_C_9"
      Var3="LvlTemp_C_9"
      Switch=T # Used to switch on and off the layer for the pressure sensor
    }
  
    all<- ggplot() +
      geom_scattermore(data=FCRdata, aes_string(x="DateTime", y=Var, color=shQuote("raw")))+
      geom_scattermore(data=catdata, aes_string(x="DateTime", y=Var, color=shQuote("QAQCd")))+
      ggtitle("All",Var) +
      labs(y = y_lab,
           color = "Legend") +
      scale_color_manual(values = colors)+
      theme_bw()
    
    cur<- ggplot() +
      geom_scattermore(data=current_raw, aes_string(x="DateTime", y=Var, color=shQuote("raw")), pointsize = 3)+
      geom_scattermore(data=current, aes_string(x="DateTime", y=Var, color=shQuote("QAQCd")), pointsize = 3) +
      ggtitle("Current",Var) +
      labs(y = y_lab,
           color = "Legend") +
      scale_color_manual(values = colors)+
      theme_bw()
    
    # density plot
    den <-ggplot(data = daily, aes_string(x = Var, group = "Year", fill = "Year"))+
      geom_density(alpha=0.5)+
      xlab("Daily avg.")+
      #xlim(0,0.5)+
      ggtitle("All",Var) +
      theme_bw()
    
    # box plot
    box <-ggplot(data = daily, aes_string(x = "Year", y = Var, group = "Year", fill = "Year"))+
      geom_boxplot()+
      #geom_jitter(alpha = 0.1)+
      ylab(y_lab)+
      #ylim(0,0.3)+
      ggtitle("Boxplot",Var) +
      theme_bw()  
    
    
    # graph all
    com_all<-ggplot(data = catdata, aes_string(x = "DateTime", y = Var)) +
      geom_scattermore(aes_string(y=Var, color=shQuote("Therm")))+ 
      geom_scattermore(aes_string(y=Var2, color=shQuote("RDO")))+
      {if(Switch)geom_scattermore(aes_string(y=Var3, color=shQuote("Pressure")))}+ # print layer if Switch is TRUE
    ggtitle(paste0("All Water Temp from"," ",Var,", ",Var2)) +
      labs(y = y_lab,
           color = "Legend") +
      scale_color_manual(values = colors2)+
      theme_bw()
    
    #Just the current year
    com_curr<-ggplot(data = current, aes_string(x = "DateTime", y = Var)) +
      geom_scattermore(aes_string(y=Var, color=shQuote("Therm")), pointsize = 3)+ 
      geom_scattermore(aes_string(y=Var2, color=shQuote("RDO")), pointsize = 3)+
      {if(Switch)geom_scattermore(aes_string(y=Var3, color=shQuote("Pressure")), pointsize = 3)}+ # print layer if Switch is TRUE
    ggtitle(paste0("Current Water Temp from"," ",Var,", ",Var2)) +
      labs(y = y_lab,
           color = "Legend") +
      scale_color_manual(values = colors2)+
      theme_bw()
    
  }else{
    all<- ggplot() +
      geom_scattermore(data=FCRdata, aes_string(x="DateTime", y=Var, color=shQuote("raw")))+
      geom_scattermore(data=catdata, aes_string(x="DateTime", y=Var, color=shQuote("QAQCd")))+
      ggtitle("All",Var) +
      labs(y = y_lab,
           color = "Legend") +
      scale_color_manual(values = colors)+
      theme_bw()
    
    cur<- ggplot() +
      geom_scattermore(data=current_raw, aes_string(x="DateTime", y=Var, color=shQuote("raw")), pointsize = 3)+
      geom_scattermore(data=current, aes_string(x="DateTime", y=Var, color=shQuote("QAQCd")), pointsize = 3) +
      ggtitle("Current",Var) +
      labs(y = y_lab,
           color = "Legend") +
      scale_color_manual(values = colors)+
      theme_bw()
    
    # density plot
    den <-ggplot(data = daily, aes_string(x = Var, group = "Year", fill = "Year"))+
      geom_density(alpha=0.5)+
      xlab("Daily avg.")+
      #xlim(0,0.5)+
      ggtitle("All",Var) +
      theme_bw()
    
    # box plot
    box <-ggplot(data = daily, aes_string(x = "Year", y = Var, group = "Year", fill = "Year"))+
      geom_boxplot()+
      #geom_jitter(alpha = 0.1)+
      ylab(y_lab)+
      #ylim(0,0.3)+
      ggtitle("Boxplot",Var) +
      theme_bw()
  }
    
    if(Var=="ThermistorTemp_C_5"|Var=="ThermistorTemp_C_9"){
    newlist <- list(all,cur,den,box,com_all,com_curr) # have to list all outputs under one name
    
    }else{
      newlist <- list(all,cur,den,box)
    }
    return(newlist)
}
```

## QAQC Plots

### Temperature
```{r Temperature data, echo=FALSE, warning = FALSE, results='hide'}
# for loop through all the temp data
for(i in names(catdata)[c(4:13,18,23:24)]){
  print(all_plot(Var=i, y_lab = expression(''*~degree*C*'')))
}
```

```{r All Temperature, echo=FALSE, warning = FALSE, results='hide'}

colors3 <-c("0.1m"="firebrick1", "1m"="DarkOrange1", "EXO_1.5m"="yellow","2m"="gold", 
                                  "3m"="greenyellow", "4m"="medium sea green", "5m"="sea green",
                                  "6m"="DeepSkyBlue4", "7m"="blue2", "8m"="darkslateblue", "9m"="darkmagenta")

# Take out Temperature values 

  All_temp<-catdata%>%
    select(DateTime, starts_with("Ther"), starts_with("EXOTemp"))%>%
    pivot_longer(-c(DateTime), names_to="Sensor", values_to="Reading", values_drop_na=TRUE)%>%
    mutate(DateTime=ymd_hms(DateTime))
  
  
  ggplot(All_temp)+
    geom_scattermore(aes(x=DateTime, y=Reading))+
    facet_wrap(.~factor(Sensor, levels=c("ThermistorTemp_C_surface","ThermistorTemp_C_1","EXOTemp_C_1", "ThermistorTemp_C_2",  "ThermistorTemp_C_3", "ThermistorTemp_C_4","ThermistorTemp_C_5","ThermistorTemp_C_6","ThermistorTemp_C_7","ThermistorTemp_C_8","ThermistorTemp_C_9")))+
    theme_bw()
  
# All on one plot
    ggplot(catdata,aes(x = DateTime))+
    geom_line(aes(y=ThermistorTemp_C_surface, color="0.1m"))+
    geom_line(aes(y=ThermistorTemp_C_1, color="1m"))+
    geom_line(aes(y=EXOTemp_C_1, color="EXO_1.5m")) +
    geom_line(aes(y=ThermistorTemp_C_2, color="2m"))+
    geom_line(aes(y=ThermistorTemp_C_3, color="3m"))+
    geom_line(aes(y=ThermistorTemp_C_4, color="4m"))+
    geom_line(aes(y=ThermistorTemp_C_5, color="5m"))+
    geom_line(aes(y=ThermistorTemp_C_6, color="6m"))+
    geom_line(aes(y=ThermistorTemp_C_7, color="7m"))+
    geom_line(aes(y=ThermistorTemp_C_8, color="8m"))+
    geom_line(aes(y=ThermistorTemp_C_9, color="9m"))+
    ggtitle("All Temperature Profile") +
    labs(y = expression(''*~degree*C*''),
           color = "Legend") +
      scale_color_manual(values = colors3)+
      theme_bw()
  
# This is all the temps and just the current year
    ggplot(current,aes(x = DateTime))+
    geom_line(aes(y=ThermistorTemp_C_surface, color="0.1m"))+
    geom_line(aes(y=ThermistorTemp_C_1, color="1m"))+
    geom_line(aes(y=EXOTemp_C_1, color="EXO_1.5m")) +
    geom_line(aes(y=ThermistorTemp_C_2, color="2m"))+
    geom_line(aes(y=ThermistorTemp_C_3, color="3m"))+
    geom_line(aes(y=ThermistorTemp_C_4, color="4m"))+
    geom_line(aes(y=ThermistorTemp_C_5, color="5m"))+
    geom_line(aes(y=ThermistorTemp_C_6, color="6m"))+
    geom_line(aes(y=ThermistorTemp_C_7, color="7m"))+
    geom_line(aes(y=ThermistorTemp_C_8, color="8m"))+
    geom_line(aes(y=ThermistorTemp_C_9, color="9m"))+
    ggtitle("Current Temperature Profile") +
    labs(y = expression(''*~degree*C*''),
           color = "Legend") +
      scale_color_manual(values = colors3)+
      theme_bw()
  
```

### Depth
```{r Pressure Sensor, echo=FALSE, warning = FALSE, results='hide'}  
### Plotting depth from pressure sensor 
   
for(i in names(catdata)[c(44,38)]){
  print(all_plot(Var=i, y_lab = "meters"))
}

```

### Dissolved Oxygen
```{r DO, echo=FALSE, warning = FALSE, results='hide'}
for(i in names(catdata)[c(14:15,19:20,29,28)]){
  print(all_plot(Var=i, y_lab = "mg/L or % sat"))
}
```

### Chlorophyll 
```{r Check the EXO Chla, echo=FALSE, warning = FALSE, results='hide'}

all_plot(Var="EXOChla_ugL_1", y_lab = "ug/L")

# chl and phyco visual qaqc-plot to see if everything looks right
 #take out the NAs
 data_comp <- daily[!is.na(daily$EXOChla_ugL_1), ]  
 
 ggplot()+
   geom_point(data=catdata, aes(x=DateTime, y=EXOChla_ugL_1))+
   geom_line(data=data_comp, aes(x=DateTime, y=EXOChla_ugL_1), col="green")+
   ggtitle("Compare 10 minute observations to Daily mean")
 
 
all_plot(Var="EXOChla_RFU_1", y_lab="RFU")

 #take out the NAs
 data_comp <- daily[!is.na(daily$EXOChla_RFU_1), ]  
 
 ggplot()+
   geom_point(data=catdata, aes(x=DateTime, y=EXOChla_RFU_1))+
   geom_line(data=data_comp, aes(x=DateTime, y=EXOChla_RFU_1), col="green")+
   ggtitle("Compare 10 minute observations to Daily mean")
```

### Phycocanin
```{r Check out the Phyco in EXO, echo=FALSE, warning = FALSE, results='hide'}
all_plot(Var="EXOBGAPC_RFU_1", y_lab="RFU")

 #take out the NAs
 data_comp <- daily[!is.na(daily$EXOBGAPC_RFU_1), ]  
 
 ggplot()+
   geom_point(data=catdata, aes(x=DateTime, y=EXOBGAPC_RFU_1))+
   geom_line(data=data_comp, aes(x=DateTime, y=EXOBGAPC_RFU_1), col="blue")+
   ggtitle("Compare 10 minute observations to Daily mean")
 
  all_plot(Var="EXOBGAPC_ugL_1", y_lab="ug/L")

 #take out the NAs
 data_comp <- daily[!is.na(daily$EXOBGAPC_ugL_1), ]  
 
 ggplot()+
   geom_point(data=catdata, aes(x=DateTime, y=EXOBGAPC_ugL_1))+
   geom_line(data=data_comp, aes(x=DateTime, y=EXOBGAPC_ugL_1), col="blue")+
   ggtitle("Compare 10 minute observations to Daily mean")
```

### fDOM
```{r fdom EXO sensor, echo=FALSE, warning = FALSE, results='hide'}
for(i in names(catdata)[34:35]){
  print(all_plot(Var=i, y_lab = "RFU or QSU"))
}
```

### Conductivity, Specific Conductivity, TDS
```{r Cond Spcond and TDS, echo=FALSE, warning = FALSE, results='hide'}
for(i in names(catdata)[25:27]){
  print(all_plot(Var=i, y_lab = "uScm or mg/L"))
}
```

### Turbidity 
```{r turbidity, echo=FALSE, warning = FALSE, results='hide'}
all_plot(Var="EXOTurbidity_FNU_1", y_lab="FNU")
```