---
title: "FCR Catwalk Plots for EDI"
output: html_document
date: "2023-01-10"
---
 Master QAQC script in prep for publishing catwalk sensor string data to EDI
 this script using the qaqc_fcr which automatically QAQCs the data. 
 This script produces figures to look over the data to visually 
 inspect it and make sure there are no  major outlines. 
 The final step is to write the final csv.
 
 To use the R mark down click the green run current chunk arrow on the right hand side. 

This step gets the right packages, sets the correct folder and then 
sources the QAQC script. Make sure you have the correct year
## Set Up
```{r Set Up}
pacman::p_load("RCurl","tidyverse","lubridate", "plotly", "magrittr")
source("FCR_catwalk_QAQC_function_2018_2022.R")


# Set up the current time end time of the file and the current year for QAQC plots

#current time of QAQC for graphing
current_time_start="2022-01-01 00:00:00, tz=UTC"
current_time_end="2022-12-31 23:59:00, tz=UTC"
```

##Create misc_data_files folder 
This chunk makes the folder where the raw data will be stored
```{r Create Data folder}
### Create a misc_data_files folder if one doesn't already exist
misc_folder <- "misc_data_files"
if (file.exists(misc_folder)) {
  cat("The folder already exists")
} else {
  dir.create(misc_folder)
}

```

## Download the Raw Data
This section downloads the data from Github and the maintenance file. 
If there are changes to the data on Github then you have to re download the files. 
If not then you can just use the version of the files in your misc_files. 
Must do if you are running the script for the first time
```{r Download data} 
# Set the timeout option to 100 seconds instead of 60
options(timeout=200)

# download most up to date catwalk data, manual downloads and maintenance log
# goal in 2023 is to have the missing files on the data logger-no time now and need to talk to CCC
download.file("https://raw.githubusercontent.com/FLARE-forecast/FCRE-data/fcre-catwalk-data/CAT_MaintenanceLog.txt", "misc_data_files/FCR_CAT_MaintenanceLog_2018_2022.txt")
download.file("https://raw.githubusercontent.com/FLARE-forecast/FCRE-data/fcre-catwalk-data/fcre-waterquality.csv", "misc_data_files/fcre-waterquality.csv")
download.file('https://raw.githubusercontent.com/CareyLabVT/ManualDownloadsSCCData/master/CR6_Files/FCRcatwalk_manual_2022.csv', "misc_data_files/CAT_2.csv")


```

## QAQC Function
This section sets up and runs the QAQC function. The out put tells you the missing observations.
If you can't find them in the manual downloads then make sure to put these times in the methods
section under missing.
```{r Run the QAQC function}
# run standard qaqc function from FCR_catwalk_QAQC_function_2018_2022.R

#current file from the data logger
data_file <-file.path(getwd(), 'misc_data_files/fcre-waterquality.csv')
#manual downloads to add missing data 
data2_file <-file.path(getwd(), 'misc_data_files/CAT_2.csv')
#maintenance file
maintenance_file <-file.path(getwd(),  "misc_data_files/FCR_CAT_MaintenanceLog_2018_2022.txt")
#name of the output file
output_file <- file.path(getwd(), "misc_data_files/Catwalk_first_QAQC_2018_2022.csv")


# Run the QAQC function
qaqc_fcr(data_file,data2_file,maintenance_file, output_file)

```

## Read in the QAQC File and Check it out
This section reads in the QAQC file and then you can look at the head, tail and structure. 
Make sure the last row is Dec. 31 23:50 of the publishing year. There should be 83 columns unless a new one has been added. 
```{r Read in QAQC file and look at it}
# read in qaqc function output

catdata <- read_csv(output_file)
#catdata <- read_csv(paste0(getwd(), '/misc_data_files/Catwalk_first_QAQC_2018_2022.csv'))

# subset file to only unpublished data
catdata <- catdata[catdata$DateTime<ymd_hms(current_time_end),]

# what does the beginning look like
head(catdata)
# Make sure it goes to Dec 31st 23:50 of the previous year or your ending period
tail(catdata)
# check out the structure
str(catdata)
```


Let's look at the flag Frequency for each variable. As a reminder here are the flag codes
 Flag values
  0: no flag
  1: value removed due to maintenance and set to NA
  2: negative or outlier value removed and set to NA, see Methods section for more detail on QAQC process
  3: negative values set to 0
  4: value removed due to fouling and set to NA
  5: questionable value due to potential fouling
  6: very questionable value due to potential fouling. Values adjusted using a linear or square root function     to match high-resolution CTD profiles are given in RDO_mgL_5 and RDO_sat_percent_5
  7: missing data
  8: Value corrected using a constant offset due to two thermistor malfunctions in Fall 2020

It gives an error but all the columns are there. 
```{r Check out the flags}

#make sure no NAS in the Flag columns
Flags=catdata%>%
  select(DateTime, starts_with("Flag"))

RowsNA=Flags[!complete.cases(Flags), ] # Keep only the complete rows

#check the flag column
Flags=catdata%>%
  select(starts_with("Flag"))

# Make a table with the number of times a flag was used
for(f in 2:nrow(Flags)){
  print(colnames(Flags[f]))
  print(table(Flags[,f], useNA = "always"))
}
```

##Lets graph all the Data

There is a lot data and lots of plots. It will most likely crash (I haven't tried to) if you try to run it all so just run a chunk at a time. 

## Temperature 
Thermistor 1
```{r Thermistor at the surface}
 m_1 <- ggplot(data = catdata, aes(x = DateTime, y = ThermistorTemp_C_surface)) +
  geom_line()
 m_1
#Only use plotly to find DateTime of questionable values
# ggplotly(m_1)

# #Just the current year
  m_1_21=catdata%>%
  filter(DateTime > as.POSIXct(current_time_start) & DateTime < as.POSIXct(current_time_end)) %>%
   ggplot(.,aes(x = DateTime, y = ThermistorTemp_C_surface)) +
   geom_point()
 m_1_21
 
#Only use plotly to find DateTime of questionable values
 #ggplotly(m_1_21)
```

```{r Thermistor at 1m}
# check 2 temp data
#Plot 2018-current
 m_2 <- ggplot(data = catdata, aes(x = DateTime, y = ThermistorTemp_C_1)) +
  geom_line()
 m_2
#Only use plotly to find DateTime of questionable values
# ggplotly(m_2)

 #Just the current year
 m_2_21=catdata%>%
  filter(DateTime>ymd_hms(current_time_start) & DateTime<ymd_hms(current_time_end))%>%
   ggplot(.,aes(x = DateTime, y = ThermistorTemp_C_1)) +
   geom_point()
 m_2_21
#Only use plotly to find DateTime of questionable values
 #ggplotly(m_2_21)
```

```{r EXO at 1.5m }
# check EXO 1.5m temp data
 # Plot 2018-current
 EXOtemp_1 <- ggplot(data = catdata, aes(x = DateTime, y = EXOTemp_C_1)) +
    geom_line()
 EXOtemp_1
 #Only use plotly to find DateTime of questionable values
 # ggplotly(EXOtemp_1)
 
 # Just the current year
 EXOtemp_1_21=catdata%>%
    filter(DateTime>ymd_hms(current_time_start) & DateTime<ymd_hms(current_time_end))%>%
    ggplot(.,aes(x = DateTime, y = EXOTemp_C_1)) +
    geom_point()
 EXOtemp_1_21
 #Only use plotly to find DateTime of questionable values
 # ggplotly(EXOtemp_1_21)
```

```{r Thermistor at 2m}
# check 3 temp data
#Plot From 2018-current
 m_3 <- ggplot(data = catdata, aes(x = DateTime, y = ThermistorTemp_C_2)) +
  geom_line()
 m_3
#Only use plotly to find DateTime of questionable values
# ggplotly(m_3)

#Just the current year
 m_3_21=catdata%>%
  filter(DateTime>ymd_hms(current_time_start) & DateTime<ymd_hms(current_time_end))%>%
   ggplot(.,aes(x = DateTime, y = ThermistorTemp_C_2)) +
   geom_point()
 m_3_21
#Only use plotly to find DateTime of questionable values
 #ggplotly(m_3_21)
```

```{r Thermistor at 3m}
# check 4 temp data
#Plot from 2018-current
 m_4 <- ggplot(data = catdata, aes(x = DateTime, y = ThermistorTemp_C_3)) +
  geom_line()
 m_4
#Only use plotly to find DateTime of questionable values
# ggplotly(m_4)

# Just from current year
 m_4_21=catdata%>%
  filter(DateTime>ymd_hms(current_time_start) & DateTime<ymd_hms(current_time_end))%>%
   ggplot(.,aes(x = DateTime, y = ThermistorTemp_C_3)) +
   geom_point()
 m_4_21
#Only use plotly to find DateTime of questionable values
 #ggplotly(m_4_21)
```

```{r Thermistor at 4m}
# check 5 temp data
# Plot from 2018-current
 m_5 <- ggplot(data = catdata, aes(x = DateTime, y = ThermistorTemp_C_4)) +
   geom_line()
 m_5
#Only use plotly to find DateTime of questionable values
# ggplotly(m_5)

# Just current year
 m_5_21=catdata%>%
  filter(DateTime>ymd_hms(current_time_start) & DateTime<ymd_hms(current_time_end))%>%
   ggplot(.,aes(x = DateTime, y = ThermistorTemp_C_4)) +
   geom_point()
 m_5_21
#Only use plotly to find DateTime of questionable values
 #ggplotly(m_5_21)
```

```{r Thermistor at 5m}
# check 6 temp data
# Plot from 2018-current
   m_6 <- ggplot(data = catdata, aes(x = DateTime, y = ThermistorTemp_C_5)) +
  geom_line()
 m_6
#Only use plotly to find DateTime of questionable values
# ggplotly(m_6)

# Just the current year
 m_6_21=catdata%>%
  filter(DateTime>ymd_hms(current_time_start) & DateTime<ymd_hms(current_time_end))%>%
   ggplot(.,aes(x = DateTime, y = ThermistorTemp_C_5)) +
   geom_point()
m_6_21
#Only use plotly to find DateTime of questionable values
 #ggplotly(m_6_21)

# Compare the bottom Thermistor with the temperature on the Do sensor at 5m
   
   # All the years
   
    comp_m_5 <- ggplot(data = catdata, aes(x = DateTime)) +
    geom_line(aes(y=ThermistorTemp_C_5, color="Therm"))+ 
      geom_line(aes(y=RDOTemp_C_5, color="RDO"))+
      labs(y=expression(''*~degree*C*'')) +
    scale_color_manual(name = "Sensor",
                       breaks = c("Therm", "RDO"),
                       values = c("Therm"="firebrick1","RDO"="blue"))
   comp_m_5
   
   
   
    #Just the current year
   comp_6_21=catdata%>%
    filter(DateTime>ymd_hms(current_time_start) & DateTime<ymd_hms(current_time_end))%>%
     ggplot(.,aes(x = DateTime))+
     geom_point(aes(y=ThermistorTemp_C_5, color="Therm"))+ 
     geom_point(aes(y=RDOTemp_C_5, color="RDO"))+
      labs(y=expression(''*~degree*C*'')) +
    scale_color_manual(name = "Sensor",
                       breaks = c("Therm", "RDO"),
                       values = c("Therm"="firebrick1", "RDO"="blue"))
 
   comp_6_21
```

```{r Thermistor at 6m}
# check 7 temp data
# all the temp 2018-current
 m_7 <- ggplot(data = catdata, aes(x = DateTime, y = ThermistorTemp_C_6)) +
  geom_line()
 m_7
#Only use plotly to find DateTime of questionable values
# ggplotly(m_7)

#filter for the current year
 m_7_21=catdata%>%
  filter(DateTime>ymd_hms(current_time_start) & DateTime<ymd_hms(current_time_end))%>%
   ggplot(.,aes(x = DateTime, y = ThermistorTemp_C_6)) +
   geom_point()
m_7_21
# plotly so you can pick out the questionable values
# ggplotly(m_7_21)
```

```{r Thermistor at 7m}
# check 8 temp data
# Plot 2018-current
 m_8 <- ggplot(data = catdata, aes(x = DateTime, y = ThermistorTemp_C_7)) +
  geom_line()
 m_8
#Only use plotly to find DateTime of questionable values
# ggplotly(m_8)

# # Plot just the current year
 m_8_21=catdata%>%
  filter(DateTime>ymd_hms(current_time_start) & DateTime<ymd_hms(current_time_end))%>%
   ggplot(.,aes(x = DateTime, y = ThermistorTemp_C_7)) +
   geom_point()
 m_8_21
#Only use plotly to find DateTime of questionable values
# ggplotly(m_8_21)
```

```{r Thermistor at 8m}
# check 9 temp data
  # Plot 2018-current
 m_9 <- ggplot(data = catdata, aes(x = DateTime, y = ThermistorTemp_C_8)) +
  geom_line()
 m_9
#Only use plotly to find DateTime of questionable values
# ggplotly(m_9)

# Just the current year
 m_9_21=catdata%>%
  filter(DateTime>ymd_hms(current_time_start) & DateTime<ymd_hms(current_time_end))%>%
   ggplot(.,aes(x = DateTime, y = ThermistorTemp_C_8)) +
   geom_point()
 m_9_21
#Only use plotly to find DateTime of questionable values
 ggplotly(m_9_21)
```

```{r Thermistor at 9m}
# check 9 temp data
  # Plot 2018-current
 m_10 <- ggplot(data = catdata, aes(x = DateTime, y = ThermistorTemp_C_9)) +
  geom_line()
 m_10
#Only use plotly to find DateTime of questionable values
# ggplotly(m_10)

# Just the current year
 m_10_21=catdata%>%
  filter(DateTime>ymd_hms(current_time_start) & DateTime<ymd_hms(current_time_end))%>%
   ggplot(.,aes(x = DateTime, y = ThermistorTemp_C_9)) +
   geom_point()
 m_10_21
#Only use plotly to find DateTime of questionable values
# ggplotly(m_10_21)
 
 # Compare Thermistor with the temperature on the Pressure sensor and temp on the DO sensor
   
   # All the years
   
    comp_m_9 <- ggplot(data = catdata, aes(x = DateTime)) +
    geom_line(aes(y=ThermistorTemp_C_9, color="Therm"))+ 
      geom_line(aes(y=LvlTemp_C_9, color="Pressure"))+
      geom_line(aes(y=RDOTemp_C_9, color="RDO"))+
      labs(y=expression(''*~degree*C*'')) +
    scale_color_manual(name = "Sensor",
                       breaks = c("Therm", "Pressure", "RDO"),
                       values = c("Therm"="firebrick1", "Pressure"="black", "RDO"="blue"))
   comp_m_9
   
   
   
    #Just the current year
   comp_9_21=catdata%>%
    filter(DateTime>ymd_hms(current_time_start) & DateTime<ymd_hms(current_time_end))%>%
     ggplot(.,aes(x = DateTime))+
     geom_point(aes(y=ThermistorTemp_C_9, color="Therm"))+ 
      geom_point(aes(y=LvlTemp_C_9, color="Pressure"))+
     geom_point(aes(y=RDOTemp_C_9, color="RDO"))+
      labs(y=expression(''*~degree*C*'')) +
    scale_color_manual(name = "Sensor",
                      breaks = c("Therm", "Pressure", "RDO"),
                      values = c("Therm"="firebrick1", "Pressure"="black","RDO"="blue"))
 
   comp_9_21
```


```{r All Temperature}

 All_temp_fcr=catdata%>%
    ggplot(.,aes(x = DateTime))+
    geom_line(aes(y=ThermistorTemp_C_surface , color="0.1m"))+
    geom_line(aes(y=ThermistorTemp_C_1, color="1m"))+  
    geom_line(aes(y=ThermistorTemp_C_2, color="2m"))+
    geom_line(aes(y=EXOTemp_C_1, color="EXO_1.6m")) +
    geom_line(aes(y=ThermistorTemp_C_3, color="3m"))+
    geom_line(aes(y=ThermistorTemp_C_4, color="4m"))+
    geom_line(aes(y=ThermistorTemp_C_5, color="5m"))+
    geom_line(aes(y=ThermistorTemp_C_6, color="6m"))+
    geom_line(aes(y=ThermistorTemp_C_7, color="7m"))+
    geom_line(aes(y=ThermistorTemp_C_8, color="8m"))+
    geom_line(aes(y=ThermistorTemp_C_9, color="9m"))+
    labs(y=expression(''*~degree*C*'')) +
    scale_color_manual(name = "Depth",
                       breaks = c("0.1m", "1m","EXO_1.6m", "2m", "3m", "4m", "5m", "6m", "7m",                                         "8m","9m"),
                       values = c("0.1m"="firebrick4", "1m"="firebrick1","EXO_1.6m"="black" ,      "2m"="DarkOrange1","3m"="gold", "4m"="greenyellow","5m"="medium sea green", "6m"="sea green",
                  "7m"="DeepSkyBlue4", "8m"="blue2", "9m"="blue4"))

All_temp_fcr
  
# This is all the temps and just the current year

Cur_temp_fcr=catdata%>%
   filter(DateTime>ymd_hms(current_time_start) & DateTime<ymd_hms(current_time_end))%>%
    ggplot(.,aes(x = DateTime))+
    geom_line(aes(y=ThermistorTemp_C_surface , color="0.1m"))+
    geom_line(aes(y=ThermistorTemp_C_1, color="1m"))+  
    geom_line(aes(y=ThermistorTemp_C_2, color="2m"))+
    geom_line(aes(y=EXOTemp_C_1, color="EXO_1.6m")) +
    geom_line(aes(y=ThermistorTemp_C_3, color="3m"))+
    geom_line(aes(y=ThermistorTemp_C_4, color="4m"))+
    geom_line(aes(y=ThermistorTemp_C_5, color="5m"))+
    geom_line(aes(y=ThermistorTemp_C_6, color="6m"))+
    geom_line(aes(y=ThermistorTemp_C_7, color="7m"))+
    geom_line(aes(y=ThermistorTemp_C_8, color="8m"))+
    geom_line(aes(y=ThermistorTemp_C_9, color="9m"))+
    labs(y=expression(''*~degree*C*'')) +
    scale_color_manual(name = "Depth",
                       breaks = c("0.1m", "1m","EXO_1.6m", "2m", "3m", "4m", "5m", "6m", "7m",                                         "8m","9m"),
                       values = c("0.1m"="firebrick4", "1m"="firebrick1","EXO_1.6m"="black" ,      "2m"="DarkOrange1","3m"="gold", "4m"="greenyellow","5m"="medium sea green", "6m"="sea green",
                  "7m"="DeepSkyBlue4", "8m"="blue2", "9m"="blue4"))
Cur_temp_fcr
  
```

## Check out the Depth sensor and EXO

```{r Pressure Sensor}  
### Plotting depth from pressure sensor 
   
   Depth_press_sensor <- ggplot(data = catdata, aes(x = DateTime, y = LvlDepth_m_9)) +
      geom_line()
   Depth_press_sensor
   #Only use plotly to find DateTime of questionable values
      #ggplotly(Depth_press_sensor)

Depth_press_sensor_current <- catdata%>%
  filter(DateTime>ymd_hms(current_time_start) & DateTime<ymd_hms(current_time_end))%>%
  ggplot(aes(x = DateTime, y = LvlDepth_m_9)) +
      geom_point()
   Depth_press_sensor_current
   #Only use plotly to find DateTime of questionable values
      #ggplotly(Depth_press_sensor_current)

```

```{r EXO 1.5m depth}
#Depth
#Making sure I didn't miss any times when the EXO was out of place according to the depth sensor

#Depth from the 1m EXO
 Depth_1 <- ggplot(data = catdata, aes(x = DateTime, y = EXODepth_m)) +
   geom_line()
 Depth_1
#Only use plotly to find DateTime of questionable values
# ggplotly(Depth_1)
 
#Just the current year
 Depth_1_21=catdata%>%
  filter(DateTime>ymd_hms(current_time_start) & DateTime<ymd_hms(current_time_end))%>%
  ggplot(.,aes(x = DateTime, y = EXODepth_m)) +
   geom_point()
 Depth_1_21
#Only use plotly to find DateTime of questionable values
# ggplotly(Depth_1_21)
``` 
 

## Let's look at the DO sensors both RDOs and  EXO
```{r DO from the EXO at 1.5m }
#Check 1.5m EXO DO data
#Plot 2021-current DO obs
 EXODO_1 <- ggplot(data = catdata, aes(x = DateTime, y = EXODO_mgL_1)) +
   geom_line()
 EXODO_1
 #Only use plotly to find DateTime of questionable values
 #ggplotly(EXODO_1)
 
 EXODOsat_1 <- ggplot(data = catdata, aes(x = DateTime, y = EXODOsat_percent_1)) +
   geom_line()
 EXODOsat_1
 #Only use plotly to find DateTime of questionable values
 #ggplotly(EXODOsat_1)
 
#Plot Just the current year
 EXODO_21=catdata%>%
  filter(DateTime>ymd_hms(current_time_start) & DateTime<ymd_hms(current_time_end))%>%
   ggplot(.,aes(x = DateTime, y = EXODO_mgL_1)) +
   geom_point()
 EXODO_21
#Only use plotly to find DateTime of questionable values
 ggplotly(EXODO_21)
 
 EXODOsat_21=catdata%>%
  filter(DateTime>ymd_hms(current_time_start) & DateTime<ymd_hms(current_time_end))%>%
   ggplot(.,aes(x = DateTime, y = EXODOsat_percent_1)) +
   geom_point()
 EXODOsat_21
#Only use plotly to find DateTime of questionable values
 #ggplotly(EXODOsat_21)
``` 

```{r DO from the 5m RDO} 
# Plot the 9m Do from EXO
# From 2018-current 
 RDO5=ggplot(catdata, aes(x = DateTime, y = RDO_mgL_5)) +
   geom_line()
 RDO5
#Only use plotly to find DateTime of questionable values
 #ggplotly(RDO5)
 
 # From 2018-current 
RDO5_sat=ggplot(catdata, aes(x = DateTime, y = RDOsat_percent_5)) +
   geom_line()
 RDO5_sat
#Only use plotly to find DateTime of questionable values
 #ggplotly(RDO5_sat)
 
 #Just the current year
 RDO5_21=catdata%>%
  filter(DateTime>ymd_hms(current_time_start) & DateTime<ymd_hms(current_time_end))%>%
   ggplot(.,aes(x = DateTime, y = RDO_mgL_5)) +
   geom_point()
 RDO5_21
#Only use plotly to find DateTime of questionable values
 #ggplotly(RDO5_21)
 
 RDO5sat_21=catdata%>%
  filter(DateTime>ymd_hms(current_time_start) & DateTime<ymd_hms(current_time_end))%>%
   ggplot(.,aes(x = DateTime, y = RDOsat_percent_5)) +
   geom_point()
 RDO5sat_21
#Only use plotly to find DateTime of questionable values
 #ggplotly(RDO5sat_21)
```

```{r DO from the 9m RDO} 
# Plot the 9m Do from the RDO DO sensor
# From 2018-current 
 RDO9=ggplot(catdata, aes(x = DateTime, y = RDO_mgL_9)) +
   geom_line()
 RDO9
#Only use plotly to find DateTime of questionable values
 #ggplotly(RDO9)
 
 # From 2018-current 
RDO9_sat=ggplot(catdata, aes(x = DateTime, y = RDOsat_percent_9)) +
   geom_line()
 RDO9_sat
#Only use plotly to find DateTime of questionable values
 #ggplotly(RDO9_sat)
 
 #Just the current year
 RDO9_21=catdata%>%
  filter(DateTime>ymd_hms(current_time_start) & DateTime<ymd_hms(current_time_end))%>%
   ggplot(.,aes(x = DateTime, y = RDO_mgL_9)) +
   geom_point()
 RDO9_21
#Only use plotly to find DateTime of questionable values
 #ggplotly(RDO9_21)
 
 RDO9sat_21=catdata%>%
  filter(DateTime>ymd_hms('2022-11-01 00:00:00') & DateTime<ymd_hms('2022-11-15 00:00:00'))%>%
   ggplot(.,aes(x = DateTime, y = RDOsat_percent_9)) +
      geom_point(aes(x = DateTime, y = RDOsat_percent_5, col = 'pink')) +
   geom_point()
 RDO9sat_21
 
 # questionable values on 2022-11-07 14:40:00 until 2022-11-08 14:40:00
 # the crash was due to the SSS coming to the surface, the increase in DO follows turning the SSS back on, so this data should be left in


 #Only use plotly to find DateTime of questionable values
 #ggplotly(RDO9sat_21)
```

##Check out the Algae Senor on the EXO
```{r Check the EXO Chla}

# chl and phyco visual qaqc-plot to see if everything looks right

# Chla 1m EXO
# Plot for 2021-current
 chl_ugl_1 <- ggplot(data = catdata, aes(x = DateTime, y = EXOChla_ugL_1)) +
   geom_line() 
 chl_ugl_1
#Only use plotly to find DateTime of questionable values
 #ggplotly(chl_ugl_1)
 
# Plot just the current year
 chl_ugl_1_21=catdata%>%
  filter(DateTime>ymd_hms(current_time_start) & DateTime<ymd_hms(current_time_end))%>%
   ggplot(.,aes(x = DateTime, y = EXOChla_ugL_1)) +
   geom_point()
 chl_ugl_1_21
 #Only use plotly to find DateTime of questionable values
 #ggplotly(chl_ugl_1_21)
 
# plot the daily mean
# calculate the daily mean
 chl_mean_1 <- catdata %>%
  select(DateTime, EXOChla_ugL_1) %>%
  mutate(day = date(DateTime)) %>%
  group_by(day) %>%
  mutate(daily_mean = mean(EXOChla_ugL_1, na.rm = TRUE)) %>%
  distinct(day, .keep_all = TRUE)
# 
# plot the daily mean
 chl_mean_plot <- ggplot(data = chl_mean_1, aes(x = day, y = daily_mean)) +
  geom_point()
 chl_mean_plot
#Only use plotly to find DateTime of questionable values
 #ggplotly(chl_mean)

# Plot the chla and the daily mean on the same graph
 plot(catdata$DateTime, catdata$EXOChla_ugL_1)
 points(chl_mean_1$DateTime, chl_mean_1$daily_mean, type="l", col="green")

 
# Chla-RFU
# Plot 2021-current
 chl_rfu <- ggplot(data = catdata, aes(x = DateTime, y = EXOChla_RFU_1)) +
   geom_line()
 chl_rfu
#Only use plotly to find DateTime of questionable values
 #ggplotly(chl_rfu)

# Just the current year
 chl_rfu_21=catdata%>%
  filter(DateTime>ymd_hms(current_time_start) & DateTime<ymd_hms(current_time_end))%>%
   ggplot(.,aes(x = DateTime, y = EXOChla_RFU_1)) +
   geom_point()
 chl_rfu_21
# ggplotly(chl_rfu_21)
```


```{r Check out the Phyco in EXO}
# Phyco-RFU
# Plot 2018-current
 phyco_rfu <- ggplot(data = catdata, aes(x = DateTime, y = EXOBGAPC_RFU_1)) +
   geom_line() 
 phyco_rfu
#Only use plotly to find DateTime of questionable values
 #ggplotly(phyco_rfu)
 
# Just the current year
 phyco_rfu_21=catdata%>%
  filter(DateTime>ymd_hms(current_time_start) & DateTime<ymd_hms(current_time_end))%>%
   ggplot(.,aes(x = DateTime, y = EXOBGAPC_RFU_1)) +
   geom_point()
#Only use plotly to find DateTime of questionable values
 #ggplotly(phyco_rfu_21)

 # Phyco-ugL
# Plot 2021-current
 phyco_ugl <- ggplot(data = catdata, aes(x = DateTime, y = EXOBGAPC_ugL_1)) +
   geom_line() 
 phyco_ugl
#Only use plotly to find DateTime of questionable values
 #ggplotly(phyco_ugl)
 
# Just the current year
 phyco_ugl_21=catdata%>%
  filter(DateTime>ymd_hms(current_time_start) & DateTime<ymd_hms(current_time_end))%>%
   ggplot(.,aes(x = DateTime, y = EXOBGAPC_ugL_1)) +
   geom_point()
# ggplotly(phyco_ugl_21)
#Only use plotly to find DateTime of questionable values
 #ggplotly(phyco_ugl_21)
```

# Check out the fDOM sensor
```{r fdom EXO sensor}
#fDOM-RFU 1m EXO
# Plot 2021-current
 fDOM_rfu_1 <- ggplot(data = catdata, aes(x = DateTime, y = EXOfDOM_RFU_1)) +
   geom_line() 
 fDOM_rfu_1
#Only use plotly to find DateTime of questionable values
 #ggplotly(fDOM_rfu_1)
 
# Just the current year
 fDOM_rfu_1_21=catdata%>%
  filter(DateTime>ymd_hms(current_time_start) & DateTime<ymd_hms(current_time_end))%>%
   ggplot(.,aes(x = DateTime, y = EXOfDOM_RFU_1)) +
   geom_point()
 fDOM_rfu_1_21
#Only use plotly to find DateTime of questionable values
 #ggplotly(fDOM_rfu_1_21)
 
  # fDOM-QSU 1m EXO
# Plot 2021-current
 fDOM_qsu_1 <- ggplot(data = catdata, aes(x = DateTime, y = EXOfDOM_QSU_1)) +
   geom_line() 
 fDOM_qsu_1
 #Only use plotly to find DateTime of questionable values
 #ggplotly(fDOM_qsu_1)
 
# Just the current year
 fDOM_qsu_1_21=catdata%>%
  filter(DateTime>ymd_hms(current_time_start) & DateTime<ymd_hms(current_time_end))%>%
   ggplot(.,aes(x = DateTime, y = EXOfDOM_QSU_1)) +
   geom_point()
 fDOM_qsu_1_21
#Only use plotly to find DateTime of questionable values
# ggplotly(fDOM_qsu_1_21)
```


## EXO Conductivity Sensor
```{r EXO Condctivity Sensor at 1.5m }

Cond_1 <- ggplot(data = catdata, aes(x = DateTime, y = EXOCond_uScm_1)) +
   geom_line()
 Cond_1
#Only use plotly to find DateTime of questionable values
 #ggplotly(Cond_1)

#Just the current year
 
 Cond_1_21=catdata%>%
  filter(DateTime>ymd_hms(current_time_start) & DateTime<ymd_hms(current_time_end))%>%
   ggplot(.,aes(x = DateTime, y = EXOCond_uScm_1)) +
   geom_point()
 Cond_1_21
#Only use plotly to find DateTime of questionable values
 #ggplotly(Cond_1_21)
 
 
 #Plot from 2018-current
 SpCond_1 <- ggplot(data = catdata, aes(x = DateTime, y = EXOSpCond_uScm_1)) +
   geom_line()
 SpCond_1
#Only use plotly to find DateTime of questionable values
 #ggplotly(SpCond_1)
 
#Just the current year
 SpCond_1_21=catdata%>%
  filter(DateTime>ymd_hms(current_time_start) & DateTime<ymd_hms(current_time_end))%>%
   ggplot(.,aes(x = DateTime, y = EXOSpCond_uScm_1)) +
   geom_point()
 SpCond_1_21
#Only use plotly to find DateTime of questionable values
# ggplotly(SpCond_1_21)
```

TDS is derived from conductivity so you don't necessarily have to plot this because if 
conductivity is fine then TDS should be too
```{r TDS at 1.5m and 9m}
# #Total Dissolved Solids
#TDS for 1m EXO
 TDS_1 <- ggplot(data = catdata, aes(x = DateTime, y = EXOTDS_mgL_1)) +
   geom_line()
 TDS_1
#Only use plotly to find DateTime of questionable values
# ggplotly(TDS_1)
 
#Just the current year
 TDS_1_21=catdata%>%
  filter(DateTime>ymd_hms(current_time_start) & DateTime<ymd_hms(current_time_end))%>%
   ggplot(.,aes(x = DateTime, y = EXOTDS_mgL_1)) +
   geom_point()
 TDS_1_21
 #Only use plotly to find DateTime of questionable values
# ggplotly(TDS_1_21)
```

# How to update the Maintenance Log
If there were any rouge observations that were missed then add them to the maintenance log.
I like to edit the maintenance file right on Github by clicking the "edit this file" pencil in the right hand corner.  

Here is the link https://github.com/FLARE-forecast/FCRE-data/blob/fcre-catwalk-data/CAT_MaintenanceLog.txt
 
How TO:
1)Add the beginning time and the end time. All times are in EST

2)Next add the *parameter*: 
For all rows use All_cat, for just the EXO use EXO*,just the temp string use wtr*,
for RDO sensors use do*, for pressure sensor use Lvl*. For just one senor use the first few letters. This is not used to subset in the maintenance log but helps know what is happening. 

3)Next add the columns that match the parameters know as *colnumber*. The column order is from the FCR_catwalk_QAQC_function.R script before the Reservoir and Site column have been added so it includes all the flags and the EXODate and EXOTime columns which are removed at the end of the script. See column order below.  You can use a single number or c(1:x)

All_cat is c(1:42), EXO* is c(21:40), wtr* is c(1:14), do* is c(15:20), Lvl*, c(41:42)

The flag column let's you know what is wrong with the data and is put in the flag column. 
See below: 
 Flag values
  0: no flag
  1: value removed due to maintenance and set to NA
  2: negative or outlier value removed and set to NA, see Methods section for more detail on QAQC process
  3: negative values set to 0
  4: value removed due to fouling and set to NA
  5: questionable value due to potential fouling
  6: very questionable value due to potential fouling. Values adjusted using a linear or square root function     to match high-resolution CTD profiles are given in RDO_mgL_5 and RDO_sat_percent_5
  7: missing data
  8: Value corrected using a constant offset due to two thermistor malfunctions in Fall 2020


4)The *flagcol* is the columns where the flag will go. See the column order to make sure you have the correct column. This functions same as the *colnumber*.

5) Last is the *notes* column where you give a brief description of what is wrong. DO NOT USE ANY PUNCTUATION ESPECIALLY COMMAS


This is the column order to figure out the column numer for *colnumber* and *flagcol*:

"DateTime"                      "RECORD"                        "CR6_Battery_V"                   
 [4] "CR6Panel_Temp_C"               "ThermistorTemp_C_surface"      "ThermistorTemp_C_1"           
 [7] "ThermistorTemp_C_2"            "ThermistorTemp_C_3"            "ThermistorTemp_C_4"           
[10] "ThermistorTemp_C_5"            "ThermistorTemp_C_6"            "ThermistorTemp_C_7"           
[13] "ThermistorTemp_C_8"            "ThermistorTemp_C_9"            "RDO_mgL_5"                    
[16] "RDOsat_percent_5"              "RDOTemp_C_5"                   "RDO_mgL_9"                    
[19] "RDOsat_percent_9"              "RDOTemp_C_9"                   "EXO_Date"                     
[22] "EXO_Time"                      "EXOTemp_C_1"                   "EXOCond_uScm_1"               
[25] "EXOSpCond_uScm_1"              "EXOTDS_mgL_1"                 "EXODOsat_percent_1"           
[28] "EXODO_mgL_1"                   "EXOChla_RFU_1"                 "EXOChla_ugL_1"                
[31] "EXOBGAPC_RFU_1"                "EXOBGAPC_ugL_1"                "EXOfDOM_RFU_1"                
[34] "EXOfDOM_QSU_1"                 "EXOTurbidity_FNU_1"            "EXOpressure_psi"             
[37] "EXODepth_m"                   "EXOBattery_V"                 "EXOcablepower_V"             
[40] "EXOwiper_V"                   "Lvlpsi_9"                     "LvlTemp_C_9"                  
[43] "Flag_ThermistorTemp_C_surface" "Flag_ThermistorTemp_C_1"  "Flag_ThermistorTemp_C_2"      
[46] "Flag_ThermistorTemp_C_3"       "Flag_ThermistorTemp_C_4"       "Flag_ThermistorTemp_C_5"      
[49] "Flag_ThermistorTemp_C_6"       "Flag_ThermistorTemp_C_7"       "Flag_ThermistorTemp_C_8"      
[52] "Flag_ThermistorTemp_C_9"       "Flag_RDO_mgL_5"                "Flag_RDOsat_percent_5"        
[55] "Flag_RDOTemp_C_5"              "Flag_RDO_mgL_9"                "Flag_RDOsat_percent_9"        
[58] "Flag_RDOTemp_C_9"              "Flag_EXOTemp_C_1"              "Flag_EXOCond_uScm_1"          
[61] "Flag_EXOSpCond_uScm_1"         "Flag_EXOTDS_mgL_1"             "Flag_EXODOsat_percent_1"      
[64] "Flag_EXODO_mgL_1"              "Flag_EXOChla_RFU_1"            "Flag_EXOChla_ugL_1"           
[67] "Flag_EXOBGAPC_RFU_1"           "Flag_EXOBGAPC_ugL_1"           "Flag_EXOfDOM_RFU_1"           
[70] "Flag_EXOfDOM_QSU_1"            "Flag_EXOTurbidity_FNU_1"       "Flag_EXOpressure_psi"        
[73] "Flag_EXODepth_m"              "Flag_EXOBattery_V"            "Flag_EXOcablepower_V"        
[76] "Flag_EXOwiper_V"              "Flag_Lvlpsi_9"                "Flag_LvlTemp_C_9"             
   

If you make any changes to the maintenance log you have to run the qaqc_fcr function again so the changes are incorporated. Make sure to re download the Maintenance log.  

## Final steps before final csv

These are the final steps before publishing the final csv.I like to put DateTime as.character when I save the file because we have had issues with timezones in the past and this ensures they stay consistent when we write to a csv. 

```{r Final Steps}

#Order by date and time this is a triple check to make sure it is in chrological order

catdata <- catdata[order(catdata$DateTime),]

#rearrange the cols. They should already be in order but just making sure. 
 catdata <- catdata %>%
  select(Reservoir, Site, DateTime, ThermistorTemp_C_surface:ThermistorTemp_C_9,
         RDO_mgL_5, RDOsat_percent_5, RDO_mgL_5_adjusted, RDOsat_percent_5_adjusted,
         RDOTemp_C_5, RDO_mgL_9, RDOsat_percent_9, RDO_mgL_9_adjusted, RDOsat_percent_9_adjusted,
         RDOTemp_C_9,EXOTemp_C_1, EXOCond_uScm_1, EXOSpCond_uScm_1, EXOTDS_mgL_1, EXODOsat_percent_1,
         EXODO_mgL_1, EXOChla_RFU_1, EXOChla_ugL_1, EXOBGAPC_RFU_1, EXOBGAPC_ugL_1,
         EXOfDOM_RFU_1, EXOfDOM_QSU_1,EXOTurbidity_FNU_1, EXOpressure_psi, EXODepth_m, EXOBattery_V,          EXOcablepower_V,EXOwiper_V, Lvlpsi_9, LvlTemp_C_9, LvlDepth_m_9, RECORD, CR6Battery_V,          CR6Panel_Temp_C,Flag_ThermistorTemp_C_surface:Flag_ThermistorTemp_C_9,Flag_RDO_mgL_5, Flag_RDOsat_percent_5, Flag_RDOTemp_C_5,
         Flag_RDO_mgL_9, Flag_RDOsat_percent_9, Flag_RDOTemp_C_9,Flag_EXOTemp_C_1, Flag_EXOCond_uScm_1, Flag_EXOSpCond_uScm_1,Flag_EXOTDS_mgL_1,
         Flag_EXODOsat_percent_1, Flag_EXODO_mgL_1, Flag_EXOChla_RFU_1,Flag_EXOChla_ugL_1, Flag_EXOBGAPC_RFU_1,Flag_EXOBGAPC_ugL_1,
         Flag_EXOfDOM_RFU_1,Flag_EXOfDOM_QSU_1,Flag_EXOTurbidity_FNU_1, Flag_EXOpressure_psi, Flag_EXODepth_m, Flag_EXOBattery_V, Flag_EXOcablepower_V,
         Flag_EXOwiper_V, Flag_Lvlpsi_9, Flag_LvlTemp_C_9)

# convert datetimes to characters so that they are properly formatted in the output file
  catdata$DateTime <- as.character(catdata$DateTime)
  
write.csv(catdata, 'FCR_Catwalk_EDI_2018_2022.csv', row.names = FALSE)
```

```{r Make Maintenance Log for pub}
# Make the Maintenance Log into a csv and add Reservoir and Site column 
  Log <- read.csv(maintenance_file)
 names(Log) = c("Station", "DateTime_start","DateTime_end", "Parameter", "ColumnNumber","Flag", "FlagColumn", "Notes") #finalized column names
Log$Reservoir= "FCR"#add reservoir name for EDI archiving
Log$Site=50 #add site column for EDI archiving

Log=Log[,c(9:10,1:8)]
 
write.csv(Log, "FCR_CAT_MaintenanceLog_2018_2022.csv", row.names=F, quote=F)
```