---
title: "Metals_inspection_2014_2024"
author: "Adrienne Breef-Pilz"
created: "2023-11-15"
output: html_document
date:  "`r Sys.Date()`"
---

This script is the visual inspection script. 

1. QAQCs all the raw data or for a reviewer reads in the data file from EDI for checking. 

2. Then the script checks for duplicates, daily, and subdaily gaps in the current file. 

3. Lists the flag frequency to check if there are any NAs or any assigned the wrong flag. 

4. Checks to see if the Maintenance Log is working correctly by inspecting rows in the data frame. 

5. Creates plots

6. Writes data to new csv

7. Downloads necessary files for EDI publishing


All files are from GitHub or EDI and the source scripts are from GitHub as well. 

If you are REVIEWING this data package, add the pasta URL from EDI in the "READ IN EDI FOR REVIEWER". Make sure eval=FALSE is in the chunk header for "Get raw files", "QAQC all files", "Write CSV" and "Download and save Maintenance Log". You don't need to remake the data files when you are reviewing the data package. These chunks of code will not be run when the R markdown is knitted together and saves you LOTTTS of time. Once that is all set than you can knit the file together as an HTML file to look at all the plots. 

If you are running the code chunk by chunk you mind need to make some adjustments to the code. To make the plots this markdown uses a function called "all_plots". In the function it creates a plots of the most current year, the whole times series, as well as, density and box plots for daily averages. You can also specify if you would like to produce a heat map. Note that heat maps are only produced if your data has a depth column. The function also allows you to choose if you want interactive plots, using plotly, for the most recent year of data. The plotly plots are designed to be in order with the other plots when knit to together. Therefore if you are running the ploting section, chunk by chunk, then you need to specify the plotly plot from the list of plots labeled "output". For this data package do not use plotly for all plots at one time. I usually use it for depth, oxygen, and chla. 

FOR DATA PRODUCT LEAD:

If you are the data product lead and making the data package then:

1. Make sure all the date ranges are up to date especially current_time_start and current_time_end.

2. Change the years in the saved data files in "Write CSV" and "Download and save Maintenance Log" chunk.

3. Make sure to un comment and change the settings for the "Get raw files", "QAQC all files",  and "Write CSV" chunks. Also check the settings for the chunk eval=TRUE or it shouldn't be there. 

4. Comment out the Reviewer section and make sure for the settings eval = FALSE.

5. Update the data frame in "Get raw files" to include the most recent file on GitHub.

6. Knit the file. This will take a long time. 

7. Look over the plots and see if there are any issues that need to be added to the maintenance log. I will usually read in the file you just made and make smaller plots with the variable and month in question. Once I have the dates, add them to the maintenance log. 

8. Re-run the inspection script until you have found all of the issues. 

9. Run the "Download and save Maintenance Log" chunk to have the most up to date files in the EDI folder.

10. Make sure large maintenance issues are also documented in the methods.txt file. 


```{r Set Up, include=FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(RCurl,devtools, tidyverse,lubridate, gsheet, rqdatatable, hms, plotly, magrittr, future.apply, scattermore, knitr, htmltools, pander, akima, reshape2, gridExtra, grid, colorRamps, RColorBrewer, cowplot)

# Source scripts from GitHub
# QAQC script
# Will need to update this link when we rename the script and move it to the Scripts/L1_functions folder
source("https://raw.githubusercontent.com/CareyLabVT/Reservoirs/master/Scripts/L1_functions/metals_create.R")


# Plotting script
source('https://raw.githubusercontent.com/CareyLabVT/Reservoirs/master/Data/DataAlreadyUploadedToEDI/EDIProductionFiles/Plotting_function.R')
#source("../../Plotting_function.R")


 #turn off pander auto asis
        pander::panderOptions('knitr.auto.asis', FALSE)

# Set up the current time end time of the file and the current year for QAQC plots

#current time of QAQC for graphing
current_time_start=ymd_hms("2025-01-01 00:00:00", tz="America/New_York")
current_time_end=ymd_hms("2025-12-31 23:59:00", tz="America/New_York")
```


```{r QAQC all files, eval=TRUE, include=FALSE}

# Run the QAQC function to QAQC all raw data. Do this when you are preparing the data #file for EDI. 

current_df <- metals_qaqc(directory = "../../../../DataNotYetUploadedToEDI/Metals_Data/Raw_Data/",
historic = "https://raw.githubusercontent.com/CareyLabVT/Reservoirs/refs/heads/master/Data/DataNotYetUploadedToEDI/Metals_Data/Raw_Data/historic_raw_2014_2019_w_unique_samp_campaign.csv",
 sample_ID_key =  "https://raw.githubusercontent.com/CareyLabVT/Reservoirs/master/Data/DataNotYetUploadedToEDI/Metals_Data/Scripts/Metals_Sample_Depth.csv", 
 maintenance_file = "https://raw.githubusercontent.com/CareyLabVT/Reservoirs/master/Data/DataNotYetUploadedToEDI/Metals_Data/Metals_Maintenance_Log.csv",
 sample_time = "https://docs.google.com/spreadsheets/d/1MbSN2G_NyKyXQUEzfMHmxEgZYI_s-VDVizOZM8qPpdg/edit#gid=0",
 MRL_file = "https://raw.githubusercontent.com/CareyLabVT/Reservoirs/master/Data/DataNotYetUploadedToEDI/Metals_Data/MRL_metals.txt",
         metals_save = TRUE,
         metals_outfile = NULL, # put Null to return the file
          ISCO_save = F, # ISCO file will not be saved and will not be returned
         ISCO_outfile = "dont_save.csv", # put Null to return the file
         start_date = as.Date('2014-01-01'),
         end_date = NULL)


# # Filter so we only go through the end of the reporting year 
  current_df <- current_df%>%
  dplyr::distinct(.)%>% # get rid of dups if they snuck in
  filter(DateTime<(current_time_end))


#reorder. Just to be certain everything is in order
  current_df<-current_df[order(current_df$DateTime),]


  
```

REVIEWERS- If you are reviewing this data package replace the pasta link with the one from EDI. If there are questions ask the data point person. There are two ways to use this script. You can either run it by chunks or you can knit it and make an html file. Knitting the file will run all the chunks and create an html page with all the plots. I like doing this because I can see all the plots in one place. The Knit button is on the top of the file with a ball of yarn and a needle next to it. 

```{r QAQC file or READ IN EDI FOR REVIEWER, include=FALSE}


# # For REVIEWERS: Run this section to pull the data from EDI which is in staging as a check of the data.
# # MAKE SURE TO UPDATE THE PASTA FROM THE VERSION YOU WANT

                                                                ### CHANGE THIS NUMBER BELOW
                                                                             ##
 #current_df <-read_csv("https://pasta-s.lternet.edu/package/data/eml/edi/718/7/9c8c61b003923f4f03ebfe55cea8bbfd")
 # 
 # # Force files from EDI to have an EST timestamp
 #current_df$DateTime <- force_tz(as.POSIXct(current_df$DateTime), tzone = "America/New_York")

```

### Flag Frequency

This section checks to make sure each observation has a data flag. It also checks to make sure the frequency of flags match what we expect to see. 

Let's look at the flag Frequency for each variable. As a reminder here are the flag codes
 Flag values
 
 0: no flag
 
 1: sample not taken
 
 2: instrument malfunction
 
 3: sample below MRL and set to MRL
 
 4: negative value set to MRL
 
 6: non-standard method
 
 7: sample run multiple times and values averaged
 
 8: abnormally high concentration that is greater than 3 sd above the mean
 
 9: total and soluble samples switched prior to analysis; fixed in QAQC
 
 10: improper procedure and set to NA
 
 63: non-standard method and sample below MRL and set to MRL
 
 64: non-standard method and negative value set to MRL

```{r Check there are no NAs in Flag columns, echo=FALSE}

#make sure no NAS in the Flag columns
Flags=current_df%>%
  select(DateTime, starts_with("Flag"))

RowsNA=Flags[!complete.cases(Flags), ] # Keep only the complete rows

#check the flag column
Flags=current_df%>%
  select(starts_with("Flag"))

# Make a table with the number of times a flag was used
for(f in 1:(ncol(Flags))){
  print(colnames(Flags[f]))
  print(table(Flags[,f], useNA = "always"))
}

```

### Check to make sure that what is in the maintenance log was actually removed

### Look at the last rows of the maintenance log 

We want to make sure that our maintenance log actually worked and took out the values or changes those it was supposed to 

```{r Read in the maintenance log and look at the tail, echo=FALSE}

# The streaming sensors use semicolons as a deliminator because of the adjustment_code column. We use the read_csv2 to read in the file. 
 maint <- read_csv("https://raw.githubusercontent.com/CareyLabVT/Reservoirs/master/Data/DataNotYetUploadedToEDI/Metals_Data/Metals_Maintenance_Log.csv",
                    show_col_types = FALSE)|>
  filter(Site != 100.1)


# name the data file for just the tail of the maintenance log

sd <- tail(maint)


knitr::kable((tail(sd)))

```

#### Check the that the columns have flags 

Look at the first few rows of the data frame and check that the observations after are flagged.
Some of the flags are added to in the script so the value was flagged with 6 in the maintenance log 
but in the script it was added to because the value was lower than the Minimum reporting level. 
Just make sure that one of the values is in the mainteance log.

#### Look at the first row in the maintenance time. Is the correct observation flagged?

Make sure the observations are flagged

```{r Print the tails, echo=FALSE}

# Print the tail of the table to make sure that data are flagged

last_row <- head(sd, n=1)

# Get parameters for subsetting
### get start and end time of one maintenance event
    start <- as.Date(last_row$Sample_Date)
    
    # Reservoir 
    Res <- last_row$Reservoir
    
    # Site 
    Sit <- as.numeric(last_row$Site)
    
    # Depth
    Dep <- as.numeric(last_row$Depth_m)
    
    # Filter
    Filt <- last_row$Filter


### Get the names of the columns affected by maintenance
    colname_start <- last_row$start_parameter
    colname_end <- last_row$end_parameter
    
     # What we want to filter from 
    
    check <- (as.Date(current_df$DateTime) %in% start & 
            current_df$Reservoir %in% Res & 
              current_df$Site %in% Sit &
              current_df$Depth_m %in% Dep) 
    
    # Make list of just the columns we want 
    
    test <- colnames(current_df%>%select(Reservoir,Site, DateTime, Depth_m,paste0(Filt, colname_start), paste0("Flag_",Filt,colname_start), paste0(Filt,colname_end), paste0("Flag_", Filt,colname_end)))
    
    

# Print the head of the table to make sure that data are flagged
    
    knitr::kable((head(current_df[check, test])))

```

#### Look at the last row of the maintenance log. Are the columns flagged?

```{r Did the maint log work head, echo=FALSE}
# get the last row of the data file
last_row <- tail(sd, n=1)

# Get parameters for subsetting
### get start and end time of one maintenance event
    start <- as.Date(last_row$Sample_Date)
    
    # Reservoir 
    Res <- last_row$Reservoir
    
    # Site 
    Sit <- as.numeric(last_row$Site)
    
    # Depth
    Dep <- as.numeric(last_row$Depth_m)
    
    # Filter
    Filt <- last_row$Filter


### Get the names of the columns affected by maintenance
    colname_start <- last_row$start_parameter
    colname_end <- last_row$end_parameter
    
    
    # What we want to filter from 
    
    check <- (as.Date(current_df$DateTime) %in% start & 
            current_df$Reservoir %in% Res & 
              current_df$Site %in% Sit &
              current_df$Depth_m %in% Dep) 
    
    # Make list of just the columns we want 
    
    test <- colnames(current_df%>%select(Reservoir,Site, DateTime, Depth_m,paste0(Filt, colname_start), paste0("Flag_",Filt,colname_start), paste0(Filt,colname_end), paste0("Flag_", Filt,colname_end)))
    
    # Print the head of the table to make sure that data are flagged
    
    knitr::kable((head(current_df[check, test]))) 

```

## QAQC Plots

##### QAQC plot information and all_plot function information

For the plots, they use a function called "all_plot". In all_plot you can specify if you want interactive plots for the current data. You can specify which plotly plots you want on. You can also look at the plotly plots manually in each chunk by running the chunk with Use_plotly=TRUE as an argument. Then look at the list of plots you have made under "output". If you click on the "output" object in your environment it will list all of the plots and which ones are interactive plotly plots. To view the plots run "output[[number of the plot in the list you want to run]]". Eg. If you want to see the 4th plot in the list write output[[4]] then run that line and the plot should appear. 

If you would like to look at one variable then in the function below replace "dx" with the variable column. The object "dx" is just a list of variables so we don't have to list out all of the variables we want to plot. This is used to speed up the process. 

The plotting function is called all_plot() which plots the 4 or more plots described below. The function is sourced from GitHub in the first chunk of the script. The arguments are:
Var, # the variable you would like to plot
data, # the data frame to use
raw_data=NULL, # Is there raw data to compare with. Usually is NULL
reservoir, # the name of the reservoir you would like to filter by 
res_site, # the reservoir Site or Sites you would like to filter by
y_lab,  # This label can take an expression aka have the proper degrees C, 
y_lab2, # This label is for the plotly function which can not handle expression argument. 
Depth=F,  # Do you want depth as a factor
Water=T, # Are these plots for streaming sensors with RDO and temperature sensors
Use_plotly = F, # Do you want to produce interactive plots for observations of the current year?
Heatmap = F) # Do you want to make a heat maps? This only works if there are multiple depths at the same site


The arguments with = followed by a True means that they are the defaults and you don't need to add them to the function when you use it. If you want to use the opposite of the default you must specify that. 
  
##### Plot Description:

The plots below are:
The first 2 plots are the ones you should focus on for the QAQC chec. Spend the most time looking at the most recent data because that one as been checked. Do pay attention to the historical to make sure there are no crazy outliers that were missed in previous years. 

1. A time series of the current years' data. This can either be a regular plot or an interactive one. If you would like it to be interactive set Use_plotly = T. The black dots are the qaqced observations and the red is the raw files that were qaqced. This is to see what kind of values were removed and if there are any the script missed or that need to be added to the maintenance log. 

2. A time series of the historical and the current data just the qaqced values. 

The next two plots are just fun to see trends over time with the data. 

3. Density plots are like a histogram and a grouped by color so you can see where the data are relative to other years. 

4. The box plots look at the spread of the data within the year and we can look at the median and see how that is changing or not. 

Do not over think the last 2 plots, although they are good to look at historical trends to ensure relative data quality consistency. 


### FCR 50 - samples from the catwalk 

```{r QAQC FCR 50 Plots, echo=FALSE, warning=FALSE, results='asis', time_it = TRUE}

dx <- colnames(current_df%>%select(TLi_mgL:SBa_mgL))

# make the plots
outputs <- lapply(dx, all_plot, data=current_df, reservoir = "FCR", res_site=50, y_lab = "mg/L", y_lab2 = "mg/L",Depth=T, Water=F, Use_plotly=T, Heatmap = T)

output <- unlist(outputs, recursive = F)

#output[[1]]

```

```{r Print plotly F50, echo=FALSE, warning=FALSE, messages=FALSE}

 # Used to print the plotly plots
  # attach the Dependencies
  # since the do not get included with renderTags(...)$html
  deps <-  lapply(
    Filter(function(x){inherits(x,"htmlwidget")},output),
    function(hw){
      renderTags(hw)$dependencies
    }
  )
  
  if(length(deps)>0){
  attachDependencies(
    tagList(),
    unlist(deps,recursive=FALSE)
  )
  }  
```



### FCR 100-samples from the weir

```{r QAQC FCR 100 Plots, eecho=FALSE, warning=FALSE, results='asis', time_it = TRUE}

dx <- colnames(current_df%>%select(TLi_mgL:SBa_mgL))

# make the plots

outputs <- lapply(dx, all_plot, data=current_df, reservoir = "FCR", res_site=100, y_lab = "mg/L", y_lab2 = "mg/L",Depth=T, Water=F, Use_plotly=T, Heatmap = T)

output <- unlist(outputs, recursive = F)

#output[[1]]

```

```{r Print plotly F100, echo=FALSE, warning=FALSE, messages=FALSE}

 # Used to print the plotly plots
  # attach the Dependencies
  # since the do not get included with renderTags(...)$html
  deps <- lapply(
    Filter(function(x){inherits(x,"htmlwidget")},output),
    function(hw){
      renderTags(hw)$dependencies
    }
  )
  
  if(length(deps)>0){
  attachDependencies(
    tagList(),
    unlist(deps,recursive=FALSE)
  )
  }  
```

### FCR 1 - samples from the outflow at FCR

```{r QAQC FCR 1 Plots, eval=FALSE, warning=FALSE, include=FALSE, results='asis', time_it=TRUE}

dx <- colnames(current_df%>%select(TLi_mgL:SBa_mgL))

# make the plots
outputs <- lapply(dx, all_plot, data=current_df, reservoir = "FCR", res_site=1, y_lab = "mg/L", y_lab2 = "mg/L",Depth=T, Water=F, Use_plotly=T, Heatmap = F)

output <- unlist(outputs, recursive = F)

#output[[1]]

```

```{r Print plotly F1, eval=FALSE, warning=FALSE, include=FALSE, messages=FALSE}

 # Used to print the plotly plots
  # attach the Dependencies
  # since the do not get included with renderTags(...)$html
  deps <-  lapply(
    Filter(function(x){inherits(x,"htmlwidget")},output),
    function(hw){
      renderTags(hw)$dependencies
    }
  )
  
  if(length(deps)>0){
  attachDependencies(
    tagList(),
    unlist(deps,recursive=FALSE)
  )
  }  
```



### BVR 50 - samples from the platform at BVR

```{r QAQC BVR 50 Plots, echo=FALSE, warning=FALSE, results='asis', time_it = TRUE}


dx <- colnames(current_df%>%select(TLi_mgL:SBa_mgL))

# make the plots

outputs <- lapply(dx, all_plot, data=current_df, reservoir = "BVR", res_site=50, y_lab = "mg/L", y_lab2 = "mg/L",Depth=T, Water=F, Use_plotly=T, Heatmap = T)

output <- unlist(outputs, recursive = F)

#output[[1]]

```

```{r Print plotly B50, echo=FALSE, warning=FALSE, messages=FALSE}

 # Used to print the plotly plots
  # attach the Dependencies
  # since the do not get included with renderTags(...)$html
  deps <- lapply(
    Filter(function(x){inherits(x,"htmlwidget")},output),
    function(hw){
      renderTags(hw)$dependencies
    }
  )
  
  if(length(deps)>0){
  attachDependencies(
    tagList(),
    unlist(deps,recursive=FALSE)
  )
  }  
```

### BVR 40 - Samples from the outflow pipe at BVR that goes to FCR. 

These samples were taken in 2022 and it might not be necessary to plot this each time. 

```{r QAQC BVR 40 Plots, eval=FALSE, warning=FALSE, include=FALSE, results='asis', time_it=TRUE}

dx <- colnames(current_df%>%select(TLi_mgL:SBa_mgL))

# make the plots

outputs <- lapply(dx, all_plot, data=current_df, reservoir = "BVR", res_site=40, y_lab = "mg/L", y_lab2 = "mg/L",Depth=T, Water=F, Use_plotly=T, Heatmap = F)

output <- unlist(outputs, recursive = F)

#output[[1]]

```

```{r Print plotly B40, eval=FALSE, warning=FALSE, include=FALSE, messages=FALSE}

 # Used to print the plotly plots
  # attach the Dependencies
  # since the do not get included with renderTags(...)$html
  deps <- lapply(
    Filter(function(x){inherits(x,"htmlwidget")},output),
    function(hw){
      renderTags(hw)$dependencies
    }
  )
  
  if(length(deps)>0){
  attachDependencies(
    tagList(),
    unlist(deps,recursive=FALSE)
  )
  }  
```

### CCR 50 - samples taken from the deepest site in CCR

These samples were taken in 2022 and might not need to be plotted each year. 

```{r QAQC CCR 50 Plots, echo=FALSE, warning=FALSE, results='asis', time_it = TRUE}

dx <- colnames(current_df%>%select(TLi_mgL:SBa_mgL))

# make the plots

outputs <- lapply(dx, all_plot, data=current_df, reservoir = "CCR", res_site=50, y_lab = "mg/L", y_lab2 = "mg/L",Depth=T, Water=F, Use_plotly=T, Heatmap = T)

output <- unlist(outputs, recursive = F)

#output[[1]]

```

```{r Print plotly C50, echo=FALSE, messages=FALSE, warning=FALSE}

 # Used to print the plotly plots
  # attach the Dependencies
  # since the do not get included with renderTags(...)$html
  deps <- lapply(
    Filter(function(x){inherits(x,"htmlwidget")},output),
    function(hw){
      renderTags(hw)$dependencies
    }
  )
  
  if(length(deps)>0){
  attachDependencies(
    tagList(),
    unlist(deps,recursive=FALSE)
  )
  }  
```



```{r Make new CSV with current and historic files, eval=FALSE, include=FALSE}

# Convert DateTime to a character
# convert datetimes to characters so that they are properly formatted in the output file
 current_df$DateTime <- as.character(format(current_df$DateTime))

# Need to decide on a naming convention for this file
write_csv(current_df, "metals_2014_2025.csv")

```



```{r Download and save Maintenance Log, eval=FALSE, include=FALSE}

# This chunkt to download files needs to be run by itself. Just click on the green arrow to download the files. 

# Maintenance Log
download.file("https://raw.githubusercontent.com/CareyLabVT/Reservoirs/master/Data/DataNotYetUploadedToEDI/Metals_Data/Metals_Maintenance_Log.csv", "metals_maintenancelog_2014_2024.csv")

## Maybe we want to take out the ISCO observations in the maintenance log
 maint <- read_csv("https://raw.githubusercontent.com/CareyLabVT/Reservoirs/master/Data/DataNotYetUploadedToEDI/Metals_Data/Metals_Maintenance_Log.csv",
                    show_col_types = FALSE)|>
  filter(Site != 100.1)
 
 # save the csv without ISCO samples in maint log
 
 write.csv(maint, "metals_maintenancelog_2014_2025.csv")

# qaqc function
# update link when change the location of the script
download.file("https://raw.githubusercontent.com/CareyLabVT/Reservoirs/master/Scripts/L1_functions/metals_create.R", "metals_qaqc_2014_2024.R")

# streaming plots function
download.file("https://raw.githubusercontent.com/CareyLabVT/Reservoirs/master/Data/DataAlreadyUploadedToEDI/EDIProductionFiles/Plotting_function.R", "Plotting_function.R")

# Heat map code. No longer using this so don't need to download it. 
# download.file("https://raw.githubusercontent.com/CareyLabVT/Reservoirs/master/Data/DataAlreadyUploadedToEDI/EDIProductionFiles/Heatmap_EDI_function.R", "Heatmap_EDI_function.R")

# 

# Anything else that needs to be added? MDL file?


```

### Make a site description file

```{r Make site description file, eval=FALSE, include=FALSE}
 # These lines of code make the csv of the site descriptions with lat and long. To generate the site description file, click the green arrow on the right. 

  # Use Gsheet because you don't need to authenticate it. 
  sites <- gsheet::gsheet2tbl("https://docs.google.com/spreadsheets/d/1TlQRdjmi_lzwFfQ6Ovv1CAozmCEkHumDmbg_L4A2e-8/edit#gid=1244423834")
  #data<- read_csv("YOUR DATA.csv")# Use this if you read in a csv
  data <- current_df #This is the line you need to modify!
  trim_sites = function(data,sites){
    data_res_site=data%>% #Create a Reservoir/Site combo column
      mutate(res_site = trimws(paste0(Reservoir,Site)))
    sites_merged = sites%>% #Filter to Sites that are in the dataframe
      mutate(res_site = trimws(paste0(Reservoir,Site)))%>%
      filter(res_site%in%data_res_site$res_site)%>%
      select(-res_site)
  }
  sites_trimmed = trim_sites(data,sites) 
  write.csv(sites_trimmed,"site_descriptions.csv", row.names=F)# Write to file

```

