---
title: "FilteredChlorophyll_inspection_2014_2024"
author: "KKH"
date: "2023-12-05"
output: html_document
---

This is the visual inspection script for Filtered Chlorophyll. 
If running for EDI Dayz, start at line 43 and update the pasta with the most recent staged version.

This script is the visual inspection script. KKH check if these are the right steps. Can add a dup check if you want. 

1.  QAQCs all the raw data or for a reviewer reads in the data file from EDI for checking.

2.  Lists the flag frequency to check if there are any NAs or any assigned the wrong flag.

3.  Creates plots

4.  Writes data to new csv

5.  Downloads necessary files for EDI publishing

INFORMATION:

There are two ways to use this script. You can either run it by chunks or you can knit it and make an html file. Knitting the file will run all the chunks and create an html page with all the plots. I like doing this because I can see all the plots in one place. The Knit button is on the top of the file with a ball of yarn and a needle next to it.

If you are REVIEWING this data package, got to the "EDIT HERE" chunk

1.  Update your role

2.  Update the pasta link from EDI

If you are running the code chunk by chunk you might need to make some adjustments to the code. 

FOR DATA PRODUCT LEAD:

If you are the data product lead and making the data package then:

1.  Make sure all the date ranges are up to date especially current_time_start and current_time_end.

2.  Change the years in the saved data files in "Write CSV" and "Download and save Maintenance Log" chunk.

3.  Comment out the Reviewer section and make sure for the settings eval = FALSE.

4.  Update the data frame in "Get raw files" to include the most recent file on GitHub.

5.  Knit the file. This is up to you. 

6.  Look over the plots and see if there are any issues that need to be added to the maintenance log. I will usually read in the file you just made and make smaller plots with the variable and month in question. Once I have the dates, add them to the maintenance log.

7.  Re-run the inspection script until you have found all of the issues.

8.  Run the "Download and save Maintenance Log" chunk to have the most up to date files in the EDI folder.

9.  Make sure large maintenance issues are also documented in the methods.txt file.

```{r setup packages, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Add the names of the packages 
pacman::p_load(tidyverse, lubridate, gsheet, arsenal)
source("https://raw.githubusercontent.com/CareyLabVT/Reservoirs/master/Scripts/L1_functions/filt_chla_create.R")
```

REVIEWERS and DATA PUBLISHERS START HERE BEFORE KNITTING

1.  Update your role

2.  Update dates for current year plots

3.  If you are a reviewer, update the edi link

```{r EDIT HERE}

# 1. How would you like to use this script. If you are a data publisher write "publisher" if you are a reviewer write "reviewer"

role <- "publisher"

# 2. DATA PUBLISHERS UPDATE DATES HERE
# Set up the current time end time of the file and the current year for QAQC plots
#current time of QAQC for graphing

current_time_start=ymd_hms("2024-01-01 00:00:00", tz="America/New_York")
current_time_end=ymd_hms("2024-12-31 23:59:00", tz="America/New_York")

# 3. DATA PUBLISHERS UPDATE FILE NAMES
# Update the name of the data files, maintenance log, and qaqc function. Double check the name of the file matches the naming convention and the start and end date of the data file. 

file_name <- "filt-chla_2014_2024.csv"

qaqc_function <- "filt-chla_qaqc_2014_2024.R"

maintenance_log <- "filt-chla_maintenancelog_2014_2024.csv"

# 3. For REVIEWERS: Run this section to pull the data from EDI which is in staging as a check of the data.
# # MAKE SURE TO UPDATE THE PASTA FROM THE VERSION YOU WANT

edi_link <- "https://pasta-s.lternet.edu/package/data/eml/edi/52/32/d321a924e9d6a839366647a8f942204e"

```

```{r set chunks on or off, echo=FALSE}
### Code to determine which chunks are turned on and off

if(role=="publisher"){
  make_data = TRUE
  edi_stage = FALSE
}else if(role == "reviewer"){
  make_data = FALSE
  edi_stage = TRUE
}

```


**Make data frame using the filt chla function**
```{r Read in Historical files from EDI, eval = make_data}
all_chla <- filt_chla_qaqc(
  directory = "../../../../DataNotYetUploadedToEDI/Raw_chla/chla_extraction/raw data from spec/",
  rack_map = "https://docs.google.com/spreadsheets/d/1N7he-0Z1gmSA5KjO96QA5tOeNXFcAKoVfAD1zix4qNk",
  filtering_log = "https://docs.google.com/spreadsheets/d/1xeF312vgwJn7d2UwN4qOD8F32ZGHE3Vv",
  final_vol_extract = 6,
  blank_vol_filt = 500,
  maintenance_file = "https://raw.githubusercontent.com/CareyLabVT/Reservoirs/master/Data/DataNotYetUploadedToEDI/Raw_chla/Filt_Chla_Maintenance_Log.csv",
  historic_file = "https://raw.githubusercontent.com/CareyLabVT/Reservoirs/refs/heads/master/Data/DataNotYetUploadedToEDI/Raw_chla/historic_filt_chla_2014_2022.csv",
  sample_times =  "https://docs.google.com/spreadsheets/d/1MbSN2G_NyKyXQUEzfMHmxEgZYI_s-VDVizOZM8qPpdg", 
  outfile = NULL, 
  #outfile = "../../../../Data/DataAlreadyUploadedToEDI/MakeEMLFilteredChlorophyll/2024/filt-chla_2014_2024_test.csv",
  start_date = NULL, # change when we update to read date from EDI
  end_date = as.Date("2024-12-31"))

```

```{r READ IN EDI data, eval = edi_stage}

 all_chla <-read_csv(edi_link)

 # Force files from EDI to have an EST timestamp
 all_chla$DateTime <- force_tz(as.POSIXct(all_chla$DateTime), tzone = "EST")

```

**Check there are no NAs in Flag columns**
This section checks to make sure each observation has a data flag. It also checks to make sure the frequency of flags matches what we expect to see. 
There should be no NAs.
```{r Check there are no NAs in Flag columns}
#make sure no NAS in the Flag columns
Flags=all_chla%>%
  select(DateTime, starts_with("Flag"))

RowsNA=Flags[!complete.cases(Flags), ] # Keep only the complete rows

#check the flag column
Flags=all_chla%>%
  select(starts_with("Flag"))

# Make a table with the number of times a flag was used
for(f in 1:(ncol(Flags))){
  #print(colnames(Flags[f]))
  print(table(Flags[,f], useNA = "always"))
}
```
**Manipulate Dataset for Plotting**
Add Year, Month, and Day of Year for plotting. Add depth groups. 
```{r Manipulate Dataset for Plotting}
# Altering dataset in order to plot stats 
chla_YMD <- all_chla %>% 
  mutate(Year = year(DateTime)) %>% 
  mutate(Month = month(DateTime)) %>% 
  mutate(DOY = yday(DateTime)) %>% 
  mutate(Depth_group = ifelse(Depth_m == 0.1, "surface", ifelse(Depth_m > 0.1 & Depth_m < 4,"epi","hypo")))

#make plots of the data by reservoir and year
#this is a check to make sure that we have all of the data in the years that we expect to have it
head(chla_YMD)
```
**Time Series for entire data set - Chlorophyll a**
ENTIRE DATASETS WILL LIKELY DISPLAY A MISSING DATA WARNING
Samples were not collected in 2017
```{r Time Series for entire data set - chla}
# Facetted plot of the datapoints within each reservoir over the entire dataset 
ggplot(subset(chla_YMD), aes(x = DateTime, y = Chla_ugL, col = Reservoir)) +
  geom_point(size = 1) + 
  facet_grid(Reservoir ~., scales = "free_y") + 
  ggtitle("Entire Dataset Timeseries - Chlorophyll a")
```
**Time Series for entire data set - Pheophyton**
```{r Time Series for entire data set - Pheophyton}
# Facetted plot of the datapoints within each reservoir over the entire dataset 
ggplot(subset(all_chla), aes(x = DateTime, y = Pheo_ugL, col = Reservoir)) +
  geom_point(size = 1) + 
  facet_grid(Reservoir ~., scales = "free_y") + 
  ggtitle("Entire Dataset Timeseries - Pheophyton")
```
**VALUES BELOW 0 FOR PHAEOPHYTIN**
DOUBLE CHECK THAT THEY ARE ALL FLAGGED WITH A 1
All values below 0 have been set to 0. This check should return a tibble with 0 rows
```{r PHAEOPHYTIN VALS BELOW 0}
#check the flag column
pheo_below0 <- subset(all_chla, Pheo_ugL < 0)
pheo_below0
#these are all flagged as 4 or 45, "pigment in extract below detection"
#Do we want to change these negative values to 0 in the future?
#Yes, as of 2023

#{r Set all Phaeophytin values that are below 0 to 0}
all_chla <- all_chla %>% mutate(Pheo_ugL = if_else(Pheo_ugL < 0, 0, Pheo_ugL))
```

**All Sites, All Years, Monthly Mean - Chlorophyll a**
Notes: 2016 in BVR has very high chla values. Might be worth looking into - KKH 2024
```{r All Sites, All Years, Monthly Mean - Chlorophyll a}
# Facetted plot of the range of each reservoir for each year and the mean of the range
ggplot(subset(chla_YMD), aes(x = Month, y = Chla_ugL, col = Reservoir))+ 
  geom_point(size = 1) + 
  #stat_summary(fun = "mean", geom = "point", pch = 0, size =2, color = 'black') + 
  stat_summary(fun = "mean", geom = "point", pch = 18, size =2, color = 'black') + 
  facet_grid(Reservoir~Year, scales = 'free_y') +
  scale_x_continuous("DateTime", breaks = seq(1, 12, 1)) + 
  scale_y_continuous("Concentration (ugL)") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = 'none') + 
  ggtitle("Range and Mean of Range - Chlorophyll a")
```
**All Sites, All Years, Monthly Mean - Pheophyton**
```{r All Sites, All Years, Monthly Average - Pheophyton}
# Facetted plot of the range of each reservoir for each year and the mean of the range
ggplot(subset(chla_YMD), aes(x = Month, y = Pheo_ugL, col = Reservoir))+ 
  geom_point(size = 1) + 
  #stat_summary(fun = "mean", geom = "point", pch = 0, size =2, color = 'black') + 
  stat_summary(fun = "mean", geom = "point", pch = 18, size =2, color = 'black') + 
  #facet_grid(Year ~ Reservoir, scales = 'free_y') + 
  facet_grid(Reservoir~Year, scales = 'free_y') +
  scale_x_continuous("DateTime", breaks = seq(1, 12, 1)) + 
  scale_y_continuous("Concentration (ugL)") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = 'none') + 
  ggtitle("Range and Mean of Range - Pheophyton")
```
**All Sites, All Years, Monthly Median - Chlorophyll a**
Sunapee EXCLUDED!!! Deep site for SNP is 200, but other reservoirs also have site 200
```{r Main sampling site, Monthly Median - Chlorophyll a}
# Facetted plot of the range of each reservoir for each year and the median of the range
ggplot(subset(chla_YMD, Site == 50), aes(x = Month, y = Chla_ugL, col = Reservoir))+ 
  geom_point(size = 1) + 
  stat_summary(fun = "median", geom = "point", pch = 8, size = 1, color = 'black') + 
  facet_grid(Reservoir~Year, scales = 'free_y') + 
  #scale_x_continuous("DateTime", breaks = seq(2014,2022, 1)) + 
  scale_x_continuous("Month of Year", breaks = seq(1,12, 1)) +
  scale_y_continuous("Concentration (ugL)") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = 'none') + 
  ggtitle("Range and Median of Range - Chlorophyll a")
```
**All Sites, All Years, Monthly Median - Pheophyton**
```{r All Sites, All Years, Monthly Median - Pheophyton}
# Facetted plot of the range of each reservoir for each year and the median of the range
ggplot(subset(chla_YMD, Site == 50), aes(x = Month, y = Pheo_ugL, col = Reservoir))+ 
  geom_point(size = 1) + 
  stat_summary(fun = "median", geom = "point", pch = 8, size = 1, color = 'black') + 
  facet_grid(Reservoir~Year, scales = 'free_y') + 
  #scale_x_continuous("DateTime", breaks = seq(2014,2022, 1)) + 
  scale_x_continuous("Month of Year", breaks = seq(1,12, 1)) +
  scale_y_continuous("Concentration (ugL)") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = 'none') + 
  ggtitle("Range and Median of Range - Pheophyton")
```
2024, July 1st seems to have a very high chla value. I am inclined to believe this is real, there was a large cyano bloom that date that was not captured on the EXO but can be seen on Flora - KKH
```{r All Sites, All Years, Monthly Median, samples colored by depth - Chlorophyll a}
# Facetted plot of the range of each reservoir for each year and the median of the range with depth
ggplot(subset(chla_YMD, Site == 50), aes(x = Month, y = Chla_ugL, col = Depth_group))+ 
  geom_point(size = 1) + 
  stat_summary(fun = "median", geom = "point", pch = 8, size = 1, color = 'black') + 
  facet_grid(Reservoir~Year, scales = 'free_y') + 
  #scale_x_continuous("DateTime", breaks = seq(2014,2022, 1)) + 
  scale_x_continuous("Month of Year", breaks = seq(1,12, 1)) +
  scale_y_continuous("Concentration (ugL)") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = 'left') + 
  ggtitle("Chla - Median, by depth")
```
```{r All Sites, All Years, Monthly Median, samples colored by depth - Pheophyton}
# Facetted plot of the range of each reservoir for each year and the median of the range with depth
ggplot(subset(chla_YMD, Site == 50), aes(x = Month, y = Pheo_ugL, col = Depth_group))+ 
  geom_point(size = 1) + 
  stat_summary(fun = "median", geom = "point", pch = 8, size = 1, color = 'black') + 
  facet_grid(Reservoir~Year, scales = 'free_y') + 
  #scale_x_continuous("DateTime", breaks = seq(2014,2022, 1)) + 
  scale_x_continuous("Month of Year", breaks = seq(1,12, 1)) +
  scale_y_continuous("Concentration (ugL)") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = 'left') + 
  ggtitle("Pheophyton - Median, by depth")
```
**Flags**
attributeName	code	definition
Flag_Chla_ugL	0	    Value acceptable. No flag  
Flag_Chla_ugL	1	    Sample below detection  
Flag_Chla_ugL	2	    Sample not taken  
Flag_Chla_ugL	3	    Duplicate check failed  
Flag_Chla_ugL	4   Pigment in extract below detection (<34 ug/L)  
Flag_Chla_ugL	5	    Duplicate values were averaged  

```{r Subset to Current Year Only (2024)}
#subset data to FCR and BVR
chla_current <- chla_YMD %>% 
  subset((Year=="2024")) %>% 
   mutate(DOY = yday(DateTime)) 

head(chla_current)
#### Graph ####
# Current Year Timeseries
ggplot(subset(chla_current), aes(x = DOY, y = Chla_ugL, pch = as.factor(Flag_Chla_ugL))) +
  geom_point(size = 1) + 
  facet_grid(Reservoir ~., scales = "free_y") + 
  ggtitle("Current Year Timeseries")

```
**Flags**
Flag_Pheo_ugL	0	    Value acceptable. No flag  
Flag_Pheo_ugL	1	    Sample below detection  
Flag_Pheo_ugL	2	    Sample not taken  
Flag_Pheo_ugL	3	    Duplicate check failed  
Flag_Pheo_ugL	4	    Pigment in extract below detection (<34 ug/L)  
Flag_Pheo_ugL	45	  Pigment in extract below detection (<34 ug/L) and duplicate values were averaged  
Flag_Pheo_ugL	5	    Duplicate values were averaged  
```{r Subset to Current Year Only (2023) - Pheophyton}
#subset data to FCR and BVR
chla_current <- chla_YMD %>% 
  subset((Year=="2024")) %>% 
   mutate(DOY = yday(DateTime)) 

head(chla_current)
#### Graph ####
# Current Year Timeseries
ggplot(subset(chla_current), aes(x = DOY, y = Pheo_ugL, pch = as.factor(Flag_Pheo_ugL))) +
  geom_point(size = 1) + 
  facet_grid(Reservoir ~., scales = "free_y") + 
  ggtitle("Current Year Timeseries")

```


```{r Time Series for entire data set - chla}
# Facetted plot of the datapoints within each reservoir over the entire dataset 
ggplot(subset(chla_YMD, Year == 2024), aes(x = DateTime, y = Chla_ugL, col = Depth_m)) +
  geom_point(size = 1) + 
  facet_grid(Reservoir ~., scales = "free_y") + 
  ggtitle("2024Timeseries - Chlorophyll a")
```
**Time Series for entire data set - Pheophyton**
```{r Time Series for entire data set - Pheophyton}
# Facetted plot of the datapoints within each reservoir over the entire dataset 
ggplot(subset(chla_YMD, Year == 2024), aes(x = DateTime, y = Pheo_ugL, col = Depth_m)) +
  geom_point(size = 1) + 
  facet_grid(Reservoir ~., scales = "free_y") + 
  ggtitle("2024 Timeseries - Pheophyton")
```

```{r Remove duplicate row}
#all_chla <- dplyr::distinct(all_chla) #as of 2023 should go from 1014 obs to 1013 obs
#this should be taken care of in the qaqc script as of 2024
```

### Write to CSV

Make the data frame here and it will save where your inspection script is saved.

```{r Make current csv, eval = make_data}

# Double Check naming convention
# Variable_StartYear_EndYear

# convert datetimes to characters so that they are properly formatted in the output file
 all_chla$DateTime <- as.character(format(all_chla$DateTime))

write_csv(all_chla, file_name)

```

### Download and save Maintenance Log, Plotting function, and QAQC function

```{r Download and save Maintenance Log, eval = make_data}

# Download the most recent maintenance log, qaqc file, and plotting function from GitHub. 

# Maintenance Log
download.file("https://raw.githubusercontent.com/CareyLabVT/Reservoirs/master/Data/DataNotYetUploadedToEDI/Raw_chla/Filt_Chla_Maintenance_Log.csv", maintenance_log)

# qaqc function
download.file("https://raw.githubusercontent.com/CareyLabVT/Reservoirs/master/Scripts/L1_functions/filt_chla_create.R", qaqc_function)


```

 Make site description file
```{Make site description file, eval = make_data}
# These lines of code make the csv of the site descriptions with lat and long
# Use Gsheet because you don't need to authenticate it.
 sites <- gsheet::gsheet2tbl("https://docs.google.com/spreadsheets/d/1TlQRdjmi_lzwFfQ6Ovv1CAozmCEkHumDmbg_L4A2e-8/edit#gid=1244423834")
 #data<- read_csv("YOUR DATA.csv")# Use this if you read in a csv
 data <- all_chla #This is the line you need to modify!
 trim_sites = function(data,sites){
   data_res_site=data %>% #Create a Reservoir/Site combo column
     mutate(res_site = trimws(paste0(Reservoir,Site)))
   sites_merged = sites %>% #Filter to Sites that are in the dataframe
     mutate(res_site = trimws(paste0(Reservoir,Site))) %>%
     filter(res_site%in%data_res_site$res_site) %>%
     select(-res_site)
 }
 sites_trimmed = trim_sites(data, sites)
 write.csv(sites_trimmed,"site_descriptions.csv", row.names=F)# Write to file
 maint_file <- read.csv(maintenance_file)
 write.csv(maint_file, "filt-chla_maintenancelog_2014_2024.csv", row.names = F)
```

