---
title: "CCR Catwalk Plots for EDI"
author: "Adrienne Breef-Pilz"
output: html_document
theme: null
original date: Jan. 2023
date: "`r Sys.Date()`"
---

This script is the visual inspection script. 

1. QAQCs all the raw data or for a reviewer reads in the data file from EDI for checking. 

2. Then the script checks for duplicates, daily, and subdaily gaps in the current file. 

3. Lists the flag frequency to check if there are any NAs or any assigned the wrong flag. 

4. Checks to see if the Maintenance Log is working correctly by inspecting rows in the data frame. 

5. Creates plots

6. Writes data to new csv

7. Downloads necessary files for EDI publishing


All files are from GitHub or EDI and the source scripts are from GitHub as well. 

If you are REVIEWING this data package, add the pasta URL from EDI in the "READ IN EDI FOR REVIEWER". Make sure eval=FALSE is in the chunk header for "Get raw files", "QAQC all files", "Write CSV" and "Download and save Maintenance Log". You don't need to remake the data files when you are reviewing the data package. These chunks of code will not be run when the R markdown is knitted together and saves you LOTTTS of time. Once that is all set than you can knit the file together as an HTML file to look at all the plots. 

If you are running the code chunk by chunk you mind need to make some adjustments to the code. To make the plots this markdown uses a function called "all_plots". In the function it creates a plots of the most current year, the whole times series, as well as, density and box plots for daily averages. You can also specify if you would like to produce a heat map. Note that heat maps are only produced if your data has a depth column. The function also allows you to choose if you want interactive plots, using plotly, for the most recent year of data. The plotly plots are designed to be in order with the other plots when knit to together. Therefore if you are running the ploting section, chunk by chunk, then you need to specify the plotly plot from the list of plots labeled "output". For this data package do not use plotly for all plots at one time. I usually use it for depth, oxygen, and chla. 

FOR DATA PRODUCT LEAD:

If you are the data product lead and making the data package then:

1. Make sure all the date ranges are up to date especially current_time_start and current_time_end.

2. Change the years in the saved data files in "Write CSV" and "Download and save Maintenance Log" chunk.

3. Make sure to un comment and change the settings for the "Get raw files", "QAQC all files",  and "Write CSV" chunks. Also check the settings for the chunk eval=TRUE or it shouldn't be there. 

4. Comment out the Reviewer section and make sure for the settings eval = FALSE.

5. Update the data frame in "Get raw files" to include the most recent file on GitHub.

6. Knit the file. This will take a long time. 

7. Look over the plots and see if there are any issues that need to be added to the maintenance log. I will usually read in the file you just made and make smaller plots with the variable and month in question. Once I have the dates, add them to the maintenance log. 

8. Re-run the inspection script until you have found all of the issues. 

9. Run the "Download and save Maintenance Log" chunk to have the most up to date files in the EDI folder.

10. Make sure large maintenance issues are also documented in the methods.txt file.

```{r Set Up, include=FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(RCurl,devtools, tidyverse,lubridate, plotly, magrittr, scattermore, knitr, htmltools, pander)

# Source scripts from GitHub
# Function to make the QAQC . This is called CCRCatwalk_qaqc_2023_2023.R in the EDI data package. 
source('https://raw.githubusercontent.com/FLARE-forecast/CCRE-data/ccre-dam-data-qaqc/R/edi_qaqc_function.R')


# Function to make the plots below
source('https://raw.githubusercontent.com/CareyLabVT/Reservoirs/master/Data/DataAlreadyUploadedToEDI/EDIProductionFiles/Plotting_function.R')


 #turn off pander auto asis. Used for making the ploty functions show up in the knitted markdown HTML
        pander::panderOptions('knitr.auto.asis', FALSE)

# Set up the current time end time of the file and the current year for QAQC plots

#current time of QAQC for graphing
current_time_start=ymd_hms("2024-01-01 00:00:00", tz = "EST")
current_time_end= ymd_hms("2024-12-31 23:59:00", tz = "EST")
```

```{r QAQC all Files, eval=FALSE, include=FALSE}

# QAQC all the raw files using the QAQC function which is sourced above. It is also the same function CCRCatwalk_qaqc_2021_2023.R which is included in the data package

current_df <-qaqc_ccr(
    data_file = 'https://raw.githubusercontent.com/FLARE-forecast/CCRE-data/ccre-dam-data/ccre-waterquality.csv',
    data2_file = 'https://raw.githubusercontent.com/CareyLabVT/ManualDownloadsSCCData/master/CCR_manual_downloads/CCRWaterquality_L1_2021_2023.csv' ,
    EXO2_manual_file = 'https://raw.githubusercontent.com/CareyLabVT/ManualDownloadsSCCData/master/CCR_manual_downloads/CCR_1_5_EXO_2021_2024.csv',
   # maintenance_file = 'ccre-waterquality_depth_offsets_2021_2024.csv',
    maintenance_file = 'https://raw.githubusercontent.com/FLARE-forecast/CCRE-data/ccre-dam-data-qaqc/CCRW_MaintenanceLog.csv',
    output_file = NULL,
    start_date = ymd_hms("2021-04-09 15:20:00", tz="EST"), # This is when we want the file to start
    end_date = Sys.Date()
)


#Make sure no dups and that we cut off the observations at
  current_df <- current_df%>%
  dplyr::distinct(.)%>% # get rid of dups if they snuck in
  filter(DateTime<(current_time_end))


# make sure no time duplicates.
 current_df<-  current_df[!duplicated(current_df$DateTime), ]

#reorder. Just to be certain everything is in order
  current_df<-current_df[order(current_df$DateTime),]


```

REVIEWERS- If you are reviewing this data package replace the pasta link with the one from EDI. If there are questions ask the data point person. There are two ways to use this script. You can either run it by chunks or you can knit it and make an html file. Knitting the file will run all the chunks and create an html page with all the plots. I like doing this because I can see all the plots in one place. The Knit button is on the top of the file with a ball of yarn and a needle next to it. 

```{r Bind files together or READ IN EDI FOR REVIEWER, include=FALSE}
  

# For REVIEWERS: Run this section to pull the data from EDI which is in staging as a check of the data.
# MAKE SURE TO UPDATE THE PASTA FROM THE VERSION YOU WANT
  
  
                                                                   ### CHANGE THIS NUMBER BELOW 
                                                                              ##      
   current_df <-read_csv("https://pasta.lternet.edu/package/data/eml/edi/1069/2/57267535da5ab0687d2fee52083699f8")
 # 
 # # Force files from EDI to have an EST timestamp
 current_df$DateTime <- force_tz(as.POSIXct(current_df$DateTime), tzone = "EST")


```

## Information for EDI methods text
This is information that is included in the methods file for EDI 

The minimum water level for CCR was `r min(current_df$LvlDepth_m_13, na.rm=T)` and the maximum water depth was `r max(current_df$LvlDepth_m_13, na.rm=T)`.

The median water level was `r median(current_df$LvlDepth_m_13, na.rm=T)` and the mean water level was `r mean(current_df$LvlDepth_m_13, na.rm=T)`.


```{r Download Raw data for plotting, include=FALSE}

# This is the raw files from the data logger before qaqc. I like to plot this with the qaqc values so we can see what has been removed by the qaqc function and maint log and what has been missed. 

CATPRES_COL_NAMES = c("DateTime", "RECORD", "CR3000Battery_V", "CR3000Panel_Temp_C", 
                        "ThermistorTemp_C_1", "ThermistorTemp_C_2", "ThermistorTemp_C_3", "ThermistorTemp_C_4",
                        "ThermistorTemp_C_5", "ThermistorTemp_C_6", "ThermistorTemp_C_7", "ThermistorTemp_C_8",
                        "ThermistorTemp_C_9","ThermistorTemp_C_10","ThermistorTemp_C_11", "ThermistorTemp_C_12",
                        "ThermistorTemp_C_13","EXO_Date_1", "EXO_Time_1", "EXOTemp_C_1", "EXOCond_uScm_1",
                        "EXOSpCond_uScm_1", "EXOTDS_mgL_1", "EXODOsat_percent_1", "EXODO_mgL_1", "EXOChla_RFU_1",
                        "EXOChla_ugL_1", "EXOBGAPC_RFU_1", "EXOBGAPC_ugL_1", "EXOfDOM_RFU_1", "EXOfDOM_QSU_1",
                        "EXOPressure_psi_1", "EXODepth_m_1", "EXOBattery_V_1", "EXOCablepower_V_1", "EXOWiper_V_1",
                        "EXO_Date_9", "EXO_Time_9", "EXOTemp_C_9", "EXOCond_uScm_9",
                        "EXOSpCond_uScm_9", "EXOTDS_mgL_9", "EXODOsat_percent_9", "EXODO_mgL_9", 
                        "EXOfDOM_RFU_9", "EXOfDOM_QSU_9","EXOPressure_psi_9", "EXODepth_m_9", "EXOBattery_V_9",
                        "EXOCablepower_V_9", "EXOWiper_V_9","LvlPressure_psi_13", "LvlTemp_C_13")
  
 
  # read catwalk data and maintenance log
  # NOTE: date-times throughout this script are not specified but they are all processed in the same timezone 
  raw <- read_csv("https://raw.githubusercontent.com/FLARE-forecast/CCRE-data/ccre-dam-data/ccre-waterquality.csv", skip = 1, col_names = CATPRES_COL_NAMES,
                      col_types = cols(.default = col_double(), DateTime = col_datetime()))
  
  
  # Take out extremly high values, EXO_Date and Time, and create depth column
   raw <- raw%>%
     select(-c("EXO_Date_1", "EXO_Time_1", "EXO_Date_9", "EXO_Time_9"))%>%
      mutate(across(ThermistorTemp_C_1:LvlTemp_C_13, ~ifelse(.x >180, NA, .x)))%>%
       mutate(LvlDepth_m_13=LvlPressure_psi_13*0.70455)#1psi=2.31ft, 1ft=0.305m

  # convert NaN to NAs in the dataframe
  raw[sapply(raw, is.nan)] <- NA
  
  # Force historical file timestamp to EST
  raw$DateTime <- force_tz(as.POSIXct(raw$DateTime), tzone = "EST")
 

```

## Check for duplicates and  gaps in the data frame

This section identifies if there are any duplicates, daily data, and sub daily gaps in the long-term record. If there are duplicates. Look to see if they are true duplicates and then check the qaqc function and the chunk above where duplicates should be removed. 


### Are there any duplicates?


```{r Check for dups , echo=FALSE}

# Make sure there are no duplicated dates. Do this here because the file is too large for Data Explore.
# Print them if there are
 dups<- current_df[duplicated(current_df$DateTime), ]

dups <- dups%>%
  select(DateTime, RECORD, ThermistorTemp_C_7,  
         EXOTemp_C_1, EXOTemp_C_9, LvlPressure_psi_13)

# Make it into a nice table when the Markdown is knitted together
knitr::kable((dups))
```


### Are there any gaps in the data file?

#### Check for daily gaps

When gaps are found in the data file, check that you do not have new gaps in the previous years' publication. For the current year, if you find gaps check that you have all of the manually downloaded files. If the data are truly missing then record the dates and times in the methods section. 


```{r Check for Gaps larger than a day, echo=FALSE}
# Check if there are daily gaps in the data. If there are record them in the 
# Get DOY
ccrwater <- current_df
 ccrwater$DOY=yday(ccrwater$DateTime)

 for(i in 2:nrow(ccrwater)){ #this identifies if there are any data gaps in the long-term record, and where they are by record number
    if(ccrwater$DOY[i]-ccrwater$DOY[i-1]>1){
      print(c(ccrwater$DateTime[i-1],ccrwater$DateTime[i]))
    }
 }
```


#### Check for sub-daily gaps

This identifies if there are any sub-daily gaps in the current record which gets recorded in the methods section. 

The first row is the time for the first observation and then the subsequent observation. Each observation should be 10 minutes apart. The second row is the number of the record for each observation. Most of these gaps happen when we change the program on the data logger. These times will be recorded in the maintenance section of the metadata and are also noted in the maintenance log.

```{r Check for sub daily gaps, echo=FALSE}

# Because we can't have NAs for this for loop let's make a new df
 ccr2 <- current_df%>%
  filter(!is.na(RECORD))%>%
  filter(DateTime>current_time_start)

  for(i in 2:length(ccr2$RECORD)){ #this identifies if there are any data gaps in the long-term record, and where they are by record number
    if( abs(ccr2$RECORD[i]-ccr2$RECORD[i-1])>1 & difftime(ccr2$DateTime[i], ccr2$DateTime[i-1], units="mins")>10){
      print(c(ccr2$DateTime[i-1], ccr2$DateTime[i]))
      print(c(ccr2$RECORD[i-1], ccr2$RECORD[i]))
    }
  }
```
 
#### Gaps in EXO2 Data
These are gaps in the EXO2 data longer than 30 minutes

```{r EXO gaps, echo=FALSE}

# Check for any gaps longer than 30 minutes in the record for the current year

 bvr2 <- current_df%>%
  select(DateTime, , starts_with("EXO"), Flag_EXOTemp_C_1)|>
  select(DateTime, ends_with("_1"))|>
  filter(Flag_EXOTemp_C_1!=7)
  #filter(DateTime>current_time_start)

  for(i in 2:length(bvr2$EXOTemp_C_1)){ #this identifies if there are any data gaps in the long-term record, and where they are by record number
    if(abs(difftime(bvr2$DateTime[i], bvr2$DateTime[i-1], units="mins")>30)){
      print(c(bvr2$DateTime[i-1], bvr2$DateTime[i]))
    }
  }

```

#### Gaps in EXO3 Data at 9 m

These are gaps in the EXO3 data longer than 30 minutes

```{r EXO3 gaps, echo=FALSE}

# Check for any gaps longer than 30 minutes in the record for the current year

 bvr2 <- current_df%>%
  select(DateTime, , starts_with("EXO"), Flag_EXOTemp_C_9)|>
  select(DateTime, ends_with("_9"))|>
  filter(Flag_EXOTemp_C_9!=7)
  #filter(DateTime>current_time_start)

  for(i in 2:length(bvr2$EXOTemp_C_9)){ #this identifies if there are any data gaps in the long-term record, and where they are by record number
    if(abs(difftime(bvr2$DateTime[i], bvr2$DateTime[i-1], units="mins")>30)){
      print(c(bvr2$DateTime[i-1], bvr2$DateTime[i]))
    }
  }

```
### Flag Frequency
Let's look at the flag Frequency for each variable. As a reminder here are the flag codes
 Flag values
 
 0: no flag
 
 1: value removed due to maintenance and set to NA
 
 2: negative or outlier value removed and set to NA, see Methods section for more detail on QAQC process
 
 3: negative values set to 0 except for temperature
 
 4: value removed due to fouling and set to NA
 
 5: questionable value but left in the dataset
 
 6: Values adjusted using a linear or square root function to match high-resolution CTD profiles and corrected other affected observations on the same sensor
 
 7: missing data
 
```{r Check out the flags, echo=FALSE}



#make sure no NAS in the Flag columns
Flags <- current_df%>%
  select(DateTime, starts_with("Flag"))

RowsNA=Flags[!complete.cases(Flags), ] # Keep only the complete rows

#check the flag column
Flags <- current_df%>%
  select(starts_with("Flag"))

# Make a table with the number of times a flag was used
for(f in 1:ncol(Flags)){
  print(colnames(Flags[f]))
  print(table(Flags[,f], useNA = "always"))
}
```


### Check to make sure that what is in the maintenance log was actually removed

### Look at the last rows of the maintenance log 

We want to make sure that our maintenance log actually worked and took out the values or changes those it was supposed to 

```{r Read in the maintenance log and look at the tail, echo=FALSE}

 maint <- read_csv2("https://raw.githubusercontent.com/FLARE-forecast/CCRE-data/ccre-dam-data-qaqc/CCRW_MaintenanceLog.csv",
                    show_col_types = FALSE)|>
  filter(TIMESTAMP_end<(current_time_end))
  


# name the data file for just the tail of the maintenance log
# you want to filter out 7 because that is if the observation is missing and there are other ways that is flagged in the data besides the maintenance log, so it is not a good check.
sd <- tail(maint)%>%
  filter(flag!=7)


knitr::kable((tail(sd)))

```
#### Check the that the columns have flags 

Look at the first few rows of the data frame and check that the observations after the TIMESTAMP_start are flagged

#### Look at the first 5 rows for that time

```{r Did the maint log work head, echo=FALSE, message=FALSE, warning=FALSE}
# get the last row of the data file
last_row <- tail(sd, n=1)

# Get starttime and end time
### get start and end time of one maintenance event
    start <- force_tz(as.POSIXct(last_row$TIMESTAMP_start), tzone = "EST")
    end <- force_tz(as.POSIXct(last_row$TIMESTAMP_end), tzone = "EST")
    
    # Get the time of the maintenance
    if(is.na(end)){
      # If there the maintenance is on going then the columns will be removed until
      # and end date is added
      Time <- current_df |> filter(DateTime >= start) |> select(DateTime)
      
    }else if (is.na(start)){
      # If there is only an end date change columns from beginning of data frame until end date
      Time <- current_df |> filter(DateTime <= end) |> select(DateTime)
      
    }else {
      Time <- current_df |> filter(DateTime >= start & DateTime <= end) |> select(DateTime)
    }


### Get the names of the columns affected by maintenance
    colname_start <- last_row$start_parameter
    colname_end <- last_row$end_parameter
    
    # Make list of just the columns we want 
    
    test <- colnames(current_df%>%select(DateTime, colname_start, paste0("Flag_",colname_start), colname_end, paste0("Flag_",colname_end)))
    
    # Print the head of the table to make sure that data are flagged
    
    knitr::kable((head(current_df[current_df$DateTime %in% Time$DateTime, test]))) 

```

#### Look at the last 6 rows for the maintenance time

Make sure the observations are flagged

```{r Print the tails, echo=FALSE, message=FALSE, warning=FALSE}

# Print the tail of the table to make sure that data are flagged
    
    knitr::kable(tail(current_df[current_df$DateTime %in% Time$DateTime, test])) 

```

### Subset and rename the files
This section will subset the files so you can make plots of the whole time series and the current year. 
Here we also get the daily average for each variable so we can make box plots and density plots to look at the data over time. 

```{r Filter for current year and daily average, include=FALSE}

# Raw files
current_raw <- raw%>%
  filter(DateTime>=current_time_start & DateTime<current_time_end)%>%
  mutate(type = "raw")

current <- current_df%>%
  filter(DateTime>=current_time_start & DateTime<current_time_end)%>%
  mutate(type = "qaqc")%>%
  select(DateTime:CR3000Panel_Temp_C,type, -contains("adjusted"))
```

## QAQC Plots

##### QAQC plot information and all_plot function information

For the plots, they use a function called "all_plot". In all_plot you can specify if you want interactive plots for the current data. You can specify which plotly plots you want on. You can also look at the plotly plots manually in each chunk by running the chunk with Use_plotly=TRUE as an argument. Then look at the list of plots you have made under "output". If you click on the "output" object in your environment it will list all of the plots and which ones are interactive plotly plots. To view the plots run "output[[number of the plot in the list you want to run]]". Eg. If you want to see the 4th plot in the list write output[[4]] then run that line and the plot should appear. 

If you would like to look at one variable then in the function below replace "dx" with the variable column. The object "dx" is just a list of variables so we don't have to list out all of the variables we want to plot. This is used to speed up the process. 

The plotting function is called all_plot() which plots the 4 or more plots described below. The function is sourced from GitHub in the first chunk of the script. The arguments are:
Var, # the variable you would like to plot
data, # the data frame to use
raw_data=NULL, # Is there raw data to compare with. Usually is NULL
reservoir, # the name of the reservoir you would like to filter by 
res_site, # the reservoir Site or Sites you would like to filter by
y_lab,  # This label can take an expression aka have the proper degrees C, 
y_lab2, # This label is for the plotly function which can not handle expression argument. 
Depth=F,  # Do you want depth as a factor
Water=T, # Are these plots for streaming sensors with RDO and temperature sensors
Use_plotly = F, # Do you want to produce interactive plots for observations of the current year?
Heatmap = F) # Do you want to make a heat maps? This only works if there are multiple depths at the same site


The arguments with = followed by a True means that they are the defaults and you don't need to add them to the function when you use it. If you want to use the opposite of the default you must specify that. 
  
##### Plot Description:

The plots below are:
The first 2 plots are the ones you should focus on for the QAQC chec. Spend the most time looking at the most recent data because that one as been checked. Do pay attention to the historical to make sure there are no crazy outliers that were missed in previous years. 

1. A time series of the current years' data. This can either be a regular plot or an interactive one. If you would like it to be interactive set Use_plotly = T. The black dots are the qaqced observations and the red is the raw files that were qaqced. This is to see what kind of values were removed and if there are any the script missed or that need to be added to the maintenance log. 

2. A time series of the historical and the current data just the qaqced values. 

The next two plots are just fun to see trends over time with the data. 

3. Density plots are like a histogram and a grouped by color so you can see where the data are relative to other years. 

4. The box plots look at the spread of the data within the year and we can look at the median and see how that is changing or not. 

Do not over think the last 2 plots, although they are good to look at historical trends to ensure relative data quality consistency. 

There are additional plots for depths that have more than one sensor such as at position 13 that has a thermistor and a pressure transducer which both measure temperature. In this case, we plot them on top of each other to make sure they are within the ballpark. For chal and the bluegreen algae sensor on the EXO2 we plot the daily observations on top of the 10 minute observations to make sure that the daily captures the same trend as the 10 minute data. 


### Temperature

```{r Temp, echo=FALSE, results='asis'}

dx <- colnames(current%>%select(grep("Temp_C_[0-9A-Za-z]",colnames(current))))


# make the plots
outputs <- lapply(dx, all_plot, data= current_df, raw_data = raw, reservoir = "CCR", y_lab = expression(''*~degree*C*''), y_lab2 = "Degrees C", Use_plotly=F)

output <- unlist(outputs, recursive = F)

# Use this if you want to look at the plotly plot in the Markdown document. Make sure that Use_plotly = T in the all_plot function above. 

#output[[1]]

```

```{r Print plotly temp, echo=FALSE, messages=FALSE, warning=FALSE}

 # Used to print the plotly plots
  # attach the Dependencies
  # since the do not get included with renderTags(...)$html
  deps <- lapply(
    Filter(function(x){inherits(x,"htmlwidget")},output),
    function(hw){
      renderTags(hw)$dependencies
    }
  )
  
  if(length(deps)>0){
  attachDependencies(
    tagList(),
    unlist(deps,recursive=FALSE)
  )
  }  
```

##### All of the temperature plots

```{r All Temperature, echo=FALSE, warning = FALSE, results='hide'}

colors3 <-c("1"="firebrick1", "2"="DarkOrange1", "EXO_1.5m"="yellow","3"="gold", 
                                  "4"="greenyellow", "5"="medium sea green", "6"="sea green",
                                  "7"="DeepSkyBlue4", "8"="blue2", "9"="cornflowerblue", "EXO_9m"="blue4",
            "10"="darkslateblue","11"="magenta2", "12"="darkmagenta", "13"="black")


# Take out Temperature values 

  All_temp<-current_df%>%
    select(DateTime, starts_with("Ther"), starts_with("EXOTemp"), "LvlTemp_C_13")%>%
    pivot_longer(-c(DateTime), names_to="Sensor", values_to="Reading", values_drop_na=TRUE)%>%
    mutate(DateTime=ymd_hms(DateTime))
  
  
  ggplot(All_temp)+
    geom_scattermore(aes(x=DateTime, y=Reading))+
    facet_wrap(.~factor(Sensor, levels=c("ThermistorTemp_C_1", "ThermistorTemp_C_2", "EXOTemp_C_1", "ThermistorTemp_C_3", "ThermistorTemp_C_4","ThermistorTemp_C_5","ThermistorTemp_C_6","ThermistorTemp_C_7","ThermistorTemp_C_8","ThermistorTemp_C_9","EXOTemp_C_9","ThermistorTemp_C_10","ThermistorTemp_C_11","ThermistorTemp_C_12","ThermistorTemp_C_13", "LvlTemp_C_13")))+
    theme_bw()
  
  
# This is all the temps and just the current year
    ggplot(current,aes(x = DateTime))+
    geom_line(aes(y=ThermistorTemp_C_1, color="1"))+
    geom_line(aes(y=ThermistorTemp_C_2, color="2"))+
    geom_line(aes(y=EXOTemp_C_1, color="EXO_1.5m")) +
    geom_line(aes(y=ThermistorTemp_C_3, color="3"))+
    geom_line(aes(y=ThermistorTemp_C_4, color="4"))+
    geom_line(aes(y=ThermistorTemp_C_5, color="5"))+
    geom_line(aes(y=ThermistorTemp_C_6, color="6"))+
    geom_line(aes(y=ThermistorTemp_C_7, color="7"))+
    geom_line(aes(y=ThermistorTemp_C_8, color="8"))+
    geom_line(aes(y=ThermistorTemp_C_9, color="9"))+
    geom_line(aes(y=EXOTemp_C_9, color = "EXO_9m"))+
    geom_line(aes(y=ThermistorTemp_C_10, color="10"))+
    geom_line(aes(y=ThermistorTemp_C_11, color="11"))+
    geom_line(aes(y=ThermistorTemp_C_12, color="12"))+
    geom_line(aes(y=ThermistorTemp_C_13, color="13"))+
    ggtitle("Current Temperature Profile") +
    labs(y = expression(''*~degree*C*''),
           color = "Legend") +
      scale_color_manual(values = colors3)+
      theme_bw()
  
```

### Depth QAQC Plots

```{r Pressure Sensor, echo=FALSE, results='asis'}
### Plotting depth from pressure sensor 
   
dx <- colnames(current%>%select(grep("Depth_m",colnames(current))))

# make the plots
outputs <- lapply(dx, all_plot, data= current_df, raw_data = raw, reservoir = "CCR", y_lab = "Meters", y_lab2 = "Meters", Use_plotly=T)

output <- unlist(outputs, recursive = F)

# Use this if you want to look at the plotly plot in the Markdown document. Make sure that Use_plotly = T in the all_plot function above. 

#output[[1]]

```

```{r Print plotly pres, echo=FALSE, messages=FALSE, warning=FALSE}

 # Used to print the plotly plots
  # attach the Dependencies
  # since the do not get included with renderTags(...)$html
  deps <- lapply(
    Filter(function(x){inherits(x,"htmlwidget")},output),
    function(hw){
      renderTags(hw)$dependencies
    }
  )
  if(length(deps)>0){
  attachDependencies(
    tagList(),
    unlist(deps,recursive=FALSE)
  )
  }  
```

### Dissolved Oxygen QAQC Plots

```{r DO, echo=FALSE, results='asis'}


dx <- colnames(current%>%select(grep("DO_mgL|sat_percent",colnames(current))))

# make the plots
outputs <- lapply(dx, all_plot, data= current_df, raw_data = raw, reservoir = "CCR", y_lab = "mg/L or % Sat", y_lab2 = "mg/L or % Sat", Use_plotly=F)

output <- unlist(outputs, recursive = F)

# Use this if you want to look at the plotly plot in the Markdown document. Make sure that Use_plotly = T in the all_plot function above. 

#output[[1]]

```

```{r Print plotly DO, echo=FALSE, messages=FALSE, warning=FALSE}

 # Used to print the plotly plots
  # attach the Dependencies
  # since the do not get included with renderTags(...)$html
  deps <- lapply(
    Filter(function(x){inherits(x,"htmlwidget")},output),
    function(hw){
      renderTags(hw)$dependencies
    }
  )
  
  if(length(deps)>0){
  attachDependencies(
    tagList(),
    unlist(deps,recursive=FALSE)
  )
  }  
```

### Chlorophyll and Phycocanin QAQC Plots

```{r Check the EXO Chla and Blue Greens, echo=FALSE, results='asis'}

dx <- colnames(current%>%select(grep("Chla|BGAPC",colnames(current))))

# make the plots
outputs <- lapply(dx, all_plot, data= current_df, raw_data = raw, reservoir = "CCR", y_lab = "RFU or ug/L", y_lab2 = "RFU or ug/L", Use_plotly=T)

output <- unlist(outputs, recursive = F)

# Use this if you want to look at the plotly plot in the Markdown document. Make sure that Use_plotly = T in the all_plot function above. 

#output[[1]]

```

```{r Print plotly algae, echo=FALSE, warning=FALSE, messages=FALSE}


 # Used to print the plotly plots
  # attach the Dependencies
  # since the do not get included with renderTags(...)$html
  deps <- lapply(
    Filter(function(x){inherits(x,"htmlwidget")},output),
    function(hw){
      renderTags(hw)$dependencies
    }
  )
  if(length(deps)>0){
  attachDependencies(
    tagList(),
    unlist(deps,recursive=FALSE)
  )
  }  
```

### fDOM QAQC Plots

```{r fdom EXO sensor, echo=FALSE, results='asis'}

dx <- colnames(current%>%select(grep("fDOM",colnames(current))))

# make the plots
outputs <- lapply(dx, all_plot, data= current_df, raw_data = raw, reservoir = "CCR", y_lab = "RFU or QSU", y_lab2 = "RFU or QSU", Use_plotly=T)

output <- unlist(outputs, recursive = F)

# Use this if you want to look at the plotly plot in the Markdown document. Make sure that Use_plotly = T in the all_plot function above. 

#output[[1]]
```

```{r Print plotly fdom, echo=FALSE, messages=FALSE, warning=FALSE}

 # Used to print the plotly plots
  # attach the Dependencies
  # since the do not get included with renderTags(...)$html
  deps <- lapply(
    Filter(function(x){inherits(x,"htmlwidget")},output),
    function(hw){
      renderTags(hw)$dependencies
    }
  )
  
  if(length(deps)>0){
  attachDependencies(
    tagList(),
    unlist(deps,recursive=FALSE)
  )
  }  
```

### Conductivity, Specific Conductivity, TDS QAQC Plots

```{r Cond Spcond and TDS, echo=FALSE, results='asis'}

dx <- colnames(current%>%select(grep("^EXOSpCond|^EXOCond|^EXOTDS",colnames(current))))

# make the plots
outputs <- lapply(dx, all_plot, data= current_df, raw_data = raw, reservoir = "CCR", y_lab = "uScm or mg/L", y_lab2 = "uScm or mg/L", Use_plotly=F)

output <- unlist(outputs, recursive = F)

# Use this if you want to look at the plotly plot in the Markdown document. Make sure that Use_plotly = T in the all_plot function above. 

#output[[1]]


```

```{r Print plotly cond, echo=FALSE, messages=FALSE, warning=FALSE}

 # Used to print the plotly plots
  # attach the Dependencies
  # since the do not get included with renderTags(...)$html
  deps <- lapply(
    Filter(function(x){inherits(x,"htmlwidget")},output),
    function(hw){
      renderTags(hw)$dependencies
    }
  )
  
  if(length(deps)>0){
  attachDependencies(
    tagList(),
    unlist(deps,recursive=FALSE)
  )
  }  
```


### Wiper, Battery, and CablePower QAQC Plots

```{r Wiper, echo=FALSE, results='asis'}

dx <- colnames(current%>%select(grep("Wiper_V|EXOBattery_V|power_V",colnames(current))))

# make the plots
outputs <- lapply(dx, all_plot, data= current_df, raw_data = raw, reservoir = "CCR", y_lab = "volts", y_lab2 = "volts", Use_plotly=F)

output <- unlist(outputs, recursive = F)

# Use this if you want to look at the plotly plot in the Markdown document. Make sure that Use_plotly = T in the all_plot function above. The only plotly function for this chunk is the Wiper. We don't need to have interactive plots for the others. 

#output[[1]]

```

```{r Print plotly power, echo=FALSE, messages=FALSE, warning=FALSE}

 # Used to print the plotly plots
  # attach the Dependencies
  # since the do not get included with renderTags(...)$html
  deps <- lapply(
    Filter(function(x){inherits(x,"htmlwidget")},output),
    function(hw){
      renderTags(hw)$dependencies
    }
  )
  
  if(length(deps)>0){
  attachDependencies(
    tagList(),
    unlist(deps,recursive=FALSE)
  )
  }  
```


```{r Make csv, eval=FALSE, include=FALSE}

# Double Check naming convention
# Variable_StartYear_EndYear

# convert datetimes to characters so that they are properly formatted in the output file
 current_df$DateTime <- as.character(format(current_df$DateTime))

write_csv(current_df, "ccre-waterquality_2021_2024.csv")

```


```{r Download files, eval=FALSE, include=FALSE}

# Maintenance Log
download.file("https://raw.githubusercontent.com/FLARE-forecast/CCRE-data/ccre-dam-data-qaqc/CCRW_MaintenanceLog.csv", "ccre-waterquality_maintenancelog_2021_2024.csv")

# qaqc function
download.file("https://raw.githubusercontent.com/FLARE-forecast/CCRE-data/ccre-dam-data-qaqc/R/edi_qaqc_function.R", "ccre-waterquality_qaqc_2021_2024.R")

# streaming plots function
download.file("https://raw.githubusercontent.com/CareyLabVT/Reservoirs/master/Data/DataAlreadyUploadedToEDI/EDIProductionFiles/Plotting_function.R", "Plotting_function.R")

# Depth offsets
download.file("https://raw.githubusercontent.com/FLARE-forecast/CCRE-data/ccre-dam-data-qaqc/CCR_Depth_offsets.csv",
              "ccre-waterquality_depth_offsets_2021_2024.csv")

# Finding depth function
download.file("https://raw.githubusercontent.com/LTREB-reservoirs/vera4cast/main/targets/target_functions/find_depths.R","find_depths.R")

# Download HOBO files from GitHub
download.file("https://raw.githubusercontent.com/CareyLabVT/ManualDownloadsSCCData/master/CCR_manual_downloads/CCR_Hobos/CCR_hobos_20_21.csv", "ccre-waterquality_hobos_2020_2021.csv")

# Download the HOBO compilation script from GitHub
download.file("https://raw.githubusercontent.com/CareyLabVT/ManualDownloadsSCCData/master/CCR_manual_downloads/CCR_Hobos/CCR_hobo_compilation.R", "ccre-waterquality_hobo_compilation.R")

```

