---
title: "GHG for EDI"
author: "Abby Lewis"
date: "12/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readxl)
library(tidyverse)
```

Lingering to do's:
1. Some CO2 samples below detection - how to handle?
- Add in BD samples as 0 and flag!
2. Add in early 2020 data
3. How best to automate/remove bad reps?
- Can't really automate; more of an art than a science

This first section reads in previous data published on EDI
```{r}
# Package ID: edi.551.2 Cataloging System:https://pasta.edirepository.org.
# Data set title: Time series of dissolved methane and carbon dioxide concentrations for Falling Creek Reservoir and Beaverdam Reservoir in southwestern Virginia, USA during 2015-2019.
# Data set creator:  Cayelan Carey - Virginia Tech 
# Data set creator:  Ryan McClure - Virginia Tech 
# Data set creator:  Barbara Niederlehner - Virginia Tech 
# Data set creator:  Mary Lofton - Virginia Tech 
# Data set creator:  Alexandria Hounshell - Virginia Tech 
# Contact:  Cayelan Carey -  Virginia Tech  - Cayelan@vt.edu
# Stylesheet v2.11 for metadata conversion into program: John H. Porter, Univ. Virginia, jporter@virginia.edu 

inUrl1  <- "https://pasta.lternet.edu/package/data/eml/edi/551/2/38d72673295864956cccd6bbba99a1a3" 
infile1 <- tempfile()
try(download.file(inUrl1,infile1,method="curl"))
if (is.na(file.size(infile1))) download.file(inUrl1,infile1,method="auto")

                   
 dt1 <-read.csv(infile1,header=F 
          ,skip=1
            ,sep=","  
        , col.names=c(
                    "DateTime",     
                    "Depth_m",     
                    "Reservoir",     
                    "Rep",     
                    "ch4_umolL",     
                    "co2_umolL",     
                    "flag_ch4",     
                    "flag_co2"    ), check.names=TRUE)
               
unlink(infile1)
		    
# Fix any interval or ratio columns mistakenly read in as nominal and nominal columns read as numeric or dates read as strings
                                                   
# attempting to convert dt1$DateTime dateTime string to R date structure (date or POSIXct)                                
tmpDateFormat<-"%m/%d/%Y"
tmp1DateTime<-as.Date(dt1$DateTime,format=tmpDateFormat)
# Keep the new dates only if they all converted correctly
if(length(tmp1DateTime) == length(tmp1DateTime[!is.na(tmp1DateTime)])){dt1$DateTime <- tmp1DateTime } else {print("Date conversion failed for dt1$DateTime. Please inspect the data and do the date conversion yourself.")}                                                                    
rm(tmpDateFormat,tmp1DateTime) 
if (class(dt1$Depth_m)=="factor") dt1$Depth_m <-as.numeric(levels(dt1$Depth_m))[as.integer(dt1$Depth_m) ]               
if (class(dt1$Depth_m)=="character") dt1$Depth_m <-as.numeric(dt1$Depth_m)
if (class(dt1$Reservoir)!="factor") dt1$Reservoir<- as.factor(dt1$Reservoir)
if (class(dt1$Rep)=="factor") dt1$Rep <-as.numeric(levels(dt1$Rep))[as.integer(dt1$Rep) ]               
if (class(dt1$Rep)=="character") dt1$Rep <-as.numeric(dt1$Rep)
if (class(dt1$ch4_umolL)=="factor") dt1$ch4_umolL <-as.numeric(levels(dt1$ch4_umolL))[as.integer(dt1$ch4_umolL) ]               
if (class(dt1$ch4_umolL)=="character") dt1$ch4_umolL <-as.numeric(dt1$ch4_umolL)
if (class(dt1$co2_umolL)=="factor") dt1$co2_umolL <-as.numeric(levels(dt1$co2_umolL))[as.integer(dt1$co2_umolL) ]               
if (class(dt1$co2_umolL)=="character") dt1$co2_umolL <-as.numeric(dt1$co2_umolL)
if (class(dt1$flag_ch4)=="factor") dt1$flag_ch4 <-as.numeric(levels(dt1$flag_ch4))[as.integer(dt1$flag_ch4) ]               
if (class(dt1$flag_ch4)=="character") dt1$flag_ch4 <-as.numeric(dt1$flag_ch4)
if (class(dt1$flag_co2)=="factor") dt1$flag_co2 <-as.numeric(levels(dt1$flag_co2))[as.integer(dt1$flag_co2) ]               
if (class(dt1$flag_co2)=="character") dt1$flag_co2 <-as.numeric(dt1$flag_co2)
                
# Convert Missing Values to NA for non-dates
                
dt1$Depth_m <- ifelse((trimws(as.character(dt1$Depth_m))==trimws("NA")),NA,dt1$Depth_m)               
suppressWarnings(dt1$Depth_m <- ifelse(!is.na(as.numeric("NA")) & (trimws(as.character(dt1$Depth_m))==as.character(as.numeric("NA"))),NA,dt1$Depth_m))
dt1$Reservoir <- as.factor(ifelse((trimws(as.character(dt1$Reservoir))==trimws("NA")),NA,as.character(dt1$Reservoir)))
dt1$Rep <- ifelse((trimws(as.character(dt1$Rep))==trimws("NA")),NA,dt1$Rep)               
suppressWarnings(dt1$Rep <- ifelse(!is.na(as.numeric("NA")) & (trimws(as.character(dt1$Rep))==as.character(as.numeric("NA"))),NA,dt1$Rep))
dt1$ch4_umolL <- ifelse((trimws(as.character(dt1$ch4_umolL))==trimws("NA")),NA,dt1$ch4_umolL)               
suppressWarnings(dt1$ch4_umolL <- ifelse(!is.na(as.numeric("NA")) & (trimws(as.character(dt1$ch4_umolL))==as.character(as.numeric("NA"))),NA,dt1$ch4_umolL))
dt1$co2_umolL <- ifelse((trimws(as.character(dt1$co2_umolL))==trimws("NA")),NA,dt1$co2_umolL)               
suppressWarnings(dt1$co2_umolL <- ifelse(!is.na(as.numeric("NA")) & (trimws(as.character(dt1$co2_umolL))==as.character(as.numeric("NA"))),NA,dt1$co2_umolL))
dt1$flag_ch4 <- ifelse((trimws(as.character(dt1$flag_ch4))==trimws("NA")),NA,dt1$flag_ch4)               
suppressWarnings(dt1$flag_ch4 <- ifelse(!is.na(as.numeric("NA")) & (trimws(as.character(dt1$flag_ch4))==as.character(as.numeric("NA"))),NA,dt1$flag_ch4))
dt1$flag_co2 <- ifelse((trimws(as.character(dt1$flag_co2))==trimws("NA")),NA,dt1$flag_co2)               
suppressWarnings(dt1$flag_co2 <- ifelse(!is.na(as.numeric("NA")) & (trimws(as.character(dt1$flag_co2))==as.character(as.numeric("NA"))),NA,dt1$flag_co2))


# Here is the structure of the input data frame:
str(dt1)                            
attach(dt1)                            
# The analyses below are basic descriptions of the variables. After testing, they should be replaced.                 

summary(DateTime)
summary(Depth_m)
summary(Reservoir)
summary(Rep)
summary(ch4_umolL)
summary(co2_umolL)
summary(flag_ch4)
summary(flag_co2) 
                # Get more details on character variables
                 
summary(as.factor(dt1$Reservoir))
detach(dt1)               
        
```

JUST FOR 2021 EDI PUSH: Check to make sure all previous data follows MDL (CH4 = 0.002 umolL; CO2 = 3.8 umolL)
```{r}
# For purpose of data - if data is reported from instrument but below MDL - keep data value but flag = 5
dt2 <- dt1 %>% 
  mutate(flag_ch4 = ifelse(ch4_umolL <= 0.002 & flag_ch4 == 1, 15, 
                           ifelse(ch4_umolL <= 0.002 & flag_ch4 == 2, 25,
                                  ifelse(ch4_umolL <= 0.002 & flag_ch4 == 3, 35,
                                         dt1$flag_ch4)))) %>% 
  mutate(flag_co2 = ifelse(co2_umolL <= 3.8 & flag_co2 == 1, 15, 
                           ifelse(co2_umolL <= 3.8 & flag_co2 == 2, 25,
                                  ifelse(co2_umolL <= 3.8 & flag_co2 == 3, 35,
                                         dt1$flag_co2))))
```

This section loads data from 2020
```{r}
#Load this year's data
ghgs <- read_excel("../2020/GHG_MEGA_GC_SHEET_EXCEL_2020.xlsx", sheet = 2, skip = 6)

#Change column names to match EDI standard
colnames(ghgs)[1:4] <- c("DateTime","Depth_m","Reservoir","Rep")
colnames(ghgs)[13:14] <- c("ch4_umolL","co2_umolL")

ghgs=ghgs%>%
  select(DateTime,Depth_m,Reservoir,Rep,ch4_umolL,co2_umolL)%>% #Select only the columns we are using
  mutate(DateTime = as.Date(DateTime), #Make sure columns are the correct type
         Depth_m = as.numeric(Depth_m),
         Reservoir = as.factor(Reservoir))%>%
  filter(!is.na(Depth_m)) #Depth cannot be missing
```

This section graphs CO2 and CH4
```{r}
ghgs%>% #Plot CH4 at Site 50 in FCR
  filter(Depth_m<100,
         Reservoir == "FCR")%>%
  ggplot(aes(x = DateTime, y = ch4_umolL, col = as.factor(Depth_m)))+
  geom_point()

ghgs%>% #Plot CO2 at Site 50 in FCR
  filter(Depth_m<100,
         Reservoir == "FCR")%>%
  ggplot(aes(x = DateTime, y = co2_umolL, col = as.factor(Depth_m)))+
  geom_point()

ghgs%>% #Plot CH4 at Site 50 in BVR
  filter(Depth_m<100,
         Reservoir == "BVR")%>%
  ggplot(aes(x = DateTime, y = ch4_umolL, col = as.factor(Depth_m)))+
  geom_point()

ghgs%>% #Plot CO2 at Site 50 in BVR
  filter(Depth_m<100,
         Reservoir == "BVR")%>%
  ggplot(aes(x = DateTime, y = co2_umolL, col = as.factor(Depth_m)))+
  geom_point()

plot = ghgs_comb_2%>%
  filter(Reservoir == "FCR")%>%
  ggplot(aes(x = DateTime, y = ch4_umolL, color = as.factor(Depth_m), shape = ISSUE_ch4))+
  scale_alpha_manual(values = c(.2,1))+
  geom_point()
library(plotly)
ggplotly(plot)
```


This section calculates % difference between replicates
Flag 1 = the % difference between replicates is <30% and both are retained
Flag 2 = the % difference between replicates is >30% and <50% - both replicates were retained but are flagged
Flag 3 = the % difference between replicates is >50%. The replicate with the largest difference was removed
Flag 4 = Sample not collected or problem with instrument
Flag 5 = Sample below detection; CH4 = 0.002 umolL; CO2 = 3.8 umolL
```{r}
# Separate into rep 1 and rep2
ghgs_rep1 <- ghgs %>% 
  filter(Rep == "1") %>% 
  rename(ch4_umolL_rep1 = ch4_umolL, co2_umolL_rep1 = co2_umolL)

ghgs_rep2 <- ghgs %>% 
  filter(Rep == "2") %>% 
  rename(ch4_umolL_rep2 = ch4_umolL, co2_umolL_rep2 = co2_umolL)

ghgs_reps <- left_join(ghgs_rep1,ghgs_rep2,by=c("DateTime","Depth_m","Reservoir"))

ghgs_reps <- ghgs_reps %>% 
  mutate(ch4_diff = round((abs(ch4_umolL_rep1-ch4_umolL_rep2)/((ch4_umolL_rep1+ch4_umolL_rep2)/2))*100),
         co2_diff = round((abs(co2_umolL_rep1-co2_umolL_rep2)/((co2_umolL_rep1+co2_umolL_rep2)/2))*100),
         ch4_abs = abs(ch4_umolL_rep1-ch4_umolL_rep2),
         co2_abs = abs(co2_umolL_rep1-co2_umolL_rep2)) #,
         #ISSUE_co2 = co2_abs > 11.4 & co2_diff>=50,
         #ISSUE_ch4 = ch4_abs > 0.6 & ch4_diff>=50)
sd(ghgs_reps$co2_abs) #76.5
sd(ghgs_reps$ch4_abs) #76.5

sum(ghgs_reps$ISSUE_co2)
sum(ghgs_reps$ISSUE_ch4)

# Flag replicates: Flag 1; Flag 2; Flag 3
ghgs_reps <- ghgs_reps %>% 
  mutate(flag_ch4 = ifelse(ch4_diff>=50,3,
                           ifelse(ch4_diff<=50 & ch4_diff>=30,2,
                           1)))

ghgs_reps <- ghgs_reps %>% 
  mutate(flag_co2 = ifelse(co2_diff>=50,3,
                           ifelse(co2_diff<=50 & co2_diff>=30,2,
                           1)))

# Recombine with reps
ghgs_rep1 <- ghgs_reps %>% 
  select(-ch4_umolL_rep2,-co2_umolL_rep2) %>% 
  mutate(Rep = "1") %>% 
  rename(ch4_umolL = ch4_umolL_rep1, co2_umolL = co2_umolL_rep1)

ghgs_rep2 <- ghgs_reps %>% 
  select(-ch4_umolL_rep1,-co2_umolL_rep1) %>% 
  mutate(Rep = "2") %>% 
  rename(ch4_umolL = ch4_umolL_rep2, co2_umolL = co2_umolL_rep2)

ghgs_comb <- rbind(ghgs_rep1,ghgs_rep2)

ghgs_comb <- ghgs_comb %>% 
  arrange(DateTime,Reservoir,Depth_m,Rep)

ghgs_comb_2 <- ghgs_comb %>% 
  select(-c("ch4_diff","co2_diff","Rep.x","Rep.y"))

ghgs_comb_2$Rep <- as.integer(ghgs_comb_2$Rep)

ghgs_comb_2$flag_ch4[is.na(ghgs_comb_2$ch4_umolL)]<-4
ghgs_comb_2$flag_co2[is.na(ghgs_comb_2$co2_umolL)]<-4

# If sample is BD then flag as 5 (below detection)
ghgs_comb_2 <- ghgs_comb_2 %>% 
  mutate(flag_co2 = ifelse(co2_umolL <= 3.8 & is.na(ghgs_comb_2$flag_co2),5,
                          ifelse(co2_umolL <= 3.8 & flag_co2 == 1, 15,
                                 ifelse(co2_umolL <= 3.8 & flag_co2 == 2, 25, 
                                        ifelse(co2_umolL <= 3.8 & flag_co2 == 3, 35,
                                               ghgs_comb_2$flag_co2))))) %>% 
  mutate(flag_ch4 = ifelse(ch4_umolL <= 0.002 & is.na(ghgs_comb_2$flag_ch4),5,
                           ifelse(ch4_umolL <= 0.002 & flag_ch4 == 1, 15,
                                  ifelse(ch4_umolL <= 0.002 & flag_ch4 == 2, 25,
                                         ifelse(ch4_umolL <= 0.002 & flag_ch4 == 3, 35,
                                                ghgs_comb_2$flag_ch4)))))
```

Create a combined file to publish on EDI
```{r}
final = dt2%>%
  full_join(ghgs_comb_2)

#Moving sites out of the depth column
final$Site = 50
final$Site[final$Depth_m > 98]<- final$Depth_m[final$Depth_m > 98]
final$Depth_m[final$Depth_m > 98] <- 0.1

#Re-order columns
col_order <- c("Reservoir","Site","DateTime","Depth_m","Rep","ch4_umolL","co2_umolL","flag_ch4","flag_co2")

final <- final[,(col_order)]

write.csv(final,"final_GHG_2015-2020.csv")
```

