---
title: "FCR Met Plots for EDI"
author: "Adrienne Breef-Pilz"
output: html_document
theme: null
original date made: 04 Jan 2024
date: "`r Sys.Date()`"
---

This script is the visual inspection scripts:

1. QAQCs all the raw data or for a reviewer reads in the data file from EDI for checking. IF YOU ARE QAQCING ALL FILES IT WILL TAKE OVER 20 MINUTES FOR THE SCRIPT TO RUN. 

2. Then the script checks for daily and subdaily gaps in the current file. 

3. Lists the flag frequency to check if there are any NAs or any assigned the wrong flag. 

4. Checks to see if the Maintenance Log is working correctly by inspecting rows in the data frame. 

5. If necessary can QAQC data already on EDI using the QAQC function

6. Creates plots

7. Writes data to new csv

8. Downloads necessary files for EDI publishing

For the plots, they use a function called "all_plot". In all_plot you can specify if you want plotly plots for the current data. BEWARE if you turn on the plotly plots and try to knit the markdown it will fail! I am working on a fix. For right now you can specify which plotly plots you want on. You can also look at the plotly plots manually in each chunk by running the chunk with Use_plotly=TRUE as an argument and then at the end of the chunk output[[1]]. 


All files are from GitHub or EDI and the source scripts are from GitHub as well. 

If you are REVIEWING this data package, add the pasta URL from EDI in the "Bind Historical and L1 files together". Make sure to comment out the row_bind section and uncomment the section that reads in the pasta. In addition, make sure eval=FALSE is in the chunk header for "Get raw files", "QAQC all files", "Write CSV" and "Download and save Maintenance Log". These chunks of code will not be run when the R markdown is knitted together and save you LOTTTS of time. Once that is all set than you can knit the file together as an HTML file to look at all the plots. 


```{r Set Up, include=FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(RCurl,devtools, tidyverse,lubridate, plotly, magrittr, scattermore, knitr, htmltools, pander, suncalc)

# Source scripts from GitHub
devtools::source_url("https://raw.githubusercontent.com/FLARE-forecast/FCRE-data/fcre-metstation-data-qaqc/R/edi_qaqc_function.R")
devtools::source_url('https://raw.githubusercontent.com/CareyLabVT/Reservoirs/master/Data/DataAlreadyUploadedToEDI/EDIProductionFiles/Plotting_function.R')


 #turn off pander auto asis
        pander::panderOptions('knitr.auto.asis', FALSE)

# Set up the current time end time of the file and the current year for QAQC plots

#current time of QAQC for graphing
current_time_start=force_tz(as.POSIXct("2023-01-01 00:00:00"), tzone = "EST")
current_time_end= force_tz(as.POSIXct("2024-01-01 00:00:00"), tzone = "EST")
```

```{r Get raw files, eval=FALSE, include=FALSE}

# This section creates a list of the raw files and the manual files 

ds <- c(
  'https://raw.githubusercontent.com/CareyLabVT/Reservoirs/master/Data/DataAlreadyUploadedToEDI/CollatedDataForEDI/MetData/RawMetData_2015_2016.csv',
  'https://raw.githubusercontent.com/CareyLabVT/Reservoirs/master/Data/DataAlreadyUploadedToEDI/CollatedDataForEDI/MetData/RawMetData_2017.csv',
        'https://raw.githubusercontent.com/FLARE-forecast/FCRE-data/fcre-metstation-data-qaqc/FCRmet_legacy_2018.csv',
        'https://raw.githubusercontent.com/FLARE-forecast/FCRE-data/fcre-metstation-data-qaqc/FCRmet_legacy_2019.csv',
        'https://raw.githubusercontent.com/FLARE-forecast/FCRE-data/fcre-metstation-data-qaqc/FCRmet_legacy_2020.csv',
        'https://raw.githubusercontent.com/FLARE-forecast/FCRE-data/fcre-metstation-data-qaqc/FCRmet_legacy_2021.csv',
        'https://raw.githubusercontent.com/FLARE-forecast/FCRE-data/fcre-metstation-data-qaqc/FCRmet_legacy_2022.csv',
        # THE CURRENT YEARS FILE
        'https://raw.githubusercontent.com/FLARE-forecast/FCRE-data/fcre-metstation-data/FCRmet.csv'
        )


# Read in and make a data frame of the manual downloaded files 

man_files <- c(
'https://raw.githubusercontent.com/CareyLabVT/ManualDownloadsSCCData/master/MetStation/FCRMet_ManualDownloads_2015_2016.csv','https://raw.githubusercontent.com/CareyLabVT/ManualDownloadsSCCData/master/MetStation/FCRMet_ManualDownloads_2017.csv',
   'https://raw.githubusercontent.com/CareyLabVT/ManualDownloadsSCCData/master/MetStation/FCRMet_ManualDownloads_2018.csv',
   'https://raw.githubusercontent.com/CareyLabVT/ManualDownloadsSCCData/master/MetStation/FCRMet_ManualDownloads_2019.csv',
   'https://raw.githubusercontent.com/CareyLabVT/ManualDownloadsSCCData/master/MetStation/FCRMet_ManualDownloads_2020.csv',
   'https://raw.githubusercontent.com/CareyLabVT/ManualDownloadsSCCData/master/MetStation/FCRMet_ManualDownloads_2021.csv',
   'https://raw.githubusercontent.com/CareyLabVT/ManualDownloadsSCCData/master/MetStation/FCRMet_ManualDownloads_2022.csv',
   'https://raw.githubusercontent.com/CareyLabVT/ManualDownloadsSCCData/master/MetStation/FCRMet_ManualDownloads_2023.csv'
  )

 # Make a tibble of the arguments going into the function. Each row are the arguments that will go into the function. Make sure you have the correct raw files that go with the manual files. If you want the same argument just repeat it each time. 
state_met <- tibble(data_file = ds, 
       data2_file = man_files,
       maintenance_file = rep('https://raw.githubusercontent.com/FLARE-forecast/FCRE-data/fcre-metstation-data-qaqc/MET_maintenancelog_new.csv',each=8),
       met_infrad = rep('https://raw.githubusercontent.com/FLARE-forecast/FCRE-data/fcre-metstation-data-qaqc/FCR_Met_Infrad_DOY_Avg_2018.csv', each=8),
       output_file = I(list(NULL, NULL, NULL, NULL, NULL, NULL, NULL, NULL)),
       start_date = I(list(NULL, NULL, NULL, NULL, NULL, NULL, NULL, NULL)),
       end_date = I(list(NULL, NULL, NULL, NULL, NULL, NULL, NULL, NULL)),
       notes = rep(TRUE, each=8))
```

```{r QAQC all files, include=FALSE}

# Use the tibble above to use pmap and run each row through the qaqc_fcrmet function.
# This creates a data frame for each or the raw files. Then we bind everything together below. 

fcrmet_files <- state_met%>% 
  pmap(qaqc_fcrmet)

```


REVIEWERS- If you are reviewing this data package replace the pasta link with the one from EDI. If there are questions ask the data point person. 

```{r Bind files together or READ IN EDI FOR REVIEWER, include=FALSE}
  
# Bind all the QAQC files from above
  current_df <- dplyr::bind_rows(fcrmet_files)

# Filter for the end of the current publishing year in the set up chunk. 
current_df <- current_df%>%
  dplyr::distinct()%>%
  filter(DateTime<(current_time_end))

# make sure no time duplicates. 
 current_df <-  current_df[!duplicated(current_df$DateTime), ]

#reorder. Just to be certain everything is in order
  current_df<-current_df[order(current_df$DateTime),]
  

# For REVIEWERS: Run this section to pull the data from EDI which is in staging as a check of the data

  #current_df2 <-read_csv("https://pasta-s.lternet.edu/package/data/eml/edi/143/27/d4c74bbb3b86ea293e5c52136347fbb0")
  
 # 
 # # Force files from EDI to have an EST timestamp
 #  current_df$DateTime <- force_tz(as.POSIXct(current_df$DateTime), tzone = "EST")
 


```

```{r Download Raw data for plotting, include=FALSE}

CATPRES_COL_NAMES =  c("DateTime","Record", "CR3000Battery_V", "CR3000Panel_Temp_C",
                   "PAR_umolm2s_Average", "PAR_Total_mmol_m2", "BP_Average_kPa", "AirTemp_C_Average",
                   "RH_percent", "Rain_Total_mm", "WindSpeed_Average_m_s", "WindDir_degrees", "ShortwaveRadiationUp_Average_W_m2",
                   "ShortwaveRadiationDown_Average_W_m2", "InfraredRadiationUp_Average_W_m2",
                   "InfraredRadiationDown_Average_W_m2", "Albedo_Average_W_m2")
  
 
  # read catwalk data and maintenance log
  # NOTE: date-times throughout this script are processed as UTC
  raw <- read_csv("https://raw.githubusercontent.com/FLARE-forecast/FCRE-data/fcre-metstation-data/FCRmet.csv", skip = 4, col_names = CATPRES_COL_NAMES,
                      col_types = cols(.default = col_double(), DateTime = col_datetime()))
  
  
  # convert NaN to NAs in the dataframe
  raw[sapply(raw, is.nan)] <- NA
  
  # set a time stamp for the raw files
  raw$DateTime <- force_tz(as.POSIXct(raw$DateTime), tzone = "EST")

```

## Check for gaps in the data frame

This first checks if there are any date duplicates and then identifies if there are any daily data gaps in the long-term record. 

```{r Check for daily gaps, echo=FALSE}

 # Make sure there are no duplicated dates. Do this here because the file is too large for Data Explore.
# Print them if there are
 dups<- current_df[duplicated(current_df$DateTime), ]

dups <- dups%>%
  select(DateTime, Record, CR3000Battery_V, CR3000Panel_Temp_C, 
         PAR_Total_mmol_m2, BP_Average_kPa, AirTemp_C_Average)

knitr::kable((dups))

# Get DOY
catwalk <- current_df
 catwalk$DOY=yday(catwalk$DateTime)

 for(i in 2:nrow(catwalk)){ #this identifies if there are any data gaps in the long-term record, and where they are by record number
    if(catwalk$DOY[i]-catwalk$DOY[i-1]>1){
      print(c(catwalk$DateTime[i-1],catwalk$DateTime[i]))
    }
 }
```

This identifies if there are any sub-daily gaps in the current record, as gaps of the long term record are found in the metadata.

The first row is the time for the first observation and then the subsequent observation. Each observation should be 10 minutes apart. The second row is the number of the record for each observation. Most of these gaps happen when we change the program on the data logger. These times will be recorded in the maintenance section of the metadata and are also noted in the maintenance log.

```{r Check for sub daily gaps, echo=FALSE}

# Because we can't have NAs for this for loop let's make a new df
 cat2 <- current_df%>%
  filter(!is.na(Record))
  #%>%filter(DateTime>current_time_start)

  for(i in 2:length(cat2$Record)){ #this identifies if there are any data gaps in the long-term record, and where they are by record number
    if(abs(cat2$Record[i]-cat2$Record[i-1])>1 & difftime(cat2$DateTime[i], cat2$DateTime[i-1], units="mins")>1){
      print(c(cat2$DateTime[i-1], cat2$DateTime[i]))
      print(c(cat2$Record[i-1], cat2$Record[i]))
    }
  }

```


### Let's look at the flag Frequency for each variable. As a reminder here are the flag codes

Let's look at the flag Frequency for each variable. 

As a reminder here are the flag codes Flag values 

0: no flag; 

1: value removed due to maintenance and set to NA; 

2: sample not collected; 

3: negative values set to 0, percent greater than 100 and set to 100, or infinite values set to NA; 

4: potentially questionable value and changed or set to NA, see note; 

5: questionable value but left in the dataset.


```{r Check out the flags, echo=FALSE}

#make sure no NAS in the Flag columns
Flags <- current_df%>%
  select(DateTime, starts_with("Flag"))

RowsNA=Flags[!complete.cases(Flags), ] # Keep only the complete rows

#check the flag column
Flags <- current_df%>%
  select(starts_with("Flag"))

# Make a table with the number of times a flag was used
for(f in 1:ncol(Flags)){
  print(colnames(Flags[f]))
  print(table(Flags[,f], useNA = "always"))
}
```


### Check to make sure that what is in the maintenance log  was actually removed

### Look at the last rows of the maintenance log 

We want to make sure that our maintenance log actually worked and took out the values or changes those it was supposed to 

```{r Read in the maintenance log and look at the tail, echo=FALSE}

 maint <- read_csv2("https://raw.githubusercontent.com/FLARE-forecast/FCRE-data/fcre-metstation-data-qaqc/MET_maintenancelog_new.csv",show_col_types = FALSE)


# name the data file for just the tail of the maintenance log
# you want to filter out 7 because that is if the observation is missing and there are other ways that is flagged in the data besides the maintenance log, so it is not a good check.
sd <- tail(maint)


knitr::kable((tail(sd)))

```
#### Check the that the columns have flags 

Look at the first few rows of the data frame and check that the observations after the TIMESTAMP_start are flagged

#### Look at the first 5 rows for that time

```{r Did the maint log work head, echo=FALSE, message=FALSE, warning=FALSE}
# get the last row of the data file
last_row <- tail(sd, n=1)

# Get starttime and end time
### get start and end time of one maintenance event
    start <- force_tz(as.POSIXct(last_row$TIMESTAMP_start), tzone = "EST")
    end <- force_tz(as.POSIXct(last_row$TIMESTAMP_end), tzone = "EST")
    
    # Get the time of the maintenance
    if(is.na(end)){
      # If there the maintenance is on going then the columns will be removed until
      # and end date is added
      Time <- current_df |> filter(DateTime >= start) |> select(DateTime)
      
    }else if (is.na(start)){
      # If there is only an end date change columns from beginning of data frame until end date
      Time <- current_df |> filter(DateTime <= end) |> select(DateTime)
      
    }else {
      Time <- current_df |> filter(DateTime >= start & DateTime <= end) |> select(DateTime)
    }


### Get the names of the columns affected by maintenance
    colname_start <- last_row$start_parameter
    colname_end <- last_row$end_parameter
    
    # Make list of just the columns we want 
    
    test <- colnames(current_df%>%select(DateTime, colname_start, paste0("Flag_",colname_start), colname_end, paste0("Flag_",colname_end)))
    
    # Print the head of the table to make sure that data are flagged
    
    knitr::kable((head(current_df[current_df$DateTime %in% Time$DateTime, test]))) 

```

#### Look at the last 6 rows for the maintenance time

Make sure the observations are flagged

```{r Print the tails, echo=FALSE, message=FALSE, warning=FALSE}

# Print the tail of the table to make sure that data are flagged
    
    knitr::kable(tail(current_df[current_df$DateTime %in% Time$DateTime, test])) 

```

### Subset and rename the files
This section will subset the files so you can make plots of the whole time series and the current year. 
Here we also get the daily average for each variable so we can make box plots and density plots to look at the data over time. 


```{r Filter for current year and daily average, include=FALSE}

# Raw files
current_raw <- raw%>%
  filter(DateTime>=current_time_start & DateTime<current_time_end)%>%
  mutate(type = "raw")

current <- current_df%>%
  filter(DateTime>=current_time_start & DateTime<current_time_end)%>%
  mutate(type = "qaqc")%>%
  select(DateTime:Albedo_Average_W_m2,type, -contains("adjusted"))


# Let's only keep values that are different instead of plotting the raw and the qaqc value
current_plot_df <- bind_rows(current, current_raw)%>%
  dplyr::distinct(across(DateTime:Albedo_Average_W_m2), .keep_all = T)
    

daily <- current_df%>% 
  group_by( Date = as.Date(DateTime)) %>% 
  summarise_if(is.numeric, mean, na.rm=T)%>%
  mutate(Year = as.factor(year(Date)),
         Month = month(Date),
         Time = "12:00:00")%>%
  mutate(DateTime= paste0(Date, Time, sep=" "))%>%
  mutate(DateTime=ymd_hms(DateTime))

  
catdata <- current_df%>%
  mutate(Year=year(DateTime))

colors <- c("raw" = "red", "qaqc" = "black")
# colors for comparing Thermistor, RDO and Pressure sensor

#colors2 <- c("Therm"="magenta","RDO"="dodgerblue2" ,"Pressure"="black")
```

## QAQC Plots

##### QAQC plot information and all_plot function information

For the plots, they use a function called "all_plot". In all_plot you can specify if you want plotly plots for the current data. BEWARE if you turn on the plotly plots and try to knit the markdown it will fail! I am working on a fix. For right now you can specify which plotly plots you want on. You can also look at the plotly plots manually in each chunk by running the chunk with Use_plotly=TRUE as an argument and then at the end of the chunk output[[1]]. 

The plotting function is called all_plot() which plots the 4 or more plots described below. The function is sourced from GitHub in the first chunk of the script. The argumenst are:
Var # The column you want to plot. Make sure it is in quotes
y_lab,  # This label can take an expression aka have the proper degrees C, 
y_lab2, # This label is for the plotly function which can not handle expression argument. 
Water=T, # Are these plots for inwater streaming sensors?
Raw_file = T, # Do you have access to raw files to compare to. This is only for streaming sensors. 
Use_plotly = F){ # Do you want to produce plotly interactive plots? 

The arguments with = followed by a True means that they are the defaults and you don't need to add them to the function when you use it. If you want to use the opposite of the default you must specify that. 
  
##### Plot Description:

The plots below are:
The first 2 plots are the ones you should focus on for the QAQC chec. Spend the most time looking at the most recent data because that one as been checked. Do pay attention to the historical to make sure there are no crazy outliers that were missed in previous years. 
1. A time series of the current years' data. The black dots are the qaqced observations and the red is the raw files that were qaqced. This is to see what kind of values were removed and if there are any the script missed or that need to be added to the maintenance log. 

2. A time series of the historical and the current data just the qaqced values. 

The next two plots are just fun to see trends over time with the data. 

3. Density plots are like a histogram and a grouped by color so you can see where the data are relative to other years. 

4. The box plots look at the spread of the data within the year and we can look at the median and see how that is changing or not. 

Do not over think the last 2 plots. 

## All Met Variables
```{r Temp, echo=FALSE, results='asis'}

dx <- colnames(raw |> select(PAR_umolm2s_Average:Albedo_Average_W_m2))

# make the plots
outputs <- lapply(dx, all_plot,y_lab = 'Var Unit', y_lab2 = "Var Unit", Water = FALSE, Use_plotly = F)

output <- unlist(outputs, recursive = F)

```

```{r Print plotly temp, echo=FALSE, messages=FALSE, warning=FALSE}

 # Used to print the plotly plots
  # attach the Dependencies
  # since the do not get included with renderTags(...)$html
  deps <- lapply(
    Filter(function(x){inherits(x,"htmlwidget")},output),
    function(hw){
      renderTags(hw)$dependencies
    }
  )
  
  if(length(deps)>0){
  attachDependencies(
    tagList(),
    unlist(deps,recursive=FALSE)
  )
  }  
```


### Write to CSV

```{r Write CSV, eval=FALSE, include=FALSE}

# make date time a character so no confusion with timezones
current_df$DateTime <- as.character(current_df$DateTime)

# Double Check naming convention
# Variable_StartYear_EndYear
write_csv(current_df, "FCRMet_2015_2023.csv")

```

### Download and save Maintenance Log, Plotting function, and QAQC function

```{r Download and save Maintenance Log, eval=FALSE, include=FALSE}

# Maintenance Log
download.file("https://raw.githubusercontent.com/FLARE-forecast/FCRE-data/fcre-metstation-data-qaqc/MET_maintenancelog_new.csv", "FCRMet_maintenancelog_2015_2023.csv")

# qaqc function
download.file("https://raw.githubusercontent.com/FLARE-forecast/FCRE-data/fcre-metstation-data-qaqc/R/edi_qaqc_function.R", "FCRMet_qaqc_2015_2023.R")

# streaming plots function
download.file("https://raw.githubusercontent.com/CareyLabVT/Reservoirs/master/Data/DataAlreadyUploadedToEDI/EDIProductionFiles/Plotting_function.R", "Plotting_function.R")

# Infrad_DOY_average
download.file("https://raw.githubusercontent.com/FLARE-forecast/FCRE-data/fcre-metstation-data-qaqc/FCR_Met_Infrad_DOY_Avg_2018.csv", "FCRMet_Infrad_DOY_Avg_2015_2017.csv")


```

