---
title: "EddyFlux Inspection Script"
author: "Adrienne Breef-Pilz"
output: html_document
original date: Jan. 2023
date: "`r Sys.Date()`"
---

This script is the visual inspection scripts. 

1. QAQCs all the raw data or for a reviewer reads in the data file from EDI for checking. 

2. Then the script checks for duplicates, daily gaps in the file. 

3. Creates plots

4. Writes data to new csv

5. Downloads necessary files for EDI publishing. This file currently does not have a maintenance log


For the plots, they use a function called "all_plot". In all_plot you can specify if you want plotly plots for the current data. BEWARE if you turn on the plotly plots and try to knit the markdown it will fail! I am working on a fix. For right now you can specify which plotly plots you want on. You can also look at the plotly plots manually in each chunk by running the chunk with Use_plotly=TRUE as an argument and then at the end of the chunk output[[1]]. 


All files are from GitHub or EDI and the source scripts are from GitHub as well. 

If you are REVIEWING this data package, add the pasta URL from EDI in the "QAQC file or READ IN EDI FOR REVIEWER". Make sure to comment out the row_bind section and un comment the section that reads in the pasta. In addition, make sure eval=FALSE is in the chunk header for "QAQC raw files", "Make new CSV with current and historic files" chunk and "Download Files". These chunks of code will not be run when the R markdown is knitted together. Once that is all set than you can knit the file together as an HTML document to look at all the plots. 


```{r setup packages, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

# Load the packages you need
pacman::p_load(tidyverse, lubridate, gsheet, hms,gridExtra,openair, googledrive, knitr, scattermore, htmltools, pander, devtools, plotly)

# Source scripts used in markdown

source("https://raw.githubusercontent.com/CareyLabVT/Reservoirs/master/Scripts/L1_functions/eddy_flux_create.R")

# Plotting function
source('https://raw.githubusercontent.com/CareyLabVT/Reservoirs/master/Data/DataAlreadyUploadedToEDI/EDIProductionFiles/Plotting_function.R')

#turn off pander auto asis
        pander::panderOptions('knitr.auto.asis', FALSE)

# Set up the current time end time of the file and the current year for QAQC plots

#current time of QAQC for graphing
# The flux system is in Eastern time and observes daylight savings
current_time_start=ymd_hms("2023-01-01 00:00:00", tz= "America/New_York")
current_time_end=ymd_hms("2023-12-31 23:59:00", tz= "America/New_York")
```



```{r QAQC raw files, eval=FALSE, include=FALSE}
# QAQC the files we have

# current_df <- eddypro_cleaning_function(
#   directory = "../../../../DataNotYetUploadedToEDI/EddyFlux_Processing/",
#   gdrive = F, # Are the files on Google Drive. True or False
#   gshared_drive = as_id("0ACybYKbCwLRPUk9PVA"),
#   current_year = NULL,
#   output_file = NULL)
# 
# # Make a DateTime column but remove it before saving the file
#  current_df$DateTime <- ymd_hms(paste0(current_df$date, " " ,current_df$time))
#  
#  # force the timezone to Eastern/New_York
#  
#  # Set timezone as EST. Streaming sensors don't observe daylight savings
#   current_df$DateTime <- force_tz(current_df$DateTime, tzone = "America/New_York")
#  

```

REVIEWERS- If you are reviewing this data package replace the pasta link with the one from EDI. If there are questions ask the data point person. 

```{r QAQC file or READ IN EDI FOR REVIEWER, include=FALSE}
  
# # If No EDI file exists with all the years you want to look at
#   current_df <- current_df%>%
#   dplyr::distinct(.)%>% # get rid of dups if they snuck in
#   filter(DateTime<(current_time_end))
# 
# # make sure no time duplicates.
#  current_df<-  current_df[!duplicated(current_df$DateTime), ]
# 
# #reorder. Just to be certain everything is in order
#   current_df<-current_df[order(current_df$DateTime),]


# For REVIEWERS: Run this section to pull the data from EDI which is in staging as a check of the data.
# MAKE SURE TO UPDATE THE PASTA FROM THE VERSION YOU WANT

                                                                  ### CHANGE THIS NUMBER BELOW 
                                                                               ##      
  current_df <-read_csv("https://pasta-s.lternet.edu/package/data/eml/edi/692/10/e0976e7a6543fada4cbf5a1bb168713b")
 #
 # # Force files from EDI to have an EST timestamp

 # Make a DateTime column but remove it before saving the file
  current_df$DateTime <- ymd_hms(paste0(current_df$date, " " ,current_df$time))
  
  # Set timezone as EST. Streaming sensors don't observe daylight savings
   current_df$DateTime <- force_tz(current_df$DateTime, tzone = "America/New_York")
  
```


## Check for duplicates and  gaps in the data frame

This section identifies if there are any duplicates, daily data, and sub daily gaps in the long-term record. If there are duplicates. Look to see if they are true duplicates and then check the qaqc function and the chunk above where duplicates should be removed. 


### Are there any duplicates?


```{r Check for dups , echo=FALSE}

# Make sure there are no duplicated dates. Do this here because the file is too large for Data Explore.
# Print them if there are
 dups<- current_df[duplicated(current_df$DateTime), ]

dups <- dups%>%
  select(DateTime, co2_flux_umolm2s,  specific_humidity_kgkg, u_star_ms) 

# Make it into a nice table when the Markdown is knitted together
knitr::kable((dups))
```


### Are there any gaps in the data file?


When gaps are found in the data file, check that you do not have new gaps in the previous years' publication. For the current year, if you find gaps check that you have all of the manually downloaded files. If the data are truly missing then record the dates and times in the methods section. 

```{r Check for daily gaps, echo=FALSE}

# Get DOY
df2 <- current_df
 df2$DOY=yday(df2$DateTime)

 for(i in 2:nrow(df2)){ #this identifies if there are any data gaps in the long-term record, and where they are by record number
    if(df2$DOY[i]-df2$DOY[i-1]>1){
      print(c(df2$DateTime[i-1],df2$DateTime[i]))
    }
 }
```

### Subset and rename the files
This section will subset the files so you can make plots of the whole time series and the current year. 
Here we also get the daily average for each variable so we can make box plots and density plots to look at the data over time. 

```{r Filter for current year and daily average, include=FALSE}


current <- current_df%>%
  filter(DateTime>=current_time_start & DateTime<current_time_end)%>%
  mutate(type = "qaqc")
 # %>%select(DateTime:CR6Panel_Temp_C,type, -contains("adjusted"))


daily <- current_df%>% 
  group_by( Date = as.Date(DateTime)) %>% 
  summarise_if(is.numeric, mean, na.rm=T)%>%
  mutate(Year = as.factor(year(Date)),
         Month = month(Date),
         Time = "12:00:00")%>%
  mutate(DateTime= paste0(Date, Time, sep=" "))%>%
  mutate(DateTime=ymd_hms(DateTime))

  
# catdata <- current_df%>%
#   mutate(Year=year(DateTime))

colors <- c("raw" = "red", "qaqc" = "black")
# colors for comparing Thermistor, RDO and Pressure sensor
colors2 <- c("Therm"="magenta","RDO"="dodgerblue2" ,"Pressure"="black")
```

## QAQC Plots

##### QAQC plot information and all_plot function information

For the plots, they use a function called "all_plot". In all_plot you can specify if you want plotly plots for the current data. BEWARE if you turn on the plotly plots and try to knit the markdown it will fail! I am working on a fix. For right now you can specify which plotly plots you want on. You can also look at the plotly plots manually in each chunk by running the chunk with Use_plotly=TRUE as an argument and then at the end of the chunk output[[1]]. 

The plotting function is called all_plot() which plots the 4 or more plots described below. The function is sourced from GitHub in the first chunk of the script. The arguments are:
Var # The column you want to plot. Make sure it is in quotes
y_lab,  # This label can take an expression aka have the proper degrees C, 
y_lab2, # This label is for the plotly function which can not handle expression argument. 
Water=T, # Are these plots for in water streaming sensors?
Raw_file = T, # Do you have access to raw files to compare to. This is only for streaming sensors. 
Use_plotly = F){ # Do you want to produce plotly interactive plots? 

The arguments with = followed by a True means that they are the defaults and you don't need to add them to the function when you use it. If you want to use the opposite of the default you must specify that. 
  
##### Plot Description:

The plots below are:
The first 2 plots are the ones you should focus on for the QAQC check. Spend the most time looking at the most recent data because that one has not been checked. Do pay attention to the historical to make sure there are no crazy outliers that were missed in previous years. 

1. A time series of the current years' data. The black dots are the qaqced observations and the red is the raw files that were qaqced. This is to see what kind of values were removed and if there are any the script missed or that need to be added to the maintenance log. 

2. A time series of the historical and the current data just the qaqced values. 

The next two plots are just fun to see trends over time with the data. 

3. Density plots are like a histogram and a grouped by color so you can see where the data are relative to other years. 

4. The box plots look at the spread of the data within the year and we can look at the median and see how that is changing or not. 

Do not over think the last 2 plots. 

### Flux Plots for CO2, H2O, and CH4

```{r Fluxes, echo=FALSE, results='asis'}

dx <- colnames(current%>%select(co2_flux_umolm2s, h2o_flux_umolm2s, ch4_flux_umolm2s))

# make the plots
outputs <- lapply(dx, all_plot, y_lab="umolm2s", y_lab2="umolm2s", Water=F, Raw_file=F, Use_plotly=T)

output <- unlist(outputs, recursive = F)

#output[[1]]
```

```{r Print plotly fluxes, echo=FALSE, messages=FALSE, warning=FALSE}

 # Used to print the plotly plots
  # attach the Dependencies
  # since the do not get included with renderTags(...)$html
  deps <- lapply(
    Filter(function(x){inherits(x,"htmlwidget")},output),
    function(hw){
      renderTags(hw)$dependencies
    }
  )
  
  if(length(deps)>0){
  attachDependencies(
    tagList(),
    unlist(deps,recursive=FALSE)
  )
  }  
```


### Compare 30 minute flux to daily flux

This is a similar figure to the one in Alex's paper. The 30 minute fluxes are black dotes and the line is the average daily flux

#### CO2

```{r CO2 Thirty Minute to Daily fluxes, echo=FALSE}
a <- daily%>%
  filter(DateTime>current_time_start)

ggplot()+
  geom_point(data = current, aes(x= DateTime, y= co2_flux_umolm2s*60*60*24*44.01/1e6),alpha = 0.1)+
  geom_hline(yintercept = 0, linetype="dashed")+
  geom_line(data = a, aes(x=DateTime, y=co2_flux_umolm2s*60*60*24*44.01/1e6),color="#E63946", linewidth = 1)+
  theme_classic(base_size = 15)+
  xlab("DateTime") + ylab(expression(~CO[2]~flux~(g~m^-2~d^-1))) +
  ggtitle("Current Year Thirty Minute Fluxes to Daily Fluxes")


ggplot()+
  geom_point(data = current_df, aes(x= DateTime, y= co2_flux_umolm2s*60*60*24*44.01/1e6),alpha = 0.1)+
  geom_hline(yintercept = 0, linetype="dashed")+
  geom_line(data = daily, aes(x=DateTime, y=co2_flux_umolm2s*60*60*24*44.01/1e6),color="blue", linewidth = 1)+
  theme_classic(base_size = 15)+
  xlab("DateTime") + ylab(expression(~CO[2]~flux~(g~m^-2~d^-1))) +
  ggtitle("Thirty Minute Fluxes to Daily Fluxes")

```

#### CH4 

```{r CH4 Thirty Minute to Daily fluxes, echo=FALSE}
a <- daily%>%
  filter(DateTime>current_time_start)

ggplot()+
  geom_point(data = current, aes(x= DateTime, y= ch4_flux_umolm2s),alpha = 0.1)+
  geom_hline(yintercept = 0, linetype="dashed")+
  geom_line(data = a, aes(x=DateTime, y=ch4_flux_umolm2s),color="#E63946", linewidth = 1)+
  theme_classic(base_size = 15)+
  xlab("DateTime") + ylab(expression(~CH[4]~flux~(g~m^-2~d^-1))) +
  ggtitle("Current Year Thirty Minute Fluxes to Daily Fluxes")


ggplot()+
  geom_point(data = current_df, aes(x= DateTime, y=ch4_flux_umolm2s*60*60*24*16.04/1e6),alpha = 0.1)+
  geom_hline(yintercept = 0, linetype="dashed")+
  geom_line(data = daily, aes(x=DateTime, y=ch4_flux_umolm2s*60*60*24*16.04/1e6),color="blue", linewidth = 1)+
  theme_classic(base_size = 15)+
  xlab("DateTime") + ylab(expression(~CH[4]~flux~(g~m^-2~d^-1))) +
  ggtitle("Thirty Minute Fluxes to Daily Fluxes")

```

### Wind Rose plots for the Current Year and All Observations

Plot the wind direction, see what it looks like. 

```{r Wind Rose, echo=FALSE}

# Visualize wind directions for just the current year 
      chicago_wind <- current%>%
        select(DateTime,wind_speed_ms,wind_dir)%>%
        dplyr::rename(date = DateTime, ws = wind_speed_ms, wd = wind_dir)

    # Make Plot
      pollutionRose(chicago_wind, pollutant="ws")
      
      
      
 # Visualize wind directions for all obs      
      chicago_wind <- current_df%>%
        select(DateTime,wind_speed_ms,wind_dir)%>%
        dplyr::rename(date = DateTime, ws = wind_speed_ms, wd = wind_dir)
      
      # Make plot
      pollutionRose(chicago_wind, pollutant="ws", type = "year")
      
```

### Ancillary Data

U_star_ms is friction velocity

sonic temperature is temperature in kelvin from the sonic anemometer

H_wm2 is Sensible heat flux

LE_wm2 is Latent heat flux

```{r other data, echo=FALSE, results='asis'}

dx <- colnames(current%>%select(u_star_ms, sonic_temperature_k, H_wm2, LE_wm2))

# make the plots
outputs <- lapply(dx, all_plot, y_lab="var", y_lab2="var", Water=F, Raw_file=F, Use_plotly=F)

output <- unlist(outputs, recursive = F)

#output[[1]]
```

```{r Print plotly other data, echo=FALSE, messages=FALSE, warning=FALSE}

 # Used to print the plotly plots
  # attach the Dependencies
  # since the do not get included with renderTags(...)$html
  deps <- lapply(
    Filter(function(x){inherits(x,"htmlwidget")},output),
    function(hw){
      renderTags(hw)$dependencies
    }
  )
  
  if(length(deps)>0){
  attachDependencies(
    tagList(),
    unlist(deps,recursive=FALSE)
  )
  }  
```

#### Write the file to csv

```{r Make new CSV with current and historic files, eval=FALSE, include=FALSE}

# Take out the DateTime column and make date and time column characters
current_df2 <- current_df%>%
  select(-DateTime)%>%
  mutate(date = as.character(date),
         time = as.character(time))


# Need to decide on a naming convention for this file
write_csv(current_df2, "EddyFlux_2020_2023.csv")

```

```{r Download Files, eval=FALSE, include=FALSE}

# save qaqc file in the folder
download.file("https://raw.githubusercontent.com/CareyLabVT/Reservoirs/master/Scripts/L1_functions/eddy_flux_create.R", "EddyFlux_qaqc_2020_2023.R")

# save plotting function in folder
download.file("https://raw.githubusercontent.com/CareyLabVT/Reservoirs/master/Data/DataAlreadyUploadedToEDI/EDIProductionFiles/Plotting_function.R", "Plotting_function")

# save processing script in folder
download.file("https://raw.githubusercontent.com/CareyLabVT/Reservoirs/master/Data/DataNotYetUploadedToEDI/EddyFlux_Processing/FCR_Process_BD_Markdown.Rmd", "EddyFlux_processing_2020_2023.Rmd")

# Despike function for EddyFlux_processing_2020_2023.Rmd
download.file("https://raw.githubusercontent.com/CareyLabVT/Reservoirs/master/Data/DataNotYetUploadedToEDI/EddyFlux_Processing/despike.R", "despike.R")

```


