---
title: "EddyFlux Check for Cold Air Drift"
author: "Adrienne"
date: "2023-09-18"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}

# Read in packages
pacman::p_load(tidyverse, lubridate)
```


```{r read in data, include=FALSE}
# Read in the current file from GitHub
dt1 <-read_csv("https://raw.githubusercontent.com/CareyLabVT/Reservoirs/master/Data/DataNotYetUploadedToEDI/EddyFlux_Processing/EddyPro_Cleaned_L1.csv")
  
  # read in historical data file 
  # EDI
  inUrl1 <- "https://pasta.lternet.edu/package/data/eml/edi/1061/2/f837d12dc12ab37a6772598578875e00"
  infile1 <- tempfile()
  try(download.file(inUrl1,infile1,method="curl"))
  if (is.na(file.size(infile1))) download.file(inUrl1,infile1,method="auto")
  
  # read in the data file downloaded from EDI
  dt2 <-read_csv(infile1) 

```


```{r combine files, echo=FALSE}

# combine EDI and current files

EF_data<-dt2%>%
  bind_rows(.,dt1)%>%
  mutate(datetime=ymd_hms(paste0(date,"",time)))
```


Let's see if we see cold air drift in our data.

Decided to use the mixing ratio because it seems to be the best way to compare across temperatures.  

From the EddyPro manual-
For closed path gas analyzers, data may be converted to mixing ratios. At this point
in the raw data processing, metadata concerning gas concentrations from closed path
systems are analyzed by EddyPro to autonomously decide whether to perform a
sample-by-sample conversion into mixing ratios (r, moles of gas per mole of dry air).
Expressing gas concentrations as mixing ratios is convenient because this makes it
unnecessary to apply the WPL correction (Webb et al., 1980). It is an alternative way
to account for air density fluctuations resulting from thermal expansion/contraction
and concentration/dilution due to water vapor (see Ibrom et al., 2007b, for
example). For a thorough discussion concerning the use of mixing ratios in closed
path instruments, see Burba et al. (2012).

First let's just look at September 6th 2023
```{r echo=FALSE}
# Plot density of CO2 and CH4 over 24 hours

# Let's do 6 Sep 23

EF_data%>%
  filter(date==ymd("2023-09-06"))%>%
  select(date,time, co2_mixing_ratio_umolmol, ch4_mixing_ratio_umolmol)%>%
  pivot_longer(cols=c(co2_mixing_ratio_umolmol, ch4_mixing_ratio_umolmol), # make the wide data frame into a long one so each observation has a depth
                 names_to='variable',
                 values_to='observation')%>%
  ggplot(., aes(x=time, y=observation))+
  geom_point()+
  facet_wrap(~variable, scales="free_y", ncol=1)+
  theme_bw()
```

Now let's look at the mixing ratio from September 5th - 12th, 2023

```{r echo=FALSE}

# add in 8 am sun up lines

EF_data%>%
  filter(date>=ymd("2023-09-05") & date <= ymd("2023-09-12"))%>%
  select(date,time, co2_mixing_ratio_umolmol, ch4_mixing_ratio_umolmol)%>%
  pivot_longer(cols=c(co2_mixing_ratio_umolmol, ch4_mixing_ratio_umolmol), # make the wide data frame into a long one so each observation has a depth
                 names_to='variable',
                 values_to='observation')%>%
  ggplot(., aes(x=time, y=observation, color=as.factor(date)))+
  geom_point()+
  geom_vline(xintercept = hms("08:00:00"))+
  facet_wrap(~variable, scales="free_y", ncol=1)+
  theme_bw()

ggsave("FCR_SeptMixingRatio.jpg", width=11, height=7, units="in")

```

```{r }
EF_data%>%
  filter(date>=ymd("2023-09-05") & date <= ymd("2023-09-12"))%>%
  select(datetime, co2_mixing_ratio_umolmol, ch4_mixing_ratio_umolmol)%>%
  pivot_longer(cols=c(co2_mixing_ratio_umolmol, ch4_mixing_ratio_umolmol), # make the wide data frame into a long one so each observation has a depth
                 names_to='variable',
                 values_to='observation')%>%
  ggplot(., aes(x=datetime, y=observation))+
  geom_point()+
  #geom_vline(xintercept = hms("08:00:00"))+
  facet_wrap(~variable, scales="free_y", ncol=1)+
  theme_bw()

ggsave("FCR_SepttsMixingRatio.jpg", width=11, height=7, units="in")

```
Let's see what the wind and temperature looked like for that week

```{r echo=FALSE}

EF_data%>%
  filter(date>=ymd("2023-09-05") & date <= ymd("2023-09-12"))%>%
  select(datetime, air_temperature_k, wind_speed_ms, air_density_kgm3)%>%
  pivot_longer(cols=c(air_temperature_k, wind_speed_ms, air_density_kgm3), # make the wide data frame into a long one so each observation has a depth
                 names_to='variable',
                 values_to='observation')%>%
  ggplot(., aes(x=datetime, y=observation))+
  geom_point()+
  facet_wrap(~variable, scales="free_y", ncol=1)+
  theme_bw()

ggsave("FCR_SepttsMixingRatio_met.jpg", width=11, height=7, units="in")

```

```{r Time series}

EF_data%>%
  filter(date>=ymd("2023-09-05") & date <= ymd("2023-09-12"))%>%
  select(date,time, air_temperature_k, wind_speed_ms, air_density_kgm3)%>%
  pivot_longer(cols=c(air_temperature_k, wind_speed_ms, air_density_kgm3), # make the wide data frame into a long one so each observation has a depth
                 names_to='variable',
                 values_to='observation')%>%
  ggplot(., aes(x=time, y=observation, color=as.factor(date)))+
  geom_point()+
  facet_wrap(~variable, scales="free_y", ncol=1)+
  theme_bw()



```




Let's see what the fluxes look like from Sept 5- 12th, 2023

```{r echo=FALSE}

EF_data%>%
  filter(date>=ymd("2023-09-05") & date <= ymd("2023-09-12"))%>%
  select(datetime, co2_flux_umolm2s, ch4_flux_umolm2s)%>%
  pivot_longer(cols=c(co2_flux_umolm2s, ch4_flux_umolm2s), # make the wide data frame into a long one so each observation has a depth
                 names_to='variable',
                 values_to='observation')%>%
  ggplot(., aes(x=datetime, y=observation))+
  geom_point()+
  geom_line()+
  facet_wrap(~variable, scales="free_y", ncol=1)+
  theme_bw()

ggsave("FCR_Septtsfluxes.jpg", width=11, height=7, units="in")

```

Let's see what February looks like when there are no leaves on the tree

```{r echo=FALSE}

# Add in sun up line at 9:15

EF_data%>%
  filter(date>=ymd("2022-02-05") & date <= ymd("2022-02-12"))%>%
  select(date,time, co2_mixing_ratio_umolmol, ch4_mixing_ratio_umolmol)%>%
  pivot_longer(cols=c(co2_mixing_ratio_umolmol, ch4_mixing_ratio_umolmol), # make the wide data frame into a long one so each observation has a depth
                 names_to='variable',
                 values_to='observation')%>%
  ggplot(., aes(x=time, y=observation, color=as.factor(date)))+
  geom_point()+
  geom_vline(xintercept = hms("09:15:00"))+
  facet_wrap(~variable, scales="free_y", ncol=1)+
  theme_bw()

```

Let's look at Air Temperature, Air density, and wind speed over the same time in February

```{r echo=FALSE}

EF_data%>%
  filter(date>=ymd("2022-02-05") & date <= ymd("2022-02-12"))%>%
  select(date,time, air_temperature_k, air_density_kgm3, wind_speed_ms)%>%
  pivot_longer(cols=c(air_temperature_k, air_density_kgm3, wind_speed_ms), # make the wide data frame into a long one so each observation has a depth
                 names_to='variable',
                 values_to='observation')%>%
  ggplot(., aes(x=time, y=observation, color=as.factor(date)))+
  geom_point()+
  facet_wrap(~variable, scales="free_y", ncol=1)+
  theme_bw()

```



Let's look at all the data averaged for each month to the 24 hour time steps for 2020-2023.

```{r echo=FALSE}
EF_data%>%
  select(date,time, co2_mixing_ratio_umolmol, ch4_mixing_ratio_umolmol)%>%
  mutate(month=month(date))%>%
  group_by(month,time)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
    ungroup()%>%
  pivot_longer(cols=c(co2_mixing_ratio_umolmol, ch4_mixing_ratio_umolmol), # make the wide data frame into a long one so each observation has a depth
                 names_to='variable',
                 values_to='observation')%>%
  filter(observation>-10)%>%
  ggplot(., aes(x=time, y=observation, color=as.factor(month)))+
  geom_point()+
  facet_wrap(~variable, scales="free_y", ncol=1)+
  theme_bw()
```

Let's do the same thing for the weather variables

```{r echo=FALSE}
EF_data%>%
  select(date,time, air_temperature_k, air_pressure_pa, wind_speed_ms)%>%
  mutate(month=month(date))%>%
  group_by(month,time)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
    ungroup()%>%
  pivot_longer(cols=c(air_temperature_k, air_pressure_pa, wind_speed_ms), # make the wide data frame into a long one so each observation has a depth
                 names_to='variable',
                 values_to='observation')%>%
  #filter(observation>-10)%>%
  ggplot(., aes(x=time, y=observation, color=as.factor(month)))+
  geom_point()+
  facet_wrap(~variable, scales="free_y", ncol=1)+
  theme_bw()
```



Let's look at the timeseries of mixing ratio

```{r echo=FALSE}
EF_data%>%
  select(datetime,date,time, co2_mixing_ratio_umolmol, ch4_mixing_ratio_umolmol)%>%
  pivot_longer(cols=c(co2_mixing_ratio_umolmol, ch4_mixing_ratio_umolmol), # make the wide data frame into a long one so each observation has a depth
                 names_to='variable',
                 values_to='observation')%>%
  filter(observation>-10)%>%
  ggplot(., aes(x=datetime, y=observation))+
  geom_point()+
  facet_wrap(~variable, scales="free_y", ncol=1)+
  theme_bw()

```

What is happening to the CH4 mixing ration in 2023?

```{r echo=FALSE}
EF_data%>%
  filter(date>ymd("2022-12-31")& date<ymd("2024-01-01"))%>%
  filter(ch4_mixing_ratio_umolmol>-10)%>%
  ggplot(.,aes(x=datetime, y= ch4_mixing_ratio_umolmol))+
  geom_point()+
  theme_bw()
```

