---
title: "Weir Inflow Data collation and Plots for EDI"
author: "Adrienne Breef-Pilz"
output: html_document
created: "2023-02-15"
date: "`r Sys.Date()`"
---

This script is the visual inspection script. 

1. QAQCs all the raw data or for a reviewer reads in the data file from EDI for checking. 

2. Then the script checks for duplicates, daily, and subdaily gaps in the current file. 

3. Lists the flag frequency to check if there are any NAs or any assigned the wrong flag. 

4. Checks to see if the Maintenance Log is working correctly by inspecting rows in the data frame. 

5. Creates plots

6. Writes data to new csv

7. Downloads necessary files for EDI publishing


All files are from GitHub or EDI and the source scripts are from GitHub as well. 

If you are REVIEWING this data package, add the pasta URL from EDI in the "READ IN EDI FOR REVIEWER". Make sure eval=FALSE is in the chunk header for "Get raw files", "QAQC all files", "Write CSV" and "Download and save Maintenance Log". You don't need to remake the data files when you are reviewing the data package. These chunks of code will not be run when the R markdown is knitted together and saves you LOTTTS of time. Once that is all set than you can knit the file together as an HTML file to look at all the plots. 

If you are running the code chunk by chunk you mind need to make some adjustments to the code. To make the plots this markdown uses a function called "all_plots". In the function it creates a plots of the most current year, the whole times series, as well as, density and box plots for daily averages. You can also specify if you would like to produce a heat map. Note that heat maps are only produced if your data has a depth column. The function also allows you to choose if you want interactive plots, using plotly, for the most recent year of data. The plotly plots are designed to be in order with the other plots when knit to together. Therefore if you are running the ploting section, chunk by chunk, then you need to specify the plotly plot from the list of plots labeled "output"

FOR DATA PRODUCT LEAD:

If you are the data product lead and making the data package then:

1. Make sure all the date ranges are up to date especially current_time_start and current_time_end.

2. Change the years in the saved data files in "Write CSV" and "Download and save Maintenance Log" chunk.

3. Make sure to un comment and change the settings for the "Get raw files", "QAQC all files",  and "Write CSV" chunks. Also check the settings for the chunk eval=TRUE or it shouldn't be there. 

4. Comment out the Reviewer section and make sure for the settings eval = FALSE.

5. Update the data frame in "Get raw files" to include the most recent file on GitHub.

6. Knit the file. This will take a long time. 

7. Look over the plots and see if there are any issues that need to be added to the maintenance log. I will usually read in the file you just made and make smaller plots with the variable and month in question. Once I have the dates, add them to the maintenance log. 

8. Re-run the inspection script until you have found all of the issues. 

9. Run the "Download and save Maintenance Log" chunk to have the most up to date files in the EDI folder.

10. Make sure large maintenance issues are also documented in the methods.txt file. 


```{r Set Up, include=FALSE}
pacman::p_load(tidyverse, knitr, scattermore, htmltools, pander, devtools, plotly, ggpubr)
# Source scripts from GitHub

# Function to make the QAQC .  
source('https://raw.githubusercontent.com/FLARE-forecast/FCRE-data/fcre-weir-data-qaqc/R/qaqc_function.R')


# Function to make the plots below
source('https://raw.githubusercontent.com/CareyLabVT/Reservoirs/master/Data/DataAlreadyUploadedToEDI/EDIProductionFiles/Plotting_function.R')
#source("Plot_function.R")

 #turn off pander auto asis. Used for making the ploty functions show up in the knitted markdown HTML
        pander::panderOptions('knitr.auto.asis', FALSE)
        
  # set theme for the background of the plots
    theme_set(theme_bw())    


# Set up the current time end time of the file and the current year for QAQC plots

#current time of QAQC for graphing
current_time_start = ymd_hms("2024-01-01 00:00:00", tz="EST")
current_time_end = ymd_hms("2024-12-31 23:59:00", tz="EST")
```

```{r QAQC all the raw files, eval=FALSE, include=FALSE}

# DATA PRODUCT LEAD START HERE
# Un comment this section and if you are going to knit the document together make sure the eval=TRUE or is not in the brackets above. 
# Update the argument with the new links to make the data file. This might take some other scripts to combine all the years of data for the manual downloads for the VT sensors and the WVWA sensors. Note that if you are testing/fixing some data files you can adjust them locally and link to the local ones until you are ready to push them to GitHub. 

current_df <- qaqc_fcrweir (
VT_data_file = 'https://raw.githubusercontent.com/FLARE-forecast/FCRE-data/fcre-weir-data/FCRweir.csv',
VT_manual_data_file = 'https://raw.githubusercontent.com/CareyLabVT/ManualDownloadsSCCData/master/WeirData/WeirData_2019_2024.csv',
WVWA_data_file = 'https://raw.githubusercontent.com/CareyLabVT/Reservoirs/master/Data/DataNotYetUploadedToEDI/Raw_inflow/WVWA_weirInflow_2013_2024.csv',
maintenance_file = "https://raw.githubusercontent.com/FLARE-forecast/FCRE-data/fcre-weir-data-qaqc/Weir_MaintenanceLog.csv",
Staff_gauge_readings = 'https://raw.githubusercontent.com/FLARE-forecast/FCRE-data/fcre-weir-data-qaqc/Inflow_Gauge_Height_at_Weir.csv',
output_file = NULL,
output_file_rating_curve = "fcre-inflow_ratingcurve_2013_2024.csv",
start_date = NULL,
end_date = NULL)

# Filter for the end of the current publishing year in the set up chunk.
current_df <- current_df%>%
  dplyr::distinct()%>%
  filter(DateTime<(current_time_end))

# make sure no time duplicates.
 current_df <-  current_df[!duplicated(current_df$DateTime), ]

#reorder. Just to be certain everything is in order
  current_df<-current_df[order(current_df$DateTime),]

# Make sure all NAs are NA and not NAN

  # convert NaN to NAs in the dataframe
  current_df[sapply(current_df, is.nan)] <- NA

```


REVIEWERS-  There are two ways to use this script. You can either run it by chunks or you can knit it and make an html file. Knitting the file will run all the chunks and create an html page with all the plots. I like doing this because I can see all the plots in one place. The Knit button is on the top of the file with a ball of yarn and a needle next to it. 

```{r READ IN EDI FOR REVIEWER, include=FALSE}

## REVIEWERS START HERE!!!
                                       
# MAKE SURE TO UPDATE THE PASTA FROM THE VERSION YOU WANT

                                                                  ### CHANGE THIS NUMBER BELOW 
                                                                               ##      
  current_df <-read_csv("https://pasta-s.lternet.edu/package/data/eml/edi/923/15/aae7888d68753b276d1623680f81d5de")
 #
 # # Force files from EDI to have an EST timestamp


  # Set timezone as EST. Streaming sensors don't observe daylight savings
   current_df$DateTime <- force_tz(current_df$DateTime, tzone = "EST")
  
```

## Check for duplicates and  gaps in the data frame

This section identifies if there are any duplicates, daily data, and sub daily gaps in the long-term record. If there are duplicates. Look to see if they are true duplicates and then check the qaqc function and the chunk above where duplicates should be removed. If there is nothing printed then there are no duplicates or missing files. 


### Are there any duplicates?

Check to see there are no duplicates in the data file. If there are then they need to be removed. 


```{r Check for dups , echo=FALSE}

# Make sure there are no duplicated dates. Do this here because the file is too large for Data Explore.
# Print them if there are
 dups<- current_df[duplicated(current_df$DateTime), ]

dups <- dups%>%
  select(DateTime, WVWA_Pressure_psi,  WVWA_Flow_cms,
         VT_Pressure_psia, VT_Flow_cms) 

# Make it into a nice table when the Markdown is knitted together
knitr::kable((dups))
```


### Are there any gaps in the data file?


When gaps are found in the data file, check that you do not have new gaps in the previous years' publication. For the current year, if you find gaps check that you have all of the manually downloaded files. If the data are truly missing then record the dates and times in the methods section. Not if this is blank, there are no missing gaps. 

```{r Check for daily gaps, echo=FALSE}

# Get DOY
df2 <- current_df
 df2$DOY=yday(df2$DateTime)

 for(i in 2:nrow(df2)){ #this identifies if there are any data gaps in the long-term record, and where they are by record number
    if(df2$DOY[i]-df2$DOY[i-1]>1){
      print(c(df2$DateTime[i-1],df2$DateTime[i]))
    }
 }
```

#### Check Gaps in WVWA files

If there are new major gaps, make sure you have all files downloaded from the sensor. This will determine if there are gaps larger than a day. 

```{r Check gaps in WVWA files, echo=FALSE}

df2 <- current_df%>%
  select(DateTime, starts_with("WVWA"))%>%
  mutate(DOY = yday(DateTime))%>%
  drop_na(WVWA_Flow_cms)

for(i in 2:nrow(df2)){ #this identifies if there are any data gaps in the long-term record, and where they are by record number
    if(df2$DOY[i]-df2$DOY[i-1]>1){
      print(c(df2$DateTime[i-1],df2$DateTime[i]))
    }
 }

```

#### Check for gaps in the VT files

```{r Check gaps in VT files, echo=FALSE}

df2 <- current_df%>%
  select(DateTime, starts_with("VT"))%>%
  mutate(DOY = yday(DateTime))%>%
  drop_na(VT_Flow_cms)

for(i in 2:nrow(df2)){ #this identifies if there are any data gaps in the long-term record, and where they are by record number
    if(df2$DOY[i]-df2$DOY[i-1]>1){
      print(c(df2$DateTime[i-1],df2$DateTime[i]))
    }
 }

```


### Check to make sure that what is in the maintenance log was actually removed

### Look at the last rows of the maintenance log 

We want to make sure that our maintenance log actually worked and took out the values or changes those it was supposed to 

```{r Read in the maintenance log and look at the tail, echo=FALSE}

# The streaming sensors use semicolons as a deliminator because of the adjustment_code column. We use the read_csv2 to read in the file. 
 maint <- read_csv2("https://raw.githubusercontent.com/FLARE-forecast/FCRE-data/fcre-weir-data-qaqc/Weir_MaintenanceLog.csv",
                    show_col_types = FALSE)


# name the data file for just the tail of the maintenance log
# you want to filter out 7 because that is if the observation is missing and there are other ways that is flagged in the data besides the maintenance log, so it is not a good check.
sd <- tail(maint)%>%
  filter(DataStream =="WEIR")%>%
  filter(flag!=7)


knitr::kable((tail(sd)))

```
#### Check the that the columns have flags 

Look at the first few rows of the data frame and check that the observations after the TIMESTAMP_start are flagged

#### Look at the first 5 rows for that time

```{r Did the maint log work head, echo=FALSE, message=FALSE, warning=FALSE}
# get the last row of the data file
last_row <- tail(sd, n=1)

# Get starttime and end time
### get start and end time of one maintenance event
    start <- force_tz(as.POSIXct(last_row$TIMESTAMP_start), tzone = "EST")
    end <- force_tz(as.POSIXct(last_row$TIMESTAMP_end), tzone = "EST")
    
    # Get the time of the maintenance
    if(is.na(end)){
      # If there the maintenance is on going then the columns will be removed until
      # and end date is added
      Time <- current_df |> filter(DateTime >= start) |> select(DateTime)
      
    }else if (is.na(start)){
      # If there is only an end date change columns from beginning of data frame until end date
      Time <- current_df |> filter(DateTime <= end) |> select(DateTime)
      
    }else {
      Time <- current_df |> filter(DateTime >= start & DateTime <= end) |> select(DateTime)
    }

### Get the names of the columns affected by maintenance
    colname_start <- last_row$start_parameter
    colname_end <- last_row$end_parameter
    
    
### Get the names of the columns affected by maintenance
    if (!is.na(colname_end)){
    test <- colnames(current_df%>%select(DateTime, colname_start, paste0("Flag_",colname_start), colname_end, paste0("Flag_",colname_end)))
    } else{
      test <- colnames(current_df%>%select(DateTime, colname_start, paste0("Flag_",colname_start)))
    }
    
    # Print the head of the table to make sure that data are flagged
    
    knitr::kable((head(current_df[current_df$DateTime %in% Time$DateTime, test]))) 

```

#### Look at the last 6 rows for the maintenance time

Make sure the observations are flagged

```{r Print the tails, echo=FALSE, message=FALSE, warning=FALSE}

# Print the tail of the table to make sure that data are flagged
    
    knitr::kable(tail(current_df[current_df$DateTime %in% Time$DateTime, test])) 

```
## Check out the Flag frequency

Let's look at the Flag frequency for each variable. 

As a reminder here are the Flag codes: 

0: no flag; 

1: value corrected to account for artificial increase in pressure after sensor maintenance; 

2: sensor malfunction; 

3: value of NA due to extremely low flows that are not well captured by rectangular or v-notch weir; 

4: demonic intrusion; 

5: value of NA due to leaking at weir;

6: flow topping the v-notch weir;

7: missing observation/not recorded;

8: values removed because of maintenance; 

13: value downcorrected due to low flows on the rectangular weir;

16: value downcorrected due to flow overtopping the rectangular weir;

24: weir damaged due to weather.


```{r Check out the flags, echo=FALSE}

#make sure no NAS in the Flag columns
Flags <- current_df%>%
  select(DateTime, starts_with("Flag"))

RowsNA=Flags[!complete.cases(Flags), ] # Keep only the complete rows

#check the flag column
Flags <- current_df%>%
  select(starts_with("Flag"))

# Make a table with the number of times a flag was used
for(f in 1:ncol(Flags)){
  print(colnames(Flags[f]))
  print(table(Flags[,f], useNA = "always"))
}
```

## QAQC Plots

##### QAQC plot information and all_plot function information

For the plots, they use a function called "all_plot". In all_plot you can specify if you want interactive plots for the current data. You can specify which plotly plots you want on. You can also look at the plotly plots manually in each chunk by running the chunk with Use_plotly=TRUE as an argument. Then look at the list of plots you have made under "output". If you click on the "output" object in your environment it will list all of the plots and which ones are interactive plotly plots. To view the plots run "output[[number of the plot in the list you want to run]]". Eg. If you want to see the 4th plot in the list write output[[4]] then run that line and the plot should appear. 

If you would like to look at one variable then in the function below replace "dx" with the variable column. The object "dx" is just a list of variables so we don't have to list out all of the variables we want to plot. This is used to speed up the process. 

The plotting function is called all_plot() which plots the 4 or more plots described below. The function is sourced from GitHub in the first chunk of the script. The arguments are:
Var, # the variable you would like to plot
data, # the data frame to use
raw_data=NULL, # Is there raw data to compare with. Usually is NULL
reservoir, # the name of the reservoir you would like to filter by 
res_site, # the reservoir Site or Sites you would like to filter by
y_lab,  # This label can take an expression aka have the proper degrees C, 
y_lab2, # This label is for the plotly function which can not handle expression argument. 
Depth=F,  # Do you want depth as a factor
Water=T, # Are these plots for streaming sensors with RDO and temperature sensors
Use_plotly = F, # Do you want to produce interactive plots for observations of the current year?
Heatmap = F) # Do you want to make a heat maps? This only works if there are multiple depths at the same site


The arguments with = followed by a True means that they are the defaults and you don't need to add them to the function when you use it. If you want to use the opposite of the default you must specify that. 
  
##### Plot Description:

The plots below are:
The first 2 plots are the ones you should focus on for the QAQC chec. Spend the most time looking at the most recent data because that one as been checked. Do pay attention to the historical to make sure there are no crazy outliers that were missed in previous years. 

1. A time series of the current years' data. This can either be a regular plot or an interactive one. If you would like it to be interactive set Use_plotly = T. 

2. A time series of the historical and the current data just the qaqced values. 

The next two plots are just fun to see trends over time with the data. 

3. Density plots are like a histogram and a grouped by color so you can see where the data are relative to other years. 

4. The box plots look at the spread of the data within the year and we can look at the median and see how that is changing or not. 

Do not over think the last 2 plots, although they are good to look at historical trends to ensure relative data quality consistency. 


### Plots of WVWA Data

```{r WVWA plots, echo=FALSE, results='asis'}

dx <- colnames(current_df%>%select(WVWA_Pressure_psi, WVWA_Baro_pressure_psi, WVWA_Pressure_psia, WVWA_Flow_cms, WVWA_Temp_C))

# If you would like to see the plots for one data column. Replace "dx" with the variable name and run the function. 

# make the plots
outputs <- lapply(dx, all_plot, data=current_df, raw_data= NULL, reservoir = "FCR", res_site=100, y_lab = "psi/psia/cms/C", y_lab2 = "psi/psia/cms/C", Water=T, Use_plotly=T, Heatmap = F)



output <- unlist(outputs, recursive = F)

# If you are running this chunk by chunk uncomment the line to make the interactive plot. Note that "output" lists 16 different plots
#output[[1]]
```

```{r Print plotly WVWA, echo=FALSE, messages=FALSE, warning=FALSE}

 # Used to print the plotly plots
  # attach the Dependencies
  # since the do not get included with renderTags(...)$html
  deps <- lapply(
    Filter(function(x){inherits(x,"htmlwidget")},output),
    function(hw){
      renderTags(hw)$dependencies
    }
  )
  
  if(length(deps)>0){
  attachDependencies(
    tagList(),
    unlist(deps,recursive=FALSE)
  )
  }  
```

### Plots of VT Data

```{r VT sensors, echo=FALSE, results='asis'}

dx <- colnames(current_df%>%select(VT_Pressure_psia, VT_Flow_cms, VT_Temp_C))

# If you would like to see the plots for one data column. Replace "dx" with the variable name and run the function. 

# make the plots
outputs <- lapply(dx, all_plot, data=current_df, raw_data= NULL, reservoir = "FCR", res_site=100, y_lab = "psi/psia/cms/C", y_lab2 = "psi/psia/cms/C", Water=T, Use_plotly=T, Heatmap = F)

output <- unlist(outputs, recursive = F)

# If you are running this chunk by chunk uncomment the line to make the interactive plot. Note that "output" lists 16 different plots
#output[[1]]
```

```{r Print plotly VT, echo=FALSE, messages=FALSE, warning=FALSE}

 # Used to print the plotly plots
  # attach the Dependencies
  # since the do not get included with renderTags(...)$html
  deps <- lapply(
    Filter(function(x){inherits(x,"htmlwidget")},output),
    function(hw){
      renderTags(hw)$dependencies
    }
  )
  
  if(length(deps)>0){
  attachDependencies(
    tagList(),
    unlist(deps,recursive=FALSE)
  )
  }  
```

#### Compare WVWA and VT Sensors

Look at the WVWA calculated flow and VT calculated flow on the same plots

```{r Compare WVWA and VT sensors, echo=FALSE}

weirdata<-current_df%>%
  mutate(Year=year(DateTime))

# weirdata<-All_Inflow%>%
#   mutate(Year=year(DateTime))

colors <- c("WVWA" = "blue", "VT" = "red")


weirdata%>%
  ggplot(., aes(x=DateTime))+
  geom_scattermore(aes(y=WVWA_Flow_cms, color="WVWA"), pointsize = 2)+
  geom_scattermore(aes(y=VT_Flow_cms, color="VT"), pointsize = 2) +
  ggtitle("All Flow Rates") +
    labs(y = "cms",
         color = "Legend") +
    scale_color_manual(values = colors)

# Just the current year

current_df%>%
  filter(DateTime>current_time_start & DateTime<current_time_end)%>%
  ggplot(., aes(x=DateTime))+
  geom_point(aes(y=WVWA_Flow_cms, color="WVWA"))+
  geom_point(aes(y=VT_Flow_cms, color="VT")) +
  ggtitle("All Flow Rates") +
    labs(y = "cms",
         color = "Legend") +
    scale_color_manual(values = colors) 


# Plot one to one of flow 
weirdata%>%
  drop_na(VT_Flow_cms)%>%
  ggplot(.,aes(x=WVWA_Flow_cms, y=VT_Flow_cms, color=as.factor(Year)))+
  geom_point()+
  #stat_smooth(method = "lm", col = "red")+
  # ggpubr::stat_regline_equation(
  #   aes(label =  paste(..eq.label.., ..adj.rr.label.., sep = "~~~~"))
  # )+
  ggtitle("Compare WVWA flow and VT flow") 
  
```

### Write to CSV

```{r Make current csv, eval=FALSE, include=FALSE}
### DATA PRODUCT LEAD SAVE FILE HERE 
# This section convert the DateTime to a character and then it save the most qaqced data file

# convert datetimes to characters so that they are properly formatted in the output file
 current_df$DateTime <- as.character(format(current_df$DateTime))

write_csv(current_df, "fcre-inflow_2013_2024.csv")

```


```{r Download and save Maintenance Log, include=FALSE, eval=FALSE}
# DATA PRODUCT LEAD DOWNLOAD FILES HERE

# This section downloads the most recent versions of the data files and scripts from GitHub. Note if you make changes to your local repo and don't push them to the main branch in GitHub then you won't see the changes in thes files. 

# Maintenance Log
download.file("https://raw.githubusercontent.com/FLARE-forecast/FCRE-data/fcre-weir-data-qaqc/Weir_MaintenanceLog.csv", "fcre-inflow_maintenancelog_2013_2024.csv")

# Gauge Height
download.file("https://raw.githubusercontent.com/FLARE-forecast/FCRE-data/fcre-weir-data-qaqc/Inflow_Gauge_Height_at_Weir.csv","fcre-inflow_gaugeheight_2019_2024.csv")

# qaqc function
download.file("https://raw.githubusercontent.com/FLARE-forecast/FCRE-data/fcre-weir-data-qaqc/R/qaqc_function.R", "fcre-inflow_qaqc_2013_2024.R")

# streaming plots function
download.file("https://raw.githubusercontent.com/CareyLabVT/Reservoirs/master/Data/DataAlreadyUploadedToEDI/EDIProductionFiles/Plotting_function.R", "Plotting_function.R")


```